### 2015-04-13 practice/docs/thesis/cover_ack_abstract.tex
adding thesis progress so far

%!TEX root = ../main_v01.tex

\title{\large should probably decide whether to include chad's thing...}
%\fontsize{15}{17}\selectfont 
\author{Harriet Li}

\prevdegrees{B.S. Aerospace Engineering (2013)\\
             Massachusetts Institute of Technology}

\department{Department of Aeronautics and Astronautics}
% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Master of Science}
\degreemonth{June}
\degreeyear{2015}
\thesisdate{May 21, 2015}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Karen Willcox}{Professor of Aeronautics and Astronautics}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Paulo Lozano}{Associate Professor of Aeronautics and Astronautics\\
        Chair, Graduate Student Committee}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}

%Uncomment the following three lines if you want an abstract page
\begin{abstractpage}
\input{abstract.tex}
\end{abstractpage}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

%Uncomment the following three command lines if you want Acknowledgements page
\cleardoublepage

\section*{Acknowledgments}

...

### 2015-04-13 practice/docs/thesis/formulation_v01.tex
adding thesis progress so far

\chapter{Formulation}

In this chapter, we...
%------------------------------------------------------------------------------%
\section{Derivation of Error Estimate}  \label{sec:deriv}
%------------------------------------------------------------------------------%
Given $n_d$ observations $d\in\R^{n_d}$, suppose we wish to infer the parameters $q\in Q$ of a PDE model $a(u,\phi;q)=f(\phi;q),\:\forall\phi\in U$, where $u\in U$ are the states and $U,Q$ are Hilbert spaces. Then this PDE-constrained inverse problem can be written as an optimization problem
\begin{equation}
\begin{array}{r@{}l}
\textrm{Minimize } & \quad J(q)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \\ \textrm{s.t. }& \quad a(u,\phi;q)=f(\phi;q),\quad\forall\phi\in U,
\end{array}
\end{equation}
for which the Langrangian is
\begin{equation}
\mathcal{L}(q,u,z)= J(q,u)-(a(u,z;q)-f(z;q)),
\end{equation}
where $z\in U$ is the adjoint.

Let $\xi=(q,u,z)$ be called the primary variables. Following the work of \cite{BecVex05}, we introduce a set of auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$ corresponding to these primary variables, and define an augmented Lagrangian
\begin{equation}
\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}'(q,u,z)(p,v,y),
\end{equation}
where $I:Q\times U\to\R$ is a functional that gives our QoI. Let $\Psi = (\xi,\chi)$ denote the stationary point of $\mathcal{M}$. Note that
\begin{equation}
\mathcal{M}(\Psi)=I(q,u),
\label{eq:MeqI}
\end{equation} since taking variations of $\mathcal{M}$ with respect to the auxiliary variables recovers the optimality conditions. If we have high-fidelity (HF) and low-fidelity (LF) models for which we can infer parameters, then for each of these we can define an augemented Lagrangian ($\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively) with corresponding stationary points $\Psi_{HF}$ and $\Psi_{LF}$.

Using Equation (\ref{eq:MeqI}), we can write
\begin{equation}
\begin{array}{r@{}l}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})\: &= \mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})\textrm{.} 
\end{array}
\end{equation}
Using Equation 21 from \cite{BecVex05}, we can write
\begin{equation}
\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
\label{eq:preadj}
\end{equation}
where $e=\Psi_{HF}-\Psi_{LF}$. We cannot solve for $\Psi_{HF}$, and we cannot replace $\Psi_{HF}-\Psi_{LF}$ with an interpolation estimate as was done for $\Psi-\Psi_h$ in \cite{BecVex05}, since we now have different models instead of different discretizations of the same model.

We take an adjoint approach to obtain the term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ by viewing it as an error in a linear output. As $\Psi_{HF}$ is a stationary point, it satisfies $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$. Let its variational form be
\begin{equation}
A_{HF}(\Psi_{HF},\Phi)=F(\Phi),\:\forall\:\Phi\in(Q\times U\times U)^2,
\end{equation}
and define an output 
\begin{equation}
\mathcal{Q}(\Psi_{HF})=\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}).
\end{equation}
We can then solve
\begin{equation}
A_{HF}(\Phi,\Lambda)=\mathcal M'_{HF}(\Psi_{LF})(\Phi),\:\forall\:\Phi\in(Q\times U\times U)^2
\label{eq:superAdjEq}
\end{equation}
for the adjoint $\Lambda$, which can be used to obtain
\begin{equation}
\mathcal M'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})=\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda).
\label{eq:adjOutErr}
\end{equation}
Combining Equations (\ref{eq:preadj}) and (\ref{eq:adjOutErr}) and dropping the higher-order term $\mathcal{R}(e^3)$, we obtain an expression for the error in the QoI from inferring the parameters of a low-fidelity model instead of a high-fidelity model:
\begin{equation}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})\approx\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}).
\label{eq:finErrExp}
\end{equation}
%there is a minus sign in the adjoint-weighted residual expression in vikram's writeup...but not in any of your stuff...looks like that depends on how you define the residual...Ax-b or b-Ax...should you define that somewhere?

The equations in this section apply also when the low-fidelity model is replaced with an intermediate model. Just as \red{error estimates} can be used to guide mesh-refinement, Equation (\ref{eq:finErrExp}) can be decomposed into elemental contributions and used to guide the creation of a mixed-fidelity model, where the high-fidelity model is used in some parts of the domain, and the low-fidelity model is used in the rest. The error estimate (\ref{eq:finErrExp}) can be calculated again, using the mixed-fidelity model as the lower-fidelity model; this process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached. %should you expand this into an "algorithm"-type section? section/note that forming a mixed-fidelity model is not always so straightfoward? should poke literature about how this is done if so (model interfacing that Oden,Prudhomme, etal talk about...also seemed to have a sort of interior-boundary-condition for stokes-ns mix)...also include de-refinement? (choices of how to pick where to refine? if so, would we need to reference other papers where similar choices are made?)

%do we have restrictions on I? the prediction process could be a whole 'nother PDE, or something as simple as our subdomain integral...needs to be at least once differentiable? with respect to? B+V just seems to have I' with respect to state, even though I(q,u)...B+V only say that I is some functional...if I is a PDE, then is it also possible that it can be excessively complex as well?

%------------------------------------------------------------------------------%
\section{Limitations and Bounds}  %\label{sec:xx}
%------------------------------------------------------------------------------%

The error estimate (\ref{eq:finErrExp}) is exact in the case where the model PDEs and QoI functional are linear. In the presence of nonlinearities, the error estimate is approximate, due to having dropped the higher order terms $\mathcal{R}(e^3)$, and due to the need to linearize about $\Psi_{HF}$ in forming the adjoint problem (\ref{eq:superAdjEq}). It will also sometimes be the case that it is cheaper to solve the inverse problem with the high-fidelity model than to calculate the quantities needed to build up to a mixed-fidelity model for which the estimated error in the QoI is acceptably low. %bounds on accuracy of error estimate? B+V doesn't say anything about bounds on the third order term...I think FE stuff can say things about e in mesh-discretization case but not for different models...if we can't come up with bounds, can we just acknowledge that as a current weakness? did oden+prudhomme have bounds? (no) 	-> there haven't really been anything published on e for multiple-models...hence why we want as high an order method as possible...perhaps once there is a defined hierarchy (poke model hierachy?), as there is for mesh-refinement, perhaps then...otherwise models could be totally unrelated...

The two models must also have a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in \cite{BecVex05} would be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The two models must also have some degree of compatibility, in that the variables of one model must have some meaning in the other. %is this something to expand on, or just give the weak form assumption and leave it at that?

%in the formulation, psiLF and psiHF share the same space...which they might not necessarily be able to be made to if psiMF has discontinuities allowed but psiHF doesn't?

%cost analysis?
	%assume LF inverse problem is cheap to solve; if we solve for auxiliary naively (not B+V's) way, then so and so many linear solves...? anything we can do for superadj other than breaking into blocks?

%more than two models? the error breakdown is only ever for two models at a time...if A>B>C, then first do between B and C, get a mix of B+C as your new 'LF', then do between B+C and A?

%%%%

%How different can the models be before the error estimate becomes unreliable? Are there any kinds of PDEs for which the error estimate is unreliable? (in forward problems, adjoint based error estimation works well for any adjoint consistent formulation; handles hyperbolic and highly nonlinear problems well (Darmofal has a paper comparing it to other methods for hyperbolic problems?); possible that this might extend to our case, though having an inverse problem might screw that up; might have to settle for running numerical experiments on simplified versions to build/decrease confidence that it would work on more complex version)

%How much of an issue would adjoint inconsistency be? (Perhaps not so much in gradient calculation in solving inverse problem, since you want to find an optimum for a particular choice of model and mesh, but it gets worse when you want to do things like mesh refinement, since then adjoint-of-discrete not corresponding to discretized-adjoint breaks up your connection to the infinite dimensional system; in our case, we are comparing two models with set discretizations, and there is no continuous ideal that we need to relate to...)

%transient case? theory should hold, since we can stack solutions at time-steps into one giant solution and theoretically solve everything in one go; should we discuss how that would be implemented though? states evolve forward, adjoints evolve backwards, auxiliary are linearly related to primary...do people automatically think of steady-state when they see a(*,*)=f(*) form? B+V's example is steady-state...but weak form can definitely encapsulate transient (DG_NonLinearSystems, slide 8) -> writing out steps for transient case doesn't really add anything to this theory; enough existing literature to see how to implement in transient case

%in B+V, they say "The form a and the observation C are assumed to be three times continuously differentiable"...what might a not-differentiable operator look like? should we include this in assumptions about form? (their C is observation operator acting on state, not params) why three times? (for HOT remainder)

### 2015-04-13 practice/docs/thesis/intro_v01.tex
adding thesis progress so far

\chapter{Introduction}
...
%------------------------------------------------------------------------------%
\section{Motivation}  %\label{sec:xx}
%------------------------------------------------------------------------------%

In studying the world, physical systems are often represented by mathematical models characterized by a set of parameters; these models are oftentimes partial differential equations (PDEs), and their parameters may be numerous, representing discretized fields. For a given forward model, often based on physical laws and relating the model parameters to predicted observations, one can infer the model parameters based on actual results of these observations \cite{Taran05, BanksKuhn89}. These parameters, especially in engineering contexts, are then used to calculate some Quantity of Interest (QoI).

A given physical system can be represented with varying degrees of fidelity by different models. A high-fidelity model may, for example, take into account more physical laws or be finely discretized, and thus more accurately represent reality; a high-fidelity model is also often more difficult to solve. Since solving the inverse problems generally requires many evaluations of the forward model, it may be cheaper to use a lower-fidelity model, and since the inverse problem is often ill-posed without regularization, it may not be the case that the addition \red{something} of the high-fidelity model is even informed by the observations.

%tarantola seems to frame parameters as independent of forward model; forward model just relates parameters to observables; but in scalar vs field case, parameter choice is part of forward model?

%Inverse problems appear in many contexts. They are difficult to solve because of so and so. In many cases, the purpose of inferring for parameters is to use them to calculate some Quantity of Interest (QoI) that we can then use to make decisions. Goal-oriented approaches trade accuracy in the inferred parameters for accuracy in QoI...?

%------------------------------------------------------------------------------%
\section{Previous Work}  %\label{sec:xx}
%------------------------------------------------------------------------------%
\subsection{Goal-Oriented Approaches}
%goal-oriented DoE from marzouk?
\subsection{Multifidelity Modeling?}

%idea of most-complex \neq best? occam's razor thing from all-hands...
%mixing models? like the thing that inspired vikram to do this model-mixing thing? (stokes-navierstokes...refered to as "classical"...is there a paper?) 
	%what oden,prudhomme,et al refer to as "concurrent" multiscale models; their first numerical example has a lower-fidelity/surrogate model with "homogeneous and deterministic coefficients"
	%other papers with mixed models? "multiscale"? -> "multifidelity"? multimodel - pressure first, then rest as update (typically what this refers to, partankar algorithm); can also think of differently coupled stacks (hierarchies) as different fidelities of models (multiphysics)...
	%poke oden branches for examples?

%------------------------------------------------------------------------------%
\section{Thesis Objectives}  %\label{sec:xx}
%------------------------------------------------------------------------------%
%need to set up the problem we are trying to solve...include LF-HF-MF cartoon? haven't seen other theses with images in intro...
%define inverse problem optimization setup here

%------------------------------------------------------------------------------%
\section{Thesis Outline}  %\label{sec:xx}
%------------------------------------------------------------------------------%

### 2015-04-13 practice/docs/thesis/results_v01.tex
adding thesis progress so far

\chapter{Numerical Results}

For simplicity of implementation, we demonstrate the results using pairs of steady-state models sharing the same states, mesh, and basis functions.

%------------------------------------------------------------------------------%
\section{Convection-Diffusion and Convection-Diffusion-Reaction Models}  %\label{sec:xx}
%------------------------------------------------------------------------------%

In this section, we demonstrate the method derived in Section \ref{sec:deriv} for two models in a 2D domain. In this case, the two models differ in the physics modeled. The high-fidelity model 
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q)
\end{equation}
is described by a single-species convection-diffusion-reaction equation with a nonlinear reaction term, where $k_d = 0.1$ is a diffusion coefficient and $k_r = -42.0$ is a reaction coefficient. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q)
\end{equation}
differs only in the removal of reaction term. The velocity is described by $\vec{V}(x,y) = (2y(1-y),0)$, with the Peclet number everywhere in the domain $\Omega=[0,5]\times[0,1]$ small enough to make stabilization unnecessary. Homogeneous Dirichlet boundary conditions are used for simplicity.

Given observations $d=(u(0.35,0.35),u(1.56,0.61),u(3.1,0.5))$ from three points in the domain, we wish to infer the forcing field $f(q)=q$ in order to calculate
\begin{equation}
I(q,u)=\int_{(x,y)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
where $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The locations of the observations and the region $\Omega_I$ over which the QoI is calculated is shown in Figure \ref{fig:baseSetup}. Since the inverse problem is ill-posed, a Tikhonov regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$ is used.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of observations and QoI region \red{ADD X TO AXIS...}}
\label{fig:baseSetup}
\end{figure}

Using the element-wise decomposition of (\ref{eq:finErrExp}), the proportion of the domain in which the high-fidelity model is used is increased until the estimated absolute relative error in the QoI is less than $1\%$. Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the areas of the domain where the low- and high-fidelity models were used. The true and estimated absolute relative errors in the QoI for these same intermediate models are shown in Figure \ref{fig:baseErr}, while the relative error in the error estimate is shown in Figure \ref{fig:baseErrErr}. %or effectivity index, since that's a standard for error estimates?
It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate, and the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $20\%$ of the domain.

\begin{figure}[h]
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_LF.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
    \end{minipage}%
    }
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_MF01.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
    \end{minipage}%
     }
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_MF02.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
    \end{minipage}%
    }
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_MF03.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_MF03_divvy.pdf}
    \end{minipage}%
    }
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_MF04.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_MF04_divvy.pdf}
    \end{minipage}%
    }
\makebox[\textwidth]{%
    \begin{minipage}[t]{0.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/err_breakdown_MF05.pdf}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.62\textwidth}
      \centering
      \includegraphics[width=\textwidth]{baseSeries/cd_cdr_MF05_divvy.pdf}
    \end{minipage}%
  }%
\caption{Model refinement series: element-wise breakdown of error estimates and corresponding subdomains (low-fidelity in red, high-fidelity in blue)}
\label{fig:baseRef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI}
\label{fig:baseErr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_err.pdf}
\caption{Absolute relative error in estimated absolute relative error in QoI \red{replace with table/graph of effectivity indices}}
\label{fig:baseErrErr}
\end{figure}

\subsection{Interaction of Observations and QoI}

The element-wise decomposition of the error estimate (\ref{eq:finErrExp}) suggests the use of the high-fidelity model in areas of the domain where \red{the parameter field?} is both informed by the observations and informative about the QoI. %can we only tie the physical domain and parameters so closely like this because these equations are localized (or what's the word...what hyperbolic equations don't have...something with "local"...)

To see this, we compare the element-wise decomposition of the error estimate for three sizes of the QoI region $\Omega_I$ given the same set of observations, and for three sets of observations given the same QoI region. Only the error estimate linearized about $\Psi_{LF}$ is shown in Figures \ref{fig:qoiStudy} and \ref{fig:dataStudy}; the later estimates have a similarly patterned decomposition.

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.8\textwidth]{vs_qoi/err_breakdown_3_3_study.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_qoi/err_breakdown_7_3_study.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_qoi/err_breakdown_5_3_study.pdf}}
\caption{Element-wise decomposition of error estimates for varying $\Omega_I$ (purple box) and same three observations (teal and white points)}
\label{fig:qoiStudy}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.8\textwidth]{vs_data/err_breakdown_7_3_studyv2.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_data/err_breakdown_7_5_study.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_data/err_breakdown_7_10_study.pdf}}
\caption{Element-wise decomposition of error estimates for varying observations (teal and white points) and same $\Omega_I$ (purple box)}
\label{fig:datStudy}
\end{figure}

These results agree with intuition, and in this case an appropriate mixed-fidelity model could have been designed by intuition. In fact, this is a case in which the models are simple enough that it is actually cheaper to solve the inverse problem with the high-fidelity model than to rigorously form a mixed-fidelity model with which to solve the inverse problem instead. The interaction between the observations and the QoI need not always be obvious, however, as might be the case for \red{what?} models, and it is in these cases that a rigorous method for forming a mixed-fidelity model would be most helpful.

\subsection{Effect of Regularization}

As the magnitude of the regularization parameter $\beta$ it increased, the error estimate seems to indicate that whether the low- or high-fidelity model is used becomes less and less important in most of the domain, except in small areas around the most relevant observations. This behavior is expected\red{, or maybe I've just stared at this too often}. As $\beta$ increases, the regularization more strongly influences the parameter field that is inferred, although the regularization does not completely determine the inferred parameters and the observations still influence the inferred parameter field in the area around them; the choice of model in the QoI region becomes less important as the inferred parameter field in that area becomes more determined by regularization.

The element-wise decomposition for the observations and QoI region shown in Figure \ref{fig:baseSetup} are shown in Figure \ref{fig:regStudy} for three values of the regularization parameter $\beta$. Only the error estimate linearized about $\Psi_{LF}$ is shown; the later estimates have a similarly patterned decomposition.

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.8\textwidth]{vs_reg/err_breakdown_0p00001.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_reg/err_breakdown_0p001.pdf}}
\subfigure{\includegraphics[width=0.8\textwidth]{vs_reg/err_breakdown_0p1.pdf}}
\caption{Element-wise decomposition of error estimates for varying $\beta$ \red{if keep make consistent}}
\label{fig:regStudy}
\end{figure}

%how to show, since a paper can't include animations or their flip-book equivalent? if showing how it picks out the important data points, how to justify only showing one (and not all from series of refinements), since linearization could contaminate error breakdown...
% -> vs measurements studies; vs qoi studies; vs reg study (?)
% -> DON'T HAVE: looking at contribution from regularization terms? indicator function QoI? boundary flux QoI? more physically meaningful boundary conditions? *different physics, one where effects propogate more*?

%effectivity index (ratio of estimated to true error) plots/tables? (oden, prudhomme, et al mention such)

%...relate back to Chad's subspace of shared qoi-data importance (emphasis on shared importance...)? although his subspace was in parameter-space, not physical domain space...
%can we make an example where the qoi region is not pointed out for refinement? even with weak regularization

%try runs with inflow boundary conditions, which make more sense?
%gunzburger only has example with homo diri around the entire boundary...how to deal with BCs if boundary split between diri and neumann? -> poke 930...

%should these be re-run on finer meshes for prettier pictures?

%------------------------------------------------------------------------------%
\section{Scalar versus Field Parameters}  %\label{sec:xx}
%------------------------------------------------------------------------------%

The models considered need not differ in the physics included. In this section, we consider two models which differ in the space in the space to which the parameter belongs. The high-fidelity model 
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
is again a single-species convection-diffusion-reaction equation with a nonlinear reaction term, where $k_d = 0.1$ is a diffusion coefficient and $k_r = -4.2$ is a reaction coefficient. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter is a scalar instead of a field.

%effect of linearization? the third point popping in and out in 4p2_deref is probably due to interplay of how fast third point's bump shrinks versus how fast the refinement percentage grows...
%can philisohically compare with chad's though, perhaps in param refinement, even though his is in parameter subspaces and ours is in physical space?

### 2015-05-20 practice/docs/thesis/abstract.tex
final thesis draft

In scientific and engineering contexts, physical systems are represented by mathematical models, characterized by a set of parameters. The inverse problem arises when the parameters are unknown and one tries to infer these parameters based on observations. Solving the inverse problem can require many model simulations, which may be expensive for complex models; multiple models of varying fidelity and complexity may be available to describe the physical system. However, inferring the parameters may only be an intermediate step, and what is ultimately desired may be a low-dimensional Quantity of Interest (QoI); we refer to this as the goal-oriented inverse problem. We present a novel algorithm for solving the goal-oriented inverse problem, which allows one to manage the fidelity of modeling choices while solving the inverse problem.

We formulate a hierarchy of models, and assume that the QoI obtained by inferring the parameters with the highest-fidelity model is the most accurate QoI. We derive an estimate for the error in the QoI from inferring the parameters using a lower-fidelity model instead of the highest-fidelity model. This estimate can be localized to individual elements of a discretized domain, and this element-wise decomposition can then be used to adaptively form mixed-fidelity models. These mixed-fidelity models can be used to infer the parameters, while controlling the error in the QoI.

We demonstrate the method with two pairs of steady-state models in 2D. In one pair, the models differ in the physics included; in the other pair, the models differ in the space to which the parameters belong. In both cases, we are able to obtain a QoI estimate with a small relative error without having to solve the inverse problem with the high-fidelity model. We also demonstrate a case where solving the inverse problem with the high-fidelity model requires a more complex algorithm, but where our method gives a mixed-fidelity model with which we can infer parameters using a simple Newton solver, while achieving a low error in the QoI.

### 2015-05-20 practice/docs/thesis/conclusion_v03.tex
final thesis draft

\chapter{Conclusion} \label{chap:conc}

In this chapter we summarize the main contributions of the thesis and discuss future work.

%------------------------------------------------------------%
\section{Thesis Summary} 
%------------------------------------------------------------%

The contribution of this work is an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters. We applied this method to pairs of models, one that differed in the physics included and one that differed in the space to which the parameters belonged. In both cases, we were able to obtain a value for the QoI with a small relative error without having to solve the inverse problem with the high-fidelity model. In these cases, the element-wise decomposition of the error estimate also indicated regions of the parameter field that were both informed by the observations and informative to the QoI.

The inverse problem with the high-fidelity models examined were not so expensive to solve as to warrant the adaptive formation of a mixed-fidelity model; however, based on existing work with concurrent multi-fidelity models, savings in computational cost are expected in cases where the high-fidelity model is more complex and solving the inverse problem with the high-fidelity model is less tractable. We demonstrated a case where the inverse problem with the high-fidelity model could not be solved without a more complex nonlinear solver, but where our method resulted in a mixed-fidelity model for which the inverse problem could be solved with a simple nonlinear solver, with a small relative error in the QoI.

%------------------------------------------------------------%
\section{Future Work} 
%------------------------------------------------------------%

An immediate direction for extension of this work is to the case of the statistical inverse problem. Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization. However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}. One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.

A popular approach to solving the statistical inverse problem is to apply a Bayesian framework. Bayes' rule is used to combine a prior distribution, which captures prior beliefs about the parameters, and a likelihood distribution, which captures the likelihood of observations given an instance of the parameter values and a model of noise in the observations, to give a posterior distribution on the parameters. Since there is generally no analytical expression for this posterior distribution, it is usually characterized by samples from the distribution. Sampling methods like the widely-used Markov chain Monte Carlo (MCMC) method require many evaluations of the forward model, and since the number of samples needed grows exponentially with the dimension of the parameter space, this problem becomes intractable for large parameter spaces. In engineering contexts, it is still usually the case, however, that we are ultimately interested in a low-dimensional QoI, and it is the uncertainty in this low-dimensional quantity that we wish to capture; this low-dimensional distribution is referred to as the predictive posterior.

One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled. Such a direction is suggested by the results presented in Section \ref{sec:constvfield}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space. In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution. In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed. Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.

Another potential approach would be to extend our method to the creation of mixed-fidelity models that are used as surrogates; these surrogate models can be evaluated in place of the high-fidelity model, thus decoupling the number of expensive forward evaluations of the high-fidelity model needed from the number of posterior parameter distribution samples that is desired \cite{Con14}. The samples obtained using such a surrogate might sacrifice accuracy in representing the posterior parameter distribution for accuracy in representing the predictive posterior distribution.

%soil chapter in Multiscale Modeling: A Bayesian Perspective - seems to do hierachical multiscale in context of mcmc
%http://arxiv.org/pdf/1402.1694v3.pdf has pointers to where people use surrogate models to avoid evaluating forward model too often...

%read http://www.stat.osu.edu/~comp_exp/jour.club/KennedyOHagan2000.pdf for the lulz?

%stochastic
%anything in chad's about curse of dimensionality?
%wolfgang bangert -> mesh refinement and stochastic, keep coarse sometimes...see if this might be related to extension?
	%can't seem to find anything by him related to this...at least, not suggested by title...
%matt parno or patrick's stuff? exploring with surrogate models mostly and then upping fidelity strategically?

%poke stochastic weak form? is that another way we could think about extending to stochastic case?

### 2015-05-20 practice/docs/thesis/cover_ack_abstract.tex
final thesis draft

@@
 
-\title{\large should probably decide whether to include chad's thing...}
+\title{Model Adaptivity for Goal-Oriented Inference}
 %\fontsize{15}{17}\selectfont 
@@
 
-...
+This work would not have been possible without the help of many others, whom I hope I have, or will be able to, thank in more meaningful ways than I am able to here.
+
+I am most deeply grateful to my advisor, Professor Karen Willcox, for her support and guidance throughout my undergraduate years and in my graduate studies, for allowing me to explore the realm of research and computational methods through UROPs when I was curious but clueless, for suggesting new directions whenever I ran myself into a corner, and for helping me work around what I feared were fatal weak points in my self.
+
+I am also very grateful to Dr.
+Vikram Garg, for allowing me to run with his ideas, for being patient in explaining new concepts, for describing these concepts in ways that were accessible to me even though my background was lacking, and for being the opposite of the scary person I was expecting when he was first introduced to me.
+
+I thank my parents, for doing their best to give me the freedom to pursue my interests, for being supportive of my choice to stay in school and conduct research even though I could no longer explain my work to them, and for forgiving me when I forgot their birthdays or to return their calls during the busiest times of the year.
+I thank my sister, for listening and reminding me of life outside of research.
+
+I thank my friends, for keeping me sane, for tempting me to take breaks and keeping me company when I refused, for providing baked goods when I began to regret my dislike for coffee, for listening when I was upset and allowing me to reciprocate, for being interesting people with interesting stories and interesting personalities.
+
+And I thank Dr. Bart van Bloemen Waanders, for allowing me to work with him over summers and explore areas of computational science outside of my thesis work.
+
+This work was supported by the United States Department of Energy, Office of Advanced Scientific Computing Research (ASCR), Applied Mathematics Program, awards DE-FG02-08ER2585 and DE-SC0009297, as part of the DiaMonD Multifaceted Mathematics Integrated Capability Center.

### 2015-05-20 practice/docs/thesis/formulation_v03.tex
final thesis draft

\chapter{Mathematical Formulation} \label{chap:form}

In Section \ref{sec:setup}, we define the goal-oriented inverse problem. In Section \ref{sec:deriv}, we derive an a posteriori estimate for the error in the QoI, as compared to that which would have resulted from solving the inverse problem with a high-fidelity model. In Section \ref{sec:limits}, we discuss the limitations of the error estimate.

%------------------------------------------------------------------------------%
\section{Problem Setup}  \label{sec:setup}
%------------------------------------------------------------------------------%

Consider a model for which the Galerkin formulation of the weak form is written as
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and $U,Q$ are Hilbert spaces. The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.

We define an observation operator $C:U\to\R^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$. The unknown parameters can then be inferred by minimizing the difference between the predicted and actual observations. This inverse problem is often ill-posed; the observations are noisy and sparse and thus insufficiently informative to uniquely determine the parameters. To remedy this, regularization is used to inject prior information or beliefs about the parameters. The inverse problem with regularization can be written as a constrained optimization problem
\begin{equation}
\begin{array}{r@{}c}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \\ \textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\end{array}
\label{eq:invOpt}
\end{equation}
where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization penalty term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model in Equation (\ref{eq:weakForm}).

In the case of a goal-oriented inverse problem, the ultimate purpose of inferring the unknown parameters is to calculate some Quantity of Interest (QoI). Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.

In the following derivation, we assume $a$ is three times continuously differentiable with respect to the state $u$ and parameters $q$, $C$ is three times continuously differentiable with respect to the state $u$, $R$ is differentiable with respect to the parameters $q$, and $I$ is differentiable with respect to the state $u$ and parameters $q$.

%------------------------------------------------------------------------------%
\section[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse \\Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%

A given physical system need not have a unique model that can describe it; there may be various models of different fidelities. For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.

%------------------------------------------------------------%
\subsection{Augmented Lagrangian} \label{sec:augLag}
%------------------------------------------------------------%

The inverse problem can be written as a constrained optimization problem, described in Equation (\ref{eq:invOpt}). Solving this constrained optimization problem is equivalent to finding the stationary point of the corresponding Lagrangian
\begin{equation}
\mathcal{L}(q,u,z)= J(q,u)-(a(u,q)(z)-\ell(q)(z)),
\end{equation}
where $z\in U$ is the adjoint.

Let $\xi=(q,u,z)$ be called the primary variables. Following the work of Becker and Vexler in \cite{BecVex05}, we introduce a set of auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$ corresponding to these primary variables, and define an augmented Lagrangian
\begin{equation}
\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}_{quz}'(q,u,z)(p,v,y),
\end{equation}
where $\mathcal{L}_{quz}'(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$. Let $\Psi = (\xi_\Psi,\chi_\Psi)$ denote the stationary point of $\mathcal{M}$, where $\xi_\Psi$ and $\chi_\Psi$ refer to the primary and auxiliary variables at $\Psi$, respectively. Note that
\begin{equation}
\mathcal{M}(\Psi)=I(q,u),
\label{eq:MeqI}
\end{equation} since taking variations of $\mathcal{M}$ with respect to the auxiliary variables gives that $\xi_\Psi$ is a stationary point of $\mathcal{L}$.

%------------------------------------------------------------%
\subsection{Expression for QoI Error} \label{sec:btwnMandadj}
%------------------------------------------------------------%

Consider two models with which we can infer parameters: a high-fidelity (HF) model and a lower-fidelity (LF) model. We then have a specific form of Equation (\ref{eq:weakForm}) for the high-fidelity model:
\begin{equation}
a_{HF}(u_{HF},q_{HF})(\phi_{HF})=\ell_{HF}(q_{HF})(\phi_{HF}),\quad\forall\phi_{HF}\in U_{HF},
\end{equation}
where $u_{HF}\in U_{HF}$ and $q_{HF}\in Q_{HF}$. Similarly, the inverse problem in Equation (\ref{eq:invOpt}) has the specific form
\begin{equation}
\begin{array}{r@{}c}
\min\limits_{q_{HF},u_{HF}} & \quad J_{HF}(q_{HF},u_{HF})=\frac{1}{2}\|d-C_{HF}(u_{HF})\|_2^2 + R_{HF}(q_{HF}) \\ \textrm{s.t. }& \quad a_{HF}(u_{HF},q_{HF})(\phi_{HF})=\ell_{HF}(q_{HF})(\phi_{HF}),\quad\forall\phi_{HF}\in U_{HF},
\end{array}
\end{equation}
for which we have the Lagrangian
\begin{equation}
\mathcal{L}_{HF}(q_{HF},u_{HF},z_{HF})= J_{HF}(q_{HF},u_{HF})-(a_{HF}(u_{HF},q_{HF})(z_{HF})-\ell_{HF}(q_{HF})(z_{HF})).
\end{equation}
Letting $\xi_{HF}=(q_{HF},u_{HF},z_{HF})$ and $\chi_{HF}=(p_{HF},v_{HF},y_{HF})$, we can thus define for the high-fidelity model an augmented Lagrangian
\begin{equation}
\mathcal{M}_{HF}(\xi_{HF},\chi_{HF}) = I(q_{HF},u_{HF}) + \mathcal{L}_{HF,\xi_{HF}}'(\xi_{HF})(\chi_{HF}),
\label{eq:MHF}
\end{equation}
the stationary point of which we denote by $\Psi_{HF}$. In a similar fashion, the lower-fidelity model is described by
\begin{equation}
a_{LF}(u_{LF},q_{LF})(\phi_{LF})=\ell_{LF}(q_{LF})(\phi_{LF}),\quad\forall\phi_{LF}\in U_{LF},
\end{equation}
where $u_{LF}\in U_{LF}$ and $q_{LF}\in Q_{LF}$, and its corresponding inverse problem can be written
\begin{equation}
\begin{array}{r@{}c}
\min\limits_{q_{LF},u_{LF}} & \quad J_{LF}(q_{LF},u_{LF})=\frac{1}{2}\|d-C_{LF}(u_{LF})\|_2^2 + R_{LF}(q_{LF}) \\ \textrm{s.t. }& \quad a_{LF}(u_{LF},q_{LF})(\phi_{LF})=\ell_{LF}(q_{LF})(\phi_{LF}),\quad\forall\phi_{LF}\in U_{LF},
\end{array}
\end{equation}
for which we have the Lagrangian
\begin{equation}
\mathcal{L}_{LF}(q_{LF},u_{LF},z_{LF})= J_{LF}(q_{LF},u_{LF})-(a_{LF}(u_{LF},q_{LF})(z_{LF})-\ell_{LF}(q_{LF})(z_{LF})),
\end{equation}
and, letting $\xi_{LF}=(q_{LF},u_{LF},z_{LF})$ and $\chi_{LF}=(p_{LF},v_{LF},y_{LF})$, an augmented Lagrangian 
\begin{equation}
\mathcal{M}_{LF}(\xi_{LF},\chi_{LF}) = I(q_{LF},u_{LF}) + \mathcal{L}_{LF,\xi_{LF}}'(\xi_{LF})(\chi_{LF}),
\label{eq:MLF}
\end{equation}
the stationary point of which we denote by $\Psi_{LF}$. We assume some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.

Extending the property in Equation (\ref{eq:MeqI}) to the specific cases in Equations (\ref{eq:MHF}) and (\ref{eq:MLF}), we can write the error in the QoI from solving the inverse problem with a lower-fidelity model rather than the high-fidelity model as
\begin{multline}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})\textrm{.} 
\label{eq:repIwithM}
\end{multline}
We rewrite the first two terms $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ in Equation (\ref{eq:repIwithM}) by extending the work of \cite{BecVex05} to the context of multiple models.

In \cite{BecVex05}, Becker and Vexler consider the error in the QoI from solving the inverse problem with a discretized model instead of the infinite-dimensional model. They describe the discretized model by
\begin{equation}
a(u_h,q_h)(\phi_h)=\ell(q_h)(\phi_h),\quad\forall\phi_h\in U_h\subset U,
\label{eq:weakFormh}
\end{equation}
where $u_h\in U_h$ is the discrete state and $q_h\in Q$ are the unknown parameters, and $U_h$ is a finite-dimensional space constructed from finite element functions on a mesh with element size $h$. The infinite-dimensional model is as described in Equation (\ref{eq:weakForm}). For these two models (\ref{eq:weakForm}) and (\ref{eq:weakFormh}) they derive the expression
\begin{equation}
I(q,u)-I(q_h,u_h)=\frac{1}{2}\mathcal{M}'_\Psi(\Psi_h)(\Psi-\Psi_h)+\mathcal{R}(e^3)
\label{eq:BVerrexp}
\end{equation}
where $\Psi$ is the stationary point of the augmented Lagrangian $\mathcal{M}$ as defined in Section \ref{sec:augLag} and $\Psi_h$ is its discretized counterpart, and where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi-\Psi_h$. Using Equation (\ref{eq:MeqI}), we can also write Equation (\ref{eq:BVerrexp}) as 
\begin{equation}
\mathcal{M}(\Psi)-\mathcal{M}(\Psi_h)=\frac{1}{2}\mathcal{M}'_\Psi(\Psi_h)(\Psi-\Psi_h)+\mathcal{R}(e^3)
\label{eq:BVerrexpM}
\end{equation}

Given our assumptions, Equation (\ref{eq:BVerrexpM}) holds when the infinite-dimensional model and discretized model are replaced with our more general higher- and lower-fidelity models, respectively. This allows us to write
\begin{equation}
\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
\end{equation}
where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$. Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:preadj}) we obtain
\begin{multline}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{.} 
\label{eq:preadj}
\end{multline}
In the work of Becker and Vexler in \cite{BecVex05}, the term $\Psi-\Psi_h$ in Equation (\ref{eq:BVerrexp}) is estimated using interpolation. In our case, we cannot similarly address the term $\Psi_{HF}-\Psi_{LF}$ in Equation (\ref{eq:preadj}), since we now have different models instead of different discretizations of the same model.

%------------------------------------------------------------%
\subsection{QoI Error Adjoint Formulation}
%------------------------------------------------------------%

As adjoints have been used to estimate the error in an output of a forward model, we take an adjoint approach to obtain the term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ by viewing it as an error in a linear output of some system. As $\Psi_{HF}$ is a stationary point of $\mathcal{M}$, it satisfies $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$; we write this equation in residual form as
\begin{equation}
\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
\label{eq:supadjsys}
\end{equation}
and define an output 
\begin{equation}
\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi)
\label{eq:supadjout}
\end{equation}
that is linear in its argument $\Phi$. We can then solve the adjoint equation corresponding to the output in Equation (\ref{eq:supadjout}) for the system in Equation (\ref{eq:supadjsys}), given by
\begin{equation}
\mathscr{R}_{\Psi}'(\Phi)(\Psi_{HF},\Lambda)=\mathcal{Q}(\Phi)=\mathcal M'_{HF}(\Psi_{LF})(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
\label{eq:superAdjEq}
\end{equation}
for the supplementary adjoint $\Lambda$. The error in the output $\mathcal{Q}$ defined in Equation (\ref{eq:supadjout}) can thus be expressed as a dual-weighted residual
\begin{equation}
\mathcal M'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})=-\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda).
\label{eq:adjOutErr}
\end{equation}

%------------------------------------------------------------%
\subsection{Error Estimate}
%------------------------------------------------------------%

Combining Equations (\ref{eq:preadj}) and (\ref{eq:adjOutErr}), we obtain a third-order expression for the error in the QoI from solving the inverse problem using a lower-fidelity model instead of the high-fidelity model:
\begin{multline}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
\label{eq:finErrExp}
\end{multline}

The error estimate (\ref{eq:finErrExp}) is general and the lower-fidelity model can also be a mixed-fidelity model that combines the high- and low-fidelity model. Given a low-fidelity model and a high-fidelity model, an intermediate, mixed-fidelity (MF) model can be formed by using the high-fidelity model in some parts of the domain, and the low-fidelity model in the rest of the domain. Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model. The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model. This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.

%------------------------------------------------------------%
\subsection{Approximations in Practice}
%------------------------------------------------------------%

Although Equation (\ref{eq:finErrExp}) is exact, the error estimate that can be calculated in practice will not generally be exact. Let us refer to a goal-oriented inverse problem as linear when the state $u$ and parameters $q$ are linearly related, the observation operator $C$ is linear in $u$, the regularization term $R$ is at most quadratic in the parameters, and the QoI functional $I$ is linear in $u$ and $q$. The remainder term $\mathcal{R}(e^3)$ is included in Equation (\ref{eq:finErrExp}) but would not, in practice, be calculated; in the case of a linear goal-oriented inverse problem, the remainder term disappears, but it is nonzero in general. In addition, the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem must be approximated by linearizing about $\Psi_{LF}$ instead.

A summary of our overall approach is presented in Algorithm \ref{alg:refSeries}, with the estimated absolute relative error chosen as a stopping criterion.

\alglanguage{pseudocode}
\begin{algorithm}[h]
\small
\caption{An algorithm to adaptively build a mixed-fidelity model for low error in the QoI.}
\label{alg:refSeries}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Define maximum number of adaptive iterations \texttt{maxIter}}
\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
	\State{$i\gets0$}
	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for

	supplementary adjoint $\Lambda_0$ (see Equation (\ref{eq:superAdjEq}))}
	\State{Compute QoI error estimate

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $e_{I,i}$ and use this element-wise decomposition to guide formation \par\hskip\algorithmicindent of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

		$\quad\quad$supplementary adjoint $\Lambda_i$ (see Equation (\ref{eq:superAdjEq}))}
		\State{Compute QoI error estimate

		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
	\EndWhile \\
\Return{model MF$_i$ and QoI estimate $I(q_{MF_i},u_{MF_i})$}
\EndProcedure
\Statex
\end{algorithmic}
\end{algorithm}

%section/note that forming a mixed-fidelity model is not always so straightforward? should poke literature about how this is done if so (model interfacing that Oden,Prudhomme, etal talk about...also seemed to have a sort of interior-boundary-condition for stokes-ns mix)...also include de-refinement? (choices of how to pick where to refine? if so, would we need to reference other papers where similar choices are made?)
	%just a note that smushing together is not always best? ex: linear diff vs convdiff, it all holds, but such a MF model is not necessarily 'closer' to HF in that qoi not necessarily closer..

%if I is a PDE, then is it also possible that it can be excessively complex as well? though in that case would there be any 'regularization' to avoid?

%------------------------------------------------------------------------------%
\section{Limitations}  \label{sec:limits}
%------------------------------------------------------------------------------%

In motivating our approach, it is assumed that one can most accurately calculate the QoI from the parameter values inferred using the highest-fidelity forward model available, but that solving the inverse problem with this model is prohibitively expensive. It is also assumed that solving the inverse problem with a mixed-fidelity model, where this highest-fidelity model is only used in a portion of the domain, will be cheaper. There is a cost incurred by using our approach to design such a mixed-fidelity model, however, and it will sometimes be the case that the cost of obtaining this mixed-fidelity model exceeds that of just solving the inverse problem with the highest-fidelity model directly. Naively, if the auxiliary variables $\chi$ have $n$ degrees of freedom, they can be found by solving an $n\times n$ linear system, while the supplementary adjoint $\Lambda$ can be found by solving a $2n\times2n$ linear system. The cost of solving for the auxiliary variables can be reduced by using a technique described in \cite{BecVex05}, and the cost of solving for the supplementary adjoint $\Lambda$ can be reduced by reusing preconditioners. In general there are no guarantees that obtaining a mixed-fidelity model that meets the desired QoI error criterion will be less costly than just solving the inverse problem with the high-fidelity model. However, our approach targets problems for which solving the inverse problem with the high-fidelity model is prohibitively expensive, in which case it is expected that the cost of obtaining a satisfactory mixed-fidelity model will be comparatively low. Even in the case where a mixed-fidelity model for which the QoI error is adequately small cannot be found before another limit (for example, a maximum number of adaptive iterations) is reached, one still has an estimate for the error in the QoI without solving the prohibitively expensive inverse problem.

The derived error estimate is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in \cite{BecVex05} would be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models must have a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. The weak form, observation operator, regularization term, and QoI functional must also have the degrees of differentiability noted in Section \ref{sec:setup}. The two models must also have some degree of compatibility, as previously described in Section \ref{sec:btwnMandadj}.

### 2015-05-20 practice/docs/thesis/intro_v03.tex
final thesis draft

\chapter{Introduction}

%------------------------------------------------------------------------------%
\section{Motivation}  %\label{sec:xx}
%------------------------------------------------------------------------------%

In scientific and engineering contexts, physical systems are represented by mathematical models, which often take the form of partial differential equations (PDEs). These models are characterized by a set of parameters, and since they relate these parameters to states that can be observed, they are referred to as forward models. The forward problem, then, involves solving the PDEs for a given set of parameters. Inverse problems, on the other hand, arise when the parameters are unknown and one tries to infer these parameters based on observations of the states or parameters \cite{Taran05, BanksKuhn89}. Inverse problems appear in many contexts, such as heat transfer \cite{Alif94}, medical imaging \cite{Arr99,Ren10}, contaminant source identification \cite{Sun99}, and reservoir characterization \cite{OliReyLiu08}.

In such applications the parameters may be numerous, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI). For example, we may wish to infer the permeability field of an aquifer to form a numerical model that can then be used to design an optimal management policy for the groundwater in the aquifer \cite{Sun99}; in this case, the QoI might be the concentration of a contaminant at a water well resulting from the implementation of a particular policy. In such a situation, where the QoI is of greatly reduced dimensionality compared to the parameters, it may not be necessary to fully resolve all the parameters to obtain the QoI accurately. We refer to the setting where the goal of inferring parameters is to use them in predicting a QoI as a \textit{goal-oriented inverse problem}. A diagram of the relationship between parameters, observations, and the QoI is given in Figure \ref{fig:qdI}.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{intro/paramObsQoI.pdf}
\caption{The observation process, which often includes the forward model, relates the unknown parameters to the observations, which are also contaminated by noise. Once these parameters have been inferred from the observations, they are related to the QoI through the prediction process.}
\label{fig:qdI}
\end{figure}

In this spirit, one way to simplify the process of inferring the parameters is to represent the physical system to a coarser degree. A given physical system can be represented with varying degrees of fidelity by different models. A high-fidelity model may, for example, take into account more physical laws or be more finely discretized, and thus more accurately represent reality. However, a high-fidelity model is also usually more difficult to solve. Since solving the inverse problems generally requires many evaluations of the forward model, it may be cheaper to use a lower-fidelity model. In addition, the inverse problem is often ill-posed without regularization; it may be the case that even if one were to use the high-fidelity model, the additional resolution (in space-time and/or physical laws) of the high-fidelity model might not even be informed by the observations. Thus, it may not be necessary to infer the parameters using the expensive, high-fidelity model in order to accurately calculate the QoI. Just as we manage models to control the error in QoI predictions from solving the forward problem, for example through mesh adaptation, our research here aims to manage the fidelity of modeling choices in solving the inverse problem, so as to achieve a desired level of accuracy in the QoI prediction, without necessarily resolving the parameters accurately. We adaptively form a mixed-fidelity model with which we solve the inverse problem by using models of different levels of fidelity in different parts of the domain.

In the next section, we describe existing work on goal-oriented approaches and multifidelity modeling.

%------------------------------------------------------------------------------%
\section{Previous Work}  %\label{sec:xx}
%------------------------------------------------------------------------------%

In this section, we describe previous work, first on goal-oriented approaches and then on multifidelity modeling.

%------------------------------------------------------------%
\subsection{Goal-Oriented Approaches}
%------------------------------------------------------------%

Especially in engineering contexts, the ultimate goal of running a forward simulation or inferring parameters is to calculate some low-dimensional quantity of interest; the exact states or parameters may not otherwise be of interest. Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters.

In the context of the forward problem, methods for goal-oriented mesh-refinement using adjoints are described in \cite{PrudOden99,VendDarm00,BecRann01}; an a posteriori error estimate in an output functional is derived, and this estimate is used to guide adaptive mesh-refinement. A framework for automated mesh-refinement to calculate a QoI to a prescribed accuracy is described in \cite{Yano12}. In \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; however, instead of targeting adaptive mesh refinement, the method adaptively divides the domain into subdomains where models describing different scales are applied. 
%read VendDarm00 for the lulz?

Work has also been done on goal-oriented methods for the inverse problem. Mesh-refinement in the goal-oriented inverse problem\footnote{What we refer to as the goal-oriented inverse problem is referred to as the problem of model calibration in \cite{BecVex05}.} is addressed in \cite{BecVex05}; in this work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite dimensional inverse problem, and this error estimate is used to adaptively refine the mesh. In \cite{LiebWill13}, Lieberman and Willcox describe, for a discretized linear inverse problem, a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI; this subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them.

%goal-oriented DoE from marzouk?
	%goal-oriented-ness seems to be not the focus of http://arxiv.org/pdf/1108.4146v3.pdf, but can be incorporated into utility function
%------------------------------------------------------------%
\subsection{Mixed-fidelity Models} \label{sec:multFid}
%------------------------------------------------------------%

A particular physical system can be represented with varying degrees of fidelity by different models. Often a lower-fidelity model will be cheaper to solve. However, it will also describe reality to a lesser degree of accuracy; it may include fewer physical laws (for example, the Euler equations ignore viscosity) or describe phenomena at a coarser scale (for example, a model of linear elasticity does not treat individual atoms). A mixed-fidelity model can combine higher- and lower-fidelity models in a way so as to be more tractable than the high-fidelity model, while maintaining accuracy.

Two main strategies exist for combining models: hierarchical and concurrent methods. Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally (for example, modeling the molecular structure of a material to determine parameters for constitutive equations \cite{Haoetal03}). Concurrent methods simultaneously solve the high-fidelity model in some small portions of interest of the domain and the low-fidelity model in the remainder of the domain; for example, in \cite{Khareetal08} atomistic models capable of describing bond-breaking behaviors are applied to small clusters of atoms in regions relevant to the formation of fractures, while a continuum model is applied in the rest of the domain.

In our approach, we focus on concurrent methods of combining models. In general, the different models need not depict different scales. For example, in \cite{vanOpstaletal15} a mixed-fidelity model is formed by dividing the domain into subdomains where either the linear Stokes equation (low-fidelity) or the nonlinear Navier-Stokes equation (high-fidelity) is solved, based on an a posteriori estimate of the error in a QoI. The different models also need not represent different physical phenomena. For example, in \cite{LucKinBer02}, the domain is decomposed into regions with and without shocks, and a reduced-order model is developed for each region independently and later combined; in \cite{AntHein10}, balanced truncation model reduction is applied to the part of the domain outside of where the optimization variables are located in order to reduce the overall cost of a forward solve. The manner in which the different models are interfaced is problem-dependent; in \cite{Abra98, AlexGarTar02}, a ``handshake'' region is used to couple concurrent particle and continuum models, and in \cite{AlexGarTar02}, interface coupling models are introduced to reconcile uncertainties in the different models.

%hierarchical vs concurrent multi models- have lf-hf-mf cartoon here?
	%also apparently HF+LF models are combined by having the HF models generate numerical observations to use as training for reduced basis models

%idea of most-complex \neq best? occam's razor thing from all-hands...we may define HF as "best" for getting QoI, but it might not necessarily be the hardest to work with...

%------------------------------------------------------------------------------%
\section{Thesis Objectives}  %\label{sec:xx}
%------------------------------------------------------------------------------%

We aim to combine the ideas in goal-oriented methods for inverse problems, and goal-oriented model adaptivity approaches for forward modeling. The objective of this work is to formulate a method that allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. To do this, we first assume that solving the inverse problem with the highest-fidelity model would result in the most accurate QoI, but that solving this inverse problem is prohibitively expensive. We derive an estimate for the error in the QoI from inferring the parameters using a lower-fidelity model. This estimate can be localized to individual elements, and the element-wise decomposition can then be used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI. This process is illustrated in Figure \ref{fig:lfhfmf}.

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[width=\textwidth]{intro/hf.pdf}
\caption{High-fidelity}
\label{subfig:hf}
\end{subfigure}
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[width=\textwidth]{intro/lf.pdf}
\caption{Low-fidelity}
\label{subfig:lf}
\end{subfigure}
\begin{subfigure}[b]{0.32\textwidth}
\includegraphics[width=\textwidth]{intro/mf.pdf}
\caption{Mixed-fidelity}
\label{subfig:mf}
\end{subfigure}
\caption{For a given QoI (e.g. average concentration in a region of an aquifer) and a set of observations (e.g. concentration measurements from wells), solving the inverse problem with a mixed-fidelity model (\subref{subfig:mf}), formed by using the high-fidelity (\subref{subfig:hf}) and low-fidelity (\subref{subfig:lf}) model in different parts of the domain, may give a QoI estimate with low error relative to that obtained from inferring the parameters with the high-fidelity model.}
\label{fig:lfhfmf}
\end{figure}

%------------------------------------------------------------------------------%
\section{Thesis Outline}  %\label{sec:xx}
%------------------------------------------------------------------------------%

In Chapter \ref{chap:form}, we define the goal-oriented inverse problem, derive an a posteriori error estimate for the QoI, and discuss its use for model adaptivity in the context of the goal-oriented inverse problem. In Chapter \ref{chap:results}, we apply the error estimate to adaptively form a mixed-fidelity model for two-dimensional convection-diffusion-reaction examples. In Chapter \ref{chap:conc}, we give a summary of the thesis, and suggest directions for future work.

### 2015-05-20 practice/docs/thesis/results_v03.tex
final thesis draft

\chapter{Numerical Results} \label{chap:results}

In this chapter we demonstrate some results from applying our approach to pairs of steady-state models, implemented using the \texttt{libMesh} library \cite{libMeshPaper}. In Section \ref{sec:cdvcdr}, we demonstrate the results using two models that differ in the physics modeled. In Section \ref{sec:constvfield}, the two models differ in the space to which the parameter belongs. In Section \ref{sec:costAnaly} we discuss the numerical costs of our approach.

%------------------------------------------------------------------------------%
\section{Convection-Diffusion and Convection-Diffusion-Reaction Models}  \label{sec:cdvcdr}
%------------------------------------------------------------------------------%

In this section, we demonstrate the method derived in Section \ref{sec:deriv} for two models which differ in the physics included. We first describe the problem setup, and then present results from applying our approach.

%------------------------------------------------------------%
\subsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%

The high- and low-fidelity models are restricted to a rectangular domain $\Omega$, defined as $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),
\label{eq:cdvcdrHF}
\end{equation}
where the state $u$ is the species concentration, $f(q)$ is a forcing field described by the parameters, $k_d = 0.1$ is a diffusion coefficient and $k_r = -42.0$ is a reaction coefficient. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
differs only in the removal of the reaction term. Both models share a common velocity field, described by $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by 
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
where $k^{MF}_r$ is a piecewise-constant reaction coefficient
\begin{equation}
k^{MF}_r=
\begin{cases}
-42.0 & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain.

We let the unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. Observations $d=(u(0.35,0.35),u(1.56,0.61),u(3.1,0.5))$ from three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with a piecewise constant source term $f_{true}$
\begin{equation}
f_{true}(x_1,x_2)=
\begin{cases}
1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
0 & \textrm{otherwise}.
\end{cases}
\end{equation}
The QoI we wish to calculate is the integral of the state,
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The locations of the observations and the region $\Omega_I$ over which the QoI is calculated is shown in Figure \ref{fig:baseSetup}. Since the inverse problem is ill-posed, we use Tikhonov regularization \cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is a regularization coefficient.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}

For the numerical simulations, we use the \texttt{libMesh} library \cite{libMeshPaper}. The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements. We implement the finite element method (FEM) for a continuous Galerkin formulation using a linear nodal basis, for a total of 76,806 degrees of freedom. The P\'{e}clet number never exceeds 0.1 in any part of the domain, so we do not require stabilization.

%------------------------------------------------------------%
\subsection{Adaptive Model Refinement} \label{sec:cdvcdrBaseRef} 
%------------------------------------------------------------%

Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error. Here we calculate the contribution to the estimated error by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element. As described in Algorithm \ref{alg:refSeries}, based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$. In this case, once an element is assigned to the high-fidelity portion of the domain $\Omega_{HF}$, it remains assigned as such for all future subsequent mixed-fidelity models. Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}, while the effectivity index for the error estimate, defined by
\begin{equation}
\textrm{effectivity index}=\frac{\textrm{estimated QoI error}}{\textrm{true QoI error}},
\end{equation}
is shown in Figure \ref{fig:baseErrEff}.

It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate. In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $15\%$ of the domain.

\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF03_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF03.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_3$ ($15\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErrEff}
\end{figure}

\subsection{Interaction of Observations and QoI}

The element-wise decomposition of the error estimate (\ref{eq:finErrExp}) suggests the use of the high-fidelity model in areas of the domain where the parameter field is both informed by the observations and informative about the QoI. To see this, we compare the element-wise decomposition of the error estimate for three sizes of the QoI region $\Omega_I$ given the same set of observations, and for three sets of observations given the same QoI region. Again we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$. The element-wise decomposition of the error estimates (from the first three iterations) for the three sizes of the QoI region $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}, and for the three sets of observations given the same QoI region is shown in Figure \ref{fig:dataStudy}. For the three cases where the observations were fixed but the QoI region allowed to vary, more iterations were required as the QoI region expanded; only the first three iterations are shown in Figure \ref{fig:qoiStudy}. For the three cases where the QoI region was fixed but the set of observations allowed to vary, only three iterations were required to achieve an estimated absolute relative QoI error of less than $1\%$; all three iterations are shown in Figure \ref{fig:dataStudy}.

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.191\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/setup_5_3.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/setup_7_3.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/setup_3_3.pdf}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_LF.pdf}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF01.pdf}
    \caption{MF$_1$ \\ ($5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF02.pdf}
    \caption{MF$_2$ \\ ($10\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.243\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF03.pdf}
    \caption{MF$_3$ \\ ($15\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
  \label{fig:qoiStudy}
\end{figure}

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.191\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/setup_3_10.pdf}
    \includegraphics[width=\textwidth]{vs_data/setup_3_5.pdf}
    \includegraphics[width=\textwidth]{vs_data/setup_3_3.pdf}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_LF.pdf}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF01.pdf}
    \caption{MF$_1$ \\ ($5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF02.pdf}
    \caption{MF$_2$ \\ ($10\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.245\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF03.pdf}
    \caption{MF$_3$ \\ ($15\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same QoI region (purple box in (\subref{subfig:obsSetup})) and varying observations (teal points in (\subref{subfig:obsSetup})).}
  \label{fig:dataStudy}
\end{figure}

The convective aspect of the models causes information to flow with the velocity field, and the diffusive aspect causes information to spread locally. Thus, it is expected that it would be most important to use the high-fidelity model in the QoI region, and in areas around observations upstream and just downstream of the QoI region. Using the high-fidelity model around observations is expected to become less important as the observations are placed further downstream from the QoI region. These expectations are supported by the results. For this pair of models and a QoI that is the integral of the state over a region, an appropriate mixed-fidelity model could have been designed by intuition. However, the interaction between the observations and the QoI may not always be so intuitive, and it is in these cases that a rigorous method for forming a mixed-fidelity model would be most helpful.

%\subsection{Effect of Regularization} %removed; more regularization doesn't seem to imply you can stop refining sooner...

\subsection{Highly Nonlinear Problems} \label{sec:solveRob}

For a highly nonlinear high-fidelity model, it may sometimes be the case that solving the inverse problem requires a more complex or specialized optimization algorithm; for example, one may need to use continuation methods (such as in \cite{BaoLiu03}), or utilize a problem-specific preconditioner (such as in \cite{Hanke00}). However, solving the inverse problem with a mixed-fidelity model, where this high-fidelity model is only used in a small portion of the domain, may be achievable using a simpler optimization algorithm. In this subsection, we give an example of such a case.

To solve the inverse problem, we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search) to solve the optimality conditions of the corresponding optimization problem (see Equation \ref{eq:invOpt}). Keeping most of the setup described in Section \ref{sec:cdvcdrSetup}, we consider a different high-fidelity model, one where the magnitude of the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) is increased from $k_r=-42$ to $k_r=-442$; let this new model be denoted by HF$_{442}$. We can no longer simply use the default nonlinear solver in \texttt{libMesh} to solve the inverse problem with this new, more nonlinear high-fidelity model, as the solver fails to converge. Convergence can be achieved by using continuation; we solve the inverse problem for a sequence of models, varying the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) from $k_r=-42$ to $k_r=-442$ at intervals of 50, and using the solution of one problem as the initial guess for the next.

Alternatively, we use Algorithm \ref{alg:refSeries} to generate a series of mixed-fidelity models using the low-fidelity model and the HF$_{442}$ model. The inverse problem can be solved for these mixed-fidelity models using the default nonlinear solver, and we are able to achieve an estimated relative QoI error of less than $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $25\%$ of the domain, as shown in Figure~\ref{fig:442Err}. Figure \ref{fig:442ErrEff} gives the effectivity index of the error estimates.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{442/err_est.pdf}
\caption{Estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
\label{fig:442Err}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{442/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
\label{fig:442ErrEff}
\end{figure}

%------------------------------------------------------------------------------%
\section{Constant versus Field Parameters}  \label{sec:constvfield}
%------------------------------------------------------------------------------%

In this section, we consider two models which differ in the space to which the parameter belongs. We first describe the problem setup, and then present results from applying our approach.

%------------------------------------------------------------%
\subsection{Problem Setup} %\label{sec:svfSetup}
%------------------------------------------------------------%

The high-fidelity model 
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
is again a single-species convection-diffusion-reaction equation with a nonlinear reaction term, where $k_d = 0.1$ is a diffusion coefficient and $k_r = -4.2$ is a reaction coefficient. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The velocity field and boundary conditions, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in Section~\ref{sec:cdvcdr}. As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient. For this case, the domain is discretized by a regular mesh of quadrilaterals, with 15 and 75 elements along the short and long boundaries, respectively, for a total of 11,250 elements. The P\'{e}clet number never exceeds 0.34 in any part of the domain, so we do not require stabilization.

%------------------------------------------------------------%
\subsection{Adaptive Model Refinement} %\label{sec:svfBaseRef}
%------------------------------------------------------------%

Based on the element-wise decomposition of the estimated error, we increase the proportion of the domain in which the high-fidelity field representation model is used until the estimated absolute relative error in the QoI is less than $5\%$. In this case, we allow an element assigned to $\Omega_{HF}$ in one mixed-fidelity model to be reassigned back to $\Omega_{LF}$ in subsequent mixed-fidelity models if its contribution to the error is not large enough. Figure~\ref{fig:svfRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the first six of the series of mixed-fidelity models thus generated. The true and estimated absolute relative errors in the QoI for these same intermediate models are shown in Figure \ref{fig:svfErr}, while the effectivity index of the error estimate is shown in Figure \ref{fig:svfErrEff}.

\begin{figure}[h!]
\begin{subfigure}[b]{\textwidth}
\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_0$ ($0\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_1$ ($5\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_2$ ($10\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF03.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_3$ ($12\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF04.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_4$ ($15\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF05.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_5$ ($20\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_6$ ($25\%$ HF)}
\end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.}
\label{fig:svfRef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErrEff}
\end{figure}

As in the previous example, the error estimates are only approximate due to the nonlinear term in both the low- and high-fidelity models. In this case, the high-fidelity model must also be used in a larger portion of the domain ($60\%$) before the estimated relative error in the QoI reaches the desired level.

%------------------------------------------------------------------------------%
\section{Cost Analysis} \label{sec:costAnaly}
%------------------------------------------------------------------------------%

In both the examples discussed in Sections \ref{sec:cdvcdr} and \ref{sec:constvfield}, the high-fidelity model is simple and solving the inverse problem with the high-fidelity model is easily achievable. Doing so actually requires less computational time than using Algorithm \ref{alg:refSeries} to rigorously form a mixed-fidelity model with which to solve the inverse problem instead. However, as discussed in Section \ref{sec:limits}, we assume in motivating our approach that solving the inverse problem with the high-fidelity model is prohibitively expensive; although there is no benefit, in terms of computational cost, to using our approach in the given examples, one would likely see such benefits for more complex models. Such a benefit is suggested in Section \ref{sec:solveRob}, where the inverse problem using the high-fidelity model is difficult to solve but our approach allows one to construct a mixed-fidelity model for which the inverse problem can be solved with a simple algorithm and yet produce a QoI with a small estimated relative error.

%can philosophically compare with chad's though, perhaps in param refinement, even though his is in parameter subspaces and ours is in physical space?

### 2015-05-20 practice/T_channel/diff_param_res/all_linear/get_psiMF_split_discon/element_qoi.C

@@ -103,10 +103,12 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
 			if(subdomain == field_subdomain_id){
 		    MHF_psiLF_elem += JxW[qp]*(-k*grad_c*grad_auxzc - U*grad_c*auxzc + R*c*c*auxzc + fc*auxzc);
 	 			MHF_psiLF_elem += JxW[qp]*(beta*grad_fc*grad_auxfc + beta*fc*auxfc + zc*auxfc);
+//std::cout << myElemID << "(field): " << c << " " << zc << " " << auxc << " " << auxzc << " " << fc << " " << auxfc << std::endl; //DEBUG
  			}
  			else{
  				MHF_psiLF_elem += JxW[qp]*(-k*grad_c*grad_auxzc - U*grad_c*auxzc + R*c*c*auxzc + fconst*auxzc);
 	 			MHF_psiLF_elem += JxW[qp]*(beta*fconst*auxfconst + zc*auxfconst);
+	//std::cout << myElemID << "(scalar): " << c << " " << zc << " " << auxc << " " << auxzc << " " << fconst << " " << auxfconst << std::endl; //DEBUG
  			}
 
    		if((qoi_option == 1 && 
@@ -152,5 +154,5 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
   MHF_psiLF[myElemID] += MHF_psiLF_elem;
   MLF_psiLF[myElemID] += MLF_psiLF_elem;
 
-
+//std::cout << myElemID << ": " << MHF_psiLF_elem << std::endl; //DEBUG
 }

### 2015-05-20 practice/T_channel/diff_param_res/all_linear/get_super_adj_discon/convdiff_mprime.C

@@ -24,20 +24,21 @@ void ConvDiff_MprimeSys::init_data (){
 	unsigned int conc_p = 1;
 	GetPot infile("convdiff_mprime.in");
 	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+	
+	//subdomain ids
+	scalar_subdomain_id = infile("scalar_id", 0);
+	field_subdomain_id = infile("field_id", 1);
 
-	// LBB needs better-than-quadratic velocities for better-than-linear
-	// pressures, and libMesh needs non-Lagrange elements for
-	// better-than-quadratic velocities.
-	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+	std::set<subdomain_id_type> active_subdom_field; 	active_subdom_field.insert(field_subdomain_id);
 
 	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
                          
 	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
 	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
-	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily, &active_subdom_field); 
 	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
 	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
-	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);  
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily, &active_subdom_field);  
 
 	//regularization
 	beta = infile("beta",0.1);
@@ -52,10 +53,6 @@ void ConvDiff_MprimeSys::init_data (){
 	this->time_evolving(aux_zc_var);
 	this->time_evolving(fc_var);
 	this->time_evolving(aux_fc_var);
-
-	//subdomain ids
-	scalar_subdomain_id = infile("scalar_id", 0);
-	field_subdomain_id = infile("field_id", 1);
 	
 	// Useful debugging options
 	// Set verify_analytic_jacobians to 1e-6 to use

### 2015-05-20 practice/T_channel/diff_param_res/all_linear/get_super_adj_discon/convdiff_mprime.h

@@ -67,24 +67,6 @@ public:
 	  	fclose(fp);
 		}
 		
-		//since mesh's xda file doesn't contain subdomain information, and since divvy is normally put in super-adj folder...
-		subdoms.resize(this->get_mesh().n_elem());
-		std::fill(subdoms.begin(),subdoms.end(), 0.);
-		std::string read_assign = "divvy.txt";
-		if(FILE *fp=fopen(read_assign.c_str(),"r")){
-			int flag = 1;
-			int elemNum, assign;
-			int ind = 0;
-			while(flag != -1){
-				flag = fscanf(fp, "%d %d",&elemNum,&assign);
-				if(flag != -1){
-					subdoms[ind] = assign;
-					ind += 1;
-				}
-			}
-			fclose(fp);
-		}
-		
 		sadj_auxc_point_stash.resize(datavals.size()); //DEBUG
 		sadj_c_point_stash.resize(datavals.size()); //DEBUG
 		
@@ -183,6 +165,5 @@ public:
   std::vector<Real> const_vars;
   
   //keep track of subdomains
-  std::vector<double> subdoms;
   int scalar_subdomain_id, field_subdomain_id;
 };

### 2015-05-20 practice/T_channel/diff_param_res/all_linear/get_super_adj_discon/element_qoi.C

@@ -26,7 +26,7 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
   ctxt.get_element_fe( c_var , elem_fe );
   
   int myElemID = ctxt.get_elem().id();
-  int subdomain = subdoms[myElemID];
+  int subdomain = ctxt.get_elem().subdomain_id();
 
   // Element Jacobian * quadrature weights for interior integration
   const std::vector<Real> &JxW = elem_fe->get_JxW();
@@ -105,11 +105,15 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
       if(subdomain == field_subdomain_id){
 		    MHF_psiLF_elem += JxW[qp]*(-k*grad_c*grad_auxzc - U*grad_c*auxzc + R*c*c*auxzc + fc*auxzc);
 	 			MHF_psiLF_elem += JxW[qp]*(beta*grad_fc*grad_auxfc + beta*fc*auxfc + zc*auxfc);
+std::cout << myElemID << "(field): " << c << " " << zc << " " << auxc << " " << auxzc << " " << fc << " " << auxfc << std::endl; //DEBUG
  			}
  			else{
  				MHF_psiLF_elem += JxW[qp]*(-k*grad_c*grad_auxzc - U*grad_c*auxzc + R*c*c*auxzc + const_vars[0]*auxzc);
 	 			MHF_psiLF_elem += JxW[qp]*(beta*const_vars[0]*const_vars[1] + zc*const_vars[1]);
+std::cout << myElemID << "(scalar): " << c << " " << zc << " " << auxc << " " << auxzc << " " << const_vars[0] << " " << const_vars[1] << std::endl; //DEBUG
  			}
+ 			
+
 
    		if((qoi_option == 1 && 
 						((dim == 2 && (fabs(ptx - 0.5) <= 0.125 && fabs(pty - 0.5) <= 0.125)) || 
@@ -232,6 +236,8 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
 	if(debug_step == 0){
 		MHF_psiLF[myElemID] += MHF_psiLF_elem;
 		MLF_psiLF[myElemID] += MLF_psiLF_elem;
+		
+//std::cout << myElemID << ": " << MHF_psiLF_elem << std::endl; //DEBUG
 	}
 	else if(debug_step == 2){
 		half_sadj_resid[myElemID] += -0.5*half_sadj_resid_elem; //DEBUG

### 2015-05-20 practice/T_channel/diff_param_res/all_linear/get_super_adj_discon/main.C

@@ -123,6 +123,13 @@ int main(int argc, char** argv)
 		system.variable(system.variable_number("aux_zc")));
 	sol_transfer.transfer(system_dummy.variable(system_dummy.variable_number("aux_fc")),
 		system.variable(system.variable_number("aux_fc")));
+
+std::cout << "c: " << system.calculate_norm(*system.solution, 0, L2) << std::endl;
+std::cout << "zc: " << system.calculate_norm(*system.solution, 1, L2) << std::endl;
+std::cout << "fc: " << system.calculate_norm(*system.solution, 2, L2) << std::endl;
+std::cout << "aux_c: " << system.calculate_norm(*system.solution, 3, L2) << std::endl;
+std::cout << "aux_zc: " << system.calculate_norm(*system.solution, 4, L2) << std::endl;
+std::cout << "aux_fc: " << system.calculate_norm(*system.solution, 5, L2) << std::endl;
 	
 	//save values of scalar variables; FEMSystem::point_value doesn't work for scalars...?!
 	//Point p(0.0333333, 0.0333333);

### 2015-05-20 practice/T_channel/diff_param_res/with_reaction/all_field/convdiff_inv.C

@@ -37,8 +37,8 @@ void ConvDiff_InvSys::init_data (){
 	zc_var = this->add_variable("zc", static_cast<Order>(pressure_p), fefamily); 
 	fc_var = this->add_variable("fc", static_cast<Order>(pressure_p), fefamily); 
 	
-	FEFamily meep = Utility::string_to_enum<FEFamily>(std::string("SCALAR"));
-	fpin_var = this->add_variable("fpin", static_cast<Order>(pressure_p), meep); 
+	//FEFamily meep = Utility::string_to_enum<FEFamily>(std::string("SCALAR"));
+	//fpin_var = this->add_variable("fpin", static_cast<Order>(pressure_p), meep); 
 
 	//regularization
 	if(infile.have_variable("beta")){
@@ -64,7 +64,7 @@ void ConvDiff_InvSys::init_data (){
 	this->time_evolving(c_var);
 	this->time_evolving(zc_var);
 	this->time_evolving(fc_var);
-	this->time_evolving(fpin_var);
+	//this->time_evolving(fpin_var);
 	
 	// Useful debugging options
 	// Set verify_analytic_jacobians to 1e-6 to use
@@ -151,19 +151,19 @@ bool ConvDiff_InvSys::element_time_derivative (bool request_jacobian, DiffContex
 
 	DenseSubMatrix<Number> &J_zc_c = ctxt.get_elem_jacobian(zc_var, c_var);
 	DenseSubMatrix<Number> &J_zc_fc = ctxt.get_elem_jacobian(zc_var, fc_var);
-	DenseSubMatrix<Number> &J_zc_fpin = ctxt.get_elem_jacobian(zc_var, fpin_var);
+	//DenseSubMatrix<Number> &J_zc_fpin = ctxt.get_elem_jacobian(zc_var, fpin_var);
 
 	DenseSubMatrix<Number> &J_fc_zc = ctxt.get_elem_jacobian(fc_var, zc_var);
 	DenseSubMatrix<Number> &J_fc_fc = ctxt.get_elem_jacobian(fc_var, fc_var);
-	DenseSubMatrix<Number> &J_fc_fpin = ctxt.get_elem_jacobian(fc_var, fpin_var);
+	//DenseSubMatrix<Number> &J_fc_fpin = ctxt.get_elem_jacobian(fc_var, fpin_var);
 	
[…]

### 2015-05-20 practice/T_channel/diff_param_res/with_reaction/all_field/convdiff_inv.h

@@ -110,7 +110,7 @@ public:
 
   // Indices for each variable;
   unsigned int c_var, zc_var, fc_var;
-  unsigned int fpin_var;
+  //unsigned int fpin_var;
   
   Real beta_grad, beta_mag; //regularization parameters
   Real k; //diffusion coefficient

### 2015-05-20 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/main.C

@@ -55,6 +55,8 @@ int main(int argc, char** argv){
 	mesh2.read(find_mesh_here);
 	//mesh.read("psiHF_mesh_1Dfused.xda");
 
+	bool doContinuation = infileForMesh("do_continuation",false);
+
   // And an object to refine it
   /*MeshRefinement mesh_refinement(mesh);
   mesh_refinement.coarsen_by_parents() = true;
@@ -90,14 +92,17 @@ int main(int argc, char** argv){
     AutoPtr<TimeSolver>(new SteadySolver(system_mix));
   libmesh_assert_equal_to (n_timesteps, 1);
 
-  /*equation_systems.read("psiLF.xda", READ,
-			EquationSystems::READ_HEADER |
-			EquationSystems::READ_DATA |
-			EquationSystems::READ_ADDITIONAL_DATA);
-  equation_systems.print_info();*/
-  
-  // Initialize the system
-  equation_systems.init ();
+	if(doContinuation){
+		equation_systems.read("psiLF_split.xda", READ,
+				EquationSystems::READ_HEADER |
+				EquationSystems::READ_DATA |
+				EquationSystems::READ_ADDITIONAL_DATA);
+		equation_systems.print_info();
+  }
+  else{
+		// Initialize the system
+		equation_systems.init ();
+	}
 
   // Set the time stepping options
   system_primary.deltat = deltat; system_aux.deltat = deltat;//this is ignored for SteadySolver...right?
@@ -311,6 +316,8 @@ int main(int argc, char** argv){
      		mesh.write("psiLF_mesh.xda");
      		equation_systems_mix.write("psiLF.xda", WRITE, EquationSystems::WRITE_DATA | 
                EquationSystems::WRITE_ADDITIONAL_DATA);
+        equation_systems.write("psiLF_split.xda", WRITE, EquationSystems::WRITE_DATA | 
+		     	EquationSystems::WRITE_ADDITIONAL_DATA);
       }
 #endif // #ifdef LIBMESH_HAVE_EXODUS_API
   }

### 2015-05-20 practice/T_channel/make_pretties.m

@@ -1,10 +1,10 @@
 %to make pretty plots from error breakdown file
 close all;
 
-refLevel = 'MF03';
+refLevel = 'MF02';
 dir_root = ['',...
-  'with_reaction/long_channel_stash/'...
-  '3by3_suite_fine/qoi3_sens3/',refLevel,'/'];
+  'diff_param_res/with_reaction/long_channel_stash/'...
+  'qoi3_setup02_r4p2_deref/',refLevel,'/'];
 
 errFileID = ...
   fopen([dir_root,'error_est_breakdown.dat'],'r');
@@ -15,9 +15,9 @@ A = fscanf(errFileID,errFormatSpec,errSizeMat);
 A = A';
 
 err = figure(1); 
-scatter(A(:,2),A(:,1),100,A(:,3),'s','filled'); colorbar
+% scatter(A(:,2),A(:,1),100,A(:,3),'s','filled'); colorbar
 % scatter(A(:,1),A(:,2),100,A(:,3),'s','filled'); colorbar
-% scatter(A(:,1),A(:,2),300,A(:,3),'s','filled'); colorbar
+scatter(A(:,1),A(:,2),300,A(:,3),'s','filled'); colorbar
 % hold on
 % patch([0.625 1.5 1.5 0.625],...
 %   [0.25 0.25 0.75 0.75],'w',...
@@ -27,33 +27,35 @@ scatter(A(:,2),A(:,1),100,A(:,3),'s','filled'); colorbar
 %   'MarkerEdgeColor','w',...
 %   'LineWidth',3,...
 %   'MarkerFaceColor',[0 .7 .7]);
-% xlabel('x'); 
+xlabel('x'); 
 % ylabel('y'); 
+set(gca,'ytick',[])
 % set(gca,'xtick',[])
 % set(gca,'YTickMode','Manual','YTickLabelMode','Manual')
 set(gca,'ytick',[])
-ylim([0 5])
+% ylim([0 5])
 % set(gca,'xtickLabel',{' ',' ',' '})
-xlabel('y','FontSize',14)
-set(gca,'XDir','Reverse')
+% xlabel('y','FontSize',14)
+% set(gca,'XDir','Reverse')
 % set(gca,'ytickLabel',{' ',' ',' '})
 % xlabel('{ }'); 
 % ylabel('{ }'); 
-% title('Elemental Decomposition of QoI Error Estimate')
+title('Elemental Decomposition of QoI Error Estimate')
 % title('QoI Error Estimate Contribution')
[…]

### 2015-05-20 practice/T_channel/make_setup.m

@@ -30,10 +30,10 @@ subreg = patch(ptsy, ptsx,...
 %data points
 % ptsx = [0.35 1.56 3.1];
 % ptsy = [0.35 0.61 0.5];
-ptsx = [0.35 0.98 1.56 2.46 3.1];
-ptsy = [0.35 0.51 0.61 0.37 0.5];
-% % ptsx = [0.35 0.98 1.11 1.56 2.23 2.46 2.92 3.1 3.49 4.79];
-% % ptsy = [0.35 0.51 0.89 0.61 0.51 0.37 0.7 0.5 0.76 0.26];
+% ptsx = [0.35 0.98 1.56 2.46 3.1];
+% ptsy = [0.35 0.51 0.61 0.37 0.5];
+ptsx = [0.35 0.98 1.11 1.56 2.23 2.46 2.92 3.1 3.49 4.79];
+ptsy = [0.35 0.51 0.89 0.61 0.51 0.37 0.7 0.5 0.76 0.26];
 datapts = scatter(ptsy,ptsx,30, ...
   'MarkerEdgeColor',[0 .5 .5],'MarkerFaceColor',[0 .7 .7]);
 

### 2015-05-20 practice/T_channel/with_reaction/get_psi_MF_split/main.C

@@ -54,6 +54,8 @@ int main(int argc, char** argv){
 	mesh.read(find_mesh_here);
 	mesh2.read(find_mesh_here);
 	//mesh.read("psiHF_mesh_1Dfused.xda");
+	
+  bool doContinuation = infileForMesh("do_continuation",false);
 
   // And an object to refine it
   /*MeshRefinement mesh_refinement(mesh);
@@ -90,14 +92,17 @@ int main(int argc, char** argv){
     AutoPtr<TimeSolver>(new SteadySolver(system_mix));
   libmesh_assert_equal_to (n_timesteps, 1);
 
-  /*equation_systems.read("psiLF.xda", READ,
-			EquationSystems::READ_HEADER |
-			EquationSystems::READ_DATA |
-			EquationSystems::READ_ADDITIONAL_DATA);
-  equation_systems.print_info();*/
-  
-  // Initialize the system
-  equation_systems.init ();
+	if(doContinuation){
+		equation_systems.read("psiLF_split.xda", READ,
+				EquationSystems::READ_HEADER |
+				EquationSystems::READ_DATA |
+				EquationSystems::READ_ADDITIONAL_DATA);
+		equation_systems.print_info();
+  }
+  else{
+		// Initialize the system
+		equation_systems.init ();
+	}
 
   // Set the time stepping options
   system_primary.deltat = deltat; system_aux.deltat = deltat;//this is ignored for SteadySolver...right?
@@ -311,6 +316,8 @@ int main(int argc, char** argv){
      		mesh.write("psiLF_mesh.xda");
      		equation_systems_mix.write("psiLF.xda", WRITE, EquationSystems::WRITE_DATA | 
                EquationSystems::WRITE_ADDITIONAL_DATA);
+		    equation_systems.write("psiLF_split.xda", WRITE, EquationSystems::WRITE_DATA | 
+		     	EquationSystems::WRITE_ADDITIONAL_DATA);
       }
 #endif // #ifdef LIBMESH_HAVE_EXODUS_API
   }

### 2015-05-20 practice/T_channel/with_reaction/get_super_adj/get_divvy.m

@@ -33,11 +33,12 @@ divvynew = bloop + divvy;
 divvynew(divvynew == 2) = 1;
 
 figure(1)
-scatter(A(:,1),A(:,2),200,divvynew,'s','filled','MarkerEdgeColor','k')
+% scatter(A(:,1),A(:,2),200,divvynew,'s','filled','MarkerEdgeColor','k')
+scatter(A(:,1),A(:,2),50,divvynew,'s','filled')
 set(gcf,'Position',[278 395 1323 183])
 
 figure(2)
-scatter(A(:,1),A(:,2),200,A(:,3),'s','filled')
+scatter(A(:,1),A(:,2),50,A(:,3),'s','filled')
 set(gcf,'Position',[278 395 1323 183])
 
 

### 2015-05-20 practice/T_channel/with_reaction/get_super_adj/main.C

@@ -396,7 +396,7 @@ int main(int argc, char** argv)
 			}
 		}
 		output.close();
-		
+		/*
 		std::string write_beta_bits_here = infileForMesh("err_est_beta_output_file", "error_est_breakdown_beta.dat");
 		std::ofstream output2(write_beta_bits_here);
 		for(unsigned int i = 0 ; i < system.get_mesh().n_elem(); i++){
@@ -406,6 +406,7 @@ int main(int argc, char** argv)
 			}
 		}
 		output2.close();
+		*/
 	  
 	} // End if at max adaptive steps
       

### 2015-05-20 practice/T_channel/with_reaction/time_study_poke/cdr_all/main.C

@@ -79,8 +79,15 @@ int main(int argc, char** argv){
     AutoPtr<TimeSolver>(new SteadySolver(system));
   libmesh_assert_equal_to (n_timesteps, 1);
   
+  std::string linearizeHere = "invHF.xda";
+  equation_systems.read(linearizeHere, READ,
+		EquationSystems::READ_HEADER |
+		EquationSystems::READ_DATA |
+		EquationSystems::READ_ADDITIONAL_DATA);
+	std::cout << "\n READING IN INITIAL GUESS" << std::endl;
+  
   // Initialize the system
-  equation_systems.init ();
+  //equation_systems.init ();
 
   // Set the time stepping options
   system.deltat = deltat; //this is ignored for SteadySolver...right?
@@ -245,6 +252,9 @@ int main(int argc, char** argv){
                                          1, /* This number indicates how many time steps
                                                are being written to the file */
                                          system.time);
+                                         
+       equation_systems.write("invHF.xda", WRITE, EquationSystems::WRITE_DATA | 
+               EquationSystems::WRITE_ADDITIONAL_DATA);
 
       }
 #endif // #ifdef LIBMESH_HAVE_EXODUS_API

### 2015-05-20 practice/T_channel/with_reaction/time_study_poke/get_super_adj/get_divvy.m

@@ -1,6 +1,6 @@
 %easier way to do refinement...
 
-refPortion = 0.25;
+refPortion = 0.12;
 
 errFileID = ...
   fopen('error_est_breakdown.dat','r');

### 2015-05-20 practice/docs/thesis/figures/topdf.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+for FILE in `find . -name "*.eps"`; do
+	epstopdf "${FILE}"
+	pdfcrop "${FILE%.eps}.pdf" "${FILE%.eps}.pdf"
+	rm "${FILE}"
+done
+
+

### 2015-05-20 practice/mesh_gen_poke/mesh_gen_poke.C

@@ -50,12 +50,13 @@ int main (int argc, char** argv){
 	
 	//nice geometry (straight channel) 
 	MeshTools::Generation::build_square (mesh, 
-																					75, 15,
+																					250, 50,
                                          -0.0, 5.0,
                                          -0.0, 1.0,
                                          QUAD9);
 
 	//read in subdomain assignments
+	
 	std::vector<double> prev_assign(mesh.n_elem(), 0.);
 	std::string read_assign = "do_divvy.txt";
 	if(FILE *fp=fopen(read_assign.c_str(),"r")){
@@ -71,6 +72,7 @@ int main (int argc, char** argv){
 		}
 		fclose(fp);
 	}
+	
 
 	//to stash subdomain assignments
 	std::string stash_assign = "divvy.txt";

### 2015-09-05 practice/docs/thesis/nomenclature.tex
hopefully this is enough to compile final thesis draft?

\clearpage
\section*{\huge{Nomenclature}}

\begin{longtable}{ p{.15\textwidth}  p{.85\textwidth} }
$a$							& 	Two-form in model weak form\\
$\mathcal{C}$		&		Observation operator \\
$d$							&		Observations \\
$e$							&		Error in stationary point of augmented Lagrangian \\
$f$							&		Forcing function \\
$HF$						&		High-fidelity \\
$I$							&		QoI functional \\
$J$							&		Objective function of optimization formulation of inverse problem \\
$k_d$						&		Diffusion coefficient \\
$k_r$						&		Reaction coefficient \\
$\ell$					&		Functional in model weak form \\
$\mathcal{L}$		&		Lagrangian \\
$LF$						&		Low-fidelity \\
$\mathcal{M}$		&		Augmented Lagrangian \\
$MF$						&		Mixed-fidelity \\
$n_d$						&		Number of observations \\
$p$							&		Auxiliary variable corresponding to parameters \\
$q$   					&   Unknown parameters \\
$Q$							&		Hilbert space \\
$\mathcal{Q}$		&		Output functional \\
$R$							&		Regularization term \\
$\mathcal{R}$		&		Higher-order remainder terms \\
$\mathscr{R}$		&		Residual form for QoI error adjoint \\
$u$   					&   State variables \\
$U$							&		Hilbert space \\
$v$							&		Auxiliary variable corresponding to state \\
$\vec{V}$				&		Velocity field \\
$x_1,\:x_2$			&		Spatial coordinates \\
$y$							&	 	Auxiliary variable corresponding to adjoint \\
$z$	  					&	  Adjoint variables \\
$\beta$					&		Regularization coefficient \\
$\Lambda$				&		Supplementary adjoint \\
$\xi$						&		Primary variables \\
$\phi$					&		Test function \\
$\Phi$					&		Test function \\
$\chi$					&		Auxiliary variables \\
$\Psi$					&		Stationary point of augmented Lagrangian \\
$\Omega$				&		Domain \\
$\Omega_{HF}$		&		Subdomain over which high-fidelity model is solved \\
$\Omega_I$			&		Region in domain over which QoI is calculated \\
$\Omega_{LF}$		&		Subdomain over which low-fidelity model is solved \\
 & \\
$a'_u(u_0)(\delta u)$	& Fr\'{e}chet derivative of form $a$ with respect to $u$, at $u_0$, in the direction $\delta u$
\end{longtable}

### 2015-09-08 paper/intro.tex
Added paper introduction

\section{Introduction}

Parameter estimation/inference is an important component of mathematical modeling. The ability to infer parameters via an inverse problem allows practitioners to gain important information about systems, processes and the models that are used to describe them. Such inference also avoids intrusive experiments, which may otherwise be prohibitively expensive or excessively intrusive. Once parameters have been inferred via an inverse problem, they can be used for forward propogation of the model and computing relevant goals and quantities of interest for the modeling/decision making process.

Data, constraints and prior information form the critical components of an inverse problem formulation. There is an extensive literature pertaining to all these components, pertaining to the ascription/filtering of noise in data, the choice of regularization/prior information, the efficient incorporation of constraints in solving the problem and so on. Specifically, the work on the constraints or 'state equations' in the inverse problem focuses on methods to reduce the computational expense of solving/inverting the models that represent them. Such work includes the use of reduced order models to represent constraints, adaptive mesh refinement to control the size of the state equations among other strategies.

Models that represent phenomena and processes can usually be organized in a hierarchy according to their fidelity and expense. The use of multiple models simultaneously for forward simulation is well established. In this work, we extend the use of the multi-fidelity models to inverse problems. We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest.

The rest of the paper is organized as follows, Section~\ref{} presents the mathematical formulation and error analysis for the multi-model inverse problem. Then, in Section~\ref{} we discuss the goal oriented inference algorithm and its application to a model problem and a contaminant flow problem. Finally, we present conclusions and direction for future work in Section~\ref{}.

### 2015-11-16 practice/post_thesis/monty_simple_pde_fwd/description.tex
a bit of documentation...

\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsfonts}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{cite}
\usepackage{wrapfig}
\usepackage[footnotesize,center,bf]{caption}
\usepackage{bbm}
\graphicspath{{./figures/}}

%\pagestyle{fancy}
%\rhead{}
%\chead{}
%\lhead{}
%\lfoot{}
\cfoot{\thepage}
%\rfoot{}

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

\newcommand{\dA}{{\:\textrm{d}A}}
\newcommand{\dV}{{\:\textrm{d}V}}
\newcommand{\dt}{{\:\textrm{d}t}}

\begin{document}

This is where the problem we're trying to solve will be written out, so that we're on the same page as to what we're trying to implement and to perhaps help with debugging (either code or derivations...). We take the low-fidelity (LF) model to be one of Monty's analytical model, and the high-fidelity model to be a transport PDE. We assume the source to be zero everywhere outside a box region. For the low-fidelity model, the strength of the source is assumed constant throughtout the box; for the high-fidelity model, the source is described by a field within the box.

\section{Monty's Simple Setup}

We have a domain $\Omega=[497150.00, 501750.00]\times[537350.00, 540650.00]\times[0,100]$ (in meters). Let the x-axis be aligned with the East-West direction (increasing x corresponds to going east), and the y-axis be aligned with the North-South direction (increasing y corresponds to going north). At the west boundary there is a constant head of $h_w=1798.61$ m, and at the east boundary there is a constant head of $h_e=1772.05$ m. There is no flow through the north and south boundaries. There is a uniform hydraulic conductivity of $k=0.003$ m/s throughout the domain. The velocity is thus $\vec{v}=<v_x,0,0>$ throughout the domain. Using Darcy's law and ignoring the effects of gravity, and letting $l_{ew}$ be the distance between the east and west boundaries, we get
\[
v_x=-k\frac{h_e-h_w}{l_{ew}}=2.415\cdot10^{-5}\textrm{ m/s}.
\]

The transport equation governing the concentration state $c$ is
\[
\frac{\partial c}{\partial t}=\nabla\cdot(\vec{v}c-nD\nabla c)+\lambda n c - f
\]
There is a uniform porosity of $n=0.1$ throughout the domain. No reaction rate was provided in Monty's description although a first-order reaction is included in some of the analytical models \cite{}; for now we keep the reaction term but set $\lambda=0.0$ 1/s. The longitudinal dispersivity $\alpha_L=60.0$ m, the transverse horizontal dispersivity $\alpha_{TH}=6.0$ m, and the transverse vertical dispersivity $\alpha_{VH}=0.6$ m. The total disperion tensor $D=D^m+D^{disp}$ is the sum of the molecular diffusion tensor $D^m$ and the dispersion tensor $D_{disp}$. In very slow flows, or when the porous medium is dominated by ``dead end pores'', the effects of molecular diffusion become significant. As no diffusion parameters were provided, we assume that we are not in one of these regimes. We use the expression for the dispersion tensor $D^{disp}$ described in \cite{}:
\[
D^{disp}_{ij}=a_{ijmn}\frac{v_n v_m}{\|\vec{v}\|}
\]
where $a_{ijmn}$ is the dispersivity of the porous medium, $v_n$ and $v_m$ are velocity components, and $\|\vec{v}\|$ is the magnitude of the velocity vector. For our velocity, we have $D_{xx}=\alpha_{LH}v_x$, $D_{yy}=\alpha_{TH}v_x$, and $D_{zz}=\alpha_{TV}v_x$.

There is an influx $(\vec{v}c-nD\nabla c)\cdot\hat{n}=5\textrm{ ppb}$ at the west boundary. There is no flux through the north and south boundaries, and no flux through the top or bottom. The east boundary $\Gamma_e$ has a ``mass flow out'' boundary condition. There does not appear to be a consensus as to how to model a lack of a boundary in a transport equation; the simplest approach is the Danckwerts boundary condition $\frac{\partial c}{\partial n}=0$.

Given these boundary conditions and the alignment of the velocity, axes and boundaries, the weak form of the governing equation with test function $w$ is
\begin{multline*}
\int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}-5 \dA,
\end{multline*}
where $\Gamma_w$ is the west boundary.

\section{KKT System}

Let $\Omega_f=[498716,498316]\times[538742,539522]\times[100-z,100]$ (m) denote the subregion over which the source term may be nonzero, and let $\Gamma_f$ denote its boundary.

The Lagrangian is
\begin{eqnarray*}
\mathcal{L}(f,c,z) &=& \frac{\beta}{2}\int_{\Omega_f}\nabla f\cdot\nabla f\dV \\
&& -\int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial c}{\partial t}-\nabla\cdot(\vec{v}c)+n\nabla\cdot (D\nabla c)-\lambda n c + f\right)\dV\dt \\
&& +\frac{1}{2}\int_{t_0}^{t_f}\int_\Omega \mathbbm{1}_{obs}(c-c^\star)^2 \dV\dt
\end{eqnarray*}
where $z$ is the adjoint, $\beta$ is a regularization scaling constant, $c^\star$ is the truth state (or observations), and $\mathbbm{1}_{obs}$ is an indicator function such that $\mathbbm{1}_{obs}(\vec{x},t)=1$ if $(\vec{x},t)$ correspond to an observation point and time, and is zero otherwise.

Taking variations with respect to the parameters gives
\begin{eqnarray*}
\frac{\delta\mathcal{L}}{\delta f} &=& \lim_{\epsilon\to0}\frac{1}{\epsilon}(\mathcal{L}(f+\epsilon\delta,c,z)-\mathcal{L}(f,c,z)) \\
&=& \frac{\beta}{2}\int_{\Omega_f} 2\nabla\delta\cdot\nabla f \dV - \int_{t_0}^{t_f}\int_\Omega z\delta \dV\dt \\
&=& \int_{\Omega_f}-\beta\delta\nabla^2 f \dV + \int_{\Gamma_f}\beta\delta\frac{\partial f}{\partial n} \dA-\int_{t_0}^{t_f}\int_\Omega z\delta \dV\dt
\end{eqnarray*}
Setting $\frac{\delta\mathcal{L}}{\delta f}=0$ for all perturbations $\delta$ gives
\[
z+\frac{\beta}{t_f-t_0}\nabla^2f=0\textrm{ in }\Omega_f,\quad\frac{\partial f}{\partial n}=0\textrm{ on }\Gamma_f.
\]

Taking variations with respect to the state gives
\begin{eqnarray*}
\frac{\delta\mathcal{L}}{\delta c} &=& \lim_{\epsilon\to0}\frac{1}{\epsilon}(\mathcal{L}(f,c+\epsilon\delta,z)-\mathcal{L}(f,c,z)) \\
&=& \frac{1}{2}\int_{t_0}^{t_f}\int_\Omega\mathbbm{1}_{obs}(2\delta (c-c^\star)) \dV\dt - \int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial \delta}{\partial t}-\nabla\cdot(\vec{v}\delta)+n\nabla\cdot (D\nabla \delta)-\lambda n \delta + f\right)\dV\dt
\end{eqnarray*}
Using
\[
\int_{t_0}^{t_f}\int_\Omega z\frac{\partial\delta}{\partial t} \dV\dt=\left.\left(\int_\Omega z\delta \dV\right)\right\vert^{t_f}_{t_0}-\int_{t_0}^{t_f}\int_\Omega \delta\frac{\partial z}{\partial n}\dV\dt
\]
\[
\int_{t_0}^{t_f}\int_\Omega z(\nabla\cdot(\vec{v}\delta)) \dV\dt = \int_{t_0}^{t_f}\left(\int_\Gamma z\delta(\vec{v}\cdot\hat{n}) \dA -\int_\Omega \delta (\vec{v}\cdot\nabla z) \dV\right)\dt
\]
\[
\int_{t_0}^{t_f}\int_\Omega zn\nabla\cdot(D\nabla\delta) \dV\dt = \int_{t_0}^{t_f}\left(\int_\Gamma zn(D\nabla\delta)\cdot\hat{n}-n\delta(D\nabla z)\cdot\hat{n}\dA + \int_\Omega n\delta\nabla\cdot(D\nabla z) \dV\right)\dt
\]
\[
\left.\delta\right\vert_{t_0}=0,\quad (\vec{v}\delta-nD\nabla\delta)\cdot\hat{n}\textrm{ on }\Gamma\backslash\Gamma_e,\quad\nabla\delta\cdot\hat{n}\textrm{ on }\Gamma_e
\]
gives
\begin{multline*}
\frac{\delta\mathcal{L}}{\delta c} = \int_{t_0}^{t_f}\left(\int_\Omega \delta\mathbbm{1}_{obs}(c-c^\star)+\delta\frac{\partial z}{\partial t} - \delta\vec{v}\cdot\nabla z - \delta n \nabla\cdot(D\nabla z) + \delta\lambda nz \dV \right. \\
 \quad \left. + \int_\Gamma \delta n(D\nabla z)\cdot\hat{n} \dA - \int_{\Gamma_e} \delta z\vec{v}\cdot\hat{n} \dA\right)\dt -\left.z\delta\right\vert_{t_f}
\end{multline*}
Setting $\frac{\delta\mathcal{L}}{\delta c}=0$ for all perturbations $\delta$ gives
\begin{eqnarray*}
& -\frac{\partial z}{\partial t} = -\vec{v}\cdot\nabla z - n\nabla\cdot(D\nabla z) + \lambda nz + \mathbbm{1}_{obs}(c-c^\star)\textrm{ in }\Omega,\\
& \quad \left.z\right\vert_{t_f}=0,
\quad n(D\nabla z)\cdot\hat{n}=0\textrm{ on }\Gamma\backslash\Gamma_e,
\quad (\vec{v}z-n(D\nabla z))\cdot\hat{n} = 0\textrm{ on }\Gamma_e
\end{eqnarray*}

Taking variations with respect to the adjoint recovers the governing equation.

\section{Solving for Auxiliary Variables}

Since the objective function is quadratic in the state and parameters, and the governing equation is linear, the auxiliary variables are related to each other in the same way as the primary variables, with the exception of the forcing term, which depends on the QoI.

\section{Solving for LF versions}

In the analytical model, $f$ is a scalar. Let $d$ be the observations and $O_e$ be a matrix so that $d=O_e f^\star$, where $f^\star$ is the true parameter value. The chosen regularization results in no penalty for a constant $f$. The inferred parameter is $f=(O_e^TO_e)^{-1}O_e^Td$.

Let $A(\vec{x},t)$ be a linear operator whose action depends on the location $\vec{x}$ and time $t$, and which corresponds to the analytical model so that we have $c=Af$. The Lagrangian is then
\[
\mathcal{L}(f,c,z) = -\int_{t_0}^{t_f}\int_\Omega z(c-Af) \dV\dt + \frac{1}{2}\int_{t_0}^{t_f}\int_\Omega \mathbbm{1}_{obs}(c-c^\star)^2 \dV\dt
\]
Taking variations with respect to the state and setting it to zero for all perturbations gives
\[
z=\mathbbm{1}_{obs}(c-c^\star)
\]

\end{document}

### 2015-11-27 practice/post_thesis/monty_simple_pde_fwd/description.tex
add scaling to influx and source terms so that they have correct/more reasonable units

@@
 
-There is an influx $(\vec{v}c-nD\nabla c)\cdot\hat{n}=5\textrm{ ppb}$ at the west boundary.
+There is an influx $(\vec{v}c-nD\nabla c)\cdot\hat{n}=(5\textrm{ ppb})\vec{v}\cdot\hat{n}$ at the west boundary.
 There is no flux through the north and south boundaries, and no flux through the top or bottom.
@@
 = \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
-= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}-5 \dA,
+= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
 \end{multline*}

### 2015-11-27 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.C

@@ -38,15 +38,24 @@ void ContamTransSys::init_data(){
 	//set Dirichlet boundary conditions (none in this case)
 
 	//set parameters
-	vx = infile("vx",2.415e-5);
-	react_rate = infile("reaction_rate",0.0);
-	porosity = infile("porosity",0.1);
-	bsource = infile("bsource", 5.0);
+	vx = infile("vx", 2.415e-5); // m/s
+	react_rate = infile("reaction_rate", 0.0); // 1/s
+	porosity = infile("porosity", 0.1); // (unitless)
+	bsource = infile("bsource", -5.0); // ppb
+	source_rate = infile("source_rate", 5.0); // kg/s
+	source_conc = infile("source_conc", 1000.0); // ppb
+	source_dz = infile("source_thickness", 1.0); // m
+	
+	xlim.push_back(498316.0); xlim.push_back(498716.0); // m
+  ylim.push_back(538742.0); ylim.push_back(539522.0); // m
+	source_vol = (xlim[1] - xlim[0])*(ylim[1] - ylim[0])*source_dz;
+	water_density = 1.0; // kg/m^3
+	source_zmax = 100.0; // m
+
+	//compute dispersion tensor (assuming for now that velocity purely in x direction)
 	double dlong = infile("dispersivity_longitudinal",60.0);
 	double dtransh = infile("dispersivity_transverse_horizontal",6.0);
 	double dtransv = infile("dispersivity_transverse_vertical",0.6);
-
-	//compute dispersion tensor (assuming for now that velocity purely in x direction)
 	dispTens = NumberTensorValue(vx*dlong, 0.0, 0.0,
 	                            0.0, vx*dtransh, 0.0,
 	                            0.0, 0.0, vx*dtransv);
@@ -197,8 +206,7 @@ bool ContamTransSys::side_time_derivative(bool request_jacobian, DiffContext & c
     {
       if(isWest) //west boundary
       {
-        R(i) += JxW[qp]*(U*face_normals[qp]*c - bsource)*phi[i][qp];
-        //std::cout << qside_point[qp](0) << " " << qside_point[qp](1) << " " << qside_point[qp](2) << std::endl; //DEBUG
+        R(i) += JxW[qp]*(U*face_normals[qp]*c - bsource*vx)*phi[i][qp];
       }
 
[…]

### 2015-11-27 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.h

@@ -38,9 +38,17 @@ public:
   // depends on which application is being used.
   Point forcing(const Point& p);
 
-  double vx; //west-east velocity (along x-axis, for now)
-  double react_rate; //reaction rate
-  double porosity; //porosity
-  Real bsource; // ppb (influx on west boundary)
-  NumberTensorValue dispTens; //dispersion tensor
+  Real vx; //west-east velocity (along x-axis, for now); m/s
+  Real react_rate; //reaction rate; 1/s
+  Real porosity; //porosity
+  Real bsource; // ppb (concentration of influx at west boundary)
+  Real source_rate; // kg/s
+	Real source_conc; // ppb
+	Real water_density; // kg/m^3
+  NumberTensorValue dispTens; //dispersion tensor; m^2/s
+  std::vector<Real> xlim; //boundaries of interior source; m
+  std::vector<Real> ylim; //boundaries of interior source; m
+  Real source_zmax; //top of domain; m
+  Real source_dz; //interior source thickness; m
+  Real source_vol; //interior source volume; m^3
 };

### 2015-11-27 practice/post_thesis/monty_simple_pde_fwd/main.C

@@ -68,10 +68,10 @@ int main(int argc, char** argv){
   	
   //solve as steady or transient
   if(transient)
-    system.time_solver = AutoPtr<TimeSolver>(new EulerSolver(system));
+    system.time_solver = AutoPtr<TimeSolver>(new EulerSolver(system)); //backward Euler
   else{
     system.time_solver = AutoPtr<TimeSolver>(new SteadySolver(system));
-    libmesh_assert_equal_to (n_timesteps, 1);
+    libmesh_assert_equal_to (n_timesteps, 1); //this doesn't seem to work?
   }
   
   // Initialize the system
@@ -109,6 +109,8 @@ int main(int argc, char** argv){
   // Print information about the system to the screen.
   equation_systems.print_info();
   
+  ExodusII_IO exodusIO = ExodusII_IO(mesh); //DEBUG
+  
   for (unsigned int t_step=0; t_step != n_timesteps; ++t_step){
   
     std::cout << "\n\nSolving time step " << t_step << ", time = "
@@ -127,12 +129,12 @@ int main(int argc, char** argv){
       std::ostringstream tplot_file_name;
 
       // We write the file in the ExodusII format.
-      ex_file_name << "out_"
-                  << std::setw(3)
-                  << std::setfill('0')
-                  << std::right
-                  << t_step+1
-                  << ".e";
+      //ex_file_name << "out_"
+      //            << std::setw(3)
+      //            << std::setfill('0')
+      //            << std::right
+      //            << t_step+1
+      //            << ".e";
                   
       tplot_file_name << "out_"
                   << std::setw(3)
@@ -141,12 +143,12 @@ int main(int argc, char** argv){
                   << t_step+1
                   << ".plt";
 
-      ExodusII_IO(mesh).write_timestep(ex_file_name.str(),
-                                       equation_systems,
-                                       1, /* This number indicates how many time steps
-                                             are being written to the file */
-                                       system.time);
-      
+      //ExodusII_IO(mesh).write_timestep(ex_file_name.str(),
+      //                                 equation_systems,
+      //                                 1, /* This number indicates how many time steps
+      //                                       are being written to the file */
+      //                                 system.time);
+      exodusIO.write_timestep("output.exo", equation_systems, t_step+1, system.time); //DEBUG
       TecplotIO(mesh).write_equation_systems(tplot_file_name.str(), equation_systems);
     }
 #endif // #ifdef LIBMESH_HAVE_EXODUS_API     

### 2016-01-18 paper/intro.tex
adding draft outline

@@
 Finally, we present conclusions and direction for future work in Section~\ref{}.
+
+\subsection{draft outline}
+\bit 
+\item background/previous work? to put this work in context?
+\item mathematical formulation
+  \bit
+  \item define inverse problem and qoi
+  \item derive error estimate
+  \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
+  \item relation to mesh refinement
+  \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem?
+(Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
+  \eit
+\item numerical results (perhaps not include all of these...)
+  \bit
+  \item convection-diffusion(-reaction)
+    \bit
+    \item interpretation of error estimate breakdown (interaction of QoI with observations)
+    \item large reaction term: MF model more cooperative with nonlinear solver
+    \eit
+  \item convection-diffusion-reaction, field vs scalar description of parameters
+    \bit
+    \item interface question: do we enforce continuity between the two models' parameters?
+    \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
+    \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
+    \eit
+  \item alternate/additional example: use setup from B+V? navier-stokes and another model? 
+    \bit
+    \item potential flow?
+model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
+    \item there would still be the question of how to interface the models...
+    \eit
+  \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
+  \eit
+\item conclusion...what goes in this section usually? summary and directions for future work?
+\eit

### 2016-01-29 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.C
added some notes on attempts to get rid of ridges; added option to use SUPG (which seems not to get rid of oscillations, even though oscillations seem related to Peclet number...)

@@ -23,6 +23,7 @@ void ContamTransSys::init_data(){
   GetPot infile("contamTrans.in");
   unsigned int poly_order = infile("poly_order",1);
   std::string fefamily = infile("fe_family", std::string("LAGRANGE"));
+  useSUPG = infile("use_SUPG",false);
 
   c_var = this->add_variable("c", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
 
@@ -59,6 +60,15 @@ void ContamTransSys::init_data(){
 	dispTens = NumberTensorValue(vx*dlong, 0.0, 0.0,
 	                            0.0, vx*dtransh, 0.0,
 	                            0.0, 0.0, vx*dtransv);
+
+  //DEBUG
+  //std::set<boundary_id_type> west_bdy;
+  ////west_bdy.insert(4);
+  //west_bdy.insert(0); west_bdy.insert(1); west_bdy.insert(2); west_bdy.insert(3); west_bdy.insert(4); west_bdy.insert(5);
+  //std::vector<unsigned int> all_vars;
+	//all_vars.push_back(c_var);
+	//ConstFunction<Number> five(5.0);
+	//this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(west_bdy, all_vars, &five));
 
 	// Do the parent's initialization after variables and boundary constraints are defined
 	FEMSystem::init_data();
@@ -129,21 +139,36 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
 
     //velocity vector
     NumberVectorValue U(vx, 0.0, 0.0);
+    
+    //SUPG
+    double tau = 0.0;
+    if(useSUPG){ //assuming isotropic dispersion for now
+      double C1 = 4.0;
+      double C2 = 2.0;
+      double k = dispTens(0,0);
+      if(dispTens(0,0) != dispTens(1,1) || dispTens(1,1) != dispTens(2,2))
+        std::cout << "SUPG currently assumed isotropic dispersion..." << std::endl;
+      Real h = ctxt.get_elem().hmax();
+      std::cout << k << " " << sqrt(U*U) << std::endl;
+      tau = 1./((C1*k)/(h*h) + (C2*sqrt(U*U)/h));
+    }
 
[…]

### 2016-01-29 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.h

@@ -51,4 +51,6 @@ public:
   Real source_zmax; //top of domain; m
   Real source_dz; //interior source thickness; m
   Real source_vol; //interior source volume; m^3
+  
+  bool useSUPG; //whether to use SUPG...
 };

### 2016-03-11 practice/post_thesis/monty_simple_pde_fwd/description.tex
added fourth stabilization option

@@
 \[
-\frac{\partial c}{\partial t}=\nabla\cdot(\vec{v}c-nD\nabla c)+\lambda n c - f
+\frac{\partial (nc)}{\partial t}=\nabla\cdot(\vec{v}c-nD\nabla c)+\lambda n c - f
 \]
@@
 \begin{multline*}
-\int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
-= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
-= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
+\int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
+= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
+= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
 \end{multline*}
@@
 \mathcal{L}(f,c,z) &=& \frac{\beta}{2}\int_{\Omega_f}\nabla f\cdot\nabla f\dV \\
-&& -\int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial c}{\partial t}-\nabla\cdot(\vec{v}c)+n\nabla\cdot (D\nabla c)-\lambda n c + f\right)\dV\dt \\
+&& -\int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial (nc)}{\partial t}-\nabla\cdot(\vec{v}c)+n\nabla\cdot (D\nabla c)-\lambda n c + f\right)\dV\dt \\
 && +\frac{1}{2}\int_{t_0}^{t_f}\int_\Omega \mathbbm{1}_{obs}(c-c^\star)^2 \dV\dt
@@
 \frac{\delta\mathcal{L}}{\delta c} &=& \lim_{\epsilon\to0}\frac{1}{\epsilon}(\mathcal{L}(f,c+\epsilon\delta,z)-\mathcal{L}(f,c,z)) \\
-&=& \frac{1}{2}\int_{t_0}^{t_f}\int_\Omega\mathbbm{1}_{obs}(2\delta (c-c^\star)) \dV\dt - \int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial \delta}{\partial t}-\nabla\cdot(\vec{v}\delta)+n\nabla\cdot (D\nabla \delta)-\lambda n \delta + f\right)\dV\dt
+&=& \frac{1}{2}\int_{t_0}^{t_f}\int_\Omega\mathbbm{1}_{obs}(2\delta (c-c^\star)) \dV\dt - \int_{t_0}^{t_f}\int_\Omega z\left(\frac{\partial (n\delta)}{\partial t}-\nabla\cdot(\vec{v}\delta)+n\nabla\cdot (D\nabla \delta)-\lambda n \delta + f\right)\dV\dt
 \end{eqnarray*}
@@
 \begin{multline*}
-\frac{\delta\mathcal{L}}{\delta c} = \int_{t_0}^{t_f}\left(\int_\Omega \delta\mathbbm{1}_{obs}(c-c^\star)+\delta\frac{\partial z}{\partial t} - \delta\vec{v}\cdot\nabla z - \delta n \nabla\cdot(D\nabla z) + \delta\lambda nz \dV \right.
+\frac{\delta\mathcal{L}}{\delta c} = \int_{t_0}^{t_f}\left(\int_\Omega \delta\mathbbm{1}_{obs}(c-c^\star)+n\delta\frac{\partial z}{\partial t} - \delta\vec{v}\cdot\nabla z - \delta n \nabla\cdot(D\nabla z) + \delta\lambda nz \dV \right.
 \\
@@
 \begin{eqnarray*}
-& -\frac{\partial z}{\partial t} = -\vec{v}\cdot\nabla z - n\nabla\cdot(D\nabla z) + \lambda nz + \mathbbm{1}_{obs}(c-c^\star)\textrm{ in }\Omega,\\
+& -\frac{\partial (nz)}{\partial t} = -\vec{v}\cdot\nabla z - n\nabla\cdot(D\nabla z) + \lambda nz + \mathbbm{1}_{obs}(c-c^\star)\textrm{ in }\Omega,\\
 & \quad \left.z\right\vert_{t_f}=0,

### 2016-03-11 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.C

@@ -158,29 +158,37 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
         //version 1, copied from MILO code
         double C1 = 4.0;
         double C2 = 2.0;
-        double k = dispTens(0,0)*porosity;
+        double k = dispTens(0,0);
         if(dispTens(0,0) != dispTens(1,1) || dispTens(1,1) != dispTens(2,2))
           std::cout << "SUPG currently assumed isotropic dispersion..." << std::endl;
         Real h = ctxt.get_elem().hmax();
-        tau = 1./((C1*k)/(h*h) + (C2*sqrt(U*U)/h));
+        tau = 1./((C1*k)/(h*h) + (C2*(sqrt(U*U)/porosity)/h));
       }else if(stab_opt == 2){
         //version 2, from http://ta.twi.tudelft.nl/TWA_Reports/06/06-03.pdf
-        double k = dispTens(0,0)*porosity;
+        double k = dispTens(0,0);
         if(dispTens(0,0) != dispTens(1,1) || dispTens(1,1) != dispTens(2,2))
           std::cout << "SUPG currently assumed isotropic dispersion..." << std::endl;
         Real h = ctxt.get_elem().hmax();
-        Real Pe = sqrt(U*U)*h/(2.*k); //element Peclet number
-        tau = (h/(2.*sqrt(U*U)))*(1./tanh(Pe) + 1./Pe);
+        Real Pe = (sqrt(U*U)/porosity)*h/(2.*k); //element Peclet number
+        tau = (h/(2.*(sqrt(U*U)/porosity)))*(1./tanh(Pe) + 1./Pe);
       }else if(stab_opt == 3){
         //version 3, from Becker + Braack (2002), assuming linear basis functions for now
         double C = 12.0; //assuming linear basis functions
         double delta0 = 0.4; //suggested 0.2 <= delta_0 <= 0.5 for linear basis functions
         Real hK = ctxt.get_elem().hmax();
-        Real betaK = std::max(std::max(std::abs(U(0)),std::abs(U(1))),std::abs(U(2)));
-        double k = dispTens(0,0)*porosity;
+        Real betaK = std::max(std::max(std::abs(U(0)),std::abs(U(1))),std::abs(U(2)))/porosity;
+        double k = dispTens(0,0);
[…]

### 2016-03-23 practice/post_thesis/monty_simple_pde_fwd/description.tex
added source-as-influx option; stash to run on workstation

@@
 = \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
-= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
+= \int_\Omega w\frac{\partial (nc)}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} w(c\vec{v}\cdot\hat{n}+5) \dA,
 \end{multline*}

### 2016-03-23 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.C

@@ -49,9 +49,9 @@ void ContamTransSys::init_data(){
 	
 	xlim.push_back(498316.0); xlim.push_back(498716.0); // m
   ylim.push_back(538742.0); ylim.push_back(539522.0); // m
-  if(this->get_mesh().mesh_dimension() == 3)
+  if(this->get_mesh().mesh_dimension() == 3 && source_dz > 0.0)
 	  source_vol = (xlim[1] - xlim[0])*(ylim[1] - ylim[0])*source_dz;
-	else if(this->get_mesh().mesh_dimension() == 2)
+	else if(this->get_mesh().mesh_dimension() == 2 || source_dz == 0.0)
 	  source_vol = (xlim[1] - xlim[0])*(ylim[1] - ylim[0]);
 	water_density = 1.0; // kg/m^3
 	source_zmax = 100.0; // m
@@ -264,10 +264,13 @@ bool ContamTransSys::side_time_derivative(bool request_jacobian, DiffContext & c
   unsigned int n_qpoints = ctxt.get_side_qrule().n_points();
 
   bool isWest = false;
-  if (dim == 3)
+  bool isUp = false;
+  if (dim == 3){
     isWest = ctxt.has_side_boundary_id(4);
-  else if (dim == 2)
+    isUp = ctxt.has_side_boundary_id(5);
+  }else if (dim == 2){
     isWest = ctxt.has_side_boundary_id(3);
+  }
 
   //set (in)flux boundary condition on west side
   //homogeneous neumann (Danckwerts) outflow boundary condition on east side
@@ -287,12 +290,23 @@ bool ContamTransSys::side_time_derivative(bool request_jacobian, DiffContext & c
       {
         R(i) += JxW[qp]*(U*face_normals[qp]*c - bsource*vx)*phi[i][qp];
       }
-
+      
+      if(isUp 
+        && qside_point[qp](0) >= xlim[0] && qside_point[qp](0) <= xlim[1] 
+        && qside_point[qp](1) >= ylim[0] && qside_point[qp](1) <= ylim[1]) //upper boundary
+      {
+        R(i) += JxW[qp]*(U*face_normals[qp]*c + source_rate*source_conc/(source_vol*water_density)*vx)*phi[i][qp];
+      }
+      
       if(request_jacobian && context.get_elem_solution_derivative())
       {
         for (unsigned int j=0; j != n_c_dofs; j++)
 	      {
[…]

### 2016-03-25 practice/post_thesis/monty_simple_pde_fwd/contamTrans_sys.C
fixed some sign errors, made SUPG a tad more general (not assuming first order basis functions)

@@ -99,6 +99,7 @@ void ContamTransSys::init_context(DiffContext & context){
 	c_elem_fe->get_JxW();
 	c_elem_fe->get_phi();
 	c_elem_fe->get_dphi();
+	c_elem_fe->get_d2phi();
 	c_elem_fe->get_xyz();
 
 	c_side_fe->get_JxW();
@@ -122,6 +123,7 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
 
   const std::vector<std::vector<Real> >& phi = c_elem_fe->get_phi();
   const std::vector<std::vector<RealGradient> >& dphi = c_elem_fe->get_dphi();
+  const std::vector<std::vector<RealTensor> >& d2phi = c_elem_fe->get_d2phi();
 
   // Physical location of the quadrature points
   const std::vector<Point>& qpoint = c_elem_fe->get_xyz();
@@ -145,6 +147,7 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
   {
     Number c = ctxt.interior_value(c_var, qp);
     Gradient grad_c = ctxt.interior_gradient(c_var, qp);
+    NumberTensorValue hess_c = ctxt.interior_hessian(c_var, qp); //for SUPG
 
     Point f = this->forcing(qpoint[qp]);
     Number fc = f(0);
@@ -206,7 +209,8 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
 		       + fc*phi[i][qp]); // Source term
 		  if(useSUPG)
 		    R(i) += JxW[qp]*((tau*U*dphi[i][qp])*
-		           (- (U*grad_c) // Convection Term
+		           (porosity*dispTens.contract(hess_c) //Dispersion term
+		           - (U*grad_c) // Convection Term
 		           - (react_rate*(porosity*c)) // Reaction Term
 		           + fc)); // Source term
       if (request_jacobian && ctxt.get_elem_solution_derivative())
@@ -219,7 +223,8 @@ bool ContamTransSys::element_time_derivative(bool request_jacobian, DiffContext 
 			           - (react_rate*(porosity*phi[j][qp]))*phi[i][qp]); // Reaction Term
 			    if(useSUPG)
 			      J(i,j) += JxW[qp]*((tau*U*dphi[i][qp])*
-		                 (- (U*dphi[j][qp]) // Convection Term
+		                 (porosity*dispTens.contract(d2phi[j][qp]) //Dispersion term
[…]

### 2016-03-25 practice/post_thesis/monty_simple_pde_fwd/initial.h

@@ -7,10 +7,12 @@ using namespace libMesh;
 void read_initial_parameters(){}
 void finish_initialization(){}
 
-Number initial_value(const Point& p, const Parameters&, const std::string&, const std::string&){
+Number initial_value(const Point& p, const Parameters& parameters, 
+    const std::string& sys_name, const std::string& unknown_name){
   return 5.0; //ppb
 }
 
-Gradient initial_grad(const Point& p, const Parameters&, const std::string&, const std::string&){
+Gradient initial_grad(const Point& p, const Parameters& parameters, 
+    const std::string& sys_name, const std::string& unknown_name){
   return Gradient(0.0, 0.0, 0.0);
 }

### 2016-03-25 practice/post_thesis/monty_simple_pde_fwd/main.C

@@ -42,8 +42,8 @@ int main(int argc, char** argv){
   //const unsigned int dim                = 3;
   const unsigned int max_r_steps        = infile("max_r_steps", 3);
   const unsigned int max_r_level        = infile("max_r_level", 3);
-  const Real refine_percentage          = infile("refine_percentage", 0.5);
-  const Real coarsen_percentage         = infile("coarsen_percentage", 0.5);
+  const Real refine_percentage          = infile("refine_percentage", 0.1);
+  const Real coarsen_percentage         = infile("coarsen_percentage", 0.0);
   const std::string indicator_type      = infile("indicator_type", "kelly");
   const bool write_error                = infile("write_error",false);
   const bool flag_by_elem_frac          = infile("flag_by_elem_frac",true);
@@ -123,7 +123,7 @@ int main(int argc, char** argv){
   solver->initial_linear_tolerance =
     infile("initial_linear_tolerance", 1.e-3);
     
-  // Mesh Refinement object
+  // Mesh Refinement object - to test effect of constant refined mesh (not refined at every timestep)
   MeshRefinement mesh_refinement(mesh);
   mesh_refinement.refine_fraction() = refine_percentage;
   mesh_refinement.coarsen_fraction() = coarsen_percentage;

### 2016-03-25 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_HF/element_qoi.C
add pure-LF and pure-HF inverse problems; still need to be debugged, but compiles at least...

@@ -1,0 +1,50 @@
+// General libMesh includes
+#include "libmesh/libmesh_common.h"
+#include "libmesh/elem.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/point.h"
+#include "libmesh/quadrature.h"
+
+// Local includes
+#include "contamTrans_inv.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// Define the postprocess function to compute QoI 0
+
+void ContamTransSysInv::element_postprocess (DiffContext &context)
+
+{
+  FEMContext &ctxt = cast_ref<FEMContext&>(context);
+
+  FEBase* elem_fe = NULL;
+  ctxt.get_element_fe( c_var , elem_fe );
+
+  // Element Jacobian * quadrature weights for interior integration
+  const std::vector<Real> &JxW = elem_fe->get_JxW();
+
+  const std::vector<Point> &xyz = elem_fe->get_xyz();
+
+  // The number of local degrees of freedom in each variable
+  unsigned int n_qpoints = ctxt.get_element_qrule().n_points();
+
+  Number dQoI = 0.;
+  
+  const unsigned int dim = this->get_mesh().mesh_dimension();
+
+  // Loop over quadrature points
+  for (unsigned int qp = 0; qp != n_qpoints; qp++)
+    {
+      // Get the solution value at the quadrature point
+      Number c = ctxt.interior_value(c_var, qp);
+
+      // Update the elemental increment dR for each qp
+      dQoI += JxW[qp] * c;
+    }
+
+  // Update the computed value of the global functional R, by adding the contribution from this element
+  computed_QoI[0] = computed_QoI[0] + dQoI;
+
+}

### 2016-03-25 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_HF/main.C

@@ -1,0 +1,277 @@
+//foward run for simple contaminant transport model
+
+// C++ includes
+#include <iomanip>
+
+// Basic include files
+#include "libmesh/equation_systems.h"
+#include "libmesh/error_vector.h"
+#include "libmesh/exodusII_io.h"
+#include "libmesh/kelly_error_estimator.h"
+#include "libmesh/mesh.h"
+#include "libmesh/mesh_generation.h"
+#include "libmesh/mesh_refinement.h"
+#include "libmesh/patch_recovery_error_estimator.h"
+#include "libmesh/uniform_refinement_estimator.h"
+#include "libmesh/getpot.h"
+#include "libmesh/tecplot_io.h"
+
+// The systems and solvers we may use
+#include "libmesh/diff_solver.h"
+#include "libmesh/steady_solver.h"
+#include "libmesh/newton_solver.h"
+#include "libmesh/euler_solver.h"
+
+//local includes
+#include "contamTrans_inv.h"
+#include "initial.h"
+
+int main(int argc, char** argv){
+
+	//initialize libMesh
+	LibMeshInit init(argc, argv);
+	
+	//parameters
+	GetPot infile("fem_system_params.in");
+  const bool transient                  = infile("transient", true);
+  const Real deltat                     = infile("deltat", 0.005);
+  unsigned int n_timesteps              = infile("n_timesteps", 20);
+  const int nx                          = infile("nx",100);
+  const int ny                          = infile("ny",100);
+  const int nz                          = infile("nz",100);
+  //const unsigned int dim                = 3;
+  const unsigned int max_r_steps        = infile("max_r_steps", 3);
+  const unsigned int max_r_level        = infile("max_r_level", 3);
+  const Real refine_percentage          = infile("refine_percentage", 0.1);
+  const Real coarsen_percentage         = infile("coarsen_percentage", 0.0);
+  const std::string indicator_type      = infile("indicator_type", "kelly");
+  const bool write_error                = infile("write_error",false);
+  const bool flag_by_elem_frac          = infile("flag_by_elem_frac",true);
+      
+#ifdef LIBMESH_HAVE_EXODUS_API
+  const unsigned int write_interval    = infile("write_interval", 5);
+#endif
+
+  // Create a mesh, with dimension to be overridden later, distributed
+  // across the default MPI communicator.
+  Mesh mesh(init.comm());
+  
+  //create mesh
[…]

### 2016-03-25 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_LF/contamTrans_inv.C

@@ -1,0 +1,401 @@
+#include "libmesh/getpot.h"
+
+#include "contamTrans_inv.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/elem.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+//system initialization
+void ContamTransSysInv::init_data(){
+  const unsigned int dim = this->get_mesh().mesh_dimension();
+
+  GetPot infile("contamTrans.in");
+  
+  //regularization
+	beta = infile("beta", 0.1);
+	
+  unsigned int poly_order = infile("poly_order",1);
+  std::string fefamily = infile("fe_family", std::string("LAGRANGE"));
+  c_var = this->add_variable("c", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
+  f_var = this->add_variable("f", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
+  z_var = this->add_variable("z", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
+
+  //indicate variables that change in time
+  this->time_evolving(c_var);
+  this->time_evolving(f_var);
+  this->time_evolving(z_var);
+
+  // Useful debugging options'
+	// Set verify_analytic_jacobians to positive to use
+	this->verify_analytic_jacobians = infile("verify_analytic_jacobians", 0.);
+	this->print_jacobians = infile("print_jacobians", false);
+	this->print_element_jacobians = infile("print_element_jacobians", false);
+
+	//set Dirichlet boundary conditions (none in this case)
+
+	//set parameters
+	vx = infile("vx", 2.415e-5); // m/s
+	react_rate = infile("reaction_rate", 0.0); // 1/s
+	porosity = infile("porosity", 0.1); // (unitless)
+	bsource = infile("bsource", -5.0); // ppb
+
[…]

### 2016-03-25 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_LF/contamTrans_inv.h

@@ -1,0 +1,106 @@
+// DiffSystem framework files
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+
+using namespace libMesh;
+
+// FEMSystem, TimeSolver and  NewtonSolver will handle most tasks,
+// but we must specify element residuals
+class ContamTransSysInv : public FEMSystem
+{
+public:
+
+  // Constructor
+  ContamTransSysInv(EquationSystems& es, const std::string& name_in, const unsigned int number_in):
+    FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("contamTrans.in");
+		std::string find_data_here = infile("data_file","Measurements0.dat");
+		qoi_option = infile("QoI_option",1);
+		
+		const unsigned int dim = this->get_mesh().mesh_dimension();
+
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+		  if(dim == 3){
+				Real x, y, z, value;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+					if(flag != -1){
+						datapts.push_back(Point(x,y,z));
+						datavals.push_back(value);
+					}
+				}
+				fclose(fp);
+	  	}else if(dim == 2){
+				Real x, y, value;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+					if(flag != -1){
+						datapts.push_back(Point(x,y));
+						datavals.push_back(value);
+					}
+				}
+				fclose(fp);
+	  	}
+	  }
+	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+
+  // Postprocessed output
+  virtual void postprocess ();
+  
+  //to calculate QoI
+  virtual void element_postprocess(DiffContext &context);
+  
+  //return QoI
+  Number &get_QoI_value(std::string type, unsigned int QoI_index){
[…]

### 2016-05-20 paper/mathematical_formulation.tex
Small additions.

--- 2015-05-20 practice/docs/thesis/formulation_v03.tex
@@
-\chapter{Mathematical Formulation} \label{chap:form}
-
-In Section \ref{sec:setup}, we define the goal-oriented inverse problem.
-In Section \ref{sec:deriv}, we derive an a posteriori estimate for the error in the QoI, as compared to that which would have resulted from solving the inverse problem with a high-fidelity model.
-In Section \ref{sec:limits}, we discuss the limitations of the error estimate.
+\section{Mathematical Formulation}\label{sect:form}
+%
+We first introduce the high fidelity goal oriented inverse problem formally, providing definitions and variational statments.
+Then we will derive a rigorous, a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower fidelity constraints.
 
@@
 
-Consider a model for which the Galerkin formulation of the weak form is written as
+We seek to infer a parameter $q \in Q$, where $Q$ is a Hilbert space. Consider a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
 \begin{equation}
@@
 \end{equation}
-where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and $U,Q$ are Hilbert spaces.
-The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
+where the form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
 
-We define an observation operator $C:U\to\R^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$.
+We define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$.
 The unknown parameters can then be inferred by minimizing the difference between the predicted and actual observations.
@@
 In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
+%
+\begin{theorem}
+\label{thm:error_estimate}
+\begin{multline}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
+\label{eq:finErrExp}
+\end{multline}
+\end{theorem}
+%
 

### 2016-05-20 paper/intro.tex
added some notes on attempts to get rid of ridges; added option to use SUPG (which seems not to get rid of oscillations, even though oscillations seem related to Peclet number...)
Small additions.
added new figures (not yet made pretty) corresponding to new error breakdown for cd vs cdr case; added cost comparison (linear solve comparison)

@@
 We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest.
+Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.
 
@@
 \item background/previous work? to put this work in context?
+  %this is probably enough? at least for previous work...
+  %what context though? is this another way to approach inverse problems?
 \item mathematical formulation
@@
 (Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
+    %solving for adjoint and forward simultaneously (KKT) might cause you to lose an order of accuracy?
+    %where was that book that Oden might have mentioned inverse application of his method?
+      %Multiscale methods : bridging the scales in science and engineering / edited by Jacob Fish. (TA335.M85 2010 in barker)
   \eit
@@
     \item interface question: do we enforce continuity between the two models' parameters?
+      %-navierstokes+stokes seems to require continuity of flux and velocity across boundary...?
+      %-is it okay to mix diff and convdiff for the forward like we did?
+does the discontinuous velocity break any intergration-by-parts   assumptions?
+(no that's only if discontinuity in diffusion bit...)
     \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
+    %alternative way to describe 'scalar' case? but here we say there is one scalar, so this would be how to combine them...if you wanted plateaus to be different, can let LF model be two-scalars...
+    %fig 3.10 -> what does the inferred field look like? does it look like two different plateaus?
+      % practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r4p2_deref/ (pushed 10/3/15)
+        %at the very last refinement, most of refined region seems to be two large humps...and a section that looks pretty much like the surrounding scalar...so maybe 3 patches...
     \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
@@
 model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
-    \item there would still be the question of how to interface the models...
+    \item there would still be the question of how to interface the models...(in stokes vs navier-stokes foward paper, they just required continuity of state variables (velocity field and presssure))
+    %do scalar + field for infer BCs on BV NS thing? try for different QoIs? (can we have a variable live on a boundary while the rest are inside? vikram will poke roy about implementing)
+    %stokes is good in slow flows...not in boundary layer cuz gradient is high...
+    %what situation would it make sense to use the LF model in some place?
     \eit

### 2016-05-20 paper/numerical_experiments.tex
added new figures (not yet made pretty) corresponding to new error breakdown for cd vs cdr case; added cost comparison (linear solve comparison)

--- 2015-05-20 practice/docs/thesis/results_v03.tex
@@
-\chapter{Numerical Results} \label{chap:results}
+\section{Numerical Experiments}
+\red{Don't forget to trim figures and convert them to pdfs!}
 
-In this chapter we demonstrate some results from applying our approach to pairs of steady-state models, implemented using the \texttt{libMesh} library \cite{libMeshPaper}.
-In Section \ref{sec:cdvcdr}, we demonstrate the results using two models that differ in the physics modeled.
-In Section \ref{sec:constvfield}, the two models differ in the space to which the parameter belongs.
-In Section \ref{sec:costAnaly} we discuss the numerical costs of our approach.
-
-%------------------------------------------------------------------------------%
-\section{Convection-Diffusion and Convection-Diffusion-Reaction Models}  \label{sec:cdvcdr}
-%------------------------------------------------------------------------------%
+\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
 
@@
 Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error.
-Here we calculate the contribution to the estimated error by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element.
 As described in Algorithm \ref{alg:refSeries}, based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$.
-In this case, once an element is assigned to the high-fidelity portion of the domain $\Omega_{HF}$, it remains assigned as such for all future subsequent mixed-fidelity models.
 Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}, while the effectivity index for the error estimate, defined by
-\begin{equation}
-\textrm{effectivity index}=\frac{\textrm{estimated QoI error}}{\textrm{true QoI error}},
-\end{equation}
-is shown in Figure \ref{fig:baseErrEff}.
+The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}.
 
 It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate.
-In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $15\%$ of the domain.
+In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $10.5\%$ of the domain.
 
@@
     \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.pdf}
+    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
     \vspace{-0.5\baselineskip}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.pdf}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
+    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
     \vspace{-0.5\baselineskip}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.pdf}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
+    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
     \vspace{-0.5\baselineskip}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{\textwidth}
-  \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF03_divvy.pdf}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF03.pdf}
-    \vspace{-0.5\baselineskip}
-    \caption{MF$_3$ ($15\%$ HF)}
-    \vspace{0.8\baselineskip}
-  \end{subfigure}
-\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
+\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.
+Since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except for some elements near the boundaries between low-fidelity and high-fidelity regions.}
 \label{fig:baseRef}
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{baseSeries/err_eff.pdf}
-\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
-\label{fig:baseErrEff}
-\end{figure}
+\subsection{Constant vs Field Parameters}
 
-\subsection{Interaction of Observations and QoI}
+\subsection{Cost Comparison}
 
-The element-wise decomposition of the error estimate (\ref{eq:finErrExp}) suggests the use of the high-fidelity model in areas of the domain where the parameter field is both informed by the observations and informative about the QoI.
-To see this, we compare the element-wise decomposition of the error estimate for three sizes of the QoI region $\Omega_I$ given the same set of observations, and for three sets of observations given the same QoI region.
-Again we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$.
-The element-wise decomposition of the error estimates (from the first three iterations) for the three sizes of the QoI region $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}, and for the three sets of observations given the same QoI region is shown in Figure \ref{fig:dataStudy}.
-For the three cases where the observations were fixed but the QoI region allowed to vary, more iterations were required as the QoI region expanded; only the first three iterations are shown in Figure \ref{fig:qoiStudy}.
-For the three cases where the QoI region was fixed but the set of observations allowed to vary, only three iterations were required to achieve an estimated absolute relative QoI error of less than $1\%$; all three iterations are shown in Figure \ref{fig:dataStudy}.
+\subsubsection{Simple Cost Analysis}
 
-\begin{figure}
-\captionsetup[subfigure]{justification=centering}
-\centering
-  \begin{subfigure}[t]{0.191\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/setup_5_3.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/setup_7_3.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/setup_3_3.pdf}
-    \caption{Locations of observations and QoI region $\Omega_I$}
-    \label{subfig:obsSetup}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_LF.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_LF.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_LF.pdf}
-    \caption{MF$_0$ \\ ($0\%$ HF)}
-    \label{subfig:obsLF}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF01.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF01.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF01.pdf}
-    \caption{MF$_1$ \\ ($5\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF02.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF02.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF02.pdf}
-    \caption{MF$_2$ \\ ($10\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.243\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF03.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF03.pdf}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF03.pdf}
-    \caption{MF$_3$ \\ ($15\%$ HF)}
-    \label{subfig:obsMFlast}
-  \end{subfigure}
-  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
-  \label{fig:qoiStudy}
-\end{figure}
+Consider a situation like that described in Section \ref{sec:cdvcdr}, where the state, adjoint, and parameter variables each have $N$ degrees of freedom.
+Suppose the low-fidelity model is linear, so that the cost of solving the inverse problem with the low-fidelity model (or with a mixed-fidelity model that is low-fidelity in most of the domain), is on the order of $(3N)^g$, where $g$ depends on the linear solver used.
+The cost for computing the auxiliary variables is also on the order of $(3N)^g$, and the cost for computing the supplementary adjoint is on the order of $(6N)^g$.
+Thus for $T$ iterations of the adaptive algorithm (where $T=1$ if one only calculates the error estimate relative to the low-fidelity model), the cost of using the adaptive algorithm is $T(2+2^g)(3N)^g$.
 
-\begin{figure}
-\captionsetup[subfigure]{justification=centering}
-\centering
-  \begin{subfigure}[t]{0.191\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/setup_3_10.pdf}
-    \includegraphics[width=\textwidth]{vs_data/setup_3_5.pdf}
-    \includegraphics[width=\textwidth]{vs_data/setup_3_3.pdf}
-    \caption{Locations of observations and QoI region $\Omega_I$}
-    \label{subfig:obsSetup}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_LF.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_LF.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_LF.pdf}
-    \caption{MF$_0$ \\ ($0\%$ HF)}
-    \label{subfig:obsLF}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF01.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF01.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF01.pdf}
-    \caption{MF$_1$ \\ ($5\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.155\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF02.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF02.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF02.pdf}
-    \caption{MF$_2$ \\ ($10\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.245\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF03.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF03.pdf}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF03.pdf}
-    \caption{MF$_3$ \\ ($15\%$ HF)}
-    \label{subfig:obsMFlast}
-  \end{subfigure}
-  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same QoI region (purple box in (\subref{subfig:obsSetup})) and varying observations (teal points in (\subref{subfig:obsSetup})).}
-  \label{fig:dataStudy}
-\end{figure}
+Suppose the inverse problem with the high-fidelity model is sufficiently nonlinear that a good initial guess is needed for convergence; one way to approach this is to use arclength continuation, a standard procedure in commercial nonlinear finite element programs.\footnote{According to Wikipedia...should see if we can confirm this elsewhere...} Letting $L_i$ represent the number of non-linear iterations required at each continuation step, the cost of solving the inverse problem with the high-fidelity model is $\sum_i L_i (3N)^g$.
+Assuming that the costs of both the high-fidelity inverse problem and adaptive algorithm are dominated by the cost of the linear solves, it is less costly to use Algorithm \ref{alg:refSeries} when $T<(2+2^g)^{-1}\sum_i L_i$.
+The bound on $T$ is strictest when $g=3$, as in the case where Gaussian elimination is used, giving $T<\frac{1}{10}\sum_i L_i$.
 
-The convective aspect of the models causes information to flow with the velocity field, and the diffusive aspect causes information to spread locally.
-Thus, it is expected that it would be most important to use the high-fidelity model in the QoI region, and in areas around observations upstream and just downstream of the QoI region.
-Using the high-fidelity model around observations is expected to become less important as the observations are placed further downstream from the QoI region.
-These expectations are supported by the results.
-For this pair of models and a QoI that is the integral of the state over a region, an appropriate mixed-fidelity model could have been designed by intuition.
-However, the interaction between the observations and the QoI may not always be so intuitive, and it is in these cases that a rigorous method for forming a mixed-fidelity model would be most helpful.
+\subsubsection{Cost Comparison Example}
 
-%\subsection{Effect of Regularization} %removed; more regularization doesn't seem to imply you can stop refining sooner...
+Here we consider the same problem as in Section \ref{sec:cdvcdr}, but with a reaction term $k_r=-616$ in the high-fidelity model.
+This reaction term is large enough that if the Newton solver will not converge with a zero initial guess.
+We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use the natural continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{NOT arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction...}, We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value).
+From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken, with $\sum_i L_i=30$ linear solves of $N\times N$ systems required.
 
-\subsection{Highly Nonlinear Problems} \label{sec:solveRob}
+Since the low-fidelity model is linear in this case, solving for the primary and auxiliary variables takes one linear solve of an $N\times N$ system each.
+The error estimate is then used to choose $10\%$ of the domain in which to use the high-fidelity model.
+For this amount of refinement, the estimated relative error is $<1\%$; estimating the error requires five $N\times N$ linear solves for the primary variables and one linear $N\times N$ solve for the auxiliary variables.
+If adaption stops at this point, then the adaptive algorithm will have required $8+2(2^g)$ solves of $N\times N$ systems.
+For $g=3$ (Gaussian elimination), this amounts to 24 solves; with iterative methods where $g<3$, this number is smaller.
 
-For a highly nonlinear high-fidelity model, it may sometimes be the case that solving the inverse problem requires a more complex or specialized optimization algorithm; for example, one may need to use continuation methods (such as in \cite{BaoLiu03}), or utilize a problem-specific preconditioner (such as in \cite{Hanke00}).
-However, solving the inverse problem with a mixed-fidelity model, where this high-fidelity model is only used in a small portion of the domain, may be achievable using a simpler optimization algorithm.
-In this subsection, we give an example of such a case.
-
-To solve the inverse problem, we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search) to solve the optimality conditions of the corresponding optimization problem (see Equation \ref{eq:invOpt}).
-Keeping most of the setup described in Section \ref{sec:cdvcdrSetup}, we consider a different high-fidelity model, one where the magnitude of the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) is increased from $k_r=-42$ to $k_r=-442$; let this new model be denoted by HF$_{442}$.
-We can no longer simply use the default nonlinear solver in \texttt{libMesh} to solve the inverse problem with this new, more nonlinear high-fidelity model, as the solver fails to converge.
-Convergence can be achieved by using continuation; we solve the inverse problem for a sequence of models, varying the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) from $k_r=-42$ to $k_r=-442$ at intervals of 50, and using the solution of one problem as the initial guess for the next.
-
-Alternatively, we use Algorithm \ref{alg:refSeries} to generate a series of mixed-fidelity models using the low-fidelity model and the HF$_{442}$ model.
-The inverse problem can be solved for these mixed-fidelity models using the default nonlinear solver, and we are able to achieve an estimated relative QoI error of less than $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $25\%$ of the domain, as shown in Figure~\ref{fig:442Err}.
-Figure \ref{fig:442ErrEff} gives the effectivity index of the error estimates.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{442/err_est.pdf}
-\caption{Estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
-\label{fig:442Err}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{442/err_eff.pdf}
-\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
-\label{fig:442ErrEff}
-\end{figure}
-
-%------------------------------------------------------------------------------%
-\section{Constant versus Field Parameters}  \label{sec:constvfield}
-%------------------------------------------------------------------------------%
-
-In this section, we consider two models which differ in the space to which the parameter belongs. We first describe the problem setup, and then present results from applying our approach.
-
-%------------------------------------------------------------%
-\subsection{Problem Setup} %\label{sec:svfSetup}
-%------------------------------------------------------------%
-
-The high-fidelity model 
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
-\end{equation}
-is again a single-species convection-diffusion-reaction equation with a nonlinear reaction term, where $k_d = 0.1$ is a diffusion coefficient and $k_r = -4.2$ is a reaction coefficient.
-The low-fidelity model
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
-\end{equation}
-differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
-Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain.
-For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The velocity field and boundary conditions, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in Section~\ref{sec:cdvcdr}.
-As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
-For this case, the domain is discretized by a regular mesh of quadrilaterals, with 15 and 75 elements along the short and long boundaries, respectively, for a total of 11,250 elements.
-The P\'{e}clet number never exceeds 0.34 in any part of the domain, so we do not require stabilization.
-
-%------------------------------------------------------------%
-\subsection{Adaptive Model Refinement} %\label{sec:svfBaseRef}
-%------------------------------------------------------------%
-
-Based on the element-wise decomposition of the estimated error, we increase the proportion of the domain in which the high-fidelity field representation model is used until the estimated absolute relative error in the QoI is less than $5\%$.
-In this case, we allow an element assigned to $\Omega_{HF}$ in one mixed-fidelity model to be reassigned back to $\Omega_{LF}$ in subsequent mixed-fidelity models if its contribution to the error is not large enough.
-Figure~\ref{fig:svfRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the first six of the series of mixed-fidelity models thus generated.
-The true and estimated absolute relative errors in the QoI for these same intermediate models are shown in Figure \ref{fig:svfErr}, while the effectivity index of the error estimate is shown in Figure \ref{fig:svfErrEff}.
-
-\begin{figure}[h!]
-\begin{subfigure}[b]{\textwidth}
-\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_0$ ($0\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_1$ ($5\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-  \centering
-  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_2$ ($10\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF03.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_3$ ($12\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF04.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_4$ ($15\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF05.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_5$ ($20\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.pdf}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_6$ ($25\%$ HF)}
-\end{subfigure}
-\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.}
-\label{fig:svfRef}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
-\label{fig:svfErr}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\textwidth]{svf/err_eff.pdf}
-\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
-\label{fig:svfErrEff}
-\end{figure}
-
-As in the previous example, the error estimates are only approximate due to the nonlinear term in both the low- and high-fidelity models.
-In this case, the high-fidelity model must also be used in a larger portion of the domain ($60\%$) before the estimated relative error in the QoI reaches the desired level.
-
-%------------------------------------------------------------------------------%
-\section{Cost Analysis} \label{sec:costAnaly}
-%------------------------------------------------------------------------------%
-
-In both the examples discussed in Sections \ref{sec:cdvcdr} and \ref{sec:constvfield}, the high-fidelity model is simple and solving the inverse problem with the high-fidelity model is easily achievable.
-Doing so actually requires less computational time than using Algorithm \ref{alg:refSeries} to rigorously form a mixed-fidelity model with which to solve the inverse problem instead.
-However, as discussed in Section \ref{sec:limits}, we assume in motivating our approach that solving the inverse problem with the high-fidelity model is prohibitively expensive; although there is no benefit, in terms of computational cost, to using our approach in the given examples, one would likely see such benefits for more complex models.
-Such a benefit is suggested in Section \ref{sec:solveRob}, where the inverse problem using the high-fidelity model is difficult to solve but our approach allows one to construct a mixed-fidelity model for which the inverse problem can be solved with a simple algorithm and yet produce a QoI with a small estimated relative error.
-
-%can philosophically compare with chad's though, perhaps in param refinement, even though his is in parameter subspaces and ours is in physical space?
+%does B+V's method for 'cheaply' getting auxiliary variables not really work when parameters are a field and not handful of scalars?
+does it even matter, since bulk of costs seem to be going to super-adjoint?

### 2016-05-20 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/qoi3_sens3_alt_err_all/plot_err.m

@@ -1,0 +1,19 @@
+%plot error vs refinement
+
+close all;
+
+fntsize = 13;
+
+errEst = [-0.0018293936; -9.84E-005; 1.41E-005];
+errTrue = [-0.0016895481; -0.0001003636; 1.32748289514697E-005];
+qoi = [0.0050801785; 0.0034909939; 0.0033773555];
+relErrEst = abs(errEst./qoi);
+relErrTrue = abs(errTrue./qoi);
+ref = [0; 0.0578; 0.105];
+
+plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',2);
+legend('True','Estimated')
+title('True and Estimated Absolute Relative Error in QoI','FontWeight','normal')
+ylabel('Absolute Relative Error in QoI')
+xlabel('% HF')
+set(gca,'FontSize',fntsize); 

### 2016-05-21 paper/mathematical_formulation.tex
added new figures (not yet made pretty) corresponding to new error breakdown for cd vs cdr case; added cost comparison (linear solve comparison)
Small edits, to be continued

@@
 %------------------------------------------------------------------------------%
-
-We seek to infer a parameter $q \in Q$, where $Q$ is a Hilbert space. Consider a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
+%
+We seek to infer an unknown parameter $q \in Q$, where $Q$ is a Hilbert space. Consider a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
+%
 \begin{equation}
+\label{eq:weakForm}
 a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
-\label{eq:weakForm}
 \end{equation}
+%
 where the form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
 
-We define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$.
-The unknown parameters can then be inferred by minimizing the difference between the predicted and actual observations.
-This inverse problem is often ill-posed; the observations are noisy and sparse and thus insufficiently informative to uniquely determine the parameters.
-To remedy this, regularization is used to inject prior information or beliefs about the parameters.
-The inverse problem with regularization can be written as a constrained optimization problem
-\begin{equation}
-\begin{array}{r@{}c}
-\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \\ \textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
-\end{array}
+We define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
+The actual observations (data) are denoted by $d\in\R^{n_d}$.
+The unknown parameter $q$ can then be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
+Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
+
+The regularized inverse problem can thus be written as a constrained optimization problem,
+%
+\begin{subequations}
 \label{eq:invOpt}
-\end{equation}
-where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization penalty term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model in Equation (\ref{eq:weakForm}).
+\begin{align}
+\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \label{eq:invOpt_obj} \\
+\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U \label{eq:invOpt_cons}
+\end{align}
+\end{subequations}
+%
+where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by Equation (\ref{eq:weakForm}).
+The constraints given by Eq.~\eqref{eq:weakForm} are typically models of physical processes or systems.
+However, a given physical system need not have a unique model that can describe it; there may be various models of different fidelities.
+This naturally introduces a hierarchy of models, introducing a tradeoff between fidelity and computational expense.
 
@@
 Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-
-In the following derivation, we assume $a$ is three times continuously differentiable with respect to the state $u$ and parameters $q$, $C$ is three times continuously differentiable with respect to the state $u$, $R$ is differentiable with respect to the parameters $q$, and $I$ is differentiable with respect to the state $u$ and parameters $q$.
-
+Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
+We thus seek to introduce the QoI functional $I$ into the inverse problem formulation, by introducing auxilary variables and additional adjoint equations.
+Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by Eq.~\eqref{eq:invOpt_cons}.
+%
 %------------------------------------------------------------------------------%
@@
 %------------------------------------------------------------------------------%
-
-A given physical system need not have a unique model that can describe it; there may be various models of different fidelities.
+%
 For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
 In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
+The main result is,
 %
@@
 \label{thm:error_estimate}
+In the following derivation, we assume $a$ is three times continuously differentiable with respect to the state $u$ and parameters $q$, $C$ is three times continuously differentiable with respect to the state $u$, $R$ is differentiable with respect to the parameters $q$, and $I$ is differentiable with respect to the state $u$ and parameters $q$.
+
 \begin{multline}
@@
 
+\red{We should include something about how to map error to elements to refine...}
+
 %------------------------------------------------------------%

### 2016-05-21 paper/abstract.tex
Reorged math formulation to make more concise for journal, express main result in theorem form Added a new algorithms section with main algorithm and complexity analysis Added abstract

Inference problems are often constrained by state equations, which arise from conservation laws, and constitutive relations. Often, a hierarchy of models can be derived from such laws and relations, reflecting varying fidelity versus cost tradeoffs. We introduce a goal oriented, model adaptive, inference algorithm, which allows users to achieve an aritrary error tolerance, while minmizing the use of high fidelity constraints. Numerical experiments test the algorithm on a highly nonlinear inverse problem, and showcase the computational savings and robustness benefits of this new approach.

### 2016-05-21 paper/intro.tex
Reorged math formulation to make more concise for journal, express main result in theorem form Added a new algorithms section with main algorithm and complexity analysis Added abstract

--- 2015-09-08 paper/intro.tex
@@
 There is an extensive literature pertaining to all these components, pertaining to the ascription/filtering of noise in data, the choice of regularization/prior information, the efficient incorporation of constraints in solving the problem and so on.
-Specifically, the work on the constraints or 'state equations' in the inverse problem focuses on methods to reduce the computational expense of solving/inverting the models that represent them.
+Specifically, the work on the constraints or `state equations' in the inverse problem focuses on methods to reduce the computational expense of solving/inverting the models that represent them.
 Such work includes the use of reduced order models to represent constraints, adaptive mesh refinement to control the size of the state equations among other strategies.
@@
 We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest.
+Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.
 
-The rest of the paper is organized as follows, Section~\ref{} presents the mathematical formulation and error analysis for the multi-model inverse problem.
-Then, in Section~\ref{} we discuss the goal oriented inference algorithm and its application to a model problem and a contaminant flow problem.
-Finally, we present conclusions and direction for future work in Section~\ref{}.
+The rest of the paper is organized as follows, Section~\ref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
+Then, in Section~\ref{sect:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis.
+Section~\ref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.
+Finally, we present conclusions and direction for future work in Section~\ref{sect:conc}.
+
+%% \subsection{draft outline}
+%% \bit 
+%% \item background/previous work? to put this work in context?
+%%   %this is probably enough? at least for previous work...
+%%   %what context though? is this another way to approach inverse problems?
+%% \item mathematical formulation
+%%   \bit
+%%   \item define inverse problem and qoi
+%%   \item derive error estimate
+%%   \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
+%%   \item relation to mesh refinement
+%%   \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem?
+(Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
+%%     %solving for adjoint and forward simultaneously (KKT) might cause you to lose an order of accuracy?
+%%     %where was that book that Oden might have mentioned inverse application of his method?
+%%       %Multiscale methods : bridging the scales in science and engineering / edited by Jacob Fish. (TA335.M85 2010 in barker)
+%%   \eit
+%% \item numerical results (perhaps not include all of these...)
+%%   \bit
+%%   \item convection-diffusion(-reaction)
+%%     \bit
+%%     \item interpretation of error estimate breakdown (interaction of QoI with observations)
+%%     \item large reaction term: MF model more cooperative with nonlinear solver
+%%     \eit
+%%   \item convection-diffusion-reaction, field vs scalar description of parameters
+%%     \bit
+%%     \item interface question: do we enforce continuity between the two models' parameters?
+%%       %-navierstokes+stokes seems to require continuity of flux and velocity across boundary...?
+%%       %-is it okay to mix diff and convdiff for the forward like we did?
+does the discontinuous velocity break any intergration-by-parts   assumptions?
+(no that's only if discontinuity in diffusion bit...)
+%%     \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
+%%     %alternative way to describe 'scalar' case?
+but here we say there is one scalar, so this would be how to combine them...if you wanted plateaus to be different, can let LF model be two-scalars...
+%%     %fig 3.10 -> what does the inferred field look like? does it look like two different plateaus?
+%%       % practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r4p2_deref/ (pushed 10/3/15)
+%%         %at the very last refinement, most of refined region seems to be two large humps...and a section that looks pretty much like the surrounding scalar...so maybe 3 patches...
+%%     \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
+%%     \eit
+%%   \item alternate/additional example: use setup from B+V? navier-stokes and another model? 
+%%     \bit
+%%     \item potential flow?
+model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
+%%     \item there would still be the question of how to interface the models...(in stokes vs navier-stokes foward paper, they just required continuity of state variables (velocity field and presssure))
+%%     %do scalar + field for infer BCs on BV NS thing? try for different QoIs? (can we have a variable live on a boundary while the rest are inside? vikram will poke roy about implementing)
+%%     %stokes is good in slow flows...not in boundary layer cuz gradient is high...
+%%     %what situation would it make sense to use the LF model in some place?
+%%     \eit
+%%   \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
+%%   \eit
+%% \item conclusion...what goes in this section usually? summary and directions for future work?
+%% \eit

### 2016-05-21 paper/mathematical_formulation.tex
Reorged math formulation to make more concise for journal, express main result in theorem form Added a new algorithms section with main algorithm and complexity analysis Added abstract

@@
 %
-We first introduce the high fidelity goal oriented inverse problem formally, providing definitions and variational statments.
+We first introduce the goal oriented inverse problem formally, providing definitions and optimization, variational statments.
 Then we will derive a rigorous, a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower fidelity constraints.
@@
 %------------------------------------------------------------------------------%
-\section{Problem Setup}  \label{sec:setup}
+\subsection{Problem Setup}  \label{sec:setup}
 %------------------------------------------------------------------------------%
@@
 where the form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
+Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
+The actual observations (data) are denoted by $d\in\R^{n_d}$.
 
-We define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
-The actual observations (data) are denoted by $d\in\R^{n_d}$.
 The unknown parameter $q$ can then be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
@@
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
-
 The regularized inverse problem can thus be written as a constrained optimization problem,
@@
 where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by Equation (\ref{eq:weakForm}).
+
 The constraints given by Eq.~\eqref{eq:weakForm} are typically models of physical processes or systems.
@@
 This naturally introduces a hierarchy of models, introducing a tradeoff between fidelity and computational expense.
-
-In the case of a goal-oriented inverse problem, the ultimate purpose of inferring the unknown parameters is to calculate some Quantity of Interest (QoI).
-Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
-We thus seek to introduce the QoI functional $I$ into the inverse problem formulation, by introducing auxilary variables and additional adjoint equations.
-Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by Eq.~\eqref{eq:invOpt_cons}.
-%
-%------------------------------------------------------------------------------%
-\section[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse \\Problem}  \label{sec:deriv}
-%------------------------------------------------------------------------------%
-%
-For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
-In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
-The main result is,
-%
-\begin{theorem}
-\label{thm:error_estimate}
-In the following derivation, we assume $a$ is three times continuously differentiable with respect to the state $u$ and parameters $q$, $C$ is three times continuously differentiable with respect to the state $u$, $R$ is differentiable with respect to the parameters $q$, and $I$ is differentiable with respect to the state $u$ and parameters $q$.
-
-\begin{multline}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
-\label{eq:finErrExp}
-\end{multline}
-\end{theorem}
-%
-
-%------------------------------------------------------------%
-\subsection{Augmented Lagrangian} \label{sec:augLag}
-%------------------------------------------------------------%
-
-The inverse problem can be written as a constrained optimization problem, described in Equation (\ref{eq:invOpt}).
-Solving this constrained optimization problem is equivalent to finding the stationary point of the corresponding Lagrangian
-\begin{equation}
-\mathcal{L}(q,u,z)= J(q,u)-(a(u,q)(z)-\ell(q)(z)),
-\end{equation}
-where $z\in U$ is the adjoint.
-
-Let $\xi=(q,u,z)$ be called the primary variables.
-Following the work of Becker and Vexler in \cite{BecVex05}, we introduce a set of auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$ corresponding to these primary variables, and define an augmented Lagrangian
-\begin{equation}
-\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}_{quz}'(q,u,z)(p,v,y),
-\end{equation}
-where $\mathcal{L}_{quz}'(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$.
-Let $\Psi = (\xi_\Psi,\chi_\Psi)$ denote the stationary point of $\mathcal{M}$, where $\xi_\Psi$ and $\chi_\Psi$ refer to the primary and auxiliary variables at $\Psi$, respectively.
-Note that
-\begin{equation}
-\mathcal{M}(\Psi)=I(q,u),
-\label{eq:MeqI}
-\end{equation} since taking variations of $\mathcal{M}$ with respect to the auxiliary variables gives that $\xi_\Psi$ is a stationary point of $\mathcal{L}$.
-
-%------------------------------------------------------------%
-\subsection{Expression for QoI Error} \label{sec:btwnMandadj}
-%------------------------------------------------------------%
-
-Consider two models with which we can infer parameters: a high-fidelity (HF) model and a lower-fidelity (LF) model.
+Consider two models with which we infer parameters: the high-fidelity (HF) model and a low fidelity (LF) model.
 We then have a specific form of Equation (\ref{eq:weakForm}) for the high-fidelity model:
@@
 \end{equation}
-Letting $\xi_{HF}=(q_{HF},u_{HF},z_{HF})$ and $\chi_{HF}=(p_{HF},v_{HF},y_{HF})$, we can thus define for the high-fidelity model an augmented Lagrangian
+The lower fidelity model can be similarly defined and identified by the subscript $LF$.
+
+In the case of a goal-oriented inverse problem, the ultimate purpose of inferring the unknown parameters is to calculate some Quantity of Interest (QoI).
+Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
+Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
+We thus seek to introduce the QoI functional $I$ into the inverse problem formulation, by introducing auxilary variables and additional adjoint equations.
+Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by Eq.~\eqref{eq:invOpt_cons}.
+%
+%------------------------------------------------------------------------------%
+\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse \\Problem}  \label{sec:deriv}
+%------------------------------------------------------------------------------%
+%
+For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
+In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
+The main result is,
+%
+\begin{theorem}
+\label{thm:error_estimate}
+Following the notation established in section~\ref{sec:setup}, let the bilinear form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
+Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
+
+Consider the Lagrangian equation induced by Eq.~\eqref{eq:invOpt},
+%
 \begin{equation}
-\mathcal{M}_{HF}(\xi_{HF},\chi_{HF}) = I(q_{HF},u_{HF}) + \mathcal{L}_{HF,\xi_{HF}}'(\xi_{HF})(\chi_{HF}),
-\label{eq:MHF}
+\label{eq:InvsOpt_lag}
+\mathcal{L}(q,u,z)= J(q,u)-(a(u,q)(z)-\ell(q)(z)),
 \end{equation}
-the stationary point of which we denote by $\Psi_{HF}$. In a similar fashion, the lower-fidelity model is described by
+%
+where $z\in U$ is the adjoint.
+Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$.
+Let the augmented Lagrangian be defined as,
+%
 \begin{equation}
-a_{LF}(u_{LF},q_{LF})(\phi_{LF})=\ell_{LF}(q_{LF})(\phi_{LF}),\quad\forall\phi_{LF}\in U_{LF},
+\label{eq:InvsOpt_auglag}
+\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}_{quz}'(q,u,z)(p,v,y),
 \end{equation}
-where $u_{LF}\in U_{LF}$ and $q_{LF}\in Q_{LF}$, and its corresponding inverse problem can be written
+%
+where $\mathcal{L}_{quz}'(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$.
+Let $\Psi = (\xi_\Psi,\chi_\Psi)$ denote the stationary point of $\mathcal{M}$.
+
+Denote by $\Psi_{HF}$ and $\Psi_{LF}$, stationary points of the high and low fidelity versions of Eq.~\eqref{eq:InvsOpt_auglag} and, consider the adjoint problem,
+%
 \begin{equation}
-\begin{array}{r@{}c}
-\min\limits_{q_{LF},u_{LF}} & \quad J_{LF}(q_{LF},u_{LF})=\frac{1}{2}\|d-C_{LF}(u_{LF})\|_2^2 + R_{LF}(q_{LF}) \\ \textrm{s.t.
-}& \quad a_{LF}(u_{LF},q_{LF})(\phi_{LF})=\ell_{LF}(q_{LF})(\phi_{LF}),\quad\forall\phi_{LF}\in U_{LF},
-\end{array}
+\label{eq:superAdjEq}
+\mathcal{M}'_{HF,\Psi}(\Lambda;\Psi_{HF})(\Phi)=\mathcal{Q}(\Phi)=\mathcal M'_{HF}(\Psi_{LF})(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
 \end{equation}
-for which we have the Lagrangian
+%
+for the supplementary adjoint $\Lambda$. Then, the error in the Quantity of Interest $I$ is given by,
+%
+\begin{multline}
+\label{eq:finErrExp}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
+\end{multline}
+%
+\end{theorem}
+%
+\begin{proof}
+%
+Observe that,
+%
 \begin{equation}
-\mathcal{L}_{LF}(q_{LF},u_{LF},z_{LF})= J_{LF}(q_{LF},u_{LF})-(a_{LF}(u_{LF},q_{LF})(z_{LF})-\ell_{LF}(q_{LF})(z_{LF})),
+\label{eq:MeqI}
+\mathcal{M}(\Psi)=I(q,u),
 \end{equation} 
-and, letting $\xi_{LF}=(q_{LF},u_{LF},z_{LF})$ and $\chi_{LF}=(p_{LF},v_{LF},y_{LF})$, an augmented Lagrangian
-\begin{equation}
-\mathcal{M}_{LF}(\xi_{LF},\chi_{LF}) = I(q_{LF},u_{LF}) + \mathcal{L}_{LF,\xi_{LF}}'(\xi_{LF})(\chi_{LF}),
-\label{eq:MLF}
-\end{equation}
-the stationary point of which we denote by $\Psi_{LF}$.
-We assume some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
+%
+since taking variations of $\mathcal{M}$ with respect to the auxiliary variables gives that $\xi_\Psi$ is a stationary point of $\mathcal{L}$.
 
-Extending the property in Equation (\ref{eq:MeqI}) to the specific cases in Equations (\ref{eq:MHF}) and (\ref{eq:MLF}), we can write the error in the QoI from solving the inverse problem with a lower-fidelity model rather than the high-fidelity model as
+Extending the property in Equation (\ref{eq:MeqI}) to the augmented Lagrangians for the high and low fidelity models, we have,
+%
 \begin{multline}
+\label{eq:repIwithM}
 I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})\textrm{.}
-\label{eq:repIwithM}
 \end{multline}
-We rewrite the first two terms $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ in Equation (\ref{eq:repIwithM}) by extending the work of \cite{BecVex05} to the context of multiple models.
-
-In \cite{BecVex05}, Becker and Vexler consider the error in the QoI from solving the inverse problem with a discretized model instead of the infinite-dimensional model.
-They describe the discretized model by
-\begin{equation}
-a(u_h,q_h)(\phi_h)=\ell(q_h)(\phi_h),\quad\forall\phi_h\in U_h\subset U,
-\label{eq:weakFormh}
-\end{equation}
-where $u_h\in U_h$ is the discrete state and $q_h\in Q$ are the unknown parameters, and $U_h$ is a finite-dimensional space constructed from finite element functions on a mesh with element size $h$.
-The infinite-dimensional model is as described in Equation (\ref{eq:weakForm}).
-For these two models (\ref{eq:weakForm}) and (\ref{eq:weakFormh}) they derive the expression
-\begin{equation}
-I(q,u)-I(q_h,u_h)=\frac{1}{2}\mathcal{M}'_\Psi(\Psi_h)(\Psi-\Psi_h)+\mathcal{R}(e^3)
-\label{eq:BVerrexp}
-\end{equation}
-where $\Psi$ is the stationary point of the augmented Lagrangian $\mathcal{M}$ as defined in Section \ref{sec:augLag} and $\Psi_h$ is its discretized counterpart, and where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi-\Psi_h$.
-Using Equation (\ref{eq:MeqI}), we can also write Equation (\ref{eq:BVerrexp}) as
-\begin{equation}
-\mathcal{M}(\Psi)-\mathcal{M}(\Psi_h)=\frac{1}{2}\mathcal{M}'_\Psi(\Psi_h)(\Psi-\Psi_h)+\mathcal{R}(e^3)
-\label{eq:BVerrexpM}
-\end{equation}
-
-Given our assumptions, Equation (\ref{eq:BVerrexpM}) holds when the infinite-dimensional model and discretized model are replaced with our more general higher- and lower-fidelity models, respectively.
-This allows us to write
+%
+Applying Proposition 3 from~\cite{BecVex05} for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,  
 \begin{equation}
@@
 \begin{multline}
+\label{eq:preadj}
 I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
-\label{eq:preadj}
 \end{multline}
-In the work of Becker and Vexler in \cite{BecVex05}, the term $\Psi-\Psi_h$ in Equation (\ref{eq:BVerrexp}) is estimated using interpolation.
-In our case, we cannot similarly address the term $\Psi_{HF}-\Psi_{LF}$ in Equation (\ref{eq:preadj}), since we now have different models instead of different discretizations of the same model.
 
-%------------------------------------------------------------%
-\subsection{QoI Error Adjoint Formulation}
-%------------------------------------------------------------%
-
-As adjoints have been used to estimate the error in an output of a forward model, we take an adjoint approach to obtain the term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ by viewing it as an error in a linear output of some system.
-As $\Psi_{HF}$ is a stationary point of $\mathcal{M}$, it satisfies $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$; we write this equation in residual form as
+Further, the error in the output $\mathcal{Q}$ defined in Equation (\ref{eq:superAdjEq}) can be expressed as a dual-weighted residual,
 \begin{equation}
-\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
-\label{eq:supadjsys}
-\end{equation}
-and define an output
-\begin{equation}
-\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi)
-\label{eq:supadjout}
-\end{equation}
-that is linear in its argument $\Phi$. We can then solve the adjoint equation corresponding to the output in Equation (\ref{eq:supadjout}) for the system in Equation (\ref{eq:supadjsys}), given by
-\begin{equation}
-\mathscr{R}_{\Psi}'(\Phi)(\Psi_{HF},\Lambda)=\mathcal{Q}(\Phi)=\mathcal M'_{HF}(\Psi_{LF})(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
-\label{eq:superAdjEq}
-\end{equation}
-for the supplementary adjoint $\Lambda$. The error in the output $\mathcal{Q}$ defined in Equation (\ref{eq:supadjout}) can thus be expressed as a dual-weighted residual
-\begin{equation}
+\label{eq:adjOutErr}
 \mathcal M'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})=-\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda).
-\label{eq:adjOutErr}
 \end{equation}
 
-%------------------------------------------------------------%
-\subsection{Error Estimate}
-%------------------------------------------------------------%
-
-Combining Equations (\ref{eq:preadj}) and (\ref{eq:adjOutErr}), we obtain a third-order expression for the error in the QoI from solving the inverse problem using a lower-fidelity model instead of the high-fidelity model:
+Combining Equations (\ref{eq:preadj}) and (\ref{eq:adjOutErr}), we have,
 \begin{multline}
 I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
-\label{eq:finErrExp}
 \end{multline}
-
-The error estimate (\ref{eq:finErrExp}) is general and the lower-fidelity model can also be a mixed-fidelity model that combines the high- and low-fidelity model.
+%
+which completes the proof.
+\end{proof}
+%
+The above error estimate is general and the lower-fidelity model can also be a mixed-fidelity model that combines the high- and low-fidelity model.
 Given a low-fidelity model and a high-fidelity model, an intermediate, mixed-fidelity (MF) model can be formed by using the high-fidelity model in some parts of the domain, and the low-fidelity model in the rest of the domain.
-Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
-The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
-This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
-
-\red{We should include something about how to map error to elements to refine...}
-
-%------------------------------------------------------------%
-\subsection{Approximations in Practice}
-%------------------------------------------------------------%
-
-Although Equation (\ref{eq:finErrExp}) is exact, the error estimate that can be calculated in practice will not generally be exact.
-Let us refer to a goal-oriented inverse problem as linear when the state $u$ and parameters $q$ are linearly related, the observation operator $C$ is linear in $u$, the regularization term $R$ is at most quadratic in the parameters, and the QoI functional $I$ is linear in $u$ and $q$.
-The remainder term $\mathcal{R}(e^3)$ is included in Equation (\ref{eq:finErrExp}) but would not, in practice, be calculated; in the case of a linear goal-oriented inverse problem, the remainder term disappears, but it is nonzero in general.
-In addition, the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem must be approximated by linearizing about $\Psi_{LF}$ instead.
-
-A summary of our overall approach is presented in Algorithm \ref{alg:refSeries}, with the estimated absolute relative error chosen as a stopping criterion.
-
-\alglanguage{pseudocode}
-\begin{algorithm}[h]
-\small
-\caption{An algorithm to adaptively build a mixed-fidelity model for low error in the QoI.}
-\label{alg:refSeries}
-\begin{algorithmic}[1]
-\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
-\State{Define maximum number of adaptive iterations \texttt{maxIter}}
-\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
-	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
-	\State{$i\gets0$}
-	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
-	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for
-
-	supplementary adjoint $\Lambda_0$ (see Equation (\ref{eq:superAdjEq}))}
-	\State{Compute QoI error estimate
-
-	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
-	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
-	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $e_{I,i}$ and use this element-wise decomposition to guide formation \par\hskip\algorithmicindent of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
-		\State{$i\gets i+1$}
-		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
-		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
-
-		$\quad\quad$supplementary adjoint $\Lambda_i$ (see Equation (\ref{eq:superAdjEq}))}
-		\State{Compute QoI error estimate
-
-		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
-		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
-	\EndWhile \\
-\Return{model MF$_i$ and QoI estimate $I(q_{MF_i},u_{MF_i})$}
-\EndProcedure
-\Statex
-\end{algorithmic}
-\end{algorithm}
-
-%section/note that forming a mixed-fidelity model is not always so straightforward?
-should poke literature about how this is done if so (model interfacing that Oden,Prudhomme, etal talk about...also seemed to have a sort of interior-boundary-condition for stokes-ns mix)...also include de-refinement?
-(choices of how to pick where to refine?
-if so, would we need to reference other papers where similar choices are made?)
-	%just a note that smushing together is not always best? ex: linear diff vs convdiff, it all holds, but such a MF model is not necessarily 'closer' to HF in that qoi not necessarily closer..
-
-%if I is a PDE, then is it also possible that it can be excessively complex as well? though in that case would there be any 'regularization' to avoid?
-
-%------------------------------------------------------------------------------%
-\section{Limitations}  \label{sec:limits}
-%------------------------------------------------------------------------------%
-
-In motivating our approach, it is assumed that one can most accurately calculate the QoI from the parameter values inferred using the highest-fidelity forward model available, but that solving the inverse problem with this model is prohibitively expensive.
-It is also assumed that solving the inverse problem with a mixed-fidelity model, where this highest-fidelity model is only used in a portion of the domain, will be cheaper.
-There is a cost incurred by using our approach to design such a mixed-fidelity model, however, and it will sometimes be the case that the cost of obtaining this mixed-fidelity model exceeds that of just solving the inverse problem with the highest-fidelity model directly.
-Naively, if the auxiliary variables $\chi$ have $n$ degrees of freedom, they can be found by solving an $n\times n$ linear system, while the supplementary adjoint $\Lambda$ can be found by solving a $2n\times2n$ linear system.
-The cost of solving for the auxiliary variables can be reduced by using a technique described in \cite{BecVex05}, and the cost of solving for the supplementary adjoint $\Lambda$ can be reduced by reusing preconditioners.
-In general there are no guarantees that obtaining a mixed-fidelity model that meets the desired QoI error criterion will be less costly than just solving the inverse problem with the high-fidelity model.
-However, our approach targets problems for which solving the inverse problem with the high-fidelity model is prohibitively expensive, in which case it is expected that the cost of obtaining a satisfactory mixed-fidelity model will be comparatively low.
-Even in the case where a mixed-fidelity model for which the QoI error is adequately small cannot be found before another limit (for example, a maximum number of adaptive iterations) is reached, one still has an estimate for the error in the QoI without solving the prohibitively expensive inverse problem.
-
-The derived error estimate is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
-The two models could also correspond to two levels of mesh-refinement, though in this case the method described in \cite{BecVex05} would be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
-The derived error estimate is not applicable to all models, however.
-The two models must have a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
-The weak form, observation operator, regularization term, and QoI functional must also have the degrees of differentiability noted in Section \ref{sec:setup}.
-The two models must also have some degree of compatibility, as previously described in Section \ref{sec:btwnMandadj}.

### 2016-05-21 paper/numerical_experiments.tex
Reorged math formulation to make more concise for journal, express main result in theorem form Added a new algorithms section with main algorithm and complexity analysis Added abstract

@@
-\section{Numerical Experiments}
+\section{Numerical Experiments}\label{sect:numexp}
 \red{Don't forget to trim figures and convert them to pdfs!}
@@
 \subsection{Constant vs Field Parameters}
-
-\subsection{Cost Comparison}
-
-\subsubsection{Simple Cost Analysis}
-
-Consider a situation like that described in Section \ref{sec:cdvcdr}, where the state, adjoint, and parameter variables each have $N$ degrees of freedom.
-Suppose the low-fidelity model is linear, so that the cost of solving the inverse problem with the low-fidelity model (or with a mixed-fidelity model that is low-fidelity in most of the domain), is on the order of $(3N)^g$, where $g$ depends on the linear solver used.
-The cost for computing the auxiliary variables is also on the order of $(3N)^g$, and the cost for computing the supplementary adjoint is on the order of $(6N)^g$.
-Thus for $T$ iterations of the adaptive algorithm (where $T=1$ if one only calculates the error estimate relative to the low-fidelity model), the cost of using the adaptive algorithm is $T(2+2^g)(3N)^g$.
-
-Suppose the inverse problem with the high-fidelity model is sufficiently nonlinear that a good initial guess is needed for convergence; one way to approach this is to use arclength continuation, a standard procedure in commercial nonlinear finite element programs.\footnote{According to Wikipedia...should see if we can confirm this elsewhere...} Letting $L_i$ represent the number of non-linear iterations required at each continuation step, the cost of solving the inverse problem with the high-fidelity model is $\sum_i L_i (3N)^g$.
-Assuming that the costs of both the high-fidelity inverse problem and adaptive algorithm are dominated by the cost of the linear solves, it is less costly to use Algorithm \ref{alg:refSeries} when $T<(2+2^g)^{-1}\sum_i L_i$.
-The bound on $T$ is strictest when $g=3$, as in the case where Gaussian elimination is used, giving $T<\frac{1}{10}\sum_i L_i$.
-
-\subsubsection{Cost Comparison Example}
-
-Here we consider the same problem as in Section \ref{sec:cdvcdr}, but with a reaction term $k_r=-616$ in the high-fidelity model.
-This reaction term is large enough that if the Newton solver will not converge with a zero initial guess.
-We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use the natural continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{NOT arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction...}, We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value).
-From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken, with $\sum_i L_i=30$ linear solves of $N\times N$ systems required.
-
-Since the low-fidelity model is linear in this case, solving for the primary and auxiliary variables takes one linear solve of an $N\times N$ system each.
-The error estimate is then used to choose $10\%$ of the domain in which to use the high-fidelity model.
-For this amount of refinement, the estimated relative error is $<1\%$; estimating the error requires five $N\times N$ linear solves for the primary variables and one linear $N\times N$ solve for the auxiliary variables.
-If adaption stops at this point, then the adaptive algorithm will have required $8+2(2^g)$ solves of $N\times N$ systems.
-For $g=3$ (Gaussian elimination), this amounts to 24 solves; with iterative methods where $g<3$, this number is smaller.
-
-%does B+V's method for 'cheaply' getting auxiliary variables not really work when parameters are a field and not handful of scalars?
-does it even matter, since bulk of costs seem to be going to super-adjoint?

### 2016-05-21 paper/algorithms.tex
Forgot to commit algorithms file

\section{Inference Algorithm and Complexity Analysis}\label{sect:alg}
%
Based on the above discussion and the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
%
\subsection{Goal Oriented Inference Algorithm}
%
Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model. The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model. This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached. \red{We should include something about how to map error to elements to refine.} We present below an algorithm that accomplishes the above goals.
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adaptively build a mixed-fidelity model for low error in the QoI.}
\label{alg:refSeries}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Define maximum number of adaptive iterations \texttt{maxIter}}
\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
	\State{$i\gets0$}
	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for

	supplementary adjoint $\Lambda_0$ (see Equation (\ref{eq:superAdjEq}))}
	\State{Compute QoI error estimate

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $e_{I,i}$ and use this element-wise decomposition to guide formation \par\hskip\algorithmicindent of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

		$\quad\quad$supplementary adjoint $\Lambda_i$ (see Equation (\ref{eq:superAdjEq}))}
		\State{Compute QoI error estimate

		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
	\EndWhile \\
\Return{model MF$_i$ and QoI estimate $I(q_{MF_i},u_{MF_i})$}
\EndProcedure
\Statex
\end{algorithmic}
\end{algorithm}
%

Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.

Algorithm~\ref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
% 
\subsection{Complexity Analysis}
%
We now derive the computational complexity of using algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies. Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an 'all at once' strategy is used to solve the KKT system. The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}. The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$, and the cost for computing the supplementary adjoint is $\orderof{6N}^{\gamma}$.

If one utilizes algorithm~\ref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
%
\begin{align}
\label{eq:cost_adapt}
C_{MF} &= \sum_{i=1}^{T}L_{i}(3N)^{\gamma} + 1(3N)^{\gamma} + 2^{\gamma}(3N)^{\gamma} \nonumber \\
&= \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) (3N)^{\gamma}
\end{align}
% 
where $L_i$ is the number of nonlinear solver steps needed to solve the KKT system for the low or mixed fidelity model. The corresponding cost for a nonadaptive algorithm, for a nonlinear inference problem, solved using a continuation scheme is,
%
\begin{equation}
\label{eq:cost_nadapt}
C_{HF} = \sum_{i=1}^{C}K_{i}(3N)^{\gamma}
\end{equation}
% 
where $K_i$ is the number of nonlinear solver steps needed to solve the KKT system for the high fidelity model, and $C$ is the number of continuation steps.

Comparing Eq.~\eqref{eq:cost_adapt} and~\eqref{eq:cost_nadapt}, we have,
%
\begin{equation}
\label{eq:cost_compare_0}
C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) < \sum_{i=1}^{C}K_{i}
\end{equation}
%
If the low and multi-fidelity models are linear or nonlinear in a very small region $L_i \approx 1$, and we have the following condition,
%
\begin{equation}
\label{eq:cost_compare_1}
T < \frac{\sum_{i=1}^{C}K_{i}}{2 + 2^{\gamma}}
\end{equation}
% 
The bound on $T$ is strictest when $\gamma = 3$, when Gaussian elimination is used, giving $T < \frac{\sum_{i=1}^{C}K_{i}}{10}$.
%
\subsubsection{Illustrative Example}
%
We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken, with $\sum_{i=1}^{C} K_i=30$. With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps. Using algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$. Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.

In other words, for a highly nonlinear problem, using algorithm~\ref{alg:refSeries}, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, while avoiding any need for continuation to handle nonlinearities.

%does B+V's method for 'cheaply' getting auxiliary variables not really work when parameters are a field and not handful of scalars? does it even matter, since bulk of costs seem to be going to super-adjoint?

%% Although Equation (\ref{eq:finErrExp}) is exact, the error estimate that can be calculated in practice will not generally be exact. Let us refer to a goal-oriented inverse problem as linear when the state $u$ and parameters $q$ are linearly related, the observation operator $C$ is linear in $u$, the regularization term $R$ is at most quadratic in the parameters, and the QoI functional $I$ is linear in $u$ and $q$. The remainder term $\mathcal{R}(e^3)$ is included in Equation (\ref{eq:finErrExp}) but would not, in practice, be calculated; in the case of a linear goal-oriented inverse problem, the remainder term disappears, but it is nonzero in general.

%% In motivating our approach, it is assumed that one can most accurately calculate the QoI from the parameter values inferred using the highest-fidelity forward model available, but that solving the inverse problem with this model is prohibitively expensive. It is also assumed that solving the inverse problem with a mixed-fidelity model, where this highest-fidelity model is only used in a portion of the domain, will be cheaper. There is a cost incurred by using our approach to design such a mixed-fidelity model, however, and it will sometimes be the case that the cost of obtaining this mixed-fidelity model exceeds that of just solving the inverse problem with the highest-fidelity model directly. Naively, if the auxiliary variables $\chi$ have $n$ degrees of freedom, they can be found by solving an $n\times n$ linear system, while the supplementary adjoint $\Lambda$ can be found by solving a $2n\times2n$ linear system. The cost of solving for the auxiliary variables can be reduced by using a technique described in \cite{BecVex05}, and the cost of solving for the supplementary adjoint $\Lambda$ can be reduced by reusing preconditioners. In general there are no guarantees that obtaining a mixed-fidelity model that meets the desired QoI error criterion will be less costly than just solving the inverse problem with the high-fidelity model. However, our approach targets problems for which solving the inverse problem with the high-fidelity model is prohibitively expensive, in which case it is expected that the cost of obtaining a satisfactory mixed-fidelity model will be comparatively low. Even in the case where a mixed-fidelity model for which the QoI error is adequately small cannot be found before another limit (for example, a maximum number of adaptive iterations) is reached, one still has an estimate for the error in the QoI without solving the prohibitively expensive inverse problem.

### 2016-05-22 paper/intro.tex
Minor typos (more to come)

@@
 The ability to infer parameters via an inverse problem allows practitioners to gain important information about systems, processes and the models that are used to describe them.
-Such inference also avoids intrusive experiments, which may otherwise be prohibitively expensive or excessively intrusive.
-Once parameters have been inferred via an inverse problem, they can be used for forward propogation of the model and computing relevant goals and quantities of interest for the modeling/decision making process.
+Such inference also avoids intrusive experiments, which may otherwise be prohibitively expensive or impractical.
+Once parameters have been inferred via an inverse problem, they can be used for forward propagation of the model and, computing relevant quantities of interest for the modeling/decision making process.
 
 Data, constraints and prior information form the critical components of an inverse problem formulation.
-There is an extensive literature pertaining to all these components, pertaining to the ascription/filtering of noise in data, the choice of regularization/prior information, the efficient incorporation of constraints in solving the problem and so on.
-Specifically, the work on the constraints or `state equations' in the inverse problem focuses on methods to reduce the computational expense of solving/inverting the models that represent them.
-Such work includes the use of reduced order models to represent constraints, adaptive mesh refinement to control the size of the state equations among other strategies.
+There is an extensive literature pertaining to all these components, including the filtering of noise in data, the choice of regularization/prior information, the efficient incorporation of constraints in solving the problem and so on.
+Specifically, the work on the constraints or `state equations' in the inverse problem focuses on reducing the computational expense of solving/inverting the models that represent them.
+Such work includes the use of reduced order models to represent constraints~\cite{}, adaptive mesh refinement to control the size of the state equation discretizations~\cite{} among other strategies.
 
@@
 The use of multiple models simultaneously for forward simulation is well established.
-In this work, we extend the use of the multi-fidelity models to inverse problems.
-We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest.
+In this work, we extend the use of multi-fidelity models to inverse problems.
+We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest.
 Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.

### 2016-05-22 paper/mathematical_formulation.tex
Minor typo
Minor typos (more to come)

@@
 %
-We seek to infer an unknown parameter $q \in Q$, where $Q$ is a Hilbert space. Consider a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
+Let $Q$, $U$ be Hilbert spaces.
+We seek to infer an unknown parameter $q \in Q$.
+The parameter is constrained by a state equation, with a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
 %
@@
 \label{eq:weakForm}
-a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
+a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U.
 \end{equation}
 %
-where the form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
+The bilinear form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
 Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
@@
 \begin{align}
-\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \label{eq:invOpt_obj} \\
-\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U \label{eq:invOpt_cons}
+\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_obj} \\
+\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U. \label{eq:invOpt_cons}
 \end{align}
@@
 %
-where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by Equation (\ref{eq:weakForm}).
+Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by Equation (\ref{eq:weakForm}).
 
@@
 However, a given physical system need not have a unique model that can describe it; there may be various models of different fidelities.
-This naturally introduces a hierarchy of models, introducing a tradeoff between fidelity and computational expense.
-Consider two models with which we infer parameters: the high-fidelity (HF) model and a low fidelity (LF) model.
-We then have a specific form of Equation (\ref{eq:weakForm}) for the high-fidelity model:
-\begin{equation}
-a_{HF}(u_{HF},q_{HF})(\phi_{HF})=\ell_{HF}(q_{HF})(\phi_{HF}),\quad\forall\phi_{HF}\in U_{HF},
-\end{equation}
-where $u_{HF}\in U_{HF}$ and $q_{HF}\in Q_{HF}$. Similarly, the inverse problem in Equation (\ref{eq:invOpt}) has the specific form
+This naturally introduces a hierarchy of models and, a tradeoff between fidelity and computational expense.
+Consider two models with which we infer parameters: a high-fidelity (HF) model and a low fidelity (LF) model.
+We then have a specific form of the inverse problem in Equation (\ref{eq:invOpt}) with this model,
 \begin{equation}
@@
 \end{equation}
-for which we have the Lagrangian
-\begin{equation}
-\mathcal{L}_{HF}(q_{HF},u_{HF},z_{HF})= J_{HF}(q_{HF},u_{HF})-(a_{HF}(u_{HF},q_{HF})(z_{HF})-\ell_{HF}(q_{HF})(z_{HF})).
-\end{equation}
-The lower fidelity model can be similarly defined and identified by the subscript $LF$.
+for which we have the Lagrangian,
+\begin{multline}
+\mathcal{L}_{HF}(q_{HF},u_{HF},z_{HF}) = \\
+J_{HF}(q_{HF},u_{HF})-(a_{HF}(u_{HF},q_{HF})(z_{HF})-\ell_{HF}(q_{HF})(z_{HF})).
+\end{multline}
+The inverse problem formulation and Lagrangian with the lower fidelity model can be similarly defined, and be identified with subscript $LF$.
 
@@
 \begin{equation}
+\label{eq:beckvex}
 \mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
 \end{equation}
-where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$. Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:preadj}) we obtain
+where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$. Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:beckvex}) we obtain
 \begin{multline}
@@
 \begin{multline}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3). \nonumber
 \end{multline}

### 2016-05-22 paper/algorithms.tex
Numerical Exp section expanded, more typos fixed.

@@
 %
-Based on the above discussion and the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
+Based on the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
 %
@@
 % 
-\subsection{Complexity Analysis}
+\subsection{Complexity Analysis}\label{sect:alg_complexity}
 %
 We now derive the computational complexity of using algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
-Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an 'all at once' strategy is used to solve the KKT system.
+Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
 The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}.
@@
 % 
-where $L_i$ is the number of nonlinear solver steps needed to solve the KKT system for the low or mixed fidelity model.
-The corresponding cost for a nonadaptive algorithm, for a nonlinear inference problem, solved using a continuation scheme is,
+where $L_i$ is the number of nonlinear solver steps needed to solve the KKT system for the low or mixed fidelity model at each adaptive step.
+The corresponding cost for solving the high fidelity inference problem, with a nonadaptive algorithm, based on a continuation scheme is,
 %
@@
 % 
-where $K_i$ is the number of nonlinear solver steps needed to solve the KKT system for the high fidelity model, and $C$ is the number of continuation steps.
+where $K_i$ is the number of nonlinear solver steps needed to solve the KKT system for the high fidelity model at each continuation step, and $C$ is the number of continuation steps.
 
@@
 \label{eq:cost_compare_0}
-C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) < \sum_{i=1}^{C}K_{i}
+C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) < \sum\limits_{i=1}^{C}K_{i}
 \end{equation}
@@
 \label{eq:cost_compare_1}
-T < \frac{\sum_{i=1}^{C}K_{i}}{2 + 2^{\gamma}}
+T < \frac{\sum\limits_{i=1}^{C}K_{i}}{2 + 2^{\gamma}}
 \end{equation}
 % 
-The bound on $T$ is strictest when $\gamma = 3$, when Gaussian elimination is used, giving $T < \frac{\sum_{i=1}^{C}K_{i}}{10}$.
+The bound on $T$ will be strictest if Gaussian elimination is used, with $\gamma = 3$, giving $T < \frac{\sum\limits_{i=1}^{C}K_{i}}{10}$.
 %
-\subsubsection{Illustrative Example}
-%
-We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
-This reaction term is large enough that the Newton solver will not converge with a zero initial guess.
-We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value).
-From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken, with $\sum_{i=1}^{C} K_i=30$.
-With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps.
-Using algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
-Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.
-
-In other words, for a highly nonlinear problem, using algorithm~\ref{alg:refSeries}, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, while avoiding any need for continuation to handle nonlinearities.
 

### 2016-05-22 paper/mathematical_formulation.tex
Numerical Exp section expanded, more typos fixed.

@@
 For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
-In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
+In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
 The main result is,
@@
 %
+where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$.
 \end{theorem}
@@
 \end{equation}
-where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$. Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:beckvex}) we obtain
+Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:beckvex}) we obtain
 \begin{multline}

### 2016-05-22 paper/numerical_experiments.tex
Numerical Exp section expanded, more typos fixed.

@@
 \section{Numerical Experiments}\label{sect:numexp}
+%
+We now use algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi model setting.
+We consider two kinds of multi-fidelity models, in a total of three experiments.
+In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
+The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.
+
+In all experiments, starting the simulation with the low fidelity model, we seek to add regions of high fidelity, until the estimated relative error in the target QoI is less than 1$\%$. 
 \red{Don't forget to trim figures and convert them to pdfs!}
+%
 
 \subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
-
+%
 In this section, we demonstrate the method derived in Section \ref{sec:deriv} for two models which differ in the physics included.
 We first describe the problem setup, and then present results from applying our approach.
-
+%
 %------------------------------------------------------------%
-\subsection{Problem Setup} \label{sec:cdvcdrSetup}
+\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
 %------------------------------------------------------------%
-
-The high- and low-fidelity models are restricted to a rectangular domain $\Omega$, defined as $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates.
-The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),
+%
+We consider a rectangular domain $\Omega$, defined as $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates.
+The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
+%
+\begin{subequations}
 \label{eq:cdvcdrHF}
-\end{equation}
-where the state $u$ is the species concentration, $f(q)$ is a forcing field described by the parameters, $k_d = 0.1$ is a diffusion coefficient and $k_r = -42.0$ is a reaction coefficient.
-The low-fidelity model
+\begin{align}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
+u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
+\end{align} 
+\end{subequations}
+%
+where the state $u$ is the species concentration and, $f(q)$ is a forcing field described by the parameters.
+The velocity field is $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$, while the diffusion coefficient $k_d = 0.1$ and, the reaction coefficient $k_r = -42.0$.
+The low-fidelity model,
+%
 \begin{equation}
@@
 \end{equation}
+%
 differs only in the removal of the reaction term.
-Both models share a common velocity field, described by $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$.
 To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively.
-The resulting mixed-fidelity models can be described by
+The resulting mixed-fidelity models can be described by,
+%
 \begin{equation}
@@
 \end{equation}
-where $k^{MF}_r$ is a piecewise-constant reaction coefficient
+%
+where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
+%
 \begin{equation}
@@
 \end{equation}
-Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain.
+%
+The QoI we wish to calculate is the integral of the state,
+%
+\begin{equation}
+I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
+\end{equation}
+%
+over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.
 
-We let the unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$.
-Observations $d=(u(0.35,0.35),u(1.56,0.61),u(3.1,0.5))$ from three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with a piecewise constant source term $f_{true}$
+The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. The `true' forcing field is given by,
+a piecewise constant source term $f_{true}$,
+%
 \begin{equation}
@@
 \end{equation}
-The QoI we wish to calculate is the integral of the state,
-\begin{equation}
-I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
-\end{equation}
-over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.
-The locations of the observations and the region $\Omega_I$ over which the QoI is calculated is shown in Figure \ref{fig:baseSetup}.
-Since the inverse problem is ill-posed, we use Tikhonov regularization \cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is a regularization coefficient.
+%
+Observations $d=(u(0.35,0.35),u(1.56,0.61),u(3.1,0.5))$ from three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with true forcing field.
 
+The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in Figure~\ref{fig:baseSetup}.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is a regularization coefficient.
+%
 \begin{figure}[h]
@@
 \end{figure}
+%
+For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements.
+We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
+The library offers both easy calculation of adjoint systems, error estimates and subdomain restricted variables.
+The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 76,806 degrees of freedom.
+No stabilization was required for these calculations, since the cell P\'{e}clet number never exceeded 0.1.
+%
+%------------------------------------------------------------%
+\subsubsection{Results} \label{sec:cdvcdrBaseRef} 
+%------------------------------------------------------------%
+%
+We now present the results for solving the inference problem using algorithm~\ref{alg:refSeries}.
+Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error.
+Based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI, is less than $1\%$.
 
-For the numerical simulations, we use the \texttt{libMesh} library \cite{libMeshPaper}.
-The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements.
-We implement the finite element method (FEM) for a continuous Galerkin formulation using a linear nodal basis, for a total of 76,806 degrees of freedom.
-The P\'{e}clet number never exceeds 0.1 in any part of the domain, so we do not require stabilization.
-
-%------------------------------------------------------------%
-\subsection{Adaptive Model Refinement} \label{sec:cdvcdrBaseRef} 
-%------------------------------------------------------------%
-
-Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error.
-As described in Algorithm \ref{alg:refSeries}, based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$.
-Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}.
-
-It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate.
-In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $10.5\%$ of the domain.
-
+Figure~\ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+%
 \begin{figure}[h!]
@@
     \caption{MF$_0$ ($0\%$ HF)}
+    \label{fig:baseRef0}
     \vspace{0.8\baselineskip}
@@
   \end{subfigure}
-\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.
-Since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except for some elements near the boundaries between low-fidelity and high-fidelity regions.}
+\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
 \label{fig:baseRef}
 \end{figure}
+%
+Note that since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except some elements near the interface, whose basis function have support in both regions.
 
+We see that model refinement is concentrated in the QoI region, and the data point closest to the QoI.
+In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is data point one.
+Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right.
+Therefore, for the calculation of the QoI, it is most important to refine the region near data point one, and the QoI region.
+We also observe that the region near the data points downstream from the QoI are not refined as much as the region immediately adjacent to the QoI.
+This indicates that the information from these two data points is not significant for the estimation of the QoI.
+\red{We should say a bit more about the refinement region here, and implications for experimental design ?}.
+
+Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by algorithm~\ref{alg:refSeries}.
+It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.
+We also see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
+%
 \begin{figure}[h]
@@
 \end{figure}
+%
+\subsection{Constant vs Field Parameters}
+%
+\subsubsection{Problem Setup}
+%
+\subsubsection{Results}
+%
+\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
+%
+\subsubsection{Results}
+%
+We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
+This reaction term is large enough that the Newton solver will not converge with a zero initial guess.
+We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value).
+From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
+%
+\subsubsection{Computational Complexity}
+%
+We compare the complexity of algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
+For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
 
-\subsection{Constant vs Field Parameters}
+With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps.
+Using algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
+Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.
+
+In other words, on using algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.

### 2016-05-24 paper/algorithms.tex
added bibliography, a bit about error breakdown (not made into math yet); added first attempt to join and streamline psi and superadj solvers

@@
 %
-We now derive the computational complexity of using algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
+We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
 Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
@@
 
-If one utilizes algorithm~\ref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
+If one utilizes Algorithm~\ref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
 %

### 2016-05-24 paper/numerical_experiments.tex
added bibliography, a bit about error breakdown (not made into math yet); added first attempt to join and streamline psi and superadj solvers

@@
 %
-We now use algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi model setting.
+We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi model setting.
 We consider two kinds of multi-fidelity models, in a total of three experiments.
@@
 %
+\subsection{Error Estimate Localization}
+%
+Algorithm~\ref{alg:refSeries} does not specify any particular method for localizing the error estimate.
+A naive approach would be to calculate the contribution to the estimated error by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element.
+While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.
 
+We instead use the alternative method described in \cite{vanOpstaletal15} to decompose the equivalent error estimate expression
+%
+\begin{multline}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
+\end{multline}
+%
+into error contributions from locally supported basis functions, and refine the model in those elements in the support of those basis functions with the largest error contributions.
+Using this method, elements in which the high-fidelity model is already being used are not seen as continuing to contribute to the error in the QoI, with the possible exception of elements near the interfaces between the low-fidelity and high-fidelity regions.
+\red{Express this mathematically?}
+%
 \subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
@@
 %
-We now present the results for solving the inference problem using algorithm~\ref{alg:refSeries}.
+We now present the results for solving the inference problem using Algorithm~\ref{alg:refSeries}.
 Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error.
@@
 
-Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by algorithm~\ref{alg:refSeries}.
+Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}.
 It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.
@@
 %
-We compare the complexity of algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
+We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
 For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
@@
 With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps.
-Using algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
+Using Algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
 Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.
 
-In other words, on using algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
+In other words, on using Algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_aux.C

@@ -1,0 +1,276 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_aux.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/equation_systems.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_AuxSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+
+	//regularization
+	beta = infile("beta",0.1);
+	
+	//diffusion coefficient
+	k = infile("k", 1.0);
+	
+	//reaction coefficient
+	Rcoeff = infile("R", 0.0);
+	
+	//subdomain ids
+	diff_subdomain_id = infile("diff_id", -1);
+	cd_subdomain_id = infile("cd_id", 0);
+	cdr_subdomain_id = infile("cdr_id", 1);
+
+	//indicate variables that change in time
+	this->time_evolving(aux_c_var);
[…]

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_aux.h

@@ -1,0 +1,66 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+
+using namespace libMesh;
+
+class ConvDiff_AuxSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_AuxSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("convdiff_mprime.in");
+		std::string find_data_here = infile("data_file","Measurements_top6.dat");
+		qoi_option = infile("QoI_option",1);
+    
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+  
+
+  // Indices for each variable;
+  unsigned int aux_c_var, aux_zc_var, aux_fc_var;
+  
+  Real beta; //regularization parameter
+  Real k; //diffusion coefficient
+  Real Rcoeff; //reaction coefficient
+  
+  //data-related stuff
+  std::vector<Point> datapts; 
+  std::vector<Real> datavals;
+  
+	int diff_subdomain_id, cd_subdomain_id, cdr_subdomain_id;
+	
+	//avoid assigning data point to two elements in on their boundary
+	std::vector<int> accounted_for;
+  
+  //options for QoI location and nature
+  int qoi_option;
+  
+};

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_mprime.C

@@ -1,0 +1,319 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_mprime.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_MprimeSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+
+	//regularization
+	beta = infile("beta",0.1);
+	
+	//diffusion coefficient
+	k = infile("k", 1.0);
+	
+	//reaction coefficient
+	Rcoeff = infile("R", -1.0);
+	
+	//subdomain ids
+	diff_subdomain_id = infile("diff_id", -1);
+	cd_subdomain_id = infile("cd_id", 0);
+	cdr_subdomain_id = infile("cdr_id", 1);
+
[…]

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_mprime.h

@@ -1,0 +1,72 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+
+using namespace libMesh;
+
+class ConvDiff_MprimeSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_MprimeSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    qoi.resize(1);
+    
+    GetPot infile("convdiff_mprime.in");
+		std::string find_data_here = infile("data_file","Measurements_top6.dat");
+		qoi_option = infile("QoI_option",1);
+    
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+
+  // Postprocessed output
+  virtual void postprocess();
+  
+  //for adjoint
+  virtual void element_qoi_derivative(DiffContext &context, const QoISet & qois);
+
+  // Indices for each variable;
+  unsigned int c_var, zc_var, fc_var, aux_c_var, aux_zc_var, aux_fc_var;
+  
+  Real beta; //regularization parameter
+  Real k; //diffusion coefficient
+  Real Rcoeff; //reaction coefficient
+  
+  //data-related stuff
+  std::vector<Point> datapts; 
+  std::vector<Real> datavals;
+	
+	int diff_subdomain_id, cd_subdomain_id, cdr_subdomain_id;
+	
+	//avoid assigning data point to two elements in on their boundary
+	std::vector<int> accounted_for;
+  
+  //options for QoI location and nature
+  int qoi_option;
+};

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_primary.C

@@ -1,0 +1,239 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_primary.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_PrimarySys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	
+	//regularization
+	beta = infile("beta",0.1);
+	
+	//diffusion coefficient
+	k = infile("k", 1.0);
+	
+	//reaction coefficient
+	Rcoeff = infile("R", -1.0);
+	
+	//subdomain ids
+	diff_subdomain_id = infile("diff_id", -1);
+	cd_subdomain_id = infile("cd_id", 0);
+	cdr_subdomain_id = infile("cdr_id", 1);
+
+	//indicate variables that change in time
+	this->time_evolving(c_var);
+	this->time_evolving(zc_var);
+	this->time_evolving(fc_var);
+
+	// Useful debugging options
[…]

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/convdiff_primary.h

@@ -1,0 +1,70 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+
+using namespace libMesh;
+
+class ConvDiff_PrimarySys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_PrimarySys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("convdiff_mprime.in");
+		std::string find_data_here = infile("data_file","Measurements_top6.dat");
+		qoi_option = infile("QoI_option",1);
+   
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+                                        
+  //to calculate QoI
+  virtual void element_postprocess(DiffContext &context);
+
+  // Indices for each variable;
+  unsigned int c_var, zc_var, fc_var;
+  
+  Real beta; //regularization parameter
+  Real k; //diffusion coefficient
+  Real Rcoeff; //reaction coefficient
+  
+  //data-related stuff
+  std::vector<Point> datapts; 
+  std::vector<Real> datavals;
+	
+	int diff_subdomain_id, cd_subdomain_id, cdr_subdomain_id;
+	
+	//avoid assigning data point to two elements in on their boundary
+	std::vector<int> accounted_for;
+  
+  //options for QoI location and nature
+  int qoi_option;
+  Real qoi;
+  double getQoI(){ return qoi; }
+  
+};

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/element_qoi_derivative.C

@@ -1,0 +1,149 @@
+// General libMesh includes
+#include "libmesh/libmesh_common.h"
+#include "libmesh/elem.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/point.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/fe_interface.h"
+
+// Local includes
+#include "convdiff_mprime.h"
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// We only have one QoI, so we don't bother checking the qois argument
+// to see if it was requested from us
+void ConvDiff_MprimeSys::element_qoi_derivative (DiffContext &context,
+                                            const QoISet & /* qois */)
+{
+
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+	
+  FEMContext &ctxt = cast_ref<FEMContext&>(context);
+
+  //some cell-specific stuff, for u's family and p's family
+  FEBase* c_elem_fe = NULL; 
+  ctxt.get_element_fe( c_var, c_elem_fe );
+
+  // Element Jacobian * quadrature weights for interior integration
+  const std::vector<Real> &JxW = c_elem_fe->get_JxW();
+  
+  //at interior quadrature points
+  const std::vector<std::vector<Real> >& phi = c_elem_fe->get_phi();
+  const std::vector<std::vector<RealGradient> >& dphi = c_elem_fe->get_dphi();
+  
+  // Physical location of the quadrature points
+  const std::vector<Point>& qpoint = c_elem_fe->get_xyz();
+  
+  // The number of local degrees of freedom in each variable
+  const unsigned int n_c_dofs = ctxt.get_dof_indices( c_var ).size();
+  unsigned int n_qpoints = ctxt.get_element_qrule().n_points();
+
+  // Fill the QoI RHS corresponding to this QoI. Since this is the 0th QoI
+  // we fill in the [0][i] subderivatives, i corresponding to the variable index.
[…]

### 2016-05-24 practice/T_channel/with_reaction/psi_and_superadj/main.C

@@ -1,0 +1,244 @@
+// C++ includes
+#include <iomanip>
+
+// Basic include files
+#include "libmesh/equation_systems.h"
+#include "libmesh/error_vector.h"
+#include "libmesh/exodusII_io.h"
+#include "libmesh/kelly_error_estimator.h"
+#include "libmesh/mesh.h"
+#include "libmesh/mesh_generation.h"
+#include "libmesh/mesh_refinement.h"
+#include "libmesh/uniform_refinement_estimator.h"
+#include "libmesh/getpot.h"
+#include "libmesh/enum_xdr_mode.h"
+
+// The systems and solvers we may use
+#include "libmesh/diff_solver.h"
+#include "libmesh/steady_solver.h"
+#include "libmesh/newton_solver.h"
+
+#include "convdiff_mprime.h"
+#include "convdiff_primary.h"
+#include "convdiff_aux.h"
+
+#include "libmesh/dof_map.h" //alternate error breakdown
+#include "libmesh/direct_solution_transfer.h"
+
+//FOR DEBUGGING
+#include "libmesh/sparse_matrix.h" //DEBUG
+#include "libmesh/gmv_io.h" //DEBUG
+
+// The main program
+int main(int argc, char** argv)
+{
+
+  // Initialize libMesh
+  LibMeshInit init(argc, argv);
+	
+  // Parameters
+  GetPot infile("fem_system_params.in");
+  const bool transient                  = infile("transient", false);
+  unsigned int n_timesteps              = infile("n_timesteps", 1);
+  GetPot infileForMesh("convdiff_mprime.in");
+  std::string find_mesh_here            = infileForMesh("divided_mesh","mesh.exo");
+  bool doContinuation                   = infileForMesh("do_continuation",false);
+
+  Mesh mesh(init.comm());
+  Mesh mesh2(init.comm()); 
+  mesh.read(find_mesh_here);
+  mesh2.read(find_mesh_here); 
+  
+  mesh.print_info(); //DEBUG
+  
+  // Create an equation systems object.
+  EquationSystems equation_systems (mesh);
+  EquationSystems equation_systems_mix(mesh2);
+  
+  //name system
+  ConvDiff_PrimarySys & system_primary = 
+  	equation_systems.add_system<ConvDiff_PrimarySys>("ConvDiff_PrimarySys"); //for primary variables
+	ConvDiff_AuxSys & system_aux = 
[…]

### 2016-06-16 paper/numerical_experiments.tex
messing around with data points
more paper edits

@@
 %
-We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi model setting.
+We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting.
 We consider two kinds of multi-fidelity models, in a total of three experiments.
 In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+We examine how the element-wise distribution of the error estimate is affected by changes in sensor placement and in the QoI region.
 In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.
+\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
 
-In all experiments, starting the simulation with the low fidelity model, we seek to add regions of high fidelity, until the estimated relative error in the target QoI is less than 1$\%$. 
-\red{Don't forget to trim figures and convert them to pdfs!}
+%In all experiments, starting the simulation with the low fidelity model, we seek to add regions of high fidelity, until the estimated relative error in the target QoI is less than 1$\%$.
+
 %
@@
 %
-Algorithm~\ref{alg:refSeries} does not specify any particular method for localizing the error estimate.
-A naive approach would be to calculate the contribution to the estimated error by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element.
+Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate.
+A na\"{i}ve approach would be to calculate the error contribution by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element.
 While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.
 
-We instead use the alternative method described in \cite{vanOpstaletal15} to decompose the equivalent error estimate expression
+We instead use the alternative method described in \cite{vanOpstaletal15}.
+For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subset Q$ and $U_{LF}=U$.
+We note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as
 %
-\begin{multline}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
-\end{multline}
+\begin{equation}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
+\end{equation}
 %
-into error contributions from locally supported basis functions, and refine the model in those elements in the support of those basis functions with the largest error contributions.
+We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
+Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum_{i\in I}\varphi_i\lambda_i,\sum_{i\in I}\upvarphi_i x_i)$.
+The error estimate
+%
+\begin{equation}
+\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
+\end{equation}
+%
+where
+%
+\begin{equation}
+\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
+\end{equation}
+%
+can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
+The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
 Using this method, elements in which the high-fidelity model is already being used are not seen as continuing to contribute to the error in the QoI, with the possible exception of elements near the interfaces between the low-fidelity and high-fidelity regions.
-\red{Express this mathematically?}
 %
@@
 %
-In this section, we demonstrate the method derived in Section \ref{sec:deriv} for two models which differ in the physics included.
-We first describe the problem setup, and then present results from applying our approach.
+In this section, we consider a pair of models which differ in the physics included.
+In Section \ref{sec:cdvcdrSetup} we describe a baseline setup for a simple problem in 2D.
+Section \ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section \ref{sec:qoivdata} describes the results of changing the placement of observations or the QoI region from the baseline.
 %
@@
 %
-We consider a rectangular domain $\Omega$, defined as $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates.
+We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates.
 The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
@@
 %
-where the state $u$ is the species concentration and, $f(q)$ is a forcing field described by the parameters.
-The velocity field is $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$, while the diffusion coefficient $k_d = 0.1$ and, the reaction coefficient $k_r = -42.0$.
+where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters.
+We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively.
 The low-fidelity model,
@@
 
-The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$. The `true' forcing field is given by,
-a piecewise constant source term $f_{true}$,
+The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$.
+For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations).
+Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
 %
@@
 %
-Observations $d=(u(0.35,0.35),u(1.56,0.61),u(3.1,0.5))$ from three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with true forcing field.
-
 The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in Figure~\ref{fig:baseSetup}.
-Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is a regularization coefficient.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
 %
@@
 %
+
 For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements.
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
-The library offers both easy calculation of adjoint systems, error estimates and subdomain restricted variables.
-The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 76,806 degrees of freedom.
-No stabilization was required for these calculations, since the cell P\'{e}clet number never exceeded 0.1.
+\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 38,403 degrees of freedom.
+The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
 %
 %------------------------------------------------------------%
-\subsubsection{Results} \label{sec:cdvcdrBaseRef} 
+\subsubsection{Adaptive Model Refinement Results} \label{sec:cdvcdrBaseRef} 
 %------------------------------------------------------------%
@@
 
-Figure~\ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+Figure~\ref{fig:baseRef} shows the element-wise decomposition of the error estimate \red{no longer constant-per-element, what exactly does this plot show?}, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+\red{note that plots show absolute values, so valleys between lobes are actually transition between positive and negative...also note which decomp method used if comparing...}
 %
@@
     \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
+    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
     \vspace{-0.5\baselineskip}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
+    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
     \vspace{-0.5\baselineskip}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
-    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
+    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
     \vspace{-0.5\baselineskip}
@@
 Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}.
-It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.
-We also see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
+\red{It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.} We also see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
 %
@@
 \end{figure}
+%
+
+\red{Does it make sense to compare the breakdowns and error vs refinement of the different error localization schemes? Or is one so obviously better than the other that we don't need to show it?}
+
+%------------------------------------------------------------%
+\subsubsection{Interaction of Observations and QoI} \label{sec:qoivdata}
+%------------------------------------------------------------%
+%
+lalala
 %

### 2016-06-16 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/make_pretties_alt_err_all.m

@@ -1,0 +1,137 @@
+%plot error distribution and domain division for alternate error breakdown
+
+%save inverse map to mat file? toggle option for coarser or finer version
+
+close all;
+
+fntsize = 28;
+finer = true; %true = 250x50, false = 75x15
+
+refLevel = 'LF';
+dir_root = ['qoi3_sens3_alt_err_all/',refLevel,'/'];
+
+if finer
+    if exist('fine_dof_info.mat','file') == 2
+        load('fine_dof_info.mat')
+    else
+        dof_global = dlmread('../../psi_and_superadj/global_dof_map.dat',' ');
+        elem_cent = dlmread('../../psi_and_superadj/elem_centroids.dat',' ');
+        
+        %remove weird 0's at end, and redundant indices at beginning
+        dof_global = dof_global(:,2:end-1);
+        
+        maxdof = max(max(dof_global(:,2:end)));
+        
+        %inverse map - which dofs have which elements in support
+        inv_dof_global = zeros(maxdof+1,ceil(length(dof_global(:))/(maxdof+1)));
+        for dof = 0:maxdof
+            [row, ~] = find(dof_global == dof);
+            inv_dof_global(dof+1,1:length(row)) = row;
+        end
+        
+        %group global dofs which have same elements in support
+        [dof_group_elems,m,n] = unique(inv_dof_global,'rows');
+        dof_groups = zeros(size(dof_group_elems,1),6);
+        for ii = 1:size(dof_groups,1)
+            dof_groups(ii,:) = find(n == ii);
+        end
+        
+        save('fine_dof_info.mat','dof_groups','elem_cent')
+    end
+else
+    if exist('coarse_dof_info.mat','file') == 2
+       load('coarse_dof_info.mat')
+    else
+        dof_global = dlmread('../../psi_and_superadj/global_dof_map.dat',' ');
+        elem_cent = dlmread('../../psi_and_superadj/elem_centroids.dat',' ');
+        
+        %remove weird 0's at end, and redundant indices at beginning
+        dof_global = dof_global(:,2:end-1);
+        
+        maxdof = max(max(dof_global(:,2:end)));
+        
[…]

### 2016-06-16 paper/algorithms.tex
more paper edits
redoing vs qoi and vs data runs from thesis with new error breakdown

@@
 This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
-\red{We should include something about how to map error to elements to refine.} We present below an algorithm that accomplishes the above goals.
+Algorithm~\ref{alg:refSeries} describes this approach.
+Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $e_{I,i}$ and use this element-wise decomposition to guide formation \par\hskip\algorithmicindent of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
@@
 
-Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
-
 Algorithm~\ref{alg:refSeries} is applicable to a large class of models.
@@
 The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$, and the cost for computing the supplementary adjoint is $\orderof{6N}^{\gamma}$.
+\red{Solving the supplementary adjoint can be split into two $N\times N$ systems...}
 

### 2016-06-16 paper/numerical_experiments.tex
redoing vs qoi and vs data runs from thesis with new error breakdown

@@
 In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
-We examine how the element-wise distribution of the error estimate is affected by changes in sensor placement and in the QoI region.
+We examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
 In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
@@
 Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate.
-A na\"{i}ve approach would be to calculate the error contribution by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element.
+A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
 While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.
 
-We instead use the alternative method described in \cite{vanOpstaletal15}.
+We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
 For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subset Q$ and $U_{LF}=U$.
@@
 %
-\begin{equation}
+\begin{equation}\label{eq:basisblame}
 \varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
@@
 The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-Using this method, elements in which the high-fidelity model is already being used are not seen as continuing to contribute to the error in the QoI, with the possible exception of elements near the interfaces between the low-fidelity and high-fidelity regions.
+Using this method, elements in which the high-fidelity model is already being used are not interpreted as continuing to contribute to the error in the QoI and thus are not marked again for refinement.
+The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution.
 %
@@
 \includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
-\caption{Locations of the observations and the QoI region.}
+\caption{Locations of the observations and the QoI region. \red{Aaaah spatial coordinates are not $x$ and $y$! ($y$ is one of the auxiliary variables...)}}
 \label{fig:baseSetup}
@@
 We now present the results for solving the inference problem using Algorithm~\ref{alg:refSeries}.
-Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error.
-Based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI, is less than $1\%$.
+Once the QoI error estimate is calculated using Equation~(\ref{eq:finErrExp}), the error estimate is then decomposed into local contributions, as described in Equation~(\ref{eq:basisblame}).
+At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
+This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
 
-Figure~\ref{fig:baseRef} shows the element-wise decomposition of the error estimate \red{no longer constant-per-element, what exactly does this plot show?}, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-\red{note that plots show absolute values, so valleys between lobes are actually transition between positive and negative...also note which decomp method used if comparing...}
+Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+Each linear Langrange basis function's contribution is plotted at its nonzero node.
 %
@@
   \centering    
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
     \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
     \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
@@
   \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
+    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
     \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
@@
   \end{subfigure}
-\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
+\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
 \label{fig:baseRef}
@@
 %
-Note that since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except some elements near the interface, whose basis function have support in both regions.
+Note that the error contribution of each basis function whose support is entirely within the high-fidelity regions is zero.
 
-We see that model refinement is concentrated in the QoI region, and the data point closest to the QoI.
-In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is data point one.
+We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI.
+In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
 Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right.
-Therefore, for the calculation of the QoI, it is most important to refine the region near data point one, and the QoI region.
-We also observe that the region near the data points downstream from the QoI are not refined as much as the region immediately adjacent to the QoI.
-This indicates that the information from these two data points is not significant for the estimation of the QoI.
-\red{We should say a bit more about the refinement region here, and implications for experimental design ?}.
+Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region.
+After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.
 
 Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}.
-\red{It can be seen that the error estimates are close to the true error, and the error estimator has an effectivity index close to one.} We also see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
+In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
+We note that there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
 %
@@
 
-\red{Does it make sense to compare the breakdowns and error vs refinement of the different error localization schemes? Or is one so obviously better than the other that we don't need to show it?}
-
 %------------------------------------------------------------%
@@
 lalala
+%bigger steps in 3D problem because qoi region bigger?
+%usually says to refine in qoi region...but what if qoi region whole domain?
 %

### 2016-06-16 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/make_pretties_alt_err_all.m

@@ -3,12 +3,16 @@
 %save inverse map to mat file? toggle option for coarser or finer version
 
 close all;
+set(0,'defaultTextInterpreter','latex');
+set(0,'defaultAxesTickLabelInterpreter','latex');
+set(0,'defaultLegendInterpreter','latex');
 
-fntsize = 28;
+fntsize = 32;
 finer = true; %true = 250x50, false = 75x15
 
 refLevel = 'LF';
-dir_root = ['qoi3_sens3_alt_err_all/',refLevel,'/'];
+% dir_root = ['qoi3_sens3_alt_err_all/',refLevel,'/'];
+dir_root = 'vs_qoi_alt_err_all/qoi3_sens3/';
 
 if finer
     if exist('fine_dof_info.mat','file') == 2
@@ -69,7 +73,7 @@ else
 end
 
 %read in things to plot
-err_dof = dlmread([dir_root,'error_est_breakdown_basis_blame.dat'],' ');
+err_dof = dlmread([dir_root,'error_est_breakdown_basis_blame3.dat'],' ');
 divFileID = ...
   fopen([dir_root,'divvy.txt'],'r');
 divFormatSpec = '%d %d';
@@ -91,47 +95,49 @@ set(gca,'ytick',[])
 shading interp
 view(2)
 axis equal tight
-xlabel('x'); 
+xlabel('$x_1$'); 
 % ylabel('y'); 
-colorbar;
-title('Elemental Decomposition of QoI Error Estimate','FontWeight','normal')
+c = colorbar; set(c,'TickLabelInterpreter','latex');
+title('Local Contributions to QoI Error Estimate','FontWeight','normal')
 set(gca,'FontSize',fntsize); 
 set(findall(gcf,'type','text'),'FontSize',fntsize)
 % set(gcf,'PaperPositionMode','auto','Position',[66 253 1535 297])
-set(gcf,'PaperPositionMode','auto','Position',[66 164 1535 383])
+% set(gcf,'PaperPositionMode','auto','Position',[66 140 1535 407])
+set(gcf,'PaperPositionMode','auto','Position',[88 202 1336 409])
 % print(h,[dir_root, 'err_breakdown_', refLevel],'-depsc');
 print(h,[dir_root, 'err_breakdown_', refLevel],'-dpng','-r300')
 
-%% plot divvy
-
-if divFileID ~= -1
[…]

### 2016-06-18 paper/numerical_experiments.tex
more paper edits

@@
 \begin{figure}[h!]
+\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
 \centering
@@
 We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI.
-In the first elemental decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
+In the first decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
 Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
+\includegraphics[width=0.7\textwidth]{baseSeries/err_est.pdf}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.\red{does this even have enough points to warrant a graph?
+or would a table be better?}}
 \label{fig:baseErr}
@@
 %
-lalala
-%bigger steps in 3D problem because qoi region bigger?
-%usually says to refine in qoi region...but what if qoi region whole domain?
+The error estimate decomposition (\ref{eq:basisblame}) suggests the use of the high-fidelity model in areas of the domain that are important to the interaction of the observations and QoI; the interaction of these two can be complex, and the areas suggested for refinement may be nonintuitive.
+To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region.
+For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate.
+However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased, but did not consistently increase or decrease with the number of data points.
+
+The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}.
+The bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger.
+Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier.
+As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.
+
+\begin{figure}
+\captionsetup[subfigure]{justification=centering}
+\centering
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/setup_5_3.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/setup_7_3.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/setup_3_3.png}
+    \caption{Locations of observations and QoI region $\Omega_I$}
+    \label{subfig:obsSetup}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_0.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_0.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_0.png}
+    \caption{MF$_0$ \\ ($0\%$ HF)}
+    \label{subfig:obsLF}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_1.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_1.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_1.png}
+    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_2.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_2.png}
+    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_2.png}
+    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
+    \label{subfig:obsMFlast}
+  \end{subfigure}
+  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
+  \label{fig:qoiStudy}
+\end{figure}
+
+The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}.
+Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger.
+Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region.
+However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases.
+The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.
+
+\begin{figure}
+\captionsetup[subfigure]{justification=centering}
+\centering
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/setup_3_10.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/setup_3_5.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/setup_3_3.png}
+    \caption{Locations of observations and QoI region $\Omega_I$}
+    \label{subfig:obsSetup2}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_0.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_0.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_0.png}
+    \caption{MF$_0$ \\ ($0\%$ HF)}
+    \label{subfig:obsLF2}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_1.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_1.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_1.png}
+    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.20\textwidth}
+  \centering
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_2.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_2.png}
+    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_2.png}
+    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
+    \label{subfig:obsMFlast2}
+  \end{subfigure}
+  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF2}-\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\subref{subfig:obsSetup2})) and varying observations (teal points in (\subref{subfig:obsSetup2})).}
+  \label{fig:dataStudy}
+\end{figure}
+
 %
@@
 %
+%bigger steps in 3D problem because qoi region bigger?
 \subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}

### 2016-06-18 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/make_pretties_alt_err_all.m

@@ -1,7 +1,5 @@
 %plot error distribution and domain division for alternate error breakdown
 
-%save inverse map to mat file? toggle option for coarser or finer version
-
 close all;
 set(0,'defaultTextInterpreter','latex');
 set(0,'defaultAxesTickLabelInterpreter','latex');

### 2016-06-18 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/vs_qoi_vs_data_alt_err_all/make_vert_figs.m

@@ -1,0 +1,119 @@
+%plot error distribution and setup (vertical, for vs-qoi and vs-data)
+
+close all;
+set(0,'defaultTextInterpreter','latex');
+set(0,'defaultAxesTickLabelInterpreter','latex');
+set(0,'defaultLegendInterpreter','latex');
+
+fntsize = 28;
+maxref = 3; %LF = 0
+
+numSens = 3; %3, 5, or 10
+qoitype = 5; %3, 5, or 7
+
+dir_root = ['qoi',num2str(qoitype),'_sens',num2str(numSens),'/'];
+
+switch qoitype
+    case 3
+        qoiptsx = [0.625 0.875 0.875 0.625]; %qoi3
+        qoiptsy = [0.375 0.375 0.625 0.625]; %qoi3
+    case 5
+        qoiptsx = [0 5 5 0]; %qoi5
+        qoiptsy = [0 0 1 1]; %qoi5
+    case 7
+        qoiptsx = [0.625 1.5 1.5 0.625]; %qoi7
+        qoiptsy = [0.25 0.25 0.75 0.75]; %qoi7
+end
+switch numSens
+    case 3
+        dataptsx = [0.35 1.56 3.1];
+        dataptsy = [0.35 0.61 0.5];
+    case 5
+        dataptsx = [0.35 0.98 1.56 2.46 3.1];
+        dataptsy = [0.35 0.51 0.61 0.37 0.5];
+    case 10
+        dataptsx = [0.35 0.98 1.11 1.56 2.23 2.46 2.92 3.1 3.49 4.79];
+        dataptsy = [0.35 0.51 0.89 0.61 0.51 0.37 0.7 0.5 0.76 0.26];
+end
+
+if exist('../fine_dof_info.mat','file') == 2
+    load('../fine_dof_info.mat')
+else
+    dof_global = dlmread('../../psi_and_superadj/global_dof_map.dat',' ');
+    elem_cent = dlmread('../../psi_and_superadj/elem_centroids.dat',' ');
+
+    %remove weird 0's at end, and redundant indices at beginning
+    dof_global = dof_global(:,2:end-1);
+
+    maxdof = max(max(dof_global(:,2:end)));
+
+    %inverse map - which dofs have which elements in support
+    inv_dof_global = zeros(maxdof+1,ceil(length(dof_global(:))/(maxdof+1)));
+    for dof = 0:maxdof
+        [row, ~] = find(dof_global == dof);
[…]

### 2016-06-19 paper/numerical_experiments.tex
scalar vs field with same fine mesh as other experiments...will try with same reaction coeff as others too...

@@
 The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}.
-Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger.
+Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger.
 Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region.

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_aux.C

@@ -320,10 +320,7 @@ bool ConvDiff_AuxSys::element_time_derivative (bool request_jacobian, DiffContex
     
 	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
 	  	Point data_point = datapts[dnum];
-	  	if(ctxt.get_elem().contains_point(data_point) && (accounted_for[dnum]>=ctxt.get_elem().id()) ){
-	  	
-	  		//help avoid double-counting if data from edge of elements, but may mess with jacobian check
-	  		accounted_for[dnum] = ctxt.get_elem().id(); 
+	  	if(dataelems[dnum] == ctxt.get_elem().id()){
 	  		
 	  		Number auxc_pointy = ctxt.point_value(aux_c_var, data_point);
 	  		

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_aux.h

@@ -1,5 +1,6 @@
 #include "libmesh/fem_system.h"
 #include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
 
 using namespace libMesh;
 
@@ -78,7 +79,14 @@ public:
 				fclose(fp);
 	  	}
 	  }
-	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
   }
 
   // System initialization
@@ -104,6 +112,7 @@ public:
   //data-related stuff
   std::vector<Point> datapts; 
   std::vector<Real> datavals;
+  std::vector<dof_id_type> dataelems;
   
   //velocity field
 	std::vector<Real> x_pts;
@@ -111,9 +120,6 @@ public:
 	std::vector<std::vector<NumberVectorValue> > vel_field;
 	
 	int scalar_subdomain_id, field_subdomain_id;
-	
-	//avoid assigning data point to two elements in on their boundary
-	std::vector<int> accounted_for;
   
   //options for QoI location and nature
   int qoi_option;

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_mprime.C

@@ -379,10 +379,7 @@ std::cout << "\n\n\n WHY ARE YOU HERE?!?!?\n\n" << std::endl;
     
 	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
 	  	Point data_point = datapts[dnum];
-	  	if(ctxt.get_elem().contains_point(data_point) && (accounted_for[dnum]>=ctxt.get_elem().id()) ){
-	  	
-	  		//help avoid double-counting if data from edge of elements, but may mess with jacobian check
-	  		accounted_for[dnum] = ctxt.get_elem().id(); 
+	  	if(dataelems[dnum] == ctxt.get_elem().id()){
 	  		
 	  		Number cpred = ctxt.point_value(c_var, data_point);
 	  		Number cstar = datavals[dnum];

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_mprime.h

@@ -1,5 +1,6 @@
 #include "libmesh/fem_system.h"
 #include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
 
 using namespace libMesh;
 
@@ -78,7 +79,14 @@ public:
 				fclose(fp);
 	  	}
 	  }
-	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
   }
 
   // System initialization
@@ -122,6 +130,7 @@ public:
   //data-related stuff
   std::vector<Point> datapts; 
   std::vector<Real> datavals;
+  std::vector<dof_id_type> dataelems;
   
   //velocity field
 	std::vector<Real> x_pts;
@@ -133,9 +142,6 @@ public:
 	//DEBUG
 	std::vector<Real> MHF_psiLF;
 	std::vector<Real> MLF_psiLF;
-	
-	//avoid assigning data point to two elements in on their boundary
-	std::vector<int> accounted_for;
   
   //options for QoI location and nature
   int qoi_option;

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_primary.C

@@ -277,10 +277,7 @@ bool ConvDiff_PrimarySys::element_time_derivative (bool request_jacobian, DiffCo
     
 	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
 	  	Point data_point = datapts[dnum];
-	  	if(ctxt.get_elem().contains_point(data_point) && (accounted_for[dnum]>=ctxt.get_elem().id()) ){
-	  	
-	  		//help avoid double-counting if data from edge of elements, but may mess with jacobian check
-	  		accounted_for[dnum] = ctxt.get_elem().id(); 
+	  	if(dataelems[dnum] == ctxt.get_elem().id()){
 	  		
 	  		Number cpred = ctxt.point_value(c_var, data_point);
 	  		Number cstar = datavals[dnum];

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split/convdiff_primary.h

@@ -1,5 +1,6 @@
 #include "libmesh/fem_system.h"
 #include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
 
 using namespace libMesh;
 
@@ -78,7 +79,14 @@ public:
 				fclose(fp);
 	  	}
 	  }
-	  accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
+	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
   }
 
   // System initialization
@@ -103,6 +111,7 @@ public:
   //data-related stuff
   std::vector<Point> datapts; 
   std::vector<Real> datavals;
+  std::vector<dof_id_type> dataelems;
   
   //velocity field
 	std::vector<Real> x_pts;
@@ -110,9 +119,6 @@ public:
 	std::vector<std::vector<NumberVectorValue> > vel_field;
 	
 	int scalar_subdomain_id, field_subdomain_id;
-	
-	//avoid assigning data point to two elements in on their boundary
-	std::vector<int> accounted_for;
   
   //options for QoI location and nature
   int qoi_option;

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/convdiff_mprime.C

@@ -308,10 +308,7 @@ bool ConvDiff_MprimeSys::element_time_derivative (bool request_jacobian, DiffCon
     
 	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
 	  	Point data_point = datapts[dnum];
-	  	if(ctxt.get_elem().contains_point(data_point) && (accounted_for[dnum]>=ctxt.get_elem().id()) ){
-	  	
-	  		//help avoid double-counting if data from edge of elements, but may mess with jacobian check
-	  		accounted_for[dnum] = ctxt.get_elem().id(); 
+	  	if(dataelems[dnum] == ctxt.get_elem().id()){
 	  		
 	  		Number cpred = ctxt.point_value(c_var, data_point);
 	  		Number cstar = datavals[dnum];

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/convdiff_mprime.h

@@ -2,6 +2,7 @@
 #include "libmesh/getpot.h"
 #include "libmesh/fem_context.h"
 #include "libmesh/equation_systems.h"
+#include "libmesh/point_locator_tree.h"
 
 #include <numeric>
 
@@ -70,8 +71,13 @@ public:
 		sadj_auxc_point_stash.resize(datavals.size()); //DEBUG
 		sadj_c_point_stash.resize(datavals.size()); //DEBUG
 		
-		accounted_for.assign(datavals.size(), this->get_mesh().n_elem()+100);
-
+		//find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
   }
 
   // System initialization
@@ -129,6 +135,7 @@ public:
   //data-related stuff
   std::vector<Point> datapts; 
   std::vector<Real> datavals;
+  std::vector<dof_id_type> dataelems;
   
   //velocity field
 	std::vector<Real> x_pts;
@@ -149,9 +156,6 @@ public:
 	std::vector<std::vector<Real> > sadj_auxfc_stash; std::vector<std::vector<Gradient> > sadj_gradauxfc_stash;
 	std::vector<Real> sadj_auxc_point_stash; std::vector<Real> sadj_c_point_stash;
 	unsigned int debug_step; //if 1, fill up sadj stash; if 2, calculate half_sadj_resid
-	
-	//avoid assigning data point to two elements in on their boundary
-	std::vector<int> accounted_for;
 
   //options for QoI location and nature
   int qoi_option;

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/element_qoi.C

@@ -190,7 +190,7 @@ void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
     } //end of quadrature loop
   for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
 		Point data_point = datapts[dnum];
-		if(ctxt.get_elem().contains_point(data_point)){
+		if(dataelems[dnum] == ctxt.get_elem().id()){
 			Number cpred = ctxt.point_value(c_var, data_point);
 			Number cstar = datavals[dnum];
 			

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/element_qoi_derivative.C

@@ -142,7 +142,7 @@ void ConvDiff_MprimeSys::element_qoi_derivative (DiffContext &context,
   for(unsigned int dnum=0; dnum<datavals.size(); dnum++)
     {
       Point data_point = datapts[dnum];
-      if(ctxt.get_elem().contains_point(data_point)){
+      if(dataelems[dnum] == ctxt.get_elem().id()){
 				Number cpred = ctxt.point_value(c_var, data_point);
 				Number cstar = datavals[dnum];
 				Number auxc_pointy = ctxt.point_value(aux_c_var, data_point);

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/get_divvy.m

@@ -2,7 +2,7 @@
 
 close all;
 
-refPortion = 0.57; %total, not in addition to previous
+refPortion = 0.65; %total, not in addition to previous
     %portion of basis functions; portion of elements will be slightly off
 fntsize = 16;
 
@@ -130,9 +130,9 @@ set(gcf,'PaperPositionMode','auto','Position',[66 253 1535 297])
 print(h,'err_breakdown','-dpng','-r300')
 
 %plot new domain division
-figure;
-% squish = reshape(divvynew(:,2),250,50)';
-squish = reshape(divvynew(:,2),75,15)';
+h = figure;
+squish = reshape(divvynew(:,2),250,50)';
+% squish = reshape(divvynew(:,2),75,15)';
 map = [91, 146, 229; 227, 38, 54]/255;
 imagesc([0 5],[0 1],-squish); 
 set(gca,'YDir','normal','Ticklength',[0 0]); colormap(map);
@@ -145,6 +145,7 @@ hold on;
 % contour(reshape(elem_cent(:,1),250,50),...
 %     reshape(elem_cent(:,2),250,50),...
 %     reshape(divvy,250,50),[0 1],'k','LineWidth',1)
-contour(reshape(elem_cent(:,1),75,15),...
-    reshape(elem_cent(:,2),75,15),...
-    reshape(divvy,75,15),[0 1],'k','LineWidth',1)
+% contour(reshape(elem_cent(:,1),75,15),...
+%     reshape(elem_cent(:,2),75,15),...
+%     reshape(divvy,75,15),[0 1],'k','LineWidth',1)
+print(h,'divvy','-dpng','-r300')

### 2016-06-19 practice/T_channel/diff_param_res/with_reaction/get_super_adj_basis_blame/main.C

@@ -419,12 +419,10 @@ int main(int argc, char** argv)
 		sol_transfer.transfer(system.variable(system.variable_number("aux_fc")),
 			system2.variable(system2.variable_number("aux_fc")));
 		std::string write_error_basis_blame = infileForMesh("error_est_output_file_basis_blame", "error_est_breakdown_basis_blame.dat");
-		AutoPtr<NumericVector<Number> > adjresid_basis_blame = system.solution->clone();
-		adjresid_basis_blame->zero();
+		AutoPtr<NumericVector<Number> > adjresid_basis_blame = system.solution->zero_clone();
 		adjresid_basis_blame->pointwise_mult(*system.rhs,dual_solution); 
 	  std::cout << "\n -0.5*M'_HF(psiLF)(superadj): " << -0.5*adjresid_basis_blame->sum() << std::endl; //check
-	  AutoPtr<NumericVector<Number> > LprimeHF_psiLF_basis_blame = system.solution->clone();
-	  LprimeHF_psiLF_basis_blame->zero();
+	  AutoPtr<NumericVector<Number> > LprimeHF_psiLF_basis_blame = system.solution->zero_clone();
 	  LprimeHF_psiLF_basis_blame->pointwise_mult(*system.rhs,*system2.solution);
 	  std::cout << " L'_HF(psiLF): " << LprimeHF_psiLF_basis_blame->sum() << " vs " 
 	    << system.get_MHF_psiLF()-system.get_MLF_psiLF() << std::endl; //check

### 2016-06-20 paper/algorithms.tex
small paper changes, new plotting scripts

@@
 The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}.
-The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$, and the cost for computing the supplementary adjoint is $\orderof{6N}^{\gamma}$.
-\red{Solving the supplementary adjoint can be split into two $N\times N$ systems...}
+The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$.
+\red{The parts of the supplementary adjoint corresponding to the primary and auxiliary variables can be solved separately, and thus the cost of computing the supplementary adjoint is also $\orderof{3N}^{\gamma}$.}
 
@@
 \label{eq:cost_adapt}
-C_{MF} &= \sum_{i=1}^{T}L_{i}(3N)^{\gamma} + 1(3N)^{\gamma} + 2^{\gamma}(3N)^{\gamma} \nonumber \\
-&= \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) (3N)^{\gamma}
+C_{MF} &= \sum_{i=1}^{T}L_{i}(3N)^{\gamma} + 1(3N)^{\gamma} + 2(3N)^{\gamma} \nonumber \\
+&= \sum_{i=1}^{T} (L_i + 3) (3N)^{\gamma}
 \end{align}
@@
 \label{eq:cost_compare_0}
-C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 1 + 2^{\gamma}) < \sum\limits_{i=1}^{C}K_{i}
+C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 3) < \sum\limits_{i=1}^{C}K_{i}
 \end{equation}
 %
-If the low and multi-fidelity models are linear or nonlinear in a very small region $L_i \approx 1$, and we have the following condition,
+If the low and multi-fidelity models are linear, or nonlinear in a very small region, then $L_i \approx 1$, and we have the following condition,
 %
@@
 \label{eq:cost_compare_1}
-T < \frac{\sum\limits_{i=1}^{C}K_{i}}{2 + 2^{\gamma}}
+T < \frac{\sum\limits_{i=1}^{C}K_{i}}{4},
 \end{equation}
 % 
-The bound on $T$ will be strictest if Gaussian elimination is used, with $\gamma = 3$, giving $T < \frac{\sum\limits_{i=1}^{C}K_{i}}{10}$.
+for the adaptive algorithm to be less costly than solving the high-fidelity inverse problem.
+%The bound on $T$ will be strictest if Gaussian elimination is used, with $\gamma = 3$, giving $T < \frac{\sum\limits_{i=1}^{C}K_{i}}{10}$.
 %

### 2016-06-20 paper/numerical_experiments.tex
small paper changes, new plotting scripts

@@
 We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subset Q$ and $U_{LF}=U$.
-We note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as
+For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
+Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as
 %
@@
 \includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
-\caption{Locations of the observations and the QoI region. \red{Aaaah spatial coordinates are not $x$ and $y$! ($y$ is one of the auxiliary variables...)}}
+\caption{Locations of the observations and the QoI region.}
 \label{fig:baseSetup}
@@
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
-\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 50 and 250 elements along the short and long boundaries, respectively, for a total of 12,500 elements, resulting in a total of 38,403 degrees of freedom.
+\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
 The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
@@
 In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
-We note that there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
+We note that, in general, there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
 %
@@
 \centering
-\includegraphics[width=0.7\textwidth]{baseSeries/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.\red{does this even have enough points to warrant a graph?
-or would a table be better?}}
+\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
 \label{fig:baseErr}
@@
 The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}.
-The bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are choesn, so the proportion of additional refined elements in each iteration is slightly larger.
+The bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
 Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier.
@@
 %
+It is not necessary for the low- and high-fidelity models to differ in the physics included.
+In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
+%
 \subsubsection{Problem Setup}
 %
-\subsubsection{Results}
+We consider the same high-fidelity model as in Section~\ref{sec:cdvcdr}:
+\begin{equation}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
+\end{equation}
+with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -4.2$. The low-fidelity model
+\begin{equation}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
+\end{equation}
+differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
+Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain.
+For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in Section~\ref{sec:cdvcdr}.
+As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
 %
-%bigger steps in 3D problem because qoi region bigger?
+\subsubsection{Adaptive Model Refinement Results}
+%
+As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition of the error estimate (\ref{eq:basisblame}) is used to select additional regions of the domain in which to use the high-fidelity model.
+The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
+With each iteration, an additional $10\%$ of the elements are marked for refinement.
+This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
+
+Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+Each linear Langrange basis function's contribution is plotted at its nonzero node.
+
+%
 \subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
+%
+\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...}
 %
@@
 In other words, on using Algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
+%
+\subsection{Convection-Diffusion(-Reaction) in 3D} 
+%previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences
+%bigger steps in 3D problem because qoi region bigger?

### 2016-06-20 practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r42_basis_blame_all_fine/plot_err.m

@@ -7,12 +7,12 @@ set(0,'defaultTextInterpreter','latex');
 set(0,'defaultAxesTickLabelInterpreter','latex');
 set(0,'defaultLegendInterpreter','latex');
 
-errEst = [-0.0018293936; -9.84E-005; 1.41E-005];
-errTrue = [-0.0016895481; -0.0001003636; 1.32748289514697E-005];
-qoi = [0.0050801785; 0.0034909939; 0.0033773555];
+errEst = [0.0022021921; -7.03E-004; 3.57E-003; 5.81E-004; 8.30E-004; 3.92E-004; 1.69E-005];
+errTrue = [0.0018260025; 0.0006062894; 0.0008967747; 0.00060295; 0.0008887619; 0.0004020916; 1.69478960580405E-005];
+qoi = [0.0018016233; 0.0030213363; 0.002730851; 0.0030246758; 0.0027388639; 0.0032255341; 0.0036106779];
 relErrEst = abs(errEst./qoi);
 relErrTrue = abs(errTrue./qoi);
-ref = [0; 0.0578; 0.105];
+ref = [0; 0.1168; 0.206; 0.3032; 0.4049; 0.5006; 0.6023];
 
 figure('Position',[470 580 765 205])
 plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',1.5);

### 2016-06-20 practice/T_channel/make_setup2.m

@@ -1,0 +1,51 @@
+%to create "setup" plots (version for paper)
+close all;
+
+close all;
+set(0,'defaultTextInterpreter','latex');
+set(0,'defaultAxesTickLabelInterpreter','latex');
+set(0,'defaultLegendInterpreter','latex');
+
+fntsize = 28;
+
+fig_h = figure(1);
+set(gcf,'Position',[110 270 1390 420])
+axes1 = axes('Parent',fig_h,'FontSize',fntsize);
+hold on;
+
+%background
+patch([0 5 5 0],[0 0 1 1],'w','edgecolor',[0 0 0],'edgealpha',1)
+
+% %QoI region
+ptsy = [0.625 0.875 0.875 0.625]; %qoi3
+ptsx = [0.375 0.375 0.625 0.625]; %qoi3
+% ptsy = [2.375 2.625 2.625 2.375]; %qoi6
+% ptsx = [0.375 0.375 0.625 0.625]; %qoi6
+% ptsy = [0.625 1.5 1.5 0.625]; %qoi7
+% ptsx = [0.25 0.25 0.75 0.75]; %qoi7
+% ptsy = [0 5 5 0]; %qoi5
+% ptsx = [0 0 1 1]; %qoi5
+subreg = patch(ptsy, ptsx,...
+  [0.87843137254902 0.690196078431373 1], ...
+  'EdgeColor','none'); 
+
+%data points
+ptsy = [0.35 1.56 3.1];
+ptsx = [0.35 0.61 0.5];
+% ptsy = [0.35 0.98 1.56 2.46 3.1];
+% ptsx = [0.35 0.51 0.61 0.37 0.5];
+% ptsy = [0.35 0.98 1.11 1.56 2.23 2.46 2.92 3.1 3.49 4.79];
+% ptsx = [0.35 0.51 0.89 0.61 0.51 0.37 0.7 0.5 0.76 0.26];
+datapts = scatter(ptsy,ptsx,80, ...
+  'MarkerEdgeColor',[0 .5 .5],'MarkerFaceColor',[0 .7 .7]);
+
+leg_h = legend([subreg datapts],{' $\Omega_I$',' Observations'},...
+  'Position',[0.776238418335466, 0.412506804633401,...
+   0.217572463768116, 0.321180555555556]);
+set(leg_h,'FontSize',fntsize)
+
+ylabel('$x_2$','FontSize',fntsize);
+xlabel('$x_1$','FontSize',fntsize);
[…]

### 2016-06-21 paper/numerical_experiments.tex
finished adding scalar vs field section

@@
 In this section, we consider a pair of models which differ in the physics included.
-In Section \ref{sec:cdvcdrSetup} we describe a baseline setup for a simple problem in 2D.
-Section \ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section \ref{sec:qoivdata} describes the results of changing the placement of observations or the QoI region from the baseline.
+In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple problem in 2D.
+Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of observations or the QoI region from the baseline.
 %
@@
 It is not necessary for the low- and high-fidelity models to differ in the physics included.
+A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity.
 In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
@@
 \end{equation}
-with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -4.2$. The low-fidelity model
+with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
 \begin{equation}
@@
 %
-As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition of the error estimate (\ref{eq:basisblame}) is used to select additional regions of the domain in which to use the high-fidelity model.
+As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition (\ref{eq:basisblame}) of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
 The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
@@
 
-Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+Figure~\ref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
 Each linear Langrange basis function's contribution is plotted at its nonzero node.
+%
+\begin{figure}[h!]
+\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
+\centering
+\begin{subfigure}[b]{\textwidth}
+\centering
+	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.png}
+  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_LF.png}
+  \vspace{-0.7\baselineskip}
+  \caption{MF$_0$ ($0\%$ HF)}
+  \vspace{0.8\baselineskip}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+	\centering
+	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.png}
+  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF01.png}
+  \vspace{-0.7\baselineskip}
+  \caption{MF$_1$ ($10\%$ HF)}
+  \vspace{0.8\baselineskip}
+\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+  \centering
+  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.png}
+  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF02.png}
+  \vspace{-0.7\baselineskip}
+  \caption{MF$_2$ ($20\%$ HF)}
+  \vspace{0.8\baselineskip}
+\end{subfigure}
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_3$ ($30\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_4$ ($40\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_5$ ($50\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+\begin{subfigure}[b]{\textwidth}
+	\centering
+	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.png}
+  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF06.png}
+  \vspace{-0.7\baselineskip}
+  \caption{MF$_6$ ($60\%$ HF)}
+\end{subfigure}
+\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.
+The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
+\label{fig:svfRef}
+\end{figure}
+%
+Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
+This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field throughout all low-fidelity regions is constant.
+
+The corresponding true and estimated absolute errors in the QoI are shown in Figure~\ref{fig:svfErr}.
+%
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
+\label{fig:svfErr}
+\end{figure}
+%
+In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
+The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
+We also see that in this case, compared to the example in Section~\ref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+\red{This example seems very close to mesh-refinement, which we estabilished would be more efficient using the original Becker+Vexler method.
+Do we still want to include this?}
 

### 2016-06-21 practice/T_channel/diff_param_res/with_reaction/long_channel_stash/make_pretties_alt_err_all.m

@@ -1,0 +1,141 @@
+%plot error distribution and domain division for alternate error breakdown
+
+close all;
+set(0,'defaultTextInterpreter','latex');
+set(0,'defaultAxesTickLabelInterpreter','latex');
+set(0,'defaultLegendInterpreter','latex');
+
+fntsize = 32;
+finer = true; %true = 250x50, false = 75x15
+
+refLevel = 'MF02';
+dir_root = ['qoi3_setup02_r42_basis_blame_all_fine/',refLevel,'/'];
+% dir_root = 'vs_qoi_alt_err_all/qoi3_sens3/';
+
+if finer
+    if exist('fine_dof_info.mat','file') == 2
+        load('fine_dof_info.mat')
+    else
+        dof_global = dlmread('../../psi_and_superadj/global_dof_map.dat',' ');
+        elem_cent = dlmread('../../psi_and_superadj/elem_centroids.dat',' ');
+        
+        %remove weird 0's at end, and redundant indices at beginning
+        dof_global = dof_global(:,2:end-1);
+        
+        maxdof = max(max(dof_global(:,2:end)));
+        
+        %inverse map - which dofs have which elements in support
+        inv_dof_global = zeros(maxdof+1,ceil(length(dof_global(:))/(maxdof+1)));
+        for dof = 0:maxdof
+            [row, ~] = find(dof_global == dof);
+            inv_dof_global(dof+1,1:length(row)) = row;
+        end
+        
+        %group global dofs which have same elements in support
+        [dof_group_elems,m,n] = unique(inv_dof_global,'rows');
+        dof_groups = zeros(size(dof_group_elems,1),6);
+        for ii = 1:size(dof_groups,1)
+            dof_groups(ii,:) = find(n == ii);
+        end
+        
+        save('fine_dof_info.mat','dof_groups','elem_cent')
+    end
+else
+    if exist('coarse_dof_info.mat','file') == 2
+       load('coarse_dof_info.mat')
+    else
+        dof_global = dlmread('../../psi_and_superadj/global_dof_map.dat',' ');
+        elem_cent = dlmread('../../psi_and_superadj/elem_centroids.dat',' ');
+        
[…]

### 2016-06-21 paper/numerical_experiments.tex
small paper edits

@@
 %
-We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting.
-We consider two kinds of multi-fidelity models, in a total of three experiments.
-In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
-We examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
+We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in Section~\ref{sec:errLocal}.
+We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
+In Section~\ref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+We apply Algorithm~\ref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
+In Section~\ref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
+\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.} Finally, in Section~\ref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using Algorithm~\ref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
 
@@
 
-%
-\subsection{Error Estimate Localization}
-%
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Error Estimate Localization} \label{sec:errLocal}
+%------------------------------------------------------------------------------------------------------------------------%
 Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate.
@@
 The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution.
-%
+%------------------------------------------------------------------------------------------------------------------------%
 \subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
-%
+%------------------------------------------------------------------------------------------------------------------------%
 In this section, we consider a pair of models which differ in the physics included.
-In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple problem in 2D.
-Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of observations or the QoI region from the baseline.
+In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
+Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
 %
@@
 %
-The QoI we wish to calculate is the integral of the state,
+Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
 %
@@
 
-%
-\subsection{Constant vs Field Parameters}
-%
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Constant vs Field Parameters} \label{sec:constvfield}
+%------------------------------------------------------------------------------------------------------------------------%
 It is not necessary for the low- and high-fidelity models to differ in the physics included.
@@
 In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
-%
+%------------------------------------------------------------%
 \subsubsection{Problem Setup}
-%
+%------------------------------------------------------------%
 We consider the same high-fidelity model as in Section~\ref{sec:cdvcdr}:
@@
 As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
-%
+
+Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that when seeking adaptive mesh refinement for the goal-oriented inverse problem, it is more efficient to use the approach discussed in \cite{BecVex05}.
+%------------------------------------------------------------%
 \subsubsection{Adaptive Model Refinement Results}
-%
+%------------------------------------------------------------%
 As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition (\ref{eq:basisblame}) of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
@@
 Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
-This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field throughout all low-fidelity regions is constant.
+This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
 
@@
 We also see that in this case, compared to the example in Section~\ref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-\red{This example seems very close to mesh-refinement, which we estabilished would be more efficient using the original Becker+Vexler method.
-Do we still want to include this?}
-
-%
+%------------------------------------------------------------------------------------------------------------------------%
 \subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
-%
-\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...}
-%
+%------------------------------------------------------------------------------------------------------------------------%
+\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...if we want to make a 'robustness' argument, then merge with whatever vikram writes about operator continuation interpretation?
+%------------------------------------------------------------%
 \subsubsection{Results}
-%
+%------------------------------------------------------------%
 We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
@@
 From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
-%
+%------------------------------------------------------------%
 \subsubsection{Computational Complexity}
-%
+%------------------------------------------------------------%
 We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
@@
 In other words, on using Algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
-%
-\subsection{Convection-Diffusion(-Reaction) in 3D} 
+}
+
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Convection-Diffusion(-Reaction) in 3D} \label{sec:cdvcdr3D}
+%------------------------------------------------------------------------------------------------------------------------%
+
+In the previous examples, while the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time.
+In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
+In Section~\ref{sec:setup3D} we describe the setup of the models and their inverse problems, and in Section~\ref{sec:ref3D} we describe the results of applying Algorithm~\ref{alg:refSeries} to this pair of models.
+
 %previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences

### 2016-06-21 paper/numerical_experiments.tex
stash paper progress

@@
 
-In the previous examples, while the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time.
+In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time.
 In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
@@
 
+%------------------------------------------------------------%
+\subsubsection{Problem Setup} \label{sec:setup3D}
+%------------------------------------------------------------%
+
+The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively.
+We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively.
+The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
+%
+\begin{subequations}
+\label{eq:cdvcdrHF3D}
+\begin{align}
+\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
+u = 5 \quad &\text{on } \partial \Omega_{west}, \\
+\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
+\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
+\end{align} 
+\end{subequations}
+%
+where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field.
+The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day.
+Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}.
+We have porosity $n=0.1$.
+The reaction coefficient is $k_r=4.2\cdot10^{-3}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
+Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
+
+The low-fidelity model,
+%
+\begin{equation}
+\nabla\cdot(n\vec{V}u - nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
+\end{equation}
+%
+differs in the removal of both the reaction term and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$.
+The boundary conditions remain unchanged.
+As in the previous examples in Section~\ref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where (\ref{eq:HFeq3D}) and (\ref{eq:LFeq3D}) are solved, respectively.
+The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.
+
+The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$.
+Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a domain twice the length in the $x_1$ and $x_2$ directions.
+The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}.
+We again require regularization, and use the regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
+%
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.3\textwidth]{placeholder.pdf}
+\caption{Locations of the observations and the QoI region.}
+\label{fig:setup3D}
+\end{figure}
+%
+We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements.
+The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom.
+The cell P\'{e}clet is small enough to not require stabilization.
+
+%------------------------------------------------------------%
+\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D}
+%------------------------------------------------------------%
+
 %previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences

### 2016-06-22 paper/numerical_experiments.tex
added 3D setup figures
small edits

@@
 We have porosity $n=0.1$.
-The reaction coefficient is $k_r=4.2\cdot10^{-3}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
+The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
 Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
@@
 The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$.
-Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a domain twice the length in the $x_1$ and $x_2$ directions.
+Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions.
 The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}.
-We again require regularization, and use the regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
+We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
 %
@@
 \centering
-\includegraphics[width=0.3\textwidth]{placeholder.pdf}
-\caption{Locations of the observations and the QoI region.}
+\includegraphics[width=0.4\textwidth]{series3D/setup_arial_nolegend.pdf} \hfill
+\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
+\vspace{\baselineskip}
+\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
+\caption{Three views of the locations of the observations and the QoI region.}
 \label{fig:setup3D}
@@
 
+We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances.
+At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement.
+All simulations are run on a single processor.
+Table~\ref{tab:ref3D} shows ...
+%
+\begin{tabular}{c|c|c|c|c|c}
+Case & $\%HF$ & QoI & Relative Error (Estimated) & Relative Error (Actual) & Time (s) \\
+LF & 0 & 1068856 &  &  &  \\
+MF01 & 16.7 &  &  &  &  \\
+MF02 & 29.0 &  &  &  &  \\
+MF03 & 42.3 &  &  &  &  \\
+HF & 100 & 547420 &  &  &  \\
+\caption{...}
+\end{tabular}
+
 %previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences

### 2016-06-22 paper/numerical_experiments.tex
camera angle for paraview processing of domain breakdown, script to convert error breakdown into exo for paraview processing as well

@@
 \begin{align}
-\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
+\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
 u = 5 \quad &\text{on } \partial \Omega_{west}, \\
@@
 %
+\begin{table}[h]
+\centering
 \begin{tabular}{c|c|c|c|c|c}
-Case & $\%HF$ & QoI & Relative Error (Estimated) & Relative Error (Actual) & Time (s) \\
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%HF$} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & \multirow{2}{*}{Time (s)} \\ 
+& & & (Estimated) & (Actual) & \\ \hline
 LF & 0 & 1068856 &  &  &  \\
@@
 HF & 100 & 547420 &  &  &  \\
-\caption{...}
 \end{tabular}
-
-%previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences
-%bigger steps in 3D problem because qoi region bigger?
+\caption{table of things}
+\end{table}

### 2016-06-22 practice/post_thesis/model_adaptivity_iso_vs_aniso/error_breakdown_to_exo/dummy_sys.h

@@ -1,0 +1,114 @@
+// DiffSystem framework files
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/equation_systems.h"
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+using namespace libMesh;
+
+// FEMSystem, TimeSolver and  NewtonSolver will handle most tasks,
+// but we must specify element residuals
+class DummySys : public FEMSystem
+{
+public:
+
+  // Constructor
+  DummySys(EquationSystems& es, const std::string& name_in, const unsigned int number_in):
+    FEMSystem(es, name_in, number_in){}
+
+  // System initialization
+  void init_data(){
+    const unsigned int dim = this->get_mesh().mesh_dimension();
+
+    GetPot infile("contamTrans.in");
+    unsigned int poly_order = infile("poly_order",1);
+    std::string fefamily = infile("fe_family", std::string("LAGRANGE"));
+
+    c_var = this->add_variable("local_error", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
+
+	  // Do the parent's initialization after variables and boundary constraints are defined
+	  FEMSystem::init_data();
+  }
+
+  // Context initialization
+  void init_context(DiffContext & context){
+    FEMContext &ctxt = cast_ref<FEMContext&>(context);
+
+    FEBase* c_elem_fe;
+    FEBase* c_side_fe;
+
+    ctxt.get_element_fe(c_var, c_elem_fe);
+
+	  c_elem_fe->get_JxW();
+	  c_elem_fe->get_phi();
+	  c_elem_fe->get_xyz();
+  }
+
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  bool element_time_derivative(bool request_jacobian, DiffContext & context)
+  {
+    const unsigned int dim = this->get_mesh().mesh_dimension();
+
+    FEMContext &ctxt = cast_ref<FEMContext&>(context);
+
+    FEBase* c_elem_fe = NULL;
[…]

### 2016-06-22 practice/post_thesis/model_adaptivity_iso_vs_aniso/error_breakdown_to_exo/main.C

@@ -1,0 +1,93 @@
+// C++ includes
+#include <iomanip>
+
+// Basic include files
+#include "libmesh/equation_systems.h"
+#include "libmesh/error_vector.h"
+#include "libmesh/exodusII_io.h"
+#include "libmesh/kelly_error_estimator.h"
+#include "libmesh/mesh.h"
+#include "libmesh/mesh_generation.h"
+#include "libmesh/mesh_refinement.h"
+#include "libmesh/uniform_refinement_estimator.h"
+#include "libmesh/getpot.h"
+#include "libmesh/enum_xdr_mode.h" //DEBUG
+#include "libmesh/gmv_io.h" //DEBUG
+#include "libmesh/direct_solution_transfer.h"
+
+// The systems and solvers we may use
+#include "libmesh/diff_solver.h"
+#include "libmesh/steady_solver.h"
+#include "libmesh/newton_solver.h"
+#include "dummy_sys.h"
+
+int main(int argc, char** argv){
+//convert error breakdown from psi_and_superadj runs to exo file that paraview can display
+
+  // Initialize libMesh
+  LibMeshInit init(argc, argv);
+
+  Mesh mesh(init.comm());
+  GetPot infile("contamTrans.in");
+  std::string find_mesh_here = infile("divided_mesh","divvy1.exo");
+	mesh.read(find_mesh_here);
+	
+	// Print information about the mesh to the screen.
+  mesh.print_info();
+
+  // Create an equation systems object.
+  EquationSystems equation_systems (mesh);
+  
+  DummySys & dummy_sys = equation_systems.add_system<DummySys>("Blah");
+  
+  dummy_sys.time_solver = AutoPtr<TimeSolver>(new SteadySolver(dummy_sys));
+  
+  // Initialize the system
+	equation_systems.init ();
+	
+	//"solve" dummy system
+	dummy_sys.solve();
+	
+	//read in error breakdown
+	std::string find_error_here = infile("error_file","error_est_breakdown_basis_blame0.dat");
+	std::vector<Real> err_vec;
+  if(FILE *fp=fopen(find_error_here.c_str(),"r")){
+		Real eep;
+		int flag = 1;
+		while(flag != -1){
+			flag = fscanf(fp, "%lf",&eep);
+			if(flag != -1){
+				err_vec.push_back(eep);
+			}
+		}
+	}
+	
+	//consolidate error breakdown into nodal contributions
+	std::vector<Real> err_vec_squish;
[…]

### 2016-06-22 paper/numerical_experiments.tex
aaaaahhhhh

@@
 
-We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances.
+We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
 At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement.
 All simulations are run on a single processor.
-Table~\ref{tab:ref3D} shows ...
+Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration.
+For the high-fidelity inverse problem, the Newton solver does not converge with the initial guess $u=5$, $z=q=0$; instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
+Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
 %

### 2016-06-23 paper/numerical_experiments.tex
more numerical result edits

@@
 %------------------------------------------------------------%
+
 We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
@@
 From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
+
 %------------------------------------------------------------%
@@
 %------------------------------------------------------------%
+
 We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
@@
 Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration.
-For the high-fidelity inverse problem, the Newton solver does not converge with the initial guess $u=5$, $z=q=0$; instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
+For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
 Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
+The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
 %
@@
 \begin{tabular}{c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%HF$} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & \multirow{2}{*}{Time (s)} \\ 
-& & & (Estimated) & (Actual) & \\ \hline
-LF & 0 & 1068856 &  &  &  \\
-MF01 & 16.7 &  &  &  &  \\
-MF02 & 29.0 &  &  &  &  \\
-MF03 & 42.3 &  &  &  &  \\
-HF & 100 & 547420 &  &  &  \\
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
+& & & (Estimated) & (Actual) & Time (s) \\ \hline
+LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
+MF01 & 16.7 & 577582  & -0.03831 & -0.05222 & 1110 \\
+MF02 & 29.0 & 548904  & 0.00219  & -0.00272 & 1800 \\
+MF03 & 42.3 & 547773  & 0.00032  & -0.00064 & 2220 \\
+HF   & 100  & 547420  & 0        & 0        & 6210 \\
 \end{tabular}
-\caption{table of things}
+\caption{Runtime and relative errors of adaptive algorithm iterations.}
+\label{tab:ref3D}
 \end{table}
+%
+Compared to the previous examples in Section~\ref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
+This is likely due to the additional difference in the diffusive coefficient of the two models in this case.
+The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within $0.1\%$, but in about a third of the time.
+%what happens if you go on forever?
+(running)
+
+The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}.
+We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
+%is there a way to see if any observations are more 'important' than others?
+%
+\begin{figure}[h]
+\centering
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/divvy1_whitebg_shiftaxes.png} 
+\caption{MF$_1$}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/divvy2_whitebg_shiftaxes.png} 
+\caption{MF$_2$}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/divvy3_whitebg_shiftaxes.png} 
+\caption{MF$_3$}
+\end{subfigure}
+\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
+\label{fig:divvy3D}
+\end{figure} 
+%
+The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
+We also compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose at each iteration the basis functions with the largest $5\%$ of the error for model refinement.
+Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations.
+%
+\begin{table}[h]
+\centering
+\begin{tabular}{c|c|c|c|c|c}
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
+& & & (Estimated) & (Actual) & Time (s) \\ \hline
+LF   & 0    &  &  & -0.48784 & 160 \\
+MF01 &  &  &  &  &  \\
+MF02 &  &  &  &  &  \\
+MF03 &  &  &  &  &  \\
+MF04 &  &  &  &  &  \\
+MF05 &  &  &  &  &  \\
+MF06 &  &  &  &  &  \\
+HF   & 100  & 547420  & 0        & 0        & 6210 \\
+\end{tabular}
+\caption{Runtime and relative errors of adaptive algorithm iterations.}
+\label{tab:ref3D}
+\end{table}
+%
+%similar final refinement percentage
+%can we get a better sense of 'important' observations?
+%same weird sign flip at end
+%actual relative error decreases monotonically in magnitude, but not estimated...

### 2016-06-23 paper/numerical_experiments.tex
small edit

@@
 \end{subfigure}
-\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
+\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
 \label{fig:divvy3D}
@@
 & & & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    &  &  & -0.48784 & 160 \\
-MF01 &  &  &  &  &  \\
-MF02 &  &  &  &  &  \\
-MF03 &  &  &  &  &  \\
-MF04 &  &  &  &  &  \\
-MF05 &  &  &  &  &  \\
-MF06 &  &  &  &  &  \\
+LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
+MF01 & 9.27 & 613419  &  &  &  \\
+MF02 & 16.9 & 558523  &  &  &  \\
+MF03 & 23.7 & 550323  &  &  &  \\
+MF04 & 30.4 & 548225  &  &  &  \\
+MF05 & 37.2 & 547744  &  &  &  \\
+MF06 & 44.6 & 547532  &  &  &  \\
 HF   & 100  & 547420  & 0        & 0        & 6210 \\
@@
 \caption{Runtime and relative errors of adaptive algorithm iterations.}
-\label{tab:ref3D}
+\label{tab:ref3D_dainty}
 \end{table}

### 2016-06-23 paper/numerical_experiments.tex
more edits to 3D example

@@
 Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-Each linear Langrange basis function's contribution is plotted at its nonzero node.
+Each linear Lagrange basis function's contribution is plotted at its nonzero node.
 %
-\begin{figure}[h!]
+\begin{figure}[h]
 \captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \captionsetup[subfigure]{justification=centering}
@@
 %
-\begin{figure}[h!]
+\begin{figure}[h]
 \captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
@@
 The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
-Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
+Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{series3D/setup_arial_nolegend.pdf} \hfill
+\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
 \includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
@@
 We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
-At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement.
+At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
 All simulations are run on a single processor.
@@
 \end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations.}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration.}
 \label{tab:ref3D}
@@
 %what happens if you go on forever?
-(running)
+the sign corrects itself in the next two iterations, and then becomes wrong again...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs)...also 'continuation' this way is faster (4600) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...
 
@@
 We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
-%is there a way to see if any observations are more 'important' than others?
+Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
 %
@@
 \centering
-\includegraphics[width=\textwidth]{series3D/divvy1_whitebg_shiftaxes.png} 
+\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
 \caption{MF$_1$}
+\label{fig:ref3D_1}
 \end{subfigure}
@@
 \centering
-\includegraphics[width=\textwidth]{series3D/divvy2_whitebg_shiftaxes.png} 
+\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
 \caption{MF$_2$}
@@
 \centering
-\includegraphics[width=\textwidth]{series3D/divvy3_whitebg_shiftaxes.png} 
+\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
 \caption{MF$_3$}
@@
 The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
-We also compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose at each iteration the basis functions with the largest $5\%$ of the error for model refinement.
-Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations.
+Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime.
+We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement.
+Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
 %
-\begin{table}[h]
+\begin{table}
 \centering
@@
 LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
-MF01 & 9.27 & 613419  &  &  &  \\
-MF02 & 16.9 & 558523  &  &  &  \\
-MF03 & 23.7 & 550323  &  &  &  \\
-MF04 & 30.4 & 548225  &  &  &  \\
-MF05 & 37.2 & 547744  &  &  &  \\
-MF06 & 44.6 & 547532  &  &  &  \\
+MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
+MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
+MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
+MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
+MF05 & 37.2 & 547744  & 0.00120  & -0.00059 & 3309 \\
+MF06 & 44.6 & 547532  & 0.00035  & -0.00020 & 3642 \\
 HF   & 100  & 547420  & 0        & 0        & 6210 \\
 \end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations.}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration.}
 \label{tab:ref3D_dainty}
@@
 %
-%similar final refinement percentage
-%can we get a better sense of 'important' observations?
-%same weird sign flip at end
-%actual relative error decreases monotonically in magnitude, but not estimated...
+\begin{figure}[h]
+\centering
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy1_whitebg_shiftaxes.png} 
+\caption{MF$_1$}
+\label{fig:ref3d_dainty1}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy2_whitebg_shiftaxes.png} 
+\caption{MF$_2$}
+\label{fig:ref3d_dainty2}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy3_whitebg_shiftaxes.png} 
+\caption{MF$_3$}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy4_whitebg_shiftaxes.png} 
+\caption{MF$_4$}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy5_whitebg_shiftaxes.png} 
+\caption{MF$_5$}
+\end{subfigure}
+\begin{subfigure}[t]{0.32\textwidth}
+\centering
+\includegraphics[width=\textwidth]{series3D/run_0p05/divvy6_whitebg_shiftaxes.png} 
+\caption{MF$_6$}
+\end{subfigure}
+\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
+\label{fig:divvy3D_dainty}
+\end{figure} 
+%
+We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
+It can also be seen in Figure~\ref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations.
+Similarly to the examples in Section~\ref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
+
+We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, the adaptive algorithm requires about a half of the time of the high-fidelity inverse problem.
+We note that, although both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$), they do not necessarily produce the same refined regions (compare Figures~\ref{fig:ref3D_1} and \ref{fig:ref3d_dainty2}) or relative error for a given refinement proportion.
+A slower refinement rate also does not necessarily produce a smaller (estimated or true) relative error, or a more accurate relative error estimate, for a given refinement proportion.

### 2016-06-23 paper/numerical_experiments.tex
so tired...

@@
 \includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.
+\red{Does this even have enough points to warrant a plot?
+table instead?}}
 \label{fig:baseErr}
@@
 At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
-All simulations are run on a single processor.
+All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}.
 Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration.
@@
 %what happens if you go on forever?
-the sign corrects itself in the next two iterations, and then becomes wrong again...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs)...also 'continuation' this way is faster (4600) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...
+the sign corrects itself in the next two iterations, and then becomes wrong again (last few iterations of 5% rate run are correct sign though...)...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs; running both rates of adaptive to 100% HF gives same qoi to 8 sig figs)...also 'continuation' this way is faster (4600 with 10% rate, but 6600 with 5% rate) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...
 

### 2016-06-24 paper/numerical_experiments.tex
garlic

@@
 %
+
 The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
@@
 We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement.
+
 Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.

### 2016-06-24 paper/algorithms.tex
changed subfigures and referencse to match siam style

@@
 %
-Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
 This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
-Algorithm~\ref{alg:refSeries} describes this approach.
-Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+\Cref{alg:refSeries} describes this approach.
+Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 
-	supplementary adjoint $\Lambda_0$ (see Equation (\ref{eq:superAdjEq}))}
+	supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
 	\State{Compute QoI error estimate
@@
 
-		$\quad\quad$supplementary adjoint $\Lambda_i$ (see Equation (\ref{eq:superAdjEq}))}
+		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \cref{eq:superAdjEq})}
 		\State{Compute QoI error estimate
@@
 
-Algorithm~\ref{alg:refSeries} is applicable to a large class of models.
+\Cref{alg:refSeries} is applicable to a large class of models.
 The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
@@
 %
-We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
+We now derive the computational complexity of using \cref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
 Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
@@
 
-If one utilizes Algorithm~\ref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
+If one utilizes \cref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
 %
@@
 
-Comparing Eq.~\eqref{eq:cost_adapt} and~\eqref{eq:cost_nadapt}, we have,
+Comparing \cref{eq:cost_adapt} and \cref{eq:cost_nadapt}, we have,
 %

### 2016-06-24 paper/intro.tex
changed subfigures and referencse to match siam style

@@
 
-The rest of the paper is organized as follows, Section~\ref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
-Then, in Section~\ref{sect:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis.
-Section~\ref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.
-Finally, we present conclusions and direction for future work in Section~\ref{sect:conc}.
+The rest of the paper is organized as follows, \cref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
+Then, in \cref{sect:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis.
+\cref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.
+Finally, we present conclusions and direction for future work in \cref{sect:conc}.
 

### 2016-06-24 paper/mathematical_formulation.tex
more paper edits
changed subfigures and referencse to match siam style

@@
 %
-Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by Equation (\ref{eq:weakForm}).
+Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by \cref{eq:weakForm}.
 
-The constraints given by Eq.~\eqref{eq:weakForm} are typically models of physical processes or systems.
+The constraints given by \cref{eq:weakForm} are typically models of physical processes or systems.
 However, a given physical system need not have a unique model that can describe it; there may be various models of different fidelities.
@@
 Consider two models with which we infer parameters: a high-fidelity (HF) model and a low fidelity (LF) model.
-We then have a specific form of the inverse problem in Equation (\ref{eq:invOpt}) with this model,
+We then have a specific form of the inverse problem in \cref{eq:invOpt} with this model,
 \begin{equation}
@@
 We thus seek to introduce the QoI functional $I$ into the inverse problem formulation, by introducing auxilary variables and additional adjoint equations.
-Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by Eq.~\eqref{eq:invOpt_cons}.
+Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by \cref{eq:invOpt_cons}.
 %
 %------------------------------------------------------------------------------%
-\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse \\Problem}  \label{sec:deriv}
+\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
 %------------------------------------------------------------------------------%
@@
 \label{thm:error_estimate}
-Following the notation established in section~\ref{sec:setup}, let the bilinear form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Following the notation established in \cref{sec:setup}, let the bilinear form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
 Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
@@
 
-Consider the Lagrangian equation induced by Eq.~\eqref{eq:invOpt},
+Consider the Lagrangian equation induced by \cref{eq:invOpt},
 %
@@
 
-Denote by $\Psi_{HF}$ and $\Psi_{LF}$, stationary points of the high and low fidelity versions of Eq.~\eqref{eq:InvsOpt_auglag} and, consider the adjoint problem,
+Denote by $\Psi_{HF}$ and $\Psi_{LF}$, stationary points of the high and low fidelity versions of \cref{eq:InvsOpt_auglag} and, consider the adjoint problem,
 %
@@
 
-Extending the property in Equation (\ref{eq:MeqI}) to the augmented Lagrangians for the high and low fidelity models, we have,
+Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high and low fidelity models, we have,
 %
@@
 \end{equation}
-Combining Equations (\ref{eq:repIwithM}) and (\ref{eq:beckvex}) we obtain
+Combining \cref{eq:repIwithM} and \cref{eq:beckvex} we obtain
 \begin{multline}
@@
 
-Further, the error in the output $\mathcal{Q}$ defined in Equation (\ref{eq:superAdjEq}) can be expressed as a dual-weighted residual,
+Further, the error in the output $\mathcal{Q}$ defined in \cref{eq:superAdjEq} can be expressed as a dual-weighted residual,
 \begin{equation}
@@
 
-Combining Equations (\ref{eq:preadj}) and (\ref{eq:adjOutErr}), we have,
+Combining \cref{eq:preadj} and \cref{eq:adjOutErr}, we have,
 \begin{multline}

### 2016-06-24 paper/numerical_experiments.tex
changed subfigures and referencse to match siam style

@@
 %
-We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in Section~\ref{sec:errLocal}.
+We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
 We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
-In Section~\ref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
-We apply Algorithm~\ref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In Section~\ref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.} Finally, in Section~\ref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using Algorithm~\ref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
+In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
+In \cref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
+\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.} Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
 
@@
 %------------------------------------------------------------------------------------------------------------------------%
-Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate.
+\Cref{alg:refSeries} does not require a particular method for localizing the error estimate.
 A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
@@
 For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
-Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as
+Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as
 %
@@
 In this section, we consider a pair of models which differ in the physics included.
-In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
-Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
+In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
+\cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
 %
@@
 %
-The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in Figure~\ref{fig:baseSetup}.
+The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in \cref{fig:baseSetup}.
 Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
@@
 %
-We now present the results for solving the inference problem using Algorithm~\ref{alg:refSeries}.
-Once the QoI error estimate is calculated using Equation~(\ref{eq:finErrExp}), the error estimate is then decomposed into local contributions, as described in Equation~(\ref{eq:basisblame}).
+
+We now present the results for solving the inference problem using \cref{alg:refSeries}.
+Once the QoI error estimate is calculated using \ref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
@@
 
-Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
+\Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
 Each linear Lagrange basis function's contribution is plotted at its nonzero node.
 %
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
+\begin{figure}[htbp]
+%\captionsetup[subfloat]{captionskip=-5pt}
 \centering
-  \begin{subfigure}[b]{\textwidth}
-  \centering    
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
-    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_LF.png}
-    \vspace{-0.5\baselineskip}
-    \caption{MF$_0$ ($0\%$ HF)}
+\subfloat[MF$_0$ ($0\%$ HF)]{
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
   \label{fig:baseRef0}
-    \vspace{0.8\baselineskip}
-  \end{subfigure}
-	\begin{subfigure}[b]{\textwidth}
-  \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
-    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF01.png}
-    \vspace{-0.5\baselineskip}
-    \caption{MF$_1$ ($5\%$ HF)}
-    \vspace{0.8\baselineskip}
-  \end{subfigure}
-  \begin{subfigure}[b]{\textwidth}
-  \centering
-    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
-    \includegraphics[width=0.51\textwidth]{baseSeries/err_breakdown_MF02.png}
-    \vspace{-0.5\baselineskip}
-    \caption{MF$_2$ ($10\%$ HF)}
-    \vspace{0.8\baselineskip}
-  \end{subfigure}
+} \\
+\subfloat[MF$_1$ ($5\%$ HF)]{
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
+} \\
+\subfloat[MF$_2$ ($10\%$ HF)]{
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
+} \\
 \caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
@@
 We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI.
-In the first decomposition of the error (Figure~\ref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
+In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
 Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right.
@@
 
-Figure~\ref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by Algorithm~\ref{alg:refSeries}.
+\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}.
 In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
@@
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
@@
 %
-The error estimate decomposition (\ref{eq:basisblame}) suggests the use of the high-fidelity model in areas of the domain that are important to the interaction of the observations and QoI; the interaction of these two can be complex, and the areas suggested for refinement may be nonintuitive.
+The error estimate decomposition \cref{eq:basisblame} suggests the use of the high-fidelity model in areas of the domain that are important to the interaction of the observations and QoI; the interaction of these two can be complex, and the areas suggested for refinement may be nonintuitive.
 To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region.
@@
 
-The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}.
-The bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
+The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in \cref{fig:qoiStudy}.
+The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
 Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier.
@@
 
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
+\begin{figure}[htbp]
 \centering
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/setup_5_3.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/setup_7_3.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/setup_3_3.png}
-    \caption{Locations of observations and QoI region $\Omega_I$}
+\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
   \label{subfig:obsSetup}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_0.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_0.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_0.png}
-    \caption{MF$_0$ \\ ($0\%$ HF)}
+}
+\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
   \label{subfig:obsLF}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_1.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_1.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_1.png}
-    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_2.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_2.png}
-    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_2.png}
-    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
+}
+\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
+}
+\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
   \label{subfig:obsMFlast}
-  \end{subfigure}
-  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
+}
+  \caption{Compare the error estimate decomposition (\protect\subref{subfig:obsLF}-\protect\subref{subfig:obsMFlast}), given the same observations (teal points in (\protect\subref{subfig:obsSetup})) and varying QoI region (purple box in (\protect\subref{subfig:obsSetup})).}
   \label{fig:qoiStudy}
@@
 
-The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in Figure \ref{fig:dataStudy}.
-Again, the bottom row gives the baseline case presented in Section~\ref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger.
+The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in \cref{fig:dataStudy}.
+Again, the bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger.
 Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region.
@@
 
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering}
+\begin{figure}[htbp]
 \centering
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/setup_3_10.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/setup_3_5.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/setup_3_3.png}
-    \caption{Locations of observations and QoI region $\Omega_I$}
+\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
   \label{subfig:obsSetup2}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_0.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_0.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_0.png}
-    \caption{MF$_0$ \\ ($0\%$ HF)}
+} 
+\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
   \label{subfig:obsLF2}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_1.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_1.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_1.png}
-    \caption{MF$_1$ \\ ($\sim5\%$ HF)}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.20\textwidth}
-  \centering
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_2.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_2.png}
-    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_2.png}
-    \caption{MF$_2$ \\ ($\sim10\%$ HF)}
+}
+\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
+}
+\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
   \label{subfig:obsMFlast2}
-  \end{subfigure}
-  \caption{Compare the error estimate decomposition (\subref{subfig:obsLF2}-\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\subref{subfig:obsSetup2})) and varying observations (teal points in (\subref{subfig:obsSetup2})).}
+}
+  \caption{Compare the error estimate decomposition (\protect\subref{subfig:obsLF2}-\protect\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\protect\subref{subfig:obsSetup2})) and varying observations (teal points in (\protect\subref{subfig:obsSetup2})).}
   \label{fig:dataStudy}
@@
 %------------------------------------------------------------%
-We consider the same high-fidelity model as in Section~\ref{sec:cdvcdr}:
+We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
 \begin{equation}
@@
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in Section~\ref{sec:cdvcdr}.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
 As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
@@
 %------------------------------------------------------------%
-As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition (\ref{eq:basisblame}) of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
+As with the previous examples in \cref{sec:cdvcdr}, the decomposition \cref{eq:basisblame} of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
 The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
@@
 
-Figure~\ref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
+\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
 Each linear Langrange basis function's contribution is plotted at its nonzero node.
 %
-\begin{figure}[h]
-\captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
+\begin{figure}[htbp]
 \centering
-\begin{subfigure}[b]{\textwidth}
-\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_LF.png}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_0$ ($0\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF01.png}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_1$ ($10\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-  \centering
-  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF02.png}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_2$ ($20\%$ HF)}
-  \vspace{0.8\baselineskip}
-\end{subfigure}
+\subfloat[MF$_0$ ($0\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
+} \\
+\subfloat[MF$_1$ ($10\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
+} \\
+\subfloat[MF$_2$ ($20\%$ HF)]{
+  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
+} \\
 %\begin{subfigure}[b]{\textwidth}
@@
 %\end{subfigure}
-\begin{subfigure}[b]{\textwidth}
-	\centering
-	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.png}
-  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF06.png}
-  \vspace{-0.7\baselineskip}
-  \caption{MF$_6$ ($60\%$ HF)}
-\end{subfigure}
+\subfloat[MF$_6$ ($60\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
+}
 \caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.
@@
 %
-Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
+Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
 This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
 
-The corresponding true and estimated absolute errors in the QoI are shown in Figure~\ref{fig:svfErr}.
+The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
@@
 The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
-We also see that in this case, compared to the example in Section~\ref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
 %------------------------------------------------------------------------------------------------------------------------%
@@
 
-We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
+We consider the convection-diffusion-reaction term described in \cref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
 This reaction term is large enough that the Newton solver will not converge with a zero initial guess.
@@
 
-We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
+We compare the complexity of\cref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in \cref{sect:alg_complexity}.
 For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
@@
 With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps.
-Using Algorithm~\ref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
+Using \cref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
 Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.
 
-In other words, on using Algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
+In other words, on using \cref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
 }
@@
 
-In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time.
+In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
 In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
-In Section~\ref{sec:setup3D} we describe the setup of the models and their inverse problems, and in Section~\ref{sec:ref3D} we describe the results of applying Algorithm~\ref{alg:refSeries} to this pair of models.
+In \cref{sec:setup3D} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D} we describe the results of applying \cref{alg:refSeries} to this pair of models.
 
@@
 The boundary conditions remain unchanged.
-As in the previous examples in Section~\ref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where (\ref{eq:HFeq3D}) and (\ref{eq:LFeq3D}) are solved, respectively.
+As in the previous examples in \cref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where \cref{eq:HFeq3D,eq:LFeq3D} are solved, respectively.
 The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.
@@
 Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions.
-The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}.
+The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}.
 We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
@@
 
-We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
+We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
 At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
 All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}.
-Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration.
+\Cref{tab:ref3D} shows the runtime and error at the end of each iteration.
 For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
@@
 %
-\begin{table}[h]
+\begin{table}[htbp]
 \centering
-\begin{tabular}{c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
-& & & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
-MF01 & 16.7 & 577582  & -0.03831 & -0.05222 & 1110 \\
-MF02 & 29.0 & 548904  & 0.00219  & -0.00272 & 1800 \\
-MF03 & 42.3 & 547773  & 0.00032  & -0.00064 & 2220 \\
-HF   & 100  & 547420  & 0        & 0        & 6210 \\
+\begin{tabular}{c|c|c|c|c|c|c|c}
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & Relative Error & Relative Error & Total \\ 
+& & & (Estimated) & (Actual) & (Estimated) & (Actual) & Time (s) \\ \hline
+LF   & 0    & 1068856 & -400936 &  &  &  & 160 \\
+MF01 & 16.7 & 577582  & -22143  &  &  &  & 1110 \\
+MF02 & 29.0 & 548904  & 1200    &  &  &  & 1800 \\
+MF03 & 42.3 & 547773  & 176     &  &  &  & 2220 \\
+HF   & 100  & 547420  & 0       & 0 &  &  & 6210 \\
 \end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration.}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to estimated or actual high-fidelity QoI.}
 \label{tab:ref3D}
@@
 %
-Compared to the previous examples in Section~\ref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
+Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
 This is likely due to the additional difference in the diffusive coefficient of the two models in this case.
@@
 
-The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}.
+The domain divisions for the three adaptive iterations are shown in \cref{fig:divvy3D}.
 We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
@@
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
-\caption{MF$_1$}
+\subfloat[MF$_1$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy1_whitebg_puff.png} 
 \label{fig:ref3D_1}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
-\caption{MF$_2$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
-\caption{MF$_3$}
-\end{subfigure}
-\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
+}
+\subfloat[MF$_2$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy2_whitebg_puff.png} 
+}
+\subfloat[MF$_3$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy3_whitebg_puff.png} 
+}
+\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
 \label{fig:divvy3D}
@@
 
-Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
+\Cref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and \cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
 %
@@
 %
-\begin{figure}[h]
+\begin{figure}[htbp]
 \centering
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy1_whitebg_shiftaxes.png} 
-\caption{MF$_1$}
+\subfloat[MF$_1$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy1_whitebg_puff.png} 
 \label{fig:ref3d_dainty1}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy2_whitebg_shiftaxes.png} 
-\caption{MF$_2$}
+}
+\subfloat[MF$_2$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy2_whitebg_puff.png} 
 \label{fig:ref3d_dainty2}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy3_whitebg_shiftaxes.png} 
-\caption{MF$_3$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy4_whitebg_shiftaxes.png} 
-\caption{MF$_4$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy5_whitebg_shiftaxes.png} 
-\caption{MF$_5$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy6_whitebg_shiftaxes.png} 
-\caption{MF$_6$}
-\end{subfigure}
-\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
+}
+\subfloat[MF$_3$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy3_whitebg_puff.png} 
+} \\
+\subfloat[MF$_4$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy4_whitebg_puff.png} 
+}
+\subfloat[MF$_5$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy5_whitebg_puff.png} 
+}
+\subfloat[MF$_6$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy6_whitebg_puff.png} 
+}
+\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
 \label{fig:divvy3D_dainty}
@@
 We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
-It can also be seen in Figure~\ref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations.
-Similarly to the examples in Section~\ref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
+It can also be seen in \cref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations.
+Similarly to the examples in \cref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
 
 We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, the adaptive algorithm requires about a half of the time of the high-fidelity inverse problem.
-We note that, although both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$), they do not necessarily produce the same refined regions (compare Figures~\ref{fig:ref3D_1} and \ref{fig:ref3d_dainty2}) or relative error for a given refinement proportion.
+We note that, although both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$), they do not necessarily produce the same refined regions (compare \cref{fig:ref3D_1,fig:ref3d_dainty2}) or relative error for a given refinement proportion.
 A slower refinement rate also does not necessarily produce a smaller (estimated or true) relative error, or a more accurate relative error estimate, for a given refinement proportion.

### 2016-06-24 paper/numerical_experiments.tex
moar edits

@@
 \begin{table}[htbp]
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
+\label{tab:ref3D}
 \centering
-\begin{tabular}{c|c|c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & Relative Error & Relative Error & Total \\ 
-& & & (Estimated) & (Actual) & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400936 &  &  &  & 160 \\
-MF01 & 16.7 & 577582  & -22143  &  &  &  & 1110 \\
-MF02 & 29.0 & 548904  & 1200    &  &  &  & 1800 \\
-MF03 & 42.3 & 547773  & 176     &  &  &  & 2220 \\
-HF   & 100  & 547420  & 0       & 0 &  &  & 6210 \\
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
+& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
+LF   & 0    & 1068856 & -400845 & -521436 & -95.2534 & 160 \\
+MF01 & 16.7 & 577582  & -22143  & -30162  & -5.5098  & 1110 \\
+MF02 & 29.0 & 548904  & 1200    & -1484   & -0.2711  & 1800 \\
+MF03 & 42.3 & 547773  & 176     & -353    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
+HF   & 100  & 547420  & --      & 0       & 0        & 6210 \\ \hline
 \end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to estimated or actual high-fidelity QoI.}
-\label{tab:ref3D}
 \end{table}
@@
 \begin{table}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
+\label{tab:ref3D_dainty}
 \centering
-\begin{tabular}{c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
-& & & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
-MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
-MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
-MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
-MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
-MF05 & 37.2 & 547744  & 0.00120  & -0.00059 & 3309 \\
-MF06 & 44.6 & 547532  & 0.00035  & -0.00020 & 3642 \\
-HF   & 100  & 547420  & 0        & 0        & 6210 \\
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
+& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
+LF   & 0    & 1068856 & -400845 & -521436 & -95.2534 & 160 \\
+MF01 & 9.27 & 613419  & -40789  & -65999  & -12.0564 & 1040 \\
+MF02 & 16.9 & 558523  & 1162    & -11103  & -2.0282  & 1860 \\
+MF03 & 23.7 & 550323  & 2510    & -2903   & -0.5303  & 2420 \\
+MF04 & 30.4 & 548225  & 1658    & -805    & -0.1471  & 2970 \\
+MF05 & 37.2 & 547744  & 655     & -324    & -0.0591  & 3309 \\
+MF06 & 44.6 & 547532  & 194     & -112    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
+HF   & 100  & 547420  & --      & 0       & 0        & 6210 \\ \hline
 \end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration.}
-\label{tab:ref3D_dainty}
 \end{table}

### 2016-06-24 practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r42_basis_blame_all_fine/plot_err.m
changed relative error plots to be relative to predicted/true HF QoI

@@ -10,8 +10,11 @@ set(0,'defaultLegendInterpreter','latex');
 errEst = [0.0022021921; -7.03E-004; 3.57E-003; 5.81E-004; 8.30E-004; 3.92E-004; 1.69E-005];
 errTrue = [0.0018260025; 0.0006062894; 0.0008967747; 0.00060295; 0.0008887619; 0.0004020916; 1.69478960580405E-005];
 qoi = [0.0018016233; 0.0030213363; 0.002730851; 0.0030246758; 0.0027388639; 0.0032255341; 0.0036106779];
-relErrEst = abs(errEst./qoi);
-relErrTrue = abs(errTrue./qoi);
+% relErrEst = abs(errEst./qoi);
+% relErrTrue = abs(errTrue./qoi);
+relErrEst = abs(errEst./(qoi+errEst)); %relative to predicted I_HF
+qoiHF = 0.0036276258;
+relErrTrue = abs(errTrue/qoiHF);
 ref = [0; 0.1168; 0.206; 0.3032; 0.4049; 0.5006; 0.6023];
 
 figure('Position',[470 580 765 205])

### 2016-06-24 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/qoi3_sens3_alt_err_all/plot_err.m

@@ -10,8 +10,11 @@ set(0,'defaultLegendInterpreter','latex');
 errEst = [-0.0018293936; -9.84E-005; 1.41E-005];
 errTrue = [-0.0016895481; -0.0001003636; 1.32748289514697E-005];
 qoi = [0.0050801785; 0.0034909939; 0.0033773555];
-relErrEst = abs(errEst./qoi);
-relErrTrue = abs(errTrue./qoi);
+% relErrEst = abs(errEst./qoi);
+% relErrTrue = abs(errTrue./qoi);
+relErrEst = abs(errEst./(qoi+errEst)); %relative to predicted I_HF
+qoiHF = 0.0033906304;
+relErrTrue = abs(errTrue/qoiHF);
 ref = [0; 0.0578; 0.105];
 
 figure('Position',[470 580 765 205])

### 2016-07-09 paper/algorithms.tex
Text and section reorg

--- 2016-06-20 paper/algorithms.tex
@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\ref{sect:error_est_localize}) and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
@@
 We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
+\subsubsection{Error Estimate Localization}\label{sect:error_est_localize}
+%
+Algorithm~\ref{alg:refSeries} does not require a specific method for localizing the error estimate.
+A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
+While simple, this method can lead to non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret and use for refinement.
+
+We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
+For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
+Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as,
+%
+\begin{equation}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
+\end{equation}
+%
+We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
+Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \chi_i)$.
+The error estimate,
+%
+\begin{equation}
+\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
+\end{equation}
+%
+where,
+%
+\begin{equation}\label{eq:basisblame}
+\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
+\end{equation}
+%
+can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
+Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution.
+The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
 % 

### 2016-07-09 paper/numerical_experiments.tex
Text and section reorg

--- 2016-06-24 paper/numerical_experiments.tex
@@
 %
-We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in Section~\ref{sec:errLocal}.
-We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
-In Section~\ref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
-We apply Algorithm~\ref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In Section~\ref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.} Finally, in Section~\ref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using Algorithm~\ref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
+We now use Algorithm~\ref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting.
+We consider two kinds of multi-fidelity models, in a total of three experiments.
+In the first experiment, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+We examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
+In the second experiment, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
+\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
 
@@
 
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Error Estimate Localization} \label{sec:errLocal}
-%------------------------------------------------------------------------------------------------------------------------%
-Algorithm~\ref{alg:refSeries} does not require a particular method for localizing the error estimate.
-A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
-While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.
-
-We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
-Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as
 %
-\begin{equation}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
-\end{equation}
+\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
 %
-We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
-Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum_{i\in I}\varphi_i\lambda_i,\sum_{i\in I}\upvarphi_i x_i)$.
-The error estimate
-%
-\begin{equation}
-\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
-\end{equation}
-%
-where
-%
-\begin{equation}\label{eq:basisblame}
-\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
-\end{equation}
-%
-can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
-The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-Using this method, elements in which the high-fidelity model is already being used are not interpreted as continuing to contribute to the error in the QoI and thus are not marked again for refinement.
-The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution.
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
-%------------------------------------------------------------------------------------------------------------------------%
 In this section, we consider a pair of models which differ in the physics included.
-In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
-Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
+In Section~\ref{sec:cdvcdrSetup} we describe a baseline setup for a simple problem in 2D.
+Section~\ref{sec:cdvcdrBaseRef} describes the results of applying Algorithm~\ref{alg:refSeries} to the baseline problem, and Section~\ref{sec:qoivdata} describes the results of changing the placement of observations or the QoI region from the baseline.
 %
@@
 %
-Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
+The QoI we wish to calculate is the integral of the state,
 %
@@
 Figure~\ref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-Each linear Lagrange basis function's contribution is plotted at its nonzero node.
+Each linear Langrange basis function's contribution is plotted at its nonzero node.
 %
-\begin{figure}[h]
+\begin{figure}[h!]
 \captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
@@
 \includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.
-\red{Does this even have enough points to warrant a plot?
-table instead?}}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
 \label{fig:baseErr}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \captionsetup[subfigure]{justification=centering}
@@
 
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Constant vs Field Parameters} \label{sec:constvfield}
-%------------------------------------------------------------------------------------------------------------------------%
+%
+\subsection{Constant vs Field Parameters}
+%
 It is not necessary for the low- and high-fidelity models to differ in the physics included.
@@
 In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
-%------------------------------------------------------------%
+%
 \subsubsection{Problem Setup}
-%------------------------------------------------------------%
+%
 We consider the same high-fidelity model as in Section~\ref{sec:cdvcdr}:
@@
 As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
-
-Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that when seeking adaptive mesh refinement for the goal-oriented inverse problem, it is more efficient to use the approach discussed in \cite{BecVex05}.
-%------------------------------------------------------------%
+%
 \subsubsection{Adaptive Model Refinement Results}
-%------------------------------------------------------------%
+%
 As with the previous examples in Section~\ref{sec:cdvcdr}, the decomposition (\ref{eq:basisblame}) of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
@@
 %
-\begin{figure}[h]
+\begin{figure}[h!]
 \captionsetup[subfigure]{justification=centering,aboveskip=-10pt}
@@
 Comparing to Figure~\ref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
-This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
+This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field throughout all low-fidelity regions is constant.
 
@@
 We also see that in this case, compared to the example in Section~\ref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-%------------------------------------------------------------------------------------------------------------------------%
+\red{This example seems very close to mesh-refinement, which we estabilished would be more efficient using the original Becker+Vexler method.
+Do we still want to include this?}
+
+%
 \subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
-%------------------------------------------------------------------------------------------------------------------------%
-\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...if we want to make a 'robustness' argument, then merge with whatever vikram writes about operator continuation interpretation?
-%------------------------------------------------------------%
+%
+\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...}
+%
 \subsubsection{Results}
-%------------------------------------------------------------%
-
+%
 We consider the convection-diffusion-reaction term described in Section \ref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
@@
 From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
-
-%------------------------------------------------------------%
+%
 \subsubsection{Computational Complexity}
-%------------------------------------------------------------%
-
+%
 We compare the complexity of Algorithm~\ref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in section~\ref{sect:alg_complexity}.
@@
 In other words, on using Algorithm~\ref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
-}
-
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Convection-Diffusion(-Reaction) in 3D} \label{sec:cdvcdr3D}
-%------------------------------------------------------------------------------------------------------------------------%
-
-In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of Algorithm~\ref{alg:refSeries}, they are both simple enough and similar enough that using Algorithm~\ref{alg:refSeries} saves little, if any, time.
-In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
-In Section~\ref{sec:setup3D} we describe the setup of the models and their inverse problems, and in Section~\ref{sec:ref3D} we describe the results of applying Algorithm~\ref{alg:refSeries} to this pair of models.
-
-%------------------------------------------------------------%
-\subsubsection{Problem Setup} \label{sec:setup3D}
-%------------------------------------------------------------%
-
-The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively.
-We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively.
-The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
 %
-\begin{subequations}
-\label{eq:cdvcdrHF3D}
-\begin{align}
-\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
-u = 5 \quad &\text{on } \partial \Omega_{west}, \\
-\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
-\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
-\end{align} 
-\end{subequations}
-%
-where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field.
-The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day.
-Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}.
-We have porosity $n=0.1$.
-The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
-Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
-
-The low-fidelity model,
-%
-\begin{equation}
-\nabla\cdot(n\vec{V}u - nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
-\end{equation}
-%
-differs in the removal of both the reaction term and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$.
-The boundary conditions remain unchanged.
-As in the previous examples in Section~\ref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where (\ref{eq:HFeq3D}) and (\ref{eq:LFeq3D}) are solved, respectively.
-The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.
-
-The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$.
-Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions.
-The locations of the observations as well as the QoI region $\Omega_I$ are shown in Figure~\ref{fig:setup3D}.
-We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
-%
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
-\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
-\vspace{\baselineskip}
-\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
-\caption{Three views of the locations of the observations and the QoI region.}
-\label{fig:setup3D}
-\end{figure}
-%
-We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements.
-The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom.
-The cell P\'{e}clet is small enough to not require stabilization.
-
-%------------------------------------------------------------%
-\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D}
-%------------------------------------------------------------%
-
-We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
-At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
-All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}.
-Table~\ref{tab:ref3D} shows the runtime and error at the end of each iteration.
-For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
-Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
-The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
-%
-\begin{table}[h]
-\centering
-\begin{tabular}{c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
-& & & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
-MF01 & 16.7 & 577582  & -0.03831 & -0.05222 & 1110 \\
-MF02 & 29.0 & 548904  & 0.00219  & -0.00272 & 1800 \\
-MF03 & 42.3 & 547773  & 0.00032  & -0.00064 & 2220 \\
-HF   & 100  & 547420  & 0        & 0        & 6210 \\
-\end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration.}
-\label{tab:ref3D}
-\end{table}
-%
-Compared to the previous examples in Section~\ref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
-This is likely due to the additional difference in the diffusive coefficient of the two models in this case.
-The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within $0.1\%$, but in about a third of the time.
-%what happens if you go on forever?
-the sign corrects itself in the next two iterations, and then becomes wrong again (last few iterations of 5% rate run are correct sign though...)...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs; running both rates of adaptive to 100% HF gives same qoi to 8 sig figs)...also 'continuation' this way is faster (4600 with 10% rate, but 6600 with 5% rate) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...
-
-The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}.
-We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
-Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
-%
-\begin{figure}[h]
-\centering
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy1_whitebg_shiftaxes.png} 
-\caption{MF$_1$}
-\label{fig:ref3D_1}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy2_whitebg_shiftaxes.png} 
-\caption{MF$_2$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p1/divvy3_whitebg_shiftaxes.png} 
-\caption{MF$_3$}
-\end{subfigure}
-\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
-\label{fig:divvy3D}
-\end{figure} 
-%
-
-The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
-Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime.
-We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement.
-
-Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and Figure~\ref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
-%
-\begin{table}
-\centering
-\begin{tabular}{c|c|c|c|c|c}
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
-& & & (Estimated) & (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
-MF01 & 9.27 & 613419  & -0.06649 & -0.10759 & 1040 \\
-MF02 & 16.9 & 558523  & 0.00208  & -0.01988 & 1860 \\
-MF03 & 23.7 & 550323  & 0.00456  & -0.00528 & 2420 \\
-MF04 & 30.4 & 548225  & 0.00302  & -0.00147 & 2970 \\
-MF05 & 37.2 & 547744  & 0.00120  & -0.00059 & 3309 \\
-MF06 & 44.6 & 547532  & 0.00035  & -0.00020 & 3642 \\
-HF   & 100  & 547420  & 0        & 0        & 6210 \\
-\end{tabular}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration.}
-\label{tab:ref3D_dainty}
-\end{table}
-%
-\begin{figure}[h]
-\centering
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy1_whitebg_shiftaxes.png} 
-\caption{MF$_1$}
-\label{fig:ref3d_dainty1}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy2_whitebg_shiftaxes.png} 
-\caption{MF$_2$}
-\label{fig:ref3d_dainty2}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy3_whitebg_shiftaxes.png} 
-\caption{MF$_3$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy4_whitebg_shiftaxes.png} 
-\caption{MF$_4$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy5_whitebg_shiftaxes.png} 
-\caption{MF$_5$}
-\end{subfigure}
-\begin{subfigure}[t]{0.32\textwidth}
-\centering
-\includegraphics[width=\textwidth]{series3D/run_0p05/divvy6_whitebg_shiftaxes.png} 
-\caption{MF$_6$}
-\end{subfigure}
-\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
-\label{fig:divvy3D_dainty}
-\end{figure} 
-%
-We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
-It can also be seen in Figure~\ref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations.
-Similarly to the examples in Section~\ref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
-
-We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, the adaptive algorithm requires about a half of the time of the high-fidelity inverse problem.
-We note that, although both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$), they do not necessarily produce the same refined regions (compare Figures~\ref{fig:ref3D_1} and \ref{fig:ref3d_dainty2}) or relative error for a given refinement proportion.
-A slower refinement rate also does not necessarily produce a smaller (estimated or true) relative error, or a more accurate relative error estimate, for a given refinement proportion.
+\subsection{Convection-Diffusion(-Reaction) in 3D} 
+%previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences
+%bigger steps in 3D problem because qoi region bigger?

### 2016-07-09 paper/algorithms.tex
Restored crefs

@@
 %
-Just as error estimates can be used to guide mesh-refinement \cite{BecRann01}, the error estimate (\ref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01}, the error estimate (\cref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
 This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
-Algorithm~\ref{alg:refSeries} describes this approach.
-Note that the QoI error adjoint problem (\ref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+Algorithm~\cref{alg:refSeries} describes this approach.
+Note that the QoI error adjoint problem (\cref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
-	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for
-
-	supplementary adjoint $\Lambda_0$ (see Equation (\ref{eq:superAdjEq}))}
+	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
 	\State{Compute QoI error estimate
@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\ref{sect:error_est_localize}) and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
@@
 
-Algorithm~\ref{alg:refSeries} is applicable to a large class of models.
+Algorithm~\cref{alg:refSeries} is applicable to a large class of models.
 The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
@@
 %
-Algorithm~\ref{alg:refSeries} does not require a specific method for localizing the error estimate.
+Algorithm~\cref{alg:refSeries} does not require a specific method for localizing the error estimate.
 A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
@@
 For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
-Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as,
+Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as,
 %
@@
 %
-We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
+We now derive the computational complexity of using Algorithm~\cref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
 Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
@@
 
-If one utilizes Algorithm~\ref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
+If one utilizes Algorithm~\cref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
 %

### 2016-07-09 paper/numerical_experiments.tex
Restored crefs

--- 2016-06-24 paper/numerical_experiments.tex
@@
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
-This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
+This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i})$, is less than $1\%$.
 
@@
 
-\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}.
+\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively.
 In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.

### 2016-07-09 paper/numerical_experiments.tex
Minor

@@
 
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Error Estimate Localization} \label{sec:errLocal}
-%------------------------------------------------------------------------------------------------------------------------%
-\Cref{alg:refSeries} does not require a particular method for localizing the error estimate.
-A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.
-While perhaps simple to compute, this method results in non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret.
-
-We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
-Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as
-%
-\begin{equation}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
-\end{equation}
-%
-We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
-Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum_{i\in I}\varphi_i\lambda_i,\sum_{i\in I}\upvarphi_i x_i)$.
-The error estimate
-%
-\begin{equation}
-\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
-\end{equation}
-%
-where
-%
-\begin{equation}\label{eq:basisblame}
-\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
-\end{equation}
-%
-can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
-The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-Using this method, elements in which the high-fidelity model is already being used are not interpreted as continuing to contribute to the error in the QoI and thus are not marked again for refinement.
-The only exceptions are elements near the interfaces between the low-fidelity and high-fidelity regions, as basis functions near the boundary may have their support divided between the two regions and thus have a nonzero error contribution.
 %------------------------------------------------------------------------------------------------------------------------%

### 2016-07-13 paper/intro.tex
Added some more to the intro

@@
 Data, constraints and prior information form the critical components of an inverse problem formulation.
-There is an extensive literature pertaining to all these components, including the filtering of noise in data, the choice of regularization/prior information, the efficient incorporation of constraints in solving the problem and so on.
-Specifically, the work on the constraints or `state equations' in the inverse problem focuses on reducing the computational expense of solving/inverting the models that represent them.
-Such work includes the use of reduced order models to represent constraints~\cite{}, adaptive mesh refinement to control the size of the state equation discretizations~\cite{} among other strategies.
+There is an extensive literature pertaining to all these components, including the filtering of noise in data~\cite{}, the choice of regularization or representation of prior information~\cite{}, the efficient incorporation of constraints in solving the problem~\cite{}, and so on.
+Specifically, the work on the constraints defined by `state equations' in the inverse problem focuses on reducing the computational expense of solving the models that represent them.
+Such work includes the use of reduced order models to represent constraints~\cite{} and adaptive mesh refinement to control the size of the state equation discretizations~\cite{BecVex05,}, among other strategies.
 
-Models that represent phenomena and processes can usually be organized in a hierarchy according to their fidelity and expense.
+Models that represent phenomena and processes can usually be organized in a hierarchy according to their fidelity and/or expense.
 The use of multiple models simultaneously for forward simulation is well established.
+Two main strategies exist for combining models: hierarchical and concurrent methods.
+Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally (for example, modeling the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03}).
+In this work, we focus on multi-fidelity models formed using concurrent methods, which simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
+For example, in~\cite{Khareetal08} atomistic models capable of describing bond-breaking behaviors are applied to small clusters of atoms in regions relevant to the formation of fractures, while a continuum model is applied in the rest of the domain.
+Concurrent methods are also applied in \cite{vanOpstaletal15} to combine the linear Stokes equation (low-fidelity) and the nonlinear Navier-Stokes equation (high-fidelity) based on an a posteriori estimate of the error in a QoI, and in \cite{LucKinBer02} to combine different reduced-order models, depending on the presence of shocks.
+
+%in \cite{AntHein10}, balanced truncation model reduction is applied to the part of the domain outside of where the optimization variables are located in order to reduce the overall cost of a forward solve.
+%The manner in which the different models are interfaced is problem-dependent; in \cite{Abra98, AlexGarTar02}, a ``handshake'' region is used to couple concurrent particle and continuum models, and in \cite{AlexGarTar02}, interface coupling models are introduced to reconcile uncertainties in the different models.
+
 In this work, we extend the use of multi-fidelity models to inverse problems.
-We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest.
+Specifically, we consider the case where there is a target quantity of interest to be computed from the inferred parameters.
+The use of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; an extension to inverse problems is described in \cite{OdenPrudetal10}.\red{\footnote{Vikram, this was known at the time of the thesis, but not not cited in the thesis.
+I'm not actually sure how to handle this, since this tries to solve the same problem we do, but I don't understand it well enough to do a detailed analysis.
+I did manage to find the book, if you'd like me to scan the pages to you...}} We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest.
 Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.

### 2016-07-13 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_HF_halved_shifted_cont_psi_and_superadj_phys/convdiff_primary.C
nicer inv problem, see if can solve HF problem now...

@@ -80,18 +80,21 @@ void ConvDiff_PrimarySys::init_data (){
   just_f.push_back(fc_var);
   ZeroFunction<Number> zero;
   this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(all_bdys, just_f, &zero)); //f=0 on boundary
-  
-  //influx side as Diri instead of flux BC
-  ConstFunction<Number> westIn(-bsource);
-  std::vector<unsigned int> just_c; just_c.push_back(c_var);
-  std::vector<unsigned int> just_z; just_z.push_back(zc_var);
-  std::set<boundary_id_type> westside; 
-  if(dim == 2)
-    westside.insert(3); 
-  else if(dim == 3)
-    westside.insert(4); 
-  this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(westside, just_c, &westIn));
-  this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(westside, just_z, &zero));
+
+  diri_dbg = infile("use_Diri_BCs",false);
+  if(diri_dbg){
+    //influx side as Diri instead of flux BC
+    ConstFunction<Number> westIn(-bsource);
+    std::vector<unsigned int> just_c; just_c.push_back(c_var);
+    std::vector<unsigned int> just_z; just_z.push_back(zc_var);
+    std::set<boundary_id_type> westside; 
+    if(dim == 2)
+      westside.insert(3); 
+    else if(dim == 3)
+      westside.insert(4); 
+    this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(westside, just_c, &westIn));
+    this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(westside, just_z, &zero));
+  }
 
   qoi = 0.0;
 
@@ -328,8 +331,8 @@ bool ConvDiff_PrimarySys::side_time_derivative(bool request_jacobian, DiffContex
     {
       if(isEast)
         Rc(i) += JxW[qp]*(-U*face_normals[qp]*z)*phi[i][qp];
-//      if(isWest) //west boundary
-//        Rz(i) += JxW[qp]*(U*face_normals[qp]*c - bsource*vx)*phi[i][qp];
+      if(isWest && !diri_dbg) //west boundary
+        Rz(i) += JxW[qp]*(U*face_normals[qp]*c - bsource*vx)*phi[i][qp];
       
       if(compute_jacobian)
       {
[…]

### 2016-07-13 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_HF_halved_shifted_cont_psi_and_superadj_phys/convdiff_primary.h

@@ -93,4 +93,6 @@ public:
   // Calculate Jacobians analytically ?
   bool _analytic_jacobians;
 
+  bool diri_dbg;
+
 };

### 2016-07-13 practice/post_thesis/monty_simple_pde_fwd_react/contamTrans_sys.C

@@ -78,9 +78,10 @@ void ContamTransSys::init_data(){
     //}
 all_bdys.insert(4);
     std::vector<unsigned int> all_of_em;
-	  all_of_em.push_back(c_var);
-	  ConstFunction<Number> five(5.0);
-	  this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(all_bdys, all_of_em, &five));
+    all_of_em.push_back(c_var);
+    //ConstFunction<Number> five(5.0);
+      ConstFunction<Number> five(-bsource);
+    this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(all_bdys, all_of_em, &five));
   }
 
 	// Do the parent's initialization after variables and boundary constraints are defined

### 2016-07-13 practice/post_thesis/monty_simple_pde_fwd_react/initial.h

@@ -1,6 +1,7 @@
 #include "libmesh/parameters.h"
 #include "libmesh/point.h"
 #include "libmesh/vector_value.h"
+#include "libmesh/getpot.h"
 
 using namespace libMesh;
 
@@ -9,7 +10,11 @@ void finish_initialization(){}
 
 Number initial_value(const Point& p, const Parameters& parameters, 
     const std::string& sys_name, const std::string& unknown_name){
-  return 5.0; //ppb
+  
+  GetPot infile("contamTrans.in");
+  Real bsource = infile("bsource", -5.0);
+
+  return -bsource; //ppb
 }
 
 Gradient initial_grad(const Point& p, const Parameters& parameters, 

### 2016-07-13 practice/post_thesis/monty_simple_pde_fwd_react/main.C

@@ -101,10 +101,10 @@ int main(int argc, char** argv){
   equation_systems.init ();
   
   //initial conditions
-  read_initial_parameters();
-  system.project_solution(initial_value, initial_grad,
-                          equation_systems.parameters);
-  finish_initialization();
+//  read_initial_parameters();
+//  system.project_solution(initial_value, initial_grad,
+//                          equation_systems.parameters);
+//  finish_initialization();
 
   // Set the time stepping options...
   system.deltat = deltat;
@@ -122,7 +122,8 @@ int main(int argc, char** argv){
     infile("relative_residual_tolerance", 0.0);
   solver->absolute_residual_tolerance =
     infile("absolute_residual_tolerance", 0.0);
-    
+  solver->require_residual_reduction = infile("require_residual_reduction",true);    
+
   //...and the linear solver options
   solver->max_linear_iterations           = infile("max_linear_iterations", 10000);
   solver->initial_linear_tolerance        = infile("initial_linear_tolerance",1.e-13);

### 2016-07-17 paper/algorithms.tex
edits to present results in slightly different light

@@
 	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
-	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
+	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
 	\State{Compute QoI error estimate
@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
@@
 We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
-\subsubsection{Error Estimate Localization}\label{sect:error_est_localize}
-%
+%------------------------------------------------------------------------------------------------------------------------%
+\subsubsection{Error Estimate Localization}\label{sec:errLocal}
+%------------------------------------------------------------------------------------------------------------------------%
 Algorithm~\cref{alg:refSeries} does not require a specific method for localizing the error estimate.
@@
 The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-% 
+%------------------------------------------------------------------------------------------------------------------------%
 \subsection{Complexity Analysis}\label{sect:alg_complexity}
-%
+%------------------------------------------------------------------------------------------------------------------------%
 We now derive the computational complexity of using Algorithm~\cref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.

### 2016-07-17 paper/conclusions.tex
edits to present results in slightly different light

\section{Conclusion}\label{sect:conc}
Future work:
\begin{itemize}
\item stochastic?
\item mixing models in time as well? (different mixes of models at different time steps?)
\end{itemize}

### 2016-07-17 paper/numerical_experiments.tex
edits to present results in slightly different light

@@
 In \cref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.} Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
+%\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
+Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
 
@@
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
-\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...} The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
+%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
+The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
 The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
@@
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
-This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i})$, is less than $1\%$.
+This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))$, is less than $1\%$.
 
@@
 
-Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that when seeking adaptive mesh refinement for the goal-oriented inverse problem, it is more efficient to use the approach discussed in \cite{BecVex05}.
+Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
+Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
 %------------------------------------------------------------%
@@
 We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
 %------------------------------------------------------------------------------------------------------------------------%
@@
 \red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...if we want to make a 'robustness' argument, then merge with whatever vikram writes about operator continuation interpretation?
+
+Can't seem to replicate this...in HF continuation code, going up to 1000 with steps of 100 is fine, with both gmres and superlu...perhaps there was a bug/copy-paste mistake in the manual continuation version?
+All notes on this run were accidentally lost, so...
 %------------------------------------------------------------%
@@
 }
+\fi{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
 
@@
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400845 & -521436 & -95.2534 & 160 \\
-MF01 & 16.7 & 577582  & -22143  & -30162  & -5.5098  & 1110 \\
-MF02 & 29.0 & 548904  & 1200    & -1484   & -0.2711  & 1800 \\
-MF03 & 42.3 & 547773  & 176     & -353    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547420  & --      & 0       & 0        & 6210 \\ \hline
+LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
+MF01 & 16.7 & 577582  & -22143  & -30164  & -5.5098  & 1110 \\
+MF02 & 29.0 & 548904  & 1200    & -1486   & -0.2711  & 1800 \\
+MF03 & 42.3 & 547773  & 176     & -355    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
+HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
 \end{tabular}
@@
 This is likely due to the additional difference in the diffusive coefficient of the two models in this case.
-The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within $0.1\%$, but in about a third of the time.
+The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within the chosen tolerance.
 %what happens if you go on forever?
@@
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400845 & -521436 & -95.2534 & 160 \\
-MF01 & 9.27 & 613419  & -40789  & -65999  & -12.0564 & 1040 \\
-MF02 & 16.9 & 558523  & 1162    & -11103  & -2.0282  & 1860 \\
-MF03 & 23.7 & 550323  & 2510    & -2903   & -0.5303  & 2420 \\
-MF04 & 30.4 & 548225  & 1658    & -805    & -0.1471  & 2970 \\
-MF05 & 37.2 & 547744  & 655     & -324    & -0.0591  & 3309 \\
-MF06 & 44.6 & 547532  & 194     & -112    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547420  & --      & 0       & 0        & 6210 \\ \hline
+LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
+MF01 & 9.27 & 613419  & -40789  & -66001  & -12.0564 & 1040 \\
+MF02 & 16.9 & 558523  & 1162    & -11105  & -2.0282  & 1860 \\
+MF03 & 23.7 & 550323  & 2510    & -2905   & -0.5303  & 2420 \\
+MF04 & 30.4 & 548225  & 1658    & -807    & -0.1471  & 2970 \\
+MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3309 \\
+MF06 & 44.6 & 547532  & 194     & -114    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
+HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
 \end{tabular}
@@
 
-We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, the adaptive algorithm requires about a half of the time of the high-fidelity inverse problem.
-We note that, although both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$), they do not necessarily produce the same refined regions (compare \cref{fig:ref3D_1,fig:ref3d_dainty2}) or relative error for a given refinement proportion.
+We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$).
+They do not, however, necessarily produce the same refined regions (compare \cref{fig:ref3D_1,fig:ref3d_dainty2}) or relative error for a given refinement proportion.
 A slower refinement rate also does not necessarily produce a smaller (estimated or true) relative error, or a more accurate relative error estimate, for a given refinement proportion.
+
+In this case, the high-fidelity inverse problem is only mildly nonlinear and requires few continuation steps and Newton iterations to converge; there are no savings in computational time from using the adaptive algorithm instead of solving the high-fidelity inverse problem.
+However, as discussed in \cref{sect:alg_complexity}, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
+
+\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
+In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model.
+As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI.
+When these linearities do not all hold, one cannot obtain an exact error estimate.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$.
+As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.
+The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems; in \cref{tab:ref3D,tab:ref3D_dainty}, the inverse problem using the final mixed-fidelity models took 250 and 290 seconds, respectively.

### 2016-07-18 paper/algorithms.tex
Added online-offline algorithm

@@
 %
+
+Algorithm~\cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase.
+In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
+The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.
+%
+\alglanguage{pseudocode}
+\begin{algorithm}[h!]
+\small
+\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
+\label{alg:refonoff}
+\begin{algorithmic}[1]
+\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
+\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use Algorithm~\ref{} to build a MF model MF$_1$} 
+\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
+	\State{$i\gets1$}
+	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
+	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
+	\State{Compute QoI error estimate
+
+	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
+	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
+	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{$i\gets i+1$}
+		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
+		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
+
+		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \cref{eq:superAdjEq})}
+		\State{Compute QoI error estimate
+
+		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
+		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
+	\EndWhile \\
+\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
+\EndProcedure
+\Statex
+\end{algorithmic}
+\end{algorithm}
+%
+Algorithm~\cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$.
+In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI.
+Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
 

### 2016-07-18 paper/algorithms.tex
darcy fwd, small paper edits, stashing notes

@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
@@
 
-Algorithm~\cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase.
+\Cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase.
 In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
@@
 \State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
-\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use Algorithm~\ref{} to build a MF model MF$_1$} 
+\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use \cref{alg:refSeries} to build a MF model MF$_1$} 
 \Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
@@
 %
-Algorithm~\cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$.
+\Cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$.
 In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI.
@@
 
-Algorithm~\cref{alg:refSeries} is applicable to a large class of models.
+\Cref{alg:refSeries} is applicable to a large class of models.
 The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.

### 2016-07-18 paper/numerical_experiments.tex
darcy fwd, small paper edits, stashing notes

@@
 MF03 & 42.3 & 547773  & 176     & -355    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
+HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
 \end{tabular}
@@
 MF06 & 44.6 & 547532  & 194     & -114    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
+HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
 \end{tabular}

### 2016-07-18 practice/post_thesis/darcy_perm_field_vs_scalar/fwd/contamTrans_sys.C

@@ -1,0 +1,273 @@
+#include "libmesh/getpot.h"
+
+#include "contamTrans_sys.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/elem.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+//system initialization
+void ContamTransSys::init_data(){
+  const unsigned int dim = this->get_mesh().mesh_dimension();
+
+  GetPot infile("general.in");
+  unsigned int poly_order = infile("poly_order",1);
+  std::string fefamily = infile("fe_family", std::string("LAGRANGE"));
+
+  p_var = this->add_variable("p", static_cast<Order>(poly_order), Utility::string_to_enum<FEFamily>(fefamily));
+
+  //indicate variables that change in time
+  this->time_evolving(p_var);
+
+  // Useful debugging options'
+	// Set verify_analytic_jacobians to positive to use
+	this->verify_analytic_jacobians = infile("verify_analytic_jacobians", 0.);
+	this->print_jacobians = infile("print_jacobians", false);
+	this->print_element_jacobians = infile("print_element_jacobians", false);
+
+	//set Dirichlet boundary conditions
+	std::set<boundary_id_type> east_bdy;
+	std::set<boundary_id_type> west_bdy;
+	if (dim == 3){
+    west_bdy.insert(4);
+    east_bdy.insert(2);
+  }
+  else if (dim == 2){
+    west_bdy.insert(3);
+    east_bdy.insert(1);
+  }
+  std::vector<unsigned int> all_of_em;
+  all_of_em.push_back(p_var);
+  Real westPressure = 2.606e5;
+  if(infile("do_square",true))
+    westPressure *= 1./46.;
+  ConstFunction<Number> WestPressure(westPressure);
+  ConstFunction<Number> EastPressure(0.0);
+  this->get_dof_map().add_dirichlet_boundary(DirichletBoundary(west_bdy, all_of_em, &WestPressure));
[…]

### 2016-07-18 practice/post_thesis/darcy_perm_field_vs_scalar/fwd/contamTrans_sys.h

@@ -1,0 +1,82 @@
+// DiffSystem framework files
+#include "libmesh/fem_system.h"
+#include "libmesh/elem.h"
+#include "libmesh/point_locator_tree.h"
+
+using namespace libMesh;
+
+// FEMSystem, TimeSolver and  NewtonSolver will handle most tasks,
+// but we must specify element residuals
+class ContamTransSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ContamTransSys(EquationSystems& es, const std::string& name_in, const unsigned int number_in):
+    FEMSystem(es, name_in, number_in){
+    
+    const unsigned int dim = this->get_mesh().mesh_dimension();
+    
+    //read in permeability field, assign values to each element (piecewise-constant field)
+    std::vector<Point> permpts; 
+    std::vector<Real> permvals;
+		if(FILE *fp=fopen("true_perm.dat","r")){
+		  if(dim == 3){
+				Real x, y, z, value;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+					if(flag != -1){
+						permpts.push_back(Point(x,y,z));
+						permvals.push_back(value);
+					}
+				}
+				fclose(fp);
+	  	}else if(dim == 2){
+				Real x, y, value;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+					if(flag != -1){
+						permpts.push_back(Point(x,y));
+						permvals.push_back(value);
+					}
+				}
+				fclose(fp);
+	  	}
+	  }
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<permpts.size(); dnum++){
+	  	Point data_point = permpts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	permelems[this_elem->id()] = permvals[dnum];
+	  }
+    
+    }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
[…]

### 2016-07-18 practice/post_thesis/darcy_perm_field_vs_scalar/fwd/initial.h

@@ -1,0 +1,18 @@
+#include "libmesh/parameters.h"
+#include "libmesh/point.h"
+#include "libmesh/vector_value.h"
+
+using namespace libMesh;
+
+void read_initial_parameters(){}
+void finish_initialization(){}
+
+Number initial_value(const Point& p, const Parameters& parameters, 
+    const std::string& sys_name, const std::string& unknown_name){
+  return 5.0; //ppb
+}
+
+Gradient initial_grad(const Point& p, const Parameters& parameters, 
+    const std::string& sys_name, const std::string& unknown_name){
+  return Gradient(0.0, 0.0, 0.0);
+}

### 2016-07-18 practice/post_thesis/darcy_perm_field_vs_scalar/fwd/main.C

@@ -1,0 +1,172 @@
+//foward run for simple contaminant transport model
+
+// C++ includes
+#include <iomanip>
+
+// Basic include files
+#include "libmesh/equation_systems.h"
+#include "libmesh/error_vector.h"
+#include "libmesh/exodusII_io.h"
+#include "libmesh/kelly_error_estimator.h"
+#include "libmesh/mesh.h"
+#include "libmesh/mesh_generation.h"
+#include "libmesh/mesh_refinement.h"
+#include "libmesh/patch_recovery_error_estimator.h"
+#include "libmesh/uniform_refinement_estimator.h"
+#include "libmesh/getpot.h"
+#include "libmesh/tecplot_io.h"
+
+// The systems and solvers we may use
+#include "libmesh/diff_solver.h"
+#include "libmesh/steady_solver.h"
+#include "libmesh/newton_solver.h"
+#include "libmesh/euler_solver.h"
+
+//local includes
+#include "contamTrans_sys.h"
+#include "initial.h"
+
+int main(int argc, char** argv){
+
+	//initialize libMesh
+	LibMeshInit init(argc, argv);
+	
+	//parameters
+	GetPot infile("general.in");
+  const bool transient                  = infile("transient", false);
+  const Real deltat                     = infile("deltat", 0.005);
+  unsigned int n_timesteps              = infile("n_timesteps", 20);
+  const int nx                          = infile("nx",100);
+  const int ny                          = infile("ny",100);
+  const int nz                          = infile("nz",100);
+  bool do_2D                            = infile("do_2D",true);
+  bool do_square                        = infile("do_square",true);
+      
+#ifdef LIBMESH_HAVE_EXODUS_API
+  const unsigned int write_interval    = infile("write_interval", 5);
+#endif
+
+  // Create a mesh, with dimension to be overridden later, distributed
+  // across the default MPI communicator.
+  Mesh mesh(init.comm());
+  
+  //create mesh
+  unsigned int dim;
+  if(do_2D){ 
+    dim = 2;
+    if(do_square)
+      MeshTools::Generation::build_square(mesh, nx, nz, 0.0, 100.0, 0.0, 100.0, QUAD9); //vertical slice
+    else{
+      MeshTools::Generation::build_square(mesh, nx, nz, 0.0, 4600.0, 0.0, 100.0, QUAD9); //vertical slice
[…]

### 2016-07-18 practice/post_thesis/darcy_perm_field_vs_scalar/fwd/perm_field.m

@@ -1,0 +1,28 @@
+%script to generate "true" permeability field
+
+close all;
+
+Nx = 50;
+Ny = 50; 
+Lx = 100; %m
+Ly = 100; %m
+clx = 10.0; %correlation length
+cly = 10.0; %correlation length
+k_avg = 2.72e-10; %m^2
+V_dp = 0.9; %Dykstra-Parsons coefficient
+
+xnodes = linspace(-Lx/2,Lx/2,Nx+1);
+ynodes = linspace(-Ly/2,Ly/2,Ny+1);
+xcent = 0.5*(xnodes(1:end-1)+xnodes(2:end));
+ycent = 0.5*(ynodes(1:end-1)+ynodes(2:end));
+[X,Y] = meshgrid(xcent,ycent);
+s = -log(1-V_dp);
+mu = log(k_avg)-s^2/2;
+Z = s*randn(Nx,Ny);
+F = exp(-(X.^2/(clx^2/2.0)+Y.^2/(cly^2/2.0)));
+f = 2.0/sqrt(pi)*Lx/sqrt(Nx*Ny)/sqrt(clx)/sqrt(cly)*ifft(fft(Z).*fft(F'));
+perm = exp(mu+real(f))';
+
+imagesc(perm);
+
+dlmwrite('true_perm.dat',[X(:)+Lx/2,Y(:)+Ly/2,perm(:)],' ')

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/diff_mesh/inv_HF/convdiff_primary.C
undoing debug changes

@@ -110,6 +110,7 @@ void ConvDiff_PrimarySys::init_context(DiffContext &context){
   c_elem_fe->get_JxW();
   c_elem_fe->get_phi();
   c_elem_fe->get_dphi();
+  c_elem_fe->get_xyz();
 
   FEBase* c_side_fe = NULL;
   ctxt.get_side_fe(c_var, c_side_fe);
@@ -117,6 +118,7 @@ void ConvDiff_PrimarySys::init_context(DiffContext &context){
   c_side_fe->get_JxW();
   c_side_fe->get_phi();
   c_side_fe->get_dphi();
+  c_side_fe->get_xyz();
 }
 
 // Element residual and jacobian calculations

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/diff_mesh/inv_HF/initial.h

@@ -16,7 +16,7 @@ Number initial_value(const Point& p, const Parameters& parameters,
   Number init_val = 0.0;  
   if(unknown_name == "c")
     init_val = -1.*(infile("bsource", -5.0));
-  
+
   return init_val;
 }
 

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/diff_mesh/inv_HF/main.C

@@ -24,6 +24,8 @@
 #include "libmesh/euler_solver.h"
 #include "libmesh/continuation_system.h"
 
+#include "libmesh/sparse_matrix.h"
+
 //local includes
 #include "convdiff_primary.h"
 #include "initial.h"
@@ -86,7 +88,7 @@ int main(int argc, char** argv){
   //system.max_continuation_parameter = std::fabs(infileForMesh("reaction_rate",1.e-3));
   
   //steady-state problem  
-  system.time_solver = AutoPtr<TimeSolver>(new SteadySolver(system));
+  system.time_solver = UniquePtr<TimeSolver>(new SteadySolver(system));
   libmesh_assert_equal_to (n_timesteps, 1);
   
   // Initialize the system
@@ -100,7 +102,7 @@ int main(int argc, char** argv){
 
   // And the nonlinear solver options
   NewtonSolver *solver = new NewtonSolver(system); 
-  system.time_solver->diff_solver() = AutoPtr<DiffSolver>(solver); 
+  system.time_solver->diff_solver() = UniquePtr<DiffSolver>(solver); 
   solver->quiet = infile("solver_quiet", true);
   solver->verbose = !solver->quiet;
   solver->max_nonlinear_iterations =
@@ -182,6 +184,14 @@ int main(int argc, char** argv){
       system.set_R(R);
       std::cout << "\n\nStarting iteration with R = " << R << "\n\n" << std::endl;
       system.solve();
+      
+      //DEBUG
+//      std::ostringstream Jfile_name;
+//      Jfile_name << "J.dat";
+//      std::ofstream outputJ(Jfile_name.str());
+//      system.matrix->print(outputJ);
+//      outputJ.close();
+
     }
   } //end continuation type switch
   

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/diff_mesh/psi_and_superadj_libmesh_1_0_0/convdiff_primary.C

@@ -185,13 +185,11 @@ bool ConvDiff_PrimarySys::element_time_derivative (bool request_jacobian, DiffCo
 				k = porosity*dispTens;
 		  }
 			else if(subdomain == cd_subdomain_id){
-			  //U = NumberVectorValue(0.0, 0.0, 0.0);
-        U = NumberVectorValue(porosity*vx, 0.0, 0.0); //DEBUG
+			  U = NumberVectorValue(0.0, 0.0, 0.0);
 				R = 0.0;
-        k = porosity*dispTens; //DEBUG
-		    //k = porosity*NumberTensorValue(dispTens(0,0), 0., 0.,
-		    //                               0., dispTens(0,0), 0.,
-		    //                               0., 0., dispTens(0,0));
+		    k = porosity*NumberTensorValue(dispTens(0,0), 0., 0.,
+		                                   0., dispTens(0,0), 0.,
+		                                   0., 0., dispTens(0,0));
 		  }
     	
 			// First, an i-loop over the  degrees of freedom.

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/diff_mesh/psi_and_superadj_libmesh_1_0_0/main.C

@@ -596,7 +596,7 @@ outputJ.close();
     std::cout << "    Time to get auxiliary variables: " << double(end_aux-begin_err_est)/CLOCKS_PER_SEC << " seconds..." << std::endl;
     std::cout << "    Time to get superadjoint: " << double(end-begin_sadj)/CLOCKS_PER_SEC << " seconds...\n" << std::endl;
     std::cout << "Primary and auxiliary system dofs (each): " << system_primary.solution->size() << std::endl;
-    std::cout << "Primary and auxiliary superadjoint system dofs (each: " << system_sadj_primary.solution->size() << "\n" << std::endl;
+    std::cout << "Primary and auxiliary superadjoint system dofs (each): " << system_sadj_primary.solution->size() << "\n" << std::endl;
     std::cout << "Refinement fraction: " << double(fullyRefined.size())/n_LF_elems << std::endl << std::endl;
 
     //output at each iteration

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/psi_and_superadj/convdiff_sadj_aux.h

@@ -1,6 +1,7 @@
 #include "libmesh/fem_system.h"
 #include "libmesh/getpot.h"
 #include "libmesh/point_locator_tree.h"
+#include "libmesh/elem.h"
 
 using namespace libMesh;
 

### 2016-08-08 paper/numerical_experiments.tex
update inv_MF

@@
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
+LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 580 \\
 MF01 & 16.7 & 577582  & -22143  & -30164  & -5.5098  & 1110 \\
@@
 
-\Cref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and \cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
+\red{\Cref{tab:ref3D_dainty} shows the total runtime and error at the end of each of these iterations; the runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
+\Cref{tab:ref3D_dainty_timebreak} shows the runtimes of each individual adaptive iteration, and the times needed to obtain the necessary solutions.
+\Cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.}
 %
@@
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
-MF01 & 9.27 & 613419  & -40789  & -66001  & -12.0564 & 1040 \\
-MF02 & 16.9 & 558523  & 1162    & -11105  & -2.0282  & 1860 \\
-MF03 & 23.7 & 550323  & 2510    & -2905   & -0.5303  & 2420 \\
-MF04 & 30.4 & 548225  & 1658    & -807    & -0.1471  & 2970 \\
-MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3309 \\
-MF06 & 44.6 & 547532  & 194     & -114    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
+LF   & 0    & 1068856 & -400937 & -521438 & -95.2534 & 570 \\
+MF01 & 9.27 & 613419  & -40667  & -66001  & -12.0564 & 1000 \\
+MF02 & 16.9 & 558523  & 1166    & -11105  & -2.0282  & 1780 \\
+MF03 & 23.7 & 550323  & 2504    & -2905   & -0.5303  & 2300 \\
+MF04 & 30.4 & 548225  & 1635    & -807    & -0.1471  & 2720 \\
+MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3060 \\
+MF06 & 44.6 & 547532  & 193     & -114    & -0.0205  & 3420 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
 HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
+\end{tabular}
+\end{table}
+%
+\begin{table}
+\caption{Runtimes of each individual adaptive iteration}
+\label{tab:ref3D_dainty_timebreak}
+\centering
+\begin{tabular}{ccc|c|c|c}
+\cline{4-5} 
+ & & & \multicolumn{2}{|c|}{Error Estimation} & \\
+\cline{1-6}
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
+\cline{1-6}
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & 160 & 245 & \multicolumn{1}{|c|}{570} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 195 & 90 & 140 & \multicolumn{1}{|c|}{430} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 520 & 95 & 160 & \multicolumn{1}{|c|}{780} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 280 & 45 & 190 & \multicolumn{1}{|c|}{520} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 206 & 55 & 100 & \multicolumn{1}{|c|}{420} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 190 & 45 & 100 & \multicolumn{1}{|c|}{340} \\ \hline
+\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 210 & 45 & 100 & \multicolumn{1}{|c|}{360} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 440 & -- & -- & \multicolumn{1}{|c|}{440} \\ \hline
 \end{tabular}

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_aux.C

@@ -1,0 +1,381 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_aux.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/equation_systems.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_AuxSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("contamTrans.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+	
+	//subdomain ids
+	cd_subdomain_id = infile("cd_id", 0);
+	cdr_subdomain_id = infile("cdr_id", 1);
+
+	//indicate variables that change in time
+	this->time_evolving(aux_c_var);
+	this->time_evolving(aux_zc_var);
+	this->time_evolving(aux_fc_var);
+	
+	// Useful debugging options
+	// Set verify_analytic_jacobians to 1e-6 to use
+	this->verify_analytic_jacobians = infile("verify_analytic_jacobians", 0.);
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_aux.h

@@ -1,0 +1,84 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/elem.h"
+#include "libmesh/point_locator_tree.h"
+
+using namespace libMesh;
+
+class ConvDiff_AuxSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_AuxSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("contamTrans.in");
+		std::string find_data_here = infile("data_file","Measurements0.dat");
+		qoi_option = infile("QoI_option",1);
+    
+    //read in data
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, z, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y,z));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+  
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+                                        
+  // Indices for each variable;
+  unsigned int aux_c_var, aux_zc_var, aux_fc_var;
+  
+  Real beta; //regularization parameter
+  Real vx; //west-east velocity (along x-axis, for now); m/s
+  Real react_rate; //reaction rate; 1/s
+  Real porosity; //porosity
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_mprime.C

@@ -1,0 +1,387 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_mprime.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_MprimeSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("contamTrans.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+
+	//set parameters
+  vx = infile("vx", 2.415e-5); // m/s
+  react_rate = infile("reaction_rate", 0.0); // 1/s
+  porosity = infile("porosity", 0.1); // (unitless)
+  bsource = infile("bsource", -5.0); // ppb
+
+  //compute dispersion tensor (assuming for now that velocity purely in x direction)
+  double dlong = infile("dispersivity_longitudinal",60.0);
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_mprime.h

@@ -1,0 +1,87 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
+#include "libmesh/elem.h"
+
+using namespace libMesh;
+
+class ConvDiff_MprimeSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_MprimeSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    qoi.resize(1);
+    
+    GetPot infile("contamTrans.in");
+		std::string find_data_here = infile("data_file","Measurements0.dat");
+		qoi_option = infile("QoI_option",1);
+    
+    //read in data
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, z, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y,z));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+  
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+                                        
+  // Postprocessed output
+  virtual void postprocess();
+  
+  //for adjoint
+  virtual void element_qoi_derivative(DiffContext &context, const QoISet & qois);
+  virtual void side_qoi_derivative(DiffContext &context, const QoISet & qois);
+
+  // Indices for each variable;
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_primary.C

@@ -1,0 +1,347 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_primary.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_PrimarySys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("contamTrans.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+
+	//subdomain ids
+	cd_subdomain_id = infile("cd_id", 0);
+	cdr_subdomain_id = infile("cdr_id", 1);
+
+	//indicate variables that change in time
+	this->time_evolving(c_var);
+	this->time_evolving(zc_var);
+	this->time_evolving(fc_var);
+
+	// Useful debugging options
+	// Set verify_analytic_jacobians to 1e-6 to use
+	this->verify_analytic_jacobians = infile("verify_analytic_jacobians", 0.);
+	this->print_jacobians = infile("print_jacobians", false);
+	this->print_element_jacobians = infile("print_element_jacobians", false);
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_sadj_aux.h

@@ -1,0 +1,93 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
+#include "libmesh/elem.h"
+
+using namespace libMesh;
+
+class ConvDiff_AuxSadjSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_AuxSadjSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("contamTrans.in");
+		std::string find_data_here = infile("data_file","Measurements0.dat");
+		qoi_option = infile("QoI_option",1);
+    
+    //read in data
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, z, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y,z));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+/*	  
+	  //read in auxiliary variables at data points
+	  if(FILE *fp=fopen("auxc_points.dat","r")){
+	    int flag = 1;
+	    Real meep;
+	    while(flag != -1){
+	      flag = fscanf(fp,"%lf",&meep);
+	      if(flag != -1)
+	        primal_auxc_vals.push_back(meep);
+	    }
+	    fclose(fp);
+	  }
+*/	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
+	  
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+  
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_sadj_primary.C

@@ -1,0 +1,350 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_sadj_primary.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/equation_systems.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_PrimarySadjSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("contamTrans.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("sadj_c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("sadj_zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("sadj_fc", static_cast<Order>(conc_p), fefamily); 
+	
+	//set parameters
+  vx = infile("vx", 2.415e-5); // m/s
+  react_rate = infile("reaction_rate", 0.0); // 1/s
+  porosity = infile("porosity", 0.1); // (unitless)
+  bsource = infile("bsource", -5.0); // ppb
+
+  //compute dispersion tensor (assuming for now that velocity purely in x direction)
+  double dlong = infile("dispersivity_longitudinal",60.0);
+  double dtransh = infile("dispersivity_transverse_horizontal",6.0);
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/convdiff_sadj_primary.h

@@ -1,0 +1,93 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
+#include "libmesh/elem.h"
+
+using namespace libMesh;
+
+class ConvDiff_PrimarySadjSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_PrimarySadjSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("contamTrans.in");
+		std::string find_data_here = infile("data_file","Measurements0.dat");
+		qoi_option = infile("QoI_option",1);
+   
+    //read in data
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			Real x, y, z, value;
+			int flag = 1;
+			while(flag != -1){
+				flag = fscanf(fp,"%lf %lf %lf %lf",&x,&y,&z,&value);
+				if(flag != -1){
+					datapts.push_back(Point(x,y,z));
+					datavals.push_back(value);
+				}
+			}
+			fclose(fp);
+	  }
+/*	  
+	  //read in primary variables at data points
+	  if(FILE *fp=fopen("c_points.dat","r")){
+	    int flag = 1;
+	    Real meep;
+	    while(flag != -1){
+	      flag = fscanf(fp,"%lf",&meep);
+	      if(flag != -1)
+	        primal_c_vals.push_back(meep);
+	    }
+	    fclose(fp);
+	  }
+*/	  
+	  //find elements in which data points reside
+	  PointLocatorTree point_locator(this->get_mesh());
+	  for(unsigned int dnum=0; dnum<datavals.size(); dnum++){
+	  	Point data_point = datapts[dnum];
+	  	Elem *this_elem = const_cast<Elem *>(point_locator(data_point));
+	  	dataelems.push_back(this_elem->id());
+	  }
+
+  }
+
+  // System initialization
+  virtual void init_data ();
+
+  // Context initialization
+  virtual void init_context(DiffContext &context);
+
+  // Element residual and jacobian calculations
+  // Time dependent parts
+  virtual bool element_time_derivative (bool request_jacobian,
+                                        DiffContext& context);
+                                        
+  //boundary residual and jacobian calculations
+  virtual bool side_time_derivative (bool request_jacobian,
[…]

### 2016-08-08 practice/post_thesis/model_adaptivity_iso_vs_aniso/inv_MF/main.C

@@ -1,0 +1,285 @@
+//foward run for simple contaminant transport model
+
+// C++ includes
+#include <iomanip>
+
+// Basic include files
+#include "libmesh/equation_systems.h"
+#include "libmesh/error_vector.h"
+#include "libmesh/exodusII_io.h"
+#include "libmesh/kelly_error_estimator.h"
+#include "libmesh/mesh.h"
+#include "libmesh/mesh_generation.h"
+#include "libmesh/mesh_refinement.h"
+#include "libmesh/patch_recovery_error_estimator.h"
+#include "libmesh/uniform_refinement_estimator.h"
+#include "libmesh/getpot.h"
+#include "libmesh/tecplot_io.h"
+
+// The systems and solvers we may use
+#include "libmesh/diff_solver.h"
+#include "libmesh/steady_solver.h"
+#include "libmesh/newton_solver.h"
+#include "libmesh/euler_solver.h"
+#include "libmesh/continuation_system.h"
+#include "libmesh/direct_solution_transfer.h"
+
+//local includes
+#include "convdiff_mprime.h"
+#include "convdiff_primary.h"
+#include "convdiff_aux.h"
+#include "convdiff_sadj_primary.h"
+#include "convdiff_sadj_aux.h"
+#include "initial.h"
+
+int main(int argc, char** argv){
+
+	//initialize libMesh
+	LibMeshInit init(argc, argv);
+	
+	//parameters
+	GetPot infile("fem_system_params.in");
+  unsigned int n_timesteps             = infile("n_timesteps", 1);
+  const int nx                         = infile("nx",100);
+  const int ny                         = infile("ny",100);
+  const int nz                         = infile("nz",100);
+  GetPot infileForMesh("contamTrans.in");
+  bool solveMF = infileForMesh("solveMF",true); //if false, then solving for LF to read in later...
+  
+  // Create a mesh, with dimension to be overridden later, distributed
+  // across the default MPI communicator.
+  Mesh mesh(init.comm());
+  Mesh mesh2(init.comm()); 
+  
+  //read in mesh (with MF divvy)
+  if(solveMF){
+    std::string find_mesh_here = infileForMesh("divided_mesh","divvy1.exo");
+    mesh.read(find_mesh_here);
+  }else{
+    MeshTools::Generation::build_cube(mesh, nx, ny, nz, 0., 2300., 0., 1650., 0., 100., HEX27);
[…]

### 2016-08-26 paper/algorithms.tex
stashing notes and some paper edits; more edits to come

@@
 %
-Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01}, the error estimate (\cref{eq:finErrExp}) can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
@@
 Algorithm~\cref{alg:refSeries} describes this approach.
-Note that the QoI error adjoint problem (\cref{eq:superAdjEq}) involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 for the adaptive algorithm to be less costly than solving the high-fidelity inverse problem.
+\red{I'm not sure this section makes sense, since this doesn't seem to hold for any of the actual runs we've done...our mixed models take fewer nonlinear steps than the HF model, but not close enough to one...}
 %The bound on $T$ will be strictest if Gaussian elimination is used, with $\gamma = 3$, giving $T < \frac{\sum\limits_{i=1}^{C}K_{i}}{10}$.

### 2016-08-26 paper/numerical_experiments.tex
stashing notes and some paper edits; more edits to come

@@
 %
-We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
+\red{We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
 We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
@@
 %\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
-Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.
+Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}
 
@@
 \end{figure}
-
+\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
 %------------------------------------------------------------------------------------------------------------------------%
@@
 We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
+%\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
 %------------------------------------------------------------------------------------------------------------------------%
@@
 
-In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
+\red{In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
 In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
-In \cref{sec:setup3D} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D} we describe the results of applying \cref{alg:refSeries} to this pair of models.
+In \cref{sec:setup3D} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D} we describe the results of applying \cref{alg:refSeries} to this pair of models.}
 
@@
 The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$.
-Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh of a larger domain with the same boundary conditions.
+Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh.
 The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}.
@@
 The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom.
-The cell P\'{e}clet is small enough to not require stabilization.
+The cell P\'{e}clet number is less than one and so no stabilization is used.
 
@@
 
-We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
-At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
-All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}.
-\Cref{tab:ref3D} shows the runtime and error at the end of each iteration.
-For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem.
+We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $1\%$.
+At each iteration, we choose the $5\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
+All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
+\Cref{tab:ref3D} shows the runtime and error at the end of each adaptive iteration; the high-fidelity QoI is given for reference.
 Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
-The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
 %
 \begin{table}[htbp]
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $1\%$; relative errors are given with respect to the true high-fidelity QoI.}
 \label{tab:ref3D}
@@
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 580 \\
-MF01 & 16.7 & 577582  & -22143  & -30164  & -5.5098  & 1110 \\
-MF02 & 29.0 & 548904  & 1200    & -1486   & -0.2711  & 1800 \\
-MF03 & 42.3 & 547773  & 176     & -355    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
+LF   & 0    & 133730 & -4024 & -6020 & -4.71 & 620 \\
+MF01 & 10   & 125073 & 4404  & 2637  & 2.06  & 420 \\
+MF02 & 17.7 & 123093 & 6761  & 4617  & 3.62  & 380 \\
+MF03 & 25   & 123460 & 6354  & 4250  & 3.33  & 370 \\
+MF04 & 32.9 & 125291 & 2242  & 2419  & 1.89  & 450 \\
+MF05 & 39.7 & 126314 & 2445  & 1396  & 1.09  & 325 \\
+MF06 & 47.2 & 126927 & 1070  & 783   & 0.61  & 350 \\
+HF   & 100  & 127710 & --    & --     & --     & -- \\ \hline
 \end{tabular}
@@
 %
-Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
-This is likely due to the additional difference in the diffusive coefficient of the two models in this case.
-The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within the chosen tolerance.
-%what happens if you go on forever?
-the sign corrects itself in the next two iterations, and then becomes wrong again (last few iterations of 5% rate run are correct sign though...)...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs; running both rates of adaptive to 100% HF gives same qoi to 8 sig figs)...also 'continuation' this way is faster (4600 with 10% rate, but 6600 with 5% rate) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...
 
-The domain divisions for the three adaptive iterations are shown in \cref{fig:divvy3D}.
+Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we observe that the error in the QoI (both true and estimated) does not decrease monotonically as the percentage of the domain in which the high-fidelity model is used increases.
+We also observe that any oscillations tend to occur within the first few iterations; continuing the adaptive algorithm beyond those iterations shown in \cref{tab:ref3D} monotonically decreases the QoI errors with increased refinement, until the high-fidelity model is used in the entire domain.
+
+The domain divisions for the six adaptive iterations are shown in \cref{fig:divvy3D}.
 We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
-Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
+\red{Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.}
 %
@@
 \subfloat[MF$_1$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy1_whitebg_puff.png} 
-\label{fig:ref3D_1}
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy1_whitebg_puff.png} 
 }
 \subfloat[MF$_2$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy2_whitebg_puff.png} 
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy2_whitebg_puff.png} 
 }
 \subfloat[MF$_3$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p1/divvy3_whitebg_puff.png} 
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy3_whitebg_puff.png} 
+} \\
+\subfloat[MF$_4$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy4_whitebg_puff.png} 
+}
+\subfloat[MF$_5$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy5_whitebg_puff.png} 
+}
+\subfloat[MF$_6$]{
+\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy6_whitebg_puff.png} 
 }
@@
 %
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% CONTINUE HERE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
@@
 %
+\begin{table}
+\caption{Runtimes of each individual adaptive iteration, given same initial guess (for the mixed- and high-fidelity iterations, the low-fidelity solution is used as the initial guess for the primary variables, and a zero initial guess is used for the auxiliary and supplementary adjoint variables); here the time for the high-fidelity iteration does not include the time required to solve for the initial guess}
+\label{tab:ref3D_dainty_timebreak_sameinit}
+\centering
+\begin{tabular}{ccc|c|c|c}
+\cline{4-5} 
+ & & & \multicolumn{2}{|c|}{Error Estimation} & \\
+\cline{1-6}
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
+\cline{1-6}
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & -- & -- & \multicolumn{1}{|c|}{170} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 260 & 160 & 285 & \multicolumn{1}{|c|}{710} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 365 & 260 & 290 & \multicolumn{1}{|c|}{930} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 250 & 160 & 315 & \multicolumn{1}{|c|}{745} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 275 & 180 & 225 & \multicolumn{1}{|c|}{700} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 245 & 160 & 225 & \multicolumn{1}{|c|}{650} \\ \hline
+\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 285 & 155 & 225 & \multicolumn{1}{|c|}{690} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 350 & -- & -- & \multicolumn{1}{|c|}{360} \\ \hline
+\end{tabular}
+\end{table}
+%
+\begin{table}
+\caption{Runtimes for inverse problem and error estimate, given same initial guess (for the mixed- and high-fidelity iterations, the low-fidelity solution is used as the initial guess for the primary variables, and a zero initial guess is used for the auxiliary and supplementary adjoint variables); here we solve the inverse problems using a different set of data than that which was used to adaptively construct the mixed-fidelity models (offline-online approach) and the low-fidelity problem is only solved to be used as an initial guess}
+\label{tab:ref3D_dainty_timebreak_sameinit_newdata}
+\centering
+\begin{tabular}{ccc|c|c|c}
+\cline{4-5} 
+ & & & \multicolumn{2}{|c|}{Error Estimation} & \\
+\cline{1-6}
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
+\cline{1-6}
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & -- & -- & \multicolumn{1}{|c|}{170} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 205 & 160 & 330 & \multicolumn{1}{|c|}{720} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 250 & 160 & 270 & \multicolumn{1}{|c|}{710} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 350 & 230 & 240 & \multicolumn{1}{|c|}{850} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 330 & 180 & 245 & \multicolumn{1}{|c|}{775} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 350 & 170 & 270 & \multicolumn{1}{|c|}{810} \\ \hline
+\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 355 & 180 & 285 & \multicolumn{1}{|c|}{840} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 460 & -- & -- & \multicolumn{1}{|c|}{470} \\ \hline
+\end{tabular}
+\end{table}
+%
+\begin{table}
+\caption{QoIs and error estimates corresponding to \cref{tab:ref3D_dainty_timebreak_sameinit_newdata}}
+\label{tab:ref3D_dainty_newdata}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
+& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
+LF   & 0    & 122663 & --       & -11245 & -10.9  \\
+MF01 & 9.27 & 104593 & 24087    & 6825   & 6.1  \\
+MF02 & 16.9 & 97432  & -80074   & 13986  & 12.6   \\
+MF03 & 23.7 & 93044  & -762774  & 18374  & 16.5   \\
+MF04 & 30.4 & 84789  & -1059225 & 26629  & 23.9   \\
+MF05 & 37.2 & 100288 & 14626    & 11130  & 10.0   \\
+MF06 & 44.6 & 105593 & 8984     & 5825   & 5.2   \\ 
+HF   & 100  & 111418 & --      & 0       & 0         \\ \hline
+\end{tabular}
+\end{table}
+%
 \begin{figure}[htbp]

### 2016-09-04 paper/conclusions.tex
paper update

@@
 \end{itemize}
+
+Extensions:
+\begin{itemize}
+\item superadj on intermediary mesh
+\item \Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
+In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model.
+As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI.
+When these linearities do not all hold, one cannot obtain an exact error estimate.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$.
+As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.
+\end{itemize}
+
+note that things can get weird if adapted and online data are very different

### 2016-09-04 paper/numerical_experiments.tex
paper update

@@
 \end{figure}
-\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
+\if{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
 %------------------------------------------------------------------------------------------------------------------------%
@@
 We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $1\%$.
-At each iteration, we choose the $5\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger.
+At each iteration, we choose the $5\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be greater.
 All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
-\Cref{tab:ref3D} shows the runtime and error at the end of each adaptive iteration; the high-fidelity QoI is given for reference.
+\Cref{tab:ref3D} shows the runtime and error at the end of each adaptive iteration.
+The high-fidelity inverse problem is solved by using natural continuation on the reaction parameter to avoid stalling the Newton iterations; only two steps are required: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
 Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
@@
 \hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Iteration \\ 
 & & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 133730 & -4024 & -6020 & -4.71 & 620 \\
-MF01 & 10   & 125073 & 4404  & 2637  & 2.06  & 420 \\
-MF02 & 17.7 & 123093 & 6761  & 4617  & 3.62  & 380 \\
-MF03 & 25   & 123460 & 6354  & 4250  & 3.33  & 370 \\
-MF04 & 32.9 & 125291 & 2242  & 2419  & 1.89  & 450 \\
-MF05 & 39.7 & 126314 & 2445  & 1396  & 1.09  & 325 \\
-MF06 & 47.2 & 126927 & 1070  & 783   & 0.61  & 350 \\
-HF   & 100  & 127710 & --    & --     & --     & -- \\ \hline
+LF   & 0    & 133730 & -4024 & -6020 & -4.71 & 622 \\
+MF01 & 10.0 & 125073 & 4404  & 2637  & 2.06  & 419 \\
+MF02 & 17.7 & 123093 & 6761  & 4617  & 3.62  & 378 \\
+MF03 & 25.0 & 123460 & 6354  & 4250  & 3.33  & 369 \\
+MF04 & 32.9 & 125291 & 2242  & 2419  & 1.89  & 454 \\
+MF05 & 39.7 & 126314 & 2445  & 1396  & 1.09  & 324 \\
+MF06 & 47.2 & 126927 & 1070  & 783   & 0.61  & 348 \\
+HF   & 100  & 127710 & --    & --     & --   & 427 \\ \hline
 \end{tabular}
@@
 The domain divisions for the six adaptive iterations are shown in \cref{fig:divvy3D}.
-We see that the error decomposition causes the first refinement iteration to target the QoI region and observations.
-\red{Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.}
+We see that the error decomposition causes the first refinement iteration to target the QoI region and observations; similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, those measurement points furthest downstream of the QoI region are refined later.
+Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
 %
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% CONTINUE HERE
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations.
-Refining a larger region per iteration runs the risks of refining in the wrong areas due to linearization about a $\Psi_{MF}$ that is very different from $\Psi_{HF}$, but can also allow one to reach the chosen error tolerance in fewer iterations and less runtime.
-We compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose the $5\%$ of the basis functions with the largest error for model refinement.
 
-\red{\Cref{tab:ref3D_dainty} shows the total runtime and error at the end of each of these iterations; the runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
-\Cref{tab:ref3D_dainty_timebreak} shows the runtimes of each individual adaptive iteration, and the times needed to obtain the necessary solutions.
-\Cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.}
+In this case, the high-fidelity inverse problem is only mildly nonlinear and requires few continuation steps and Newton iterations to converge; there are no savings in computational time from using the adaptive algorithm instead of solving the high-fidelity inverse problem.
+However, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
+
+\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
+When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
+The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
+
+To illustrate the offline-online application, we generate ten sets of noisy observations to represent the new data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.05$ (equivalent to anywhere from $1.7\%$ to $17\%$ of the observed values).
+We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D,fig:divvy3D} as well as the high-fidelity model.
+The high-fidelity inverse problem is solved using the same two continuation steps; the first continuation step is also used as an initial guess for the mixed-fidelity inverse problems.
+The auxiliary and supplementary adjoint variables simply have a zero initial guess.
+\Cref{tab:ref3D_newdata_QoI,tab:ref3D_newdata_times} shows the average QoI values and error estimates and solution times over the ten datasets.
 %
 \begin{table}
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
-\label{tab:ref3D_dainty}
+\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
+\label{tab:ref3D_newdata_QoI}
 \centering
-\begin{tabular}{|c|c|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
-& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 1068856 & -400937 & -521438 & -95.2534 & 570 \\
-MF01 & 9.27 & 613419  & -40667  & -66001  & -12.0564 & 1000 \\
-MF02 & 16.9 & 558523  & 1166    & -11105  & -2.0282  & 1780 \\
-MF03 & 23.7 & 550323  & 2504    & -2905   & -0.5303  & 2300 \\
-MF04 & 30.4 & 548225  & 1635    & -807    & -0.1471  & 2720 \\
-MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3060 \\
-MF06 & 44.6 & 547532  & 193     & -114    & -0.0205  & 3420 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
-HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
+& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
+MF01 & 10.0 & 123672 & 4328 & 2599 & 2.08  \\
+MF02 & 17.7 & 122073 & 6331 & 4197 & 3.34  \\
+MF03 & 25.0 & 122409 & 5972 & 3861 & 3.06  \\
+MF04 & 32.9 & 124011 & 3449 & 2260 & 1.79  \\
+MF05 & 39.7 & 124852 & 2481 & 1418 & 1.12  \\
+MF06 & 47.2 & 125440 & 1123 & 830  & 0.66  \\ 
+HF   & 100  & 126270 & --   & --   & --     \\ \hline
 \end{tabular}
@@
 \begin{table}
-\caption{Runtimes of each individual adaptive iteration}
-\label{tab:ref3D_dainty_timebreak}
+\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy data.}
+\label{tab:ref3D_newdata_times}
 \centering
@@
 \multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
 \multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
 \cline{1-6}
-\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & 160 & 245 & \multicolumn{1}{|c|}{570} \\ \hline
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 195 & 90 & 140 & \multicolumn{1}{|c|}{430} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 520 & 95 & 160 & \multicolumn{1}{|c|}{780} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 280 & 45 & 190 & \multicolumn{1}{|c|}{520} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 206 & 55 & 100 & \multicolumn{1}{|c|}{420} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 190 & 45 & 100 & \multicolumn{1}{|c|}{340} \\ \hline
-\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 210 & 45 & 100 & \multicolumn{1}{|c|}{360} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 440 & -- & -- & \multicolumn{1}{|c|}{440} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{10.0}  & 173 & 48 & 103 & \multicolumn{1}{|c|}{323} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17.7}  & 191 & 49 & 104 & \multicolumn{1}{|c|}{343} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{25.0}  & 192 & 51 & 109 & \multicolumn{1}{|c|}{352} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{32.9}  & 190 & 49 & 96  & \multicolumn{1}{|c|}{334} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{39.7}  & 188 & 49 & 92  & \multicolumn{1}{|c|}{329} \\ \hline
+\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{47.2}  & 189 & 50 & 89  & \multicolumn{1}{|c|}{327} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 214 & -- & --  & \multicolumn{1}{|c|}{214} \\ \hline
+\end{tabular}
+\end{table}
+%
+
+We see that in this case, when the mixed-fidelity models are used to infer from observations different from those they were generated with, they continue to give similar relative accuracy in their QoI.
+We also note that the mixed-fidelity inverse problems consistently take less time to solve than the high-fidelity inverse problems; however, the high-fidelity inverse problem is still only mildly nonlinear and requires few nonlinear steps to converge, so the difference in their solution times is not large enough to justify estimating the mixed-fidelity QoI errors as well.
+
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Combining Meshes and Physics} \label{sec:diffvcdr3D}
+%------------------------------------------------------------------------------------------------------------------------%
+
+Here we consider two models which differ in both their mesh resolution and the physics included.
+
+%------------------------------------------------------------%
+\subsubsection{Problem Setup}
+%------------------------------------------------------------%
+
+The high-fidelity model remains the same as that described in \cref{sec:setup3D}, with the exception of the boundary condition $u=0$ on $\partial\Omega_{west}$.
+The low-fidelity model shares the domain and boundary condition of the high-fidelity model, but again lacks a reaction term and has a scalar dispersion coefficient; the low-fidelity model also lacks a convection term.
+The lack of a convection term allows the low-fidelity model to be solved on a coarser mesh.
+For the high-fidelity model, the domain is descretized by 32, 64, and 32 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; for the low-fidelity model, the domain is descretized by 16, 32, and 16 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively.
+The regularization term, QoI region, and measurements remain the same as described in \cref{sec:setup3D}.
+
+%------------------------------------------------------------%
+\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D_diffmesh}
+%------------------------------------------------------------%
+
+We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
+At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; again, since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater.
+\Cref{tab:ref3D_diffmesh} shows the runtime and true and estimated QoI errors for each adaptive iteration; the high-fidelity inverse problem is solved in the same way as described in \cref{sec:ref3D}.
+The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem.
+%
+\begin{table}[htbp]
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the true high-fidelity QoI.}
+\label{tab:ref3D_diffmesh}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Iteration \\ 
+& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
+LF   & 9537  & 168710 & -16463 & -85663 & -103   & 1023 \\
+MF01 & 13417 & 167366 & -7207  & -84319 & -102   & 814 \\
+MF02 & 17895 & 89777  & -6208  & -6730  & -8.10  & 858 \\
+MF03 & 21001 & 85880  & -2473  & -2833  & -3.41  & 922 \\
+MF04 & 24528 & 83902  & -711   & -855   & -1.03  & 973 \\
+MF05 & 27984 & 83119  & 32     & -72    & -0.087 & 1187 \\
+HF   & 70785 & 83047  & --    & --     & --   & 457 \\ \hline
+\end{tabular}
+\end{table}
+%
+We notice that, compared to the results in \cref{sec:ref3D}, the error estimates for the low-fidelity and first mixed-fidelity models are very far from the true errors.
+This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are very different from $\Psi_{HF}$.
+This suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the predicted high-fidelity QoI $I(q_{MF},u_{MF})+\epsilon_i$ for two consecutive iterations agree to within some tolerance.
+
+The domain divisions for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}.
+We note some similarities with the series of mixed-fidelity models in \cref{fig:divvy3D}, namely that in both, the QoI region has been refined after $10\%$ refinement, and those measurement points furthest downstream of the QoI are the last to be refined around.
+We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, again possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
+%
+\begin{figure}[htbp]
+\centering
+\subfloat[MF$_1$ ($5.2\%$ HF)]{
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png} 
+}
+\subfloat[MF$_2$ ($11.4\%$ HF)]{
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png} 
+}
+\subfloat[MF$_3$ ($16.3\%$ HF)]{
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png} 
+} \\
+\subfloat[MF$_4$ ($22.0\%$ HF)]{
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png} 
+}
+\subfloat[MF$_5$ ($27.7\%$ HF)]{
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png} 
+}
+\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
+\label{fig:divvy3D_diffmesh}
+\end{figure} 
+%
+We notice in \cref{tab:ref3D_diffmesh} that although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is still faster to solve the high-fidelity inverse problem than to solve a mixed-fidelity inverse problem and obtain an error estimate.
+This can be attributed to the extra time needed to construct systems and project solutions when seeking an error estimate, as well as the mild nonlinearity of the high-fidelity problem and solving for the supplementary adjoint on the high-fidelity mesh.
+For larger problems, it is expected that the computational costs will be dominated by the linear solves.
+For comparison, we select one of the sets of noisy observations described in \cref{sec:ref3D} and solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
+The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
+\Cref{tab:ref3D_newdata_QoI_diffmesh,tab:ref3D_newdata_times_diffmesh} shows the QoI values and error estimates and solution times for the (non)linear solves, not including the time needed to obtain the initial guess.
+%
+\begin{table}
+\caption{QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy dataset; relative errors are with respect to true high-fidelity QoI.}
+\label{tab:ref3D_newdata_QoI_diffmesh}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
+& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
+MF01 & 13417 & 153999 & 2786500 & -74228 & -93.05  \\
+MF02 & 17895 & 85705  & -6496   & -5934  & -7.44  \\
+MF03 & 21001 & 82544  & -3721   & -2773  & -3.48  \\
+MF04 & 24528 & 80684  & -2139   & -913   & -1.14  \\
+MF05 & 27984 & 80154  & -1688   & -383   & -0.48 \\
+HF   & 70785 & 79771  & -- & -- &   \\ \hline
 \end{tabular}
@@
 \begin{table}
-\caption{Runtimes of each individual adaptive iteration, given same initial guess (for the mixed- and high-fidelity iterations, the low-fidelity solution is used as the initial guess for the primary variables, and a zero initial guess is used for the auxiliary and supplementary adjoint variables); here the time for the high-fidelity iteration does not include the time required to solve for the initial guess}
-\label{tab:ref3D_dainty_timebreak_sameinit}
+\caption{Times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy dataset.}
+\label{tab:ref3D_newdata_times_diffmesh}
 \centering
@@
 \cline{1-6}
-\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{DOFs}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
 \multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
 \cline{1-6}
-\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & -- & -- & \multicolumn{1}{|c|}{170} \\ \hline
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 260 & 160 & 285 & \multicolumn{1}{|c|}{710} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 365 & 260 & 290 & \multicolumn{1}{|c|}{930} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 250 & 160 & 315 & \multicolumn{1}{|c|}{745} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 275 & 180 & 225 & \multicolumn{1}{|c|}{700} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 245 & 160 & 225 & \multicolumn{1}{|c|}{650} \\ \hline
-\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 285 & 155 & 225 & \multicolumn{1}{|c|}{690} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 350 & -- & -- & \multicolumn{1}{|c|}{360} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 132  & 141 & 785 & \multicolumn{1}{|c|}{1058} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 209  & 172 & 177 & \multicolumn{1}{|c|}{558} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 312  & 169 & 188 & \multicolumn{1}{|c|}{669} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 275  & 177 & 184 & \multicolumn{1}{|c|}{636} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 403  & 283 & 189 & \multicolumn{1}{|c|}{875} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 2364 & --  & --  & \multicolumn{1}{|c|}{2364} \\ \hline
 \end{tabular}
@@
 %
-\begin{table}
-\caption{Runtimes for inverse problem and error estimate, given same initial guess (for the mixed- and high-fidelity iterations, the low-fidelity solution is used as the initial guess for the primary variables, and a zero initial guess is used for the auxiliary and supplementary adjoint variables); here we solve the inverse problems using a different set of data than that which was used to adaptively construct the mixed-fidelity models (offline-online approach) and the low-fidelity problem is only solved to be used as an initial guess}
-\label{tab:ref3D_dainty_timebreak_sameinit_newdata}
-\centering
-\begin{tabular}{ccc|c|c|c}
-\cline{4-5} 
- & & & \multicolumn{2}{|c|}{Error Estimation} & \\
-\cline{1-6}
-\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Iteration}\\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
-\cline{1-6}
-\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0}     & 160 & -- & -- & \multicolumn{1}{|c|}{170} \\ \hline
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{9.27}  & 205 & 160 & 330 & \multicolumn{1}{|c|}{720} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{16.9}  & 250 & 160 & 270 & \multicolumn{1}{|c|}{710} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{23.7}  & 350 & 230 & 240 & \multicolumn{1}{|c|}{850} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{30.4}  & 330 & 180 & 245 & \multicolumn{1}{|c|}{775} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{37.2}  & 350 & 170 & 270 & \multicolumn{1}{|c|}{810} \\ \hline
-\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{44.6}  & 355 & 180 & 285 & \multicolumn{1}{|c|}{840} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 460 & -- & -- & \multicolumn{1}{|c|}{470} \\ \hline
-\end{tabular}
-\end{table}
-%
-\begin{table}
-\caption{QoIs and error estimates corresponding to \cref{tab:ref3D_dainty_timebreak_sameinit_newdata}}
-\label{tab:ref3D_dainty_newdata}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
-& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
-LF   & 0    & 122663 & --       & -11245 & -10.9  \\
-MF01 & 9.27 & 104593 & 24087    & 6825   & 6.1  \\
-MF02 & 16.9 & 97432  & -80074   & 13986  & 12.6   \\
-MF03 & 23.7 & 93044  & -762774  & 18374  & 16.5   \\
-MF04 & 30.4 & 84789  & -1059225 & 26629  & 23.9   \\
-MF05 & 37.2 & 100288 & 14626    & 11130  & 10.0   \\
-MF06 & 44.6 & 105593 & 8984     & 5825   & 5.2   \\ 
-HF   & 100  & 111418 & --      & 0       & 0         \\ \hline
-\end{tabular}
-\end{table}
-%
-\begin{figure}[htbp]
-\centering
-\subfloat[MF$_1$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy1_whitebg_puff.png} 
-\label{fig:ref3d_dainty1}
-}
-\subfloat[MF$_2$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy2_whitebg_puff.png} 
-\label{fig:ref3d_dainty2}
-}
-\subfloat[MF$_3$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy3_whitebg_puff.png} 
-} \\
-\subfloat[MF$_4$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy4_whitebg_puff.png} 
-}
-\subfloat[MF$_5$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy5_whitebg_puff.png} 
-}
-\subfloat[MF$_6$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy6_whitebg_puff.png} 
-}
-\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
-\label{fig:divvy3D_dainty}
-\end{figure} 
-%
-We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign.
-It can also be seen in \cref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations.
-Similarly to the examples in \cref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
-
-We see that although the more conservative refinement rate requires more iterations and runtime to reach the desired error tolerance, both refinement rates result in similar final refinement proportions for our chosen error tolerance ($42.4\%$ versus $44.6\%$).
-They do not, however, necessarily produce the same refined regions (compare \cref{fig:ref3D_1,fig:ref3d_dainty2}) or relative error for a given refinement proportion.
-A slower refinement rate also does not necessarily produce a smaller (estimated or true) relative error, or a more accurate relative error estimate, for a given refinement proportion.
-
-In this case, the high-fidelity inverse problem is only mildly nonlinear and requires few continuation steps and Newton iterations to converge; there are no savings in computational time from using the adaptive algorithm instead of solving the high-fidelity inverse problem.
-However, as discussed in \cref{sect:alg_complexity}, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
-
-\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
-In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model.
-As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI.
-When these linearities do not all hold, one cannot obtain an exact error estimate.
-The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$.
-As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.
-The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems; in \cref{tab:ref3D,tab:ref3D_dainty}, the inverse problem using the final mixed-fidelity models took 250 and 290 seconds, respectively.

### 2016-09-08 paper/numerical_experiments.tex
cleaned up / update numerical results; extraneous examples moved to different tex file

@@
 \end{figure}
-\if{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
+
 %------------------------------------------------------------------------------------------------------------------------%
-\subsection{Constant vs Field Parameters} \label{sec:constvfield}
+\subsection{Combining Meshes and Physics in 3D} \label{sec:diffvcdr3D}
 %------------------------------------------------------------------------------------------------------------------------%
-It is not necessary for the low- and high-fidelity models to differ in the physics included.
-A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity.
-In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
-%------------------------------------------------------------%
-\subsubsection{Problem Setup}
-%------------------------------------------------------------%
-We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
-\end{equation}
-with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
-\end{equation}
-differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
-Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain.
-For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
-As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
 
-Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
-Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
-%------------------------------------------------------------%
-\subsubsection{Adaptive Model Refinement Results}
-%------------------------------------------------------------%
-As with the previous examples in \cref{sec:cdvcdr}, the decomposition \cref{eq:basisblame} of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
-The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
-With each iteration, an additional $10\%$ of the elements are marked for refinement.
-This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
-
-\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
-Each linear Langrange basis function's contribution is plotted at its nonzero node.
-%
-\begin{figure}[htbp]
-\centering
-\subfloat[MF$_0$ ($0\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
-} \\
-\subfloat[MF$_1$ ($10\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
-} \\
-\subfloat[MF$_2$ ($20\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
-} \\
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_3$ ($30\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_4$ ($40\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_5$ ($50\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
-\subfloat[MF$_6$ ($60\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
-}
-\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.
-The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
-\label{fig:svfRef}
-\end{figure}
-%
-Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
-This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
-
-The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
-%
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
-\label{fig:svfErr}
-\end{figure}
-%
-In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
-The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
-We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-%\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
-%------------------------------------------------------------------------------------------------------------------------%
-\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...if we want to make a 'robustness' argument, then merge with whatever vikram writes about operator continuation interpretation?
-
-Can't seem to replicate this...in HF continuation code, going up to 1000 with steps of 100 is fine, with both gmres and superlu...perhaps there was a bug/copy-paste mistake in the manual continuation version?
-All notes on this run were accidentally lost, so...
-%------------------------------------------------------------%
-\subsubsection{Results}
-%------------------------------------------------------------%
-
-We consider the convection-diffusion-reaction term described in \cref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model.
-This reaction term is large enough that the Newton solver will not converge with a zero initial guess.
-We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value).
-From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.
+In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
+In this section, we consider a more realistic pair of models which differ in both the physics included and the mesh resolution, and demonstrate \red{something}.
+In \cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D_diffmesh} we describe the results of applying \cref{alg:refSeries} to this pair of models.
 
 %------------------------------------------------------------%
-\subsubsection{Computational Complexity}
-%------------------------------------------------------------%
-
-We compare the complexity of\cref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in \cref{sect:alg_complexity}.
-For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.
-
-With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps.
-Using \cref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$.
-Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.
-
-In other words, on using \cref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities.
-}
-\fi{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
-
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Convection-Diffusion(-Reaction) in 3D} \label{sec:cdvcdr3D}
-%------------------------------------------------------------------------------------------------------------------------%
-
-\red{In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
-In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI.
-In \cref{sec:setup3D} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D} we describe the results of applying \cref{alg:refSeries} to this pair of models.}
-
-%------------------------------------------------------------%
-\subsubsection{Problem Setup} \label{sec:setup3D}
+\subsubsection{Problem Setup} \label{sec:setup3D_diffmesh}
 %------------------------------------------------------------%
@@
 \nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
-u = 5 \quad &\text{on } \partial \Omega_{west}, \\
+u = 0 \quad &\text{on } \partial \Omega_{west}, \\
 \frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
@@
 \begin{equation}
-\nabla\cdot(n\vec{V}u - nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
+\nabla\cdot(- nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
 \end{equation}
 %
-differs in the removal of both the reaction term and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$.
+differs in the removal of the reaction and convection terms and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$.
 The boundary conditions remain unchanged.
@@
 We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements.
-The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom.
-The cell P\'{e}clet number is less than one and so no stabilization is used.
-
-%------------------------------------------------------------%
-\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D}
-%------------------------------------------------------------%
-
-We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $1\%$.
-At each iteration, we choose the $5\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be greater.
-All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
-\Cref{tab:ref3D} shows the runtime and error at the end of each adaptive iteration.
-The high-fidelity inverse problem is solved by using natural continuation on the reaction parameter to avoid stalling the Newton iterations; only two steps are required: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
-Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
-%
-\begin{table}[htbp]
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $1\%$; relative errors are given with respect to the true high-fidelity QoI.}
-\label{tab:ref3D}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Iteration \\ 
-& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 0    & 133730 & -4024 & -6020 & -4.71 & 622 \\
-MF01 & 10.0 & 125073 & 4404  & 2637  & 2.06  & 419 \\
-MF02 & 17.7 & 123093 & 6761  & 4617  & 3.62  & 378 \\
-MF03 & 25.0 & 123460 & 6354  & 4250  & 3.33  & 369 \\
-MF04 & 32.9 & 125291 & 2242  & 2419  & 1.89  & 454 \\
-MF05 & 39.7 & 126314 & 2445  & 1396  & 1.09  & 324 \\
-MF06 & 47.2 & 126927 & 1070  & 783   & 0.61  & 348 \\
-HF   & 100  & 127710 & --    & --     & --   & 427 \\ \hline
-\end{tabular}
-\end{table}
-%
-
-Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we observe that the error in the QoI (both true and estimated) does not decrease monotonically as the percentage of the domain in which the high-fidelity model is used increases.
-We also observe that any oscillations tend to occur within the first few iterations; continuing the adaptive algorithm beyond those iterations shown in \cref{tab:ref3D} monotonically decreases the QoI errors with increased refinement, until the high-fidelity model is used in the entire domain.
-
-The domain divisions for the six adaptive iterations are shown in \cref{fig:divvy3D}.
-We see that the error decomposition causes the first refinement iteration to target the QoI region and observations; similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, those measurement points furthest downstream of the QoI region are refined later.
-Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
-%
-\begin{figure}[htbp]
-\centering
-\subfloat[MF$_1$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy1_whitebg_puff.png} 
-}
-\subfloat[MF$_2$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy2_whitebg_puff.png} 
-}
-\subfloat[MF$_3$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy3_whitebg_puff.png} 
-} \\
-\subfloat[MF$_4$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy4_whitebg_puff.png} 
-}
-\subfloat[MF$_5$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy5_whitebg_puff.png} 
-}
-\subfloat[MF$_6$]{
-\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy6_whitebg_puff.png} 
-}
-\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
-\label{fig:divvy3D}
-\end{figure} 
-%
-
-In this case, the high-fidelity inverse problem is only mildly nonlinear and requires few continuation steps and Newton iterations to converge; there are no savings in computational time from using the adaptive algorithm instead of solving the high-fidelity inverse problem.
-However, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
-
-\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
-The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
-When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
-The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
-
-To illustrate the offline-online application, we generate ten sets of noisy observations to represent the new data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.05$ (equivalent to anywhere from $1.7\%$ to $17\%$ of the observed values).
-We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D,fig:divvy3D} as well as the high-fidelity model.
-The high-fidelity inverse problem is solved using the same two continuation steps; the first continuation step is also used as an initial guess for the mixed-fidelity inverse problems.
-The auxiliary and supplementary adjoint variables simply have a zero initial guess.
-\Cref{tab:ref3D_newdata_QoI,tab:ref3D_newdata_times} shows the average QoI values and error estimates and solution times over the ten datasets.
-%
-\begin{table}
-\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
-\label{tab:ref3D_newdata_QoI}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
-& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
-MF01 & 10.0 & 123672 & 4328 & 2599 & 2.08  \\
-MF02 & 17.7 & 122073 & 6331 & 4197 & 3.34  \\
-MF03 & 25.0 & 122409 & 5972 & 3861 & 3.06  \\
-MF04 & 32.9 & 124011 & 3449 & 2260 & 1.79  \\
-MF05 & 39.7 & 124852 & 2481 & 1418 & 1.12  \\
-MF06 & 47.2 & 125440 & 1123 & 830  & 0.66  \\ 
-HF   & 100  & 126270 & --   & --   & --     \\ \hline
-\end{tabular}
-\end{table}
-%
-\begin{table}
-\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy data.}
-\label{tab:ref3D_newdata_times}
-\centering
-\begin{tabular}{ccc|c|c|c}
-\cline{4-5} 
- & & & \multicolumn{2}{|c|}{Error Estimation} & \\
-\cline{1-6}
-\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
-\cline{1-6}
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{10.0}  & 173 & 48 & 103 & \multicolumn{1}{|c|}{323} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17.7}  & 191 & 49 & 104 & \multicolumn{1}{|c|}{343} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{25.0}  & 192 & 51 & 109 & \multicolumn{1}{|c|}{352} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{32.9}  & 190 & 49 & 96  & \multicolumn{1}{|c|}{334} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{39.7}  & 188 & 49 & 92  & \multicolumn{1}{|c|}{329} \\ \hline
-\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{47.2}  & 189 & 50 & 89  & \multicolumn{1}{|c|}{327} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 214 & -- & --  & \multicolumn{1}{|c|}{214} \\ \hline
-\end{tabular}
-\end{table}
-%
-
-We see that in this case, when the mixed-fidelity models are used to infer from observations different from those they were generated with, they continue to give similar relative accuracy in their QoI.
-We also note that the mixed-fidelity inverse problems consistently take less time to solve than the high-fidelity inverse problems; however, the high-fidelity inverse problem is still only mildly nonlinear and requires few nonlinear steps to converge, so the difference in their solution times is not large enough to justify estimating the mixed-fidelity QoI errors as well.
-
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Combining Meshes and Physics} \label{sec:diffvcdr3D}
-%------------------------------------------------------------------------------------------------------------------------%
-
-Here we consider two models which differ in both their mesh resolution and the physics included.
-
-%------------------------------------------------------------%
-\subsubsection{Problem Setup}
-%------------------------------------------------------------%
-
-The high-fidelity model remains the same as that described in \cref{sec:setup3D}, with the exception of the boundary condition $u=0$ on $\partial\Omega_{west}$.
-The low-fidelity model shares the domain and boundary condition of the high-fidelity model, but again lacks a reaction term and has a scalar dispersion coefficient; the low-fidelity model also lacks a convection term.
 The lack of a convection term allows the low-fidelity model to be solved on a coarser mesh.
 For the high-fidelity model, the domain is descretized by 32, 64, and 32 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; for the low-fidelity model, the domain is descretized by 16, 32, and 16 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively.
-The regularization term, QoI region, and measurements remain the same as described in \cref{sec:setup3D}.
+The cell P\'{e}clet number is less than one and so no stabilization is used.
 
@@
 We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
-At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; again, since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater.
-\Cref{tab:ref3D_diffmesh} shows the runtime and true and estimated QoI errors for each adaptive iteration; the high-fidelity inverse problem is solved in the same way as described in \cref{sec:ref3D}.
+At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater.
+All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
+\Cref{tab:ref3D_diffmesh} shows the error at the end of each adaptive iteration.
+The high-fidelity inverse problem is solved by using natural continuation on the reaction parameter to avoid stalling the Newton iterations; only two steps are required: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
+Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
 The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem.
@@
 \hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Iteration \\ 
-& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
-LF   & 9537  & 168710 & -16463 & -85663 & -103   & 1023 \\
-MF01 & 13417 & 167366 & -7207  & -84319 & -102   & 814 \\
-MF02 & 17895 & 89777  & -6208  & -6730  & -8.10  & 858 \\
-MF03 & 21001 & 85880  & -2473  & -2833  & -3.41  & 922 \\
-MF04 & 24528 & 83902  & -711   & -855   & -1.03  & 973 \\
-MF05 & 27984 & 83119  & 32     & -72    & -0.087 & 1187 \\
-HF   & 70785 & 83047  & --    & --     & --   & 457 \\ \hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
+& & & (Estimated) & (Actual) & Error (Actual)  \\ \hline
+LF   & 9537  & 168710 & -16463 & -85663 & -103    \\
+MF01 & 13417 & 167366 & -7207  & -84319 & -102    \\
+MF02 & 17895 & 89777  & -6208  & -6730  & -8.10   \\
+MF03 & 21001 & 85880  & -2473  & -2833  & -3.41   \\
+MF04 & 24528 & 83902  & -711   & -855   & -1.03   \\
+MF05 & 27984 & 83119  & 32     & -72    & -0.087  \\
+HF   & 70785 & 83047  & --     & --     & --    \\ \hline
 \end{tabular}
@@
 %
-We notice that, compared to the results in \cref{sec:ref3D}, the error estimates for the low-fidelity and first mixed-fidelity models are very far from the true errors.
+We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are very far from the true errors.
 This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are very different from $\Psi_{HF}$.
@@
 The domain divisions for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}.
-We note some similarities with the series of mixed-fidelity models in \cref{fig:divvy3D}, namely that in both, the QoI region has been refined after $10\%$ refinement, and those measurement points furthest downstream of the QoI are the last to be refined around.
-We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, again possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
+Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to be refined around.
+We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
 %
@@
 %
-We notice in \cref{tab:ref3D_diffmesh} that although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is still faster to solve the high-fidelity inverse problem than to solve a mixed-fidelity inverse problem and obtain an error estimate.
-This can be attributed to the extra time needed to construct systems and project solutions when seeking an error estimate, as well as the mild nonlinearity of the high-fidelity problem and solving for the supplementary adjoint on the high-fidelity mesh.
-For larger problems, it is expected that the computational costs will be dominated by the linear solves.
-For comparison, we select one of the sets of noisy observations described in \cref{sec:ref3D} and solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
-The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
-\Cref{tab:ref3D_newdata_QoI_diffmesh,tab:ref3D_newdata_times_diffmesh} shows the QoI values and error estimates and solution times for the (non)linear solves, not including the time needed to obtain the initial guess.
+In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error.
+This can be attributed to multiple factors: the high-fidelity problem is only mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh.
+Generally, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
+
+\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
+When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
+The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
+
+To illustrate the offline-online application, we generate ten sets of noisy observations to represent the new data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to anywhere from $2.1\%$ to $8.3\%$ of the observed values).
+We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
+The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
+The auxiliary and supplementary adjoint variables simply have a zero initial guess.
+
+\Cref{tab:ref3D_newdata_QoI_diffmesh} shows the average QoI values and error estimates and solution times for the (non)linear solves.
+\Cref{tab:ref3D_newdata_times_diffmesh} shows the times needed to solve the inverse problems and to solve for the additional variables needed to obtain an error estimate.
+For six of the ten datasets, the high-fidelity inverse problem does not converge given the low-fidelity solution as an initial guess; these are solved using the $k_r=0$ solution as an initial guess so that true QoI errors can be calculated.
+The average time high-fidelity inverse problem solution time shown in \cref{tab:ref3D_newdata_times_diffmesh} includes only those that converged with the low-fidelity initial guess.
 %
 \begin{table}
-\caption{QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy dataset; relative errors are with respect to true high-fidelity QoI.}
+\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
 \label{tab:ref3D_newdata_QoI_diffmesh}
@@
 & & & (Estimated) & (Actual) & Error (Actual) \\ \hline
-MF01 & 13417 & 153999 & 2786500 & -74228 & -93.05  \\
-MF02 & 17895 & 85705  & -6496   & -5934  & -7.44  \\
-MF03 & 21001 & 82544  & -3721   & -2773  & -3.48  \\
-MF04 & 24528 & 80684  & -2139   & -913   & -1.14  \\
-MF05 & 27984 & 80154  & -1688   & -383   & -0.48 \\
-HF   & 70785 & 79771  & -- & -- &   \\ \hline
+LF   & 9537  & 166774 & --    & -84326 & -102.3 \\
+MF01 & 13417 & 164597 & 4347  & -82149 & -99.65  \\
+MF02 & 17895 & 88867  & -5921 & -6418  & -7.79  \\
+MF03 & 21001 & 85237  & -2414 & -2789  & -3.38  \\
+MF04 & 24528 & 83411  & -724  & -963   & -1.17  \\
+MF05 & 27984 & 82664  & -18   & -216   & -0.26 \\
+HF   & 70785 & 82500  & --    & --     & --  \\ \hline
 \end{tabular}
@@
 \begin{table}
-\caption{Times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy dataset.}
+\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets.}
 \label{tab:ref3D_newdata_times_diffmesh}
@@
 \cline{1-6}
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 132  & 141 & 785 & \multicolumn{1}{|c|}{1058} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 209  & 172 & 177 & \multicolumn{1}{|c|}{558} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 312  & 169 & 188 & \multicolumn{1}{|c|}{669} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 275  & 177 & 184 & \multicolumn{1}{|c|}{636} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 403  & 283 & 189 & \multicolumn{1}{|c|}{875} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 2364 & --  & --  & \multicolumn{1}{|c|}{2364} \\ \hline
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{9537}   & 16   & --  & -- & \multicolumn{1}{|c|}{--} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 185  & 107 & 235 & \multicolumn{1}{|c|}{526} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 328  & 169 & 206 & \multicolumn{1}{|c|}{703} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 435  & 202 & 185 & \multicolumn{1}{|c|}{821} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 406  & 201 & 188 & \multicolumn{1}{|c|}{795} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 498  & 263 & 198 & \multicolumn{1}{|c|}{959} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 1185 & --  & --  & \multicolumn{1}{|c|}{1185} \\ \hline
 \end{tabular}
@@
 %
+\begin{table}
+\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets; all averages only over those datasets for which the high-fidelity problem converged when given the low-fidelity problem as an intial guess.}
+%\label{tab:ref3D_newdata_times_diffmesh}
+\centering
+\begin{tabular}{ccc|c|c|c}
+\cline{4-5} 
+ & & & \multicolumn{2}{|c|}{Error Estimation} & \\
+\cline{1-6}
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{DOFs}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
+\cline{1-6}
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{9537}   & 16   & --  & -- & \multicolumn{1}{|c|}{--} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 156  & 101 & 261 & \multicolumn{1}{|c|}{517} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 304  & 175 & 183 & \multicolumn{1}{|c|}{662} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 385  & 228 & 187 & \multicolumn{1}{|c|}{801} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 347  & 202 & 193 & \multicolumn{1}{|c|}{743} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 470  & 275 & 212 & \multicolumn{1}{|c|}{957} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 1185 & --  & --  & \multicolumn{1}{|c|}{1185} \\ \hline
+\end{tabular}
+\end{table}
+%

### 2016-09-08 paper/old_sections.tex
cleaned up / update numerical results; extraneous examples moved to different tex file

\if{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
%------------------------------------------------------------------------------------------------------------------------%
\subsection{Constant vs Field Parameters} \label{sec:constvfield}
%------------------------------------------------------------------------------------------------------------------------%
It is not necessary for the low- and high-fidelity models to differ in the physics included. A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity. In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
%------------------------------------------------------------%
\subsubsection{Problem Setup}
%------------------------------------------------------------%
We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}. As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state. Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results}
%------------------------------------------------------------%
As with the previous examples in \cref{sec:cdvcdr}, the decomposition \cref{eq:basisblame} of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model. The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field. With each iteration, an additional $10\%$ of the elements are marked for refinement. This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. Each linear Langrange basis function's contribution is plotted at its nonzero node. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
}
\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.

The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain. We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI. 
%\if{0} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Highly Nonlinear Reaction)}
%------------------------------------------------------------------------------------------------------------------------%
\red{Not sure should even keep this section...if we split the supplementary adjoint solve, then the condition for adaptivity being more efficient doesn't depend on the linear solver...we don't need this section to make a cost argument if we have the 3D example...having this section seems to be overkill/redundant if all we want to say is that 'sometimes we need continuation for the HF inverse problem'...if we want to make a 'robustness' argument, then merge with whatever vikram writes about operator continuation interpretation?

Can't seem to replicate this...in HF continuation code, going up to 1000 with steps of 100 is fine, with both gmres and superlu...perhaps there was a bug/copy-paste mistake in the manual continuation version? All notes on this run were accidentally lost, so...
%------------------------------------------------------------%
\subsubsection{Results}
%------------------------------------------------------------%

We consider the convection-diffusion-reaction term described in \cref{sec:cdvcdr}, with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use a simple continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{not arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction} We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken.

%------------------------------------------------------------%
\subsubsection{Computational Complexity}
%------------------------------------------------------------%

We compare the complexity of\cref{alg:refSeries} and the continuation method for the high fidelity problem, in the context of the analysis developed in \cref{sect:alg_complexity}. For the high fidelity problem, with  with 9 continuation steps, we have $\sum\limits_{i=1}^{C} K_i=30$.

With Gaussian elimination chosen as the linear solver, this gives us $T < 3$, i.e.\ a budget of 2 adaptive steps. Using \cref{alg:refSeries} with 2 refinement steps, and only $10\%$ of the domain refined to use the high-fidelity model, the estimated relative error is $<1\%$. Indeed, the ratio $\frac{C_{MF}}{C_{HF}}$ was $\frac{24}{30}$, indicating about $20\%$ reduction in computational cost, with the worst case linear solver used.

In other words, on using \cref{alg:refSeries} for a highly nonlinear problem, even with the worst case linear solver, one can get to $<1\%$ error in the QoI, with a $20\%$ reduction in computational cost, while avoiding any need for continuation to handle nonlinearities. }
\fi{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Convection-Diffusion(-Reaction) in 3D} \label{sec:cdvcdr3D}
%------------------------------------------------------------------------------------------------------------------------%

\red{In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time. In this section, we consider a more realistic pair of models which differ in the physics included, and demonstrate computational savings when using the adaptive algorithm, while still achieving a small error in the QoI. In \cref{sec:setup3D} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D} we describe the results of applying \cref{alg:refSeries} to this pair of models.}

%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:setup3D}
%------------------------------------------------------------%

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

The low-fidelity model,
%
\begin{equation}
\nabla\cdot(n\vec{V}u - nk_d\nabla u) = f(q) \quad \text{in } \Omega, \label{eq:LFeq3D}
\end{equation}
%
differs in the removal of both the reaction term and the anisotropy of the dispersion tensor; the dispersion tensor $D$ is replaced with a scalar $k_d=D_{11}$. The boundary conditions remain unchanged. As in the previous examples in \cref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where \cref{eq:HFeq3D,eq:LFeq3D} are solved, respectively. The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh. The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}. We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\ 
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%
We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements. The domain is discretized by a regular mesh of hexahedrons, with 25, 45, and 30 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; each variable has 37,076 degrees of freedom. The cell P\'{e}clet number is less than one and so no stabilization is used.

%------------------------------------------------------------%
\subsubsection{Adaptive Model Refinement Results} \label{sec:ref3D}
%------------------------------------------------------------%

We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $1\%$. At each iteration, we choose the $5\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be greater. All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization. \Cref{tab:ref3D} shows the error at the end of each adaptive iteration. The high-fidelity inverse problem is solved by using natural continuation on the reaction parameter to avoid stalling the Newton iterations; only two steps are required: $k_r=0$, then $k_r=4.2\cdot10^{-4}$. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. 
%
\begin{table}[htbp]
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $1\%$; relative errors are given with respect to the true high-fidelity QoI.}
\label{tab:ref3D}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
LF   & 0    & 133730 & -4024 & -6020 & -4.71  \\
MF01 & 10.0 & 125073 & 4404  & 2637  & 2.06   \\
MF02 & 17.7 & 123093 & 6761  & 4617  & 3.62   \\
MF03 & 25.0 & 123460 & 6354  & 4250  & 3.33   \\
MF04 & 32.9 & 125291 & 2242  & 2419  & 1.89   \\
MF05 & 39.7 & 126314 & 2445  & 1396  & 1.09   \\
MF06 & 47.2 & 126927 & 1070  & 783   & 0.61   \\
HF   & 100  & 127710 & --    & --     & --    \\ \hline
\end{tabular}
\end{table}
%

Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we observe that the error in the QoI (both true and estimated) does not decrease monotonically as the percentage of the domain in which the high-fidelity model is used increases. We also observe that any oscillations tend to occur within the first few iterations; continuing the adaptive algorithm beyond those iterations shown in \cref{tab:ref3D} monotonically decreases the QoI errors with increased refinement, until the high-fidelity model is used in the entire domain.

The domain divisions for the six adaptive iterations are shown in \cref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations; similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, those measurement points furthest downstream of the QoI region are refined later. Around the QoI region, the first iteration refines the domain completely in the $x_3$ direction, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy1_whitebg_puff.png} 
}
\subfloat[MF$_2$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy2_whitebg_puff.png} 
}
\subfloat[MF$_3$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy3_whitebg_puff.png} 
} \\
\subfloat[MF$_4$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy4_whitebg_puff.png} 
}
\subfloat[MF$_5$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy5_whitebg_puff.png} 
}
\subfloat[MF$_6$]{
\includegraphics[width=0.31\textwidth]{series3D/run_invcrime/divvy6_whitebg_puff.png} 
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D}
\end{figure} 
%

In this case, the high-fidelity inverse problem is only mildly nonlinear and requires few continuation steps and Newton iterations to converge; there are no savings in computational time from using the adaptive algorithm instead of solving the high-fidelity inverse problem. However, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.

\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}. The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$. When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI. The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.

To illustrate the offline-online application, we generate ten sets of noisy observations to represent the new data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.05$ (equivalent to anywhere from $1.7\%$ to $17\%$ of the observed values). We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D,fig:divvy3D} as well as the high-fidelity model. The high-fidelity inverse problem is solved using the same two continuation steps; the first continuation step is also used as an initial guess for the mixed-fidelity inverse problems. The auxiliary and supplementary adjoint variables simply have a zero initial guess. \Cref{tab:ref3D_newdata_QoI,tab:ref3D_newdata_times} shows the average QoI values and error estimates and solution times over the ten datasets.
%
\begin{table}
\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
\label{tab:ref3D_newdata_QoI}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
& & & (Estimated) & (Actual) & Error (Actual) \\ \hline
LF   & 0.0  &  &  &  &  \\
MF01 & 10.0 & 123672 & 4328 & 2599 & 2.08  \\
MF02 & 17.7 & 122073 & 6331 & 4197 & 3.34  \\
MF03 & 25.0 & 122409 & 5972 & 3861 & 3.06  \\
MF04 & 32.9 & 124011 & 3449 & 2260 & 1.79  \\
MF05 & 39.7 & 124852 & 2481 & 1418 & 1.12  \\
MF06 & 47.2 & 125440 & 1123 & 830  & 0.66  \\ 
HF   & 100  & 126270 & --   & --   & --     \\ \hline
\end{tabular}
\end{table}
%
\begin{table}
\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy data.}
\label{tab:ref3D_newdata_times}
\centering
\begin{tabular}{ccc|c|c|c}
\cline{4-5} 
 & & & \multicolumn{2}{|c|}{Error Estimation} & \\
\cline{1-6}
\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{$\%$HF}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
\cline{1-6}
\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{0.0}   &  &  &  & \multicolumn{1}{|c|}{} \\ \hline
\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{10.0}  & 173 & 48 & 103 & \multicolumn{1}{|c|}{323} \\ \hline
\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17.7}  & 191 & 49 & 104 & \multicolumn{1}{|c|}{343} \\ \hline
\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{25.0}  & 192 & 51 & 109 & \multicolumn{1}{|c|}{352} \\ \hline
\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{32.9}  & 190 & 49 & 96  & \multicolumn{1}{|c|}{334} \\ \hline
\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{39.7}  & 188 & 49 & 92  & \multicolumn{1}{|c|}{329} \\ \hline
\multicolumn{1}{|c|}{MF06}  & \multicolumn{1}{|c|}{47.2}  & 189 & 50 & 89  & \multicolumn{1}{|c|}{327} \\ \hline
\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{100}   & 214 & -- & --  & \multicolumn{1}{|c|}{214} \\ \hline
\end{tabular}
\end{table}
%

We see that in this case, when the mixed-fidelity models are used to infer from observations different from those they were generated with, they continue to give similar relative accuracy in their QoI. We also note that the mixed-fidelity inverse problems consistently take less time to solve than the high-fidelity inverse problems; however, the high-fidelity inverse problem is still only mildly nonlinear and requires few nonlinear steps to converge, so the difference in their solution times is not large enough to justify estimating the mixed-fidelity QoI errors as well.

### 2016-09-13 paper/algorithms.tex
stashing some paper changes

@@
-\section{Inference Algorithm and Complexity Analysis}\label{sect:alg}
+\section{Goal Oriented Inference Algorithm}\label{sect:alg}
 %
-Based on the theoretical developments in the last section, we present below a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
-%
-\subsection{Goal Oriented Inference Algorithm}
-%
+Based on the theoretical developments in the last section, we now give a goal-oriented inference algorithm that allows one to combine models of varying fidelity, while maintaining rigorous control of QoI error.
+
 Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
@@
 	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
-	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
+	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))|>$ \texttt{errTol}}
 		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
@@
 
-\Cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase.
-In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
-The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.
-%
-\alglanguage{pseudocode}
-\begin{algorithm}[h!]
-\small
-\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
-\label{alg:refonoff}
-\begin{algorithmic}[1]
-\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
-\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use \cref{alg:refSeries} to build a MF model MF$_1$} 
-\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
-	\State{$i\gets1$}
-	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
-	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
-	\State{Compute QoI error estimate
-
-	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
-	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
-	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
-		\State{$i\gets i+1$}
-		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
-		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
-
-		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \cref{eq:superAdjEq})}
-		\State{Compute QoI error estimate
-
-		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
-		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
-	\EndWhile \\
-\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
-\EndProcedure
-\Statex
-\end{algorithmic}
-\end{algorithm}
-%
-\Cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$.
-In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI.
-Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
-
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space~\cite{thesis/SIAM talk?}.
 The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
@@
 We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
+
 %------------------------------------------------------------------------------------------------------------------------%
-\subsubsection{Error Estimate Localization}\label{sec:errLocal}
+\subsection{Extension to Offline-Online Setting}\label{sec:onoff}
+%------------------------------------------------------------------------------------------------------------------------%
+
+\Cref{alg:refSeries} can be naturally extended to an offline-online setting.
+One variation would be analagous to the offline-online decomposition proposed in \cite{LiebWill13}.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
+When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
+The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
+
+Another variation occurs in the context of a quasi-incremental data assimilation approach.
+A multi-fidelity model adaptive constraint can be generated for a given dataset $d_1$ in the offline phase.
+In the online phase, additional data points are included to form an augmented dataset $d_2$, and instead of solving the complete inverse problem with all the data points and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
+The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.
+In such a situation where $d_1\in d_2$, we expect that the model refinement will be concentrated around those of the new data points that also inform the QoI.
+Thus, in the online phase, even though the inverse problem will be solved with all data points $d_2$, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
+
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Error Estimate Localization}\label{sec:errLocal}
 %------------------------------------------------------------------------------------------------------------------------%
@@
 The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-%------------------------------------------------------------------------------------------------------------------------%
-\subsection{Complexity Analysis}\label{sect:alg_complexity}
-%------------------------------------------------------------------------------------------------------------------------%
-We now derive the computational complexity of using Algorithm~\cref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
-Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
-The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}.
-The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$.
-\red{The parts of the supplementary adjoint corresponding to the primary and auxiliary variables can be solved separately, and thus the cost of computing the supplementary adjoint is also $\orderof{3N}^{\gamma}$.}
-
-If one utilizes Algorithm~\cref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
-%
-\begin{align}
-\label{eq:cost_adapt}
-C_{MF} &= \sum_{i=1}^{T}L_{i}(3N)^{\gamma} + 1(3N)^{\gamma} + 2(3N)^{\gamma} \nonumber \\
-&= \sum_{i=1}^{T} (L_i + 3) (3N)^{\gamma}
-\end{align}
-% 
-where $L_i$ is the number of nonlinear solver steps needed to solve the KKT system for the low or mixed fidelity model at each adaptive step.
-The corresponding cost for solving the high fidelity inference problem, with a nonadaptive algorithm, based on a continuation scheme is,
-%
-\begin{equation}
-\label{eq:cost_nadapt}
-C_{HF} = \sum_{i=1}^{C}K_{i}(3N)^{\gamma}
-\end{equation}
-% 
-where $K_i$ is the number of nonlinear solver steps needed to solve the KKT system for the high fidelity model at each continuation step, and $C$ is the number of continuation steps.
-
-Comparing Eq.~\eqref{eq:cost_adapt} and~\eqref{eq:cost_nadapt}, we have,
-%
-\begin{equation}
-\label{eq:cost_compare_0}
-C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 3) < \sum\limits_{i=1}^{C}K_{i}
-\end{equation}
-%
-If the low and multi-fidelity models are linear, or nonlinear in a very small region, then $L_i \approx 1$, and we have the following condition,
-%
-\begin{equation}
-\label{eq:cost_compare_1}
-T < \frac{\sum\limits_{i=1}^{C}K_{i}}{4},
-\end{equation}
-% 
-for the adaptive algorithm to be less costly than solving the high-fidelity inverse problem.
-\red{I'm not sure this section makes sense, since this doesn't seem to hold for any of the actual runs we've done...our mixed models take fewer nonlinear steps than the HF model, but not close enough to one...}
-%The bound on $T$ will be strictest if Gaussian elimination is used, with $\gamma = 3$, giving $T < \frac{\sum\limits_{i=1}^{C}K_{i}}{10}$.
-%
 

### 2016-09-13 paper/numerical_experiments.tex
stashing some paper changes

@@
 %
-\red{We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
+We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
 We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
@@
 We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In \cref{sec:constvfield}, the high fidelity model uses an infinite dimensional (field) representation of the inferred parameter, while the low fidelity model uses a scalar representation.
-%\red{The third experiment has the same setting as the first one, except a highly nonlinear version of the reaction term is considered, and showcases the robustness and computatioanal cost benefits of using the adaptive algorithm.}
-Finally, in \cref{sec:cdvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}
+Finally, in \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings \red{when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}\footnote{\red{Well, compuational savings are only seen in the online-offline case, so that's not the referenced algorithm per se...}}
 
@@
 In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
-In this section, we consider a more realistic pair of models which differ in both the physics included and the mesh resolution, and demonstrate \red{something}.
+In this section, we consider a more realistic pair of models which differ in both the physics included and the mesh resolution, and demonstrate computational savings.
 In \cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D_diffmesh} we describe the results of applying \cref{alg:refSeries} to this pair of models.
@@
 %
+
 We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements.
@@
 All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
+
 \Cref{tab:ref3D_diffmesh} shows the error at the end of each adaptive iteration.
-The high-fidelity inverse problem is solved by using natural continuation on the reaction parameter to avoid stalling the Newton iterations; only two steps are required: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
 Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess.
 The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem.
+The high-fidelity inverse problem does not converge when the low-fidelity solution is used as an initial guess.
+Instead, we solve the inverse problem for an intermediate model
+%
+\begin{equation}
+\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q)
+\end{equation}
+%
+and use the solution as an initial guess for the high-fidelity problem; equivalently, we use two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$. 
 %
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
-& & & (Estimated) & (Actual) & Error (Actual)  \\ \hline
-LF   & 9537  & 168710 & -16463 & -85663 & -103    \\
-MF01 & 13417 & 167366 & -7207  & -84319 & -102    \\
-MF02 & 17895 & 89777  & -6208  & -6730  & -8.10   \\
-MF03 & 21001 & 85880  & -2473  & -2833  & -3.41   \\
-MF04 & 24528 & 83902  & -711   & -855   & -1.03   \\
-MF05 & 27984 & 83119  & 32     & -72    & -0.087  \\
-HF   & 70785 & 83047  & --     & --     & --    \\ \hline
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative \\ 
+& & & & (Estimated) & (Actual) & Error (Actual)  \\ \hline
+LF   & 0    & 9537  & 168710 & -16463 & -85663 & -103    \\
+MF01 & 5.2  & 13417 & 167366 & -7207  & -84319 & -102    \\
+MF02 & 11.4 & 17895 & 89777  & -6208  & -6730  & -8.10   \\
+MF03 & 16.3 & 21001 & 85880  & -2473  & -2833  & -3.41   \\
+MF04 & 22.0 & 24528 & 83902  & -711   & -855   & -1.03   \\
+MF05 & 27.7 & 27984 & 83119  & 32     & -72    & -0.087  \\
+HF   & 100  & 70785 & 83047  & --     & --     & --    \\ \hline
 \end{tabular}
@@
 %
+
 We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are very far from the true errors.
 This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are very different from $\Psi_{HF}$.
-This suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the predicted high-fidelity QoI $I(q_{MF},u_{MF})+\epsilon_i$ for two consecutive iterations agree to within some tolerance.
+Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models are more disimilar, even though the nonlinear term in the high-fidelity models remain the same.
+This behavior suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the predicted high-fidelity QoI $I(q_{MF},u_{MF})+\epsilon_i$ for two consecutive iterations agree to within some tolerance.
 
@@
 %
-In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error.
-This can be attributed to multiple factors: the high-fidelity problem is only mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh.
+In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error, starting from the low-fidelity model.
+This can be attributed to multiple factors: the high-fidelity problem is mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh.
 Generally, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
 
-\Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
-The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
-When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
-The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
-
-To illustrate the offline-online application, we generate ten sets of noisy observations to represent the new data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to anywhere from $2.1\%$ to $8.3\%$ of the observed values).
+To illustrate the first offline-online application described in \cref{sec:onoff}, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values).
 We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
@@
 \hline
-\multirow{2}{*}{Case} & \multirow{2}{*}{DOFs} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
+\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative  \\ 
 & & & (Estimated) & (Actual) & Error (Actual) \\ \hline
-LF   & 9537  & 166774 & --    & -84326 & -102.3 \\
-MF01 & 13417 & 164597 & 4347  & -82149 & -99.65  \\
-MF02 & 17895 & 88867  & -5921 & -6418  & -7.79  \\
-MF03 & 21001 & 85237  & -2414 & -2789  & -3.38  \\
-MF04 & 24528 & 83411  & -724  & -963   & -1.17  \\
-MF05 & 27984 & 82664  & -18   & -216   & -0.26 \\
-HF   & 70785 & 82500  & --    & --     & --  \\ \hline
+LF   & 0    & 166774 & --    & -84326 & -102.3 \\
+MF01 & 5.2  & 164597 & 4347  & -82149 & -99.65  \\
+MF02 & 11.4 & 88867  & -5921 & -6418  & -7.79  \\
+MF03 & 16.3 & 85237  & -2414 & -2789  & -3.38  \\
+MF04 & 22.0 & 83411  & -724  & -963   & -1.17  \\
+MF05 & 27.7 & 82664  & -18   & -216   & -0.26 \\
+HF   & 100 & 82500  & --    & --     & --  \\ \hline
 \end{tabular}
 \end{table}
+
 %

### 2016-09-13 paper/old_sections.tex
stashing some paper changes

@@
-\if{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Complexity Analysis}\label{sect:alg_complexity}
+%------------------------------------------------------------------------------------------------------------------------%
+We now derive the computational complexity of using Algorithm~\cref{alg:refSeries} to solve an inference problem, and compare it to extant strategies.
+Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system.
+The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}.
+The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$.
+\red{The parts of the supplementary adjoint corresponding to the primary and auxiliary variables can be solved separately, and thus the cost of computing the supplementary adjoint is also $\orderof{3N}^{\gamma}$.}
+
+If one utilizes Algorithm~\cref{alg:refSeries} to solve the inference problem, with $T$ adaptive iterations the total computational cost is,
+%
+\begin{align}
+\label{eq:cost_adapt}
+C_{MF} &= \sum_{i=1}^{T}L_{i}(3N)^{\gamma} + 1(3N)^{\gamma} + 2(3N)^{\gamma} \nonumber \\
+&= \sum_{i=1}^{T} (L_i + 3) (3N)^{\gamma}
+\end{align}
+% 
+where $L_i$ is the number of nonlinear solver steps needed to solve the KKT system for the low or mixed fidelity model at each adaptive step.
+The corresponding cost for solving the high fidelity inference problem, with a nonadaptive algorithm, based on a continuation scheme is,
+%
+\begin{equation}
+\label{eq:cost_nadapt}
+C_{HF} = \sum_{i=1}^{C}K_{i}(3N)^{\gamma}
+\end{equation}
+% 
+where $K_i$ is the number of nonlinear solver steps needed to solve the KKT system for the high fidelity model at each continuation step, and $C$ is the number of continuation steps.
+
+Comparing Eq.~\eqref{eq:cost_adapt} and~\eqref{eq:cost_nadapt}, we have,
+%
+\begin{equation}
+\label{eq:cost_compare_0}
+C_{MF} < C_{HF} \implies \sum_{i=1}^{T} (L_i + 3) < \sum\limits_{i=1}^{C}K_{i}
+\end{equation}
+%
+If the low and multi-fidelity models are linear, or nonlinear in a very small region, then $L_i \approx 1$, and we have the following condition,
+%
+\begin{equation}
+\label{eq:cost_compare_1}
+T < \frac{\sum\limits_{i=1}^{C}K_{i}}{4},
+\end{equation}
+% 
+for the adaptive algorithm to be less costly than solving the high-fidelity inverse problem.
+\red{I'm not sure this section makes sense, since this doesn't seem to hold for any of the actual runs we've done...our mixed models take fewer nonlinear steps than the HF model, but not close enough to one...}
+
+%
+%
+%
+%
+%
+%
+%
+%
+
+\red{\Cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase.
+In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
+The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.
+}
+%
+\alglanguage{pseudocode}
+\begin{algorithm}[h!]
+\small
+\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
+\label{alg:refonoff}
+\begin{algorithmic}[1]
+\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
+\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use \cref{alg:refSeries} to build a MF model MF$_1$} 
+\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
+	\State{$i\gets1$}
+	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
+	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
+	\State{Compute QoI error estimate
+
+	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
+	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
+	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{$i\gets i+1$}
+		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
+		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
+
+		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \cref{eq:superAdjEq})}
+		\State{Compute QoI error estimate
+
+		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
+		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
+	\EndWhile \\
+\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
+\EndProcedure
+\Statex
+\end{algorithmic}
+\end{algorithm}
+%
+\Cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$.
+In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI.
+Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
+
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+
 %------------------------------------------------------------------------------------------------------------------------%
@@
 }
-\fi{false} %--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--*--
+
+%
+%
+%
+%
+%
+%
+%
+%
 

### 2016-09-13 paper/old_sections.tex
added a bit to numerical results, transplanted conclusion from thesis

@@
 We also note that the mixed-fidelity inverse problems consistently take less time to solve than the high-fidelity inverse problems; however, the high-fidelity inverse problem is still only mildly nonlinear and requires few nonlinear steps to converge, so the difference in their solution times is not large enough to justify estimating the mixed-fidelity QoI errors as well.
+
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+
+\begin{table}
+\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets; all averages only over those datasets for which the high-fidelity problem converged when given the low-fidelity problem as an intial guess.}
+%\label{tab:ref3D_newdata_times_diffmesh}
+\centering
+\begin{tabular}{ccc|c|c|c}
+\cline{4-5} 
+ & & & \multicolumn{2}{|c|}{Error Estimation} & \\
+\cline{1-6}
+\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{DOFs}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
+\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
+\cline{1-6}
+\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{9537}   & 16   & --  & -- & \multicolumn{1}{|c|}{--} \\ \hline
+\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 156  & 101 & 261 & \multicolumn{1}{|c|}{517} \\ \hline
+\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 304  & 175 & 183 & \multicolumn{1}{|c|}{662} \\ \hline
+\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 385  & 228 & 187 & \multicolumn{1}{|c|}{801} \\ \hline
+\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 347  & 202 & 193 & \multicolumn{1}{|c|}{743} \\ \hline
+\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 470  & 275 & 212 & \multicolumn{1}{|c|}{957} \\ \hline
+\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 1185 & --  & --  & \multicolumn{1}{|c|}{1185} \\ \hline
+\end{tabular}
+\end{table}
+%

### 2016-09-29 paper/abstract.tex
small paper edits

@@
-Inference problems are often constrained by state equations, which arise from conservation laws, and constitutive relations.
+\red{Inference problems are often constrained by state equations, which arise from conservation laws, and constitutive relations.
 Often, a hierarchy of models can be derived from such laws and relations, reflecting varying fidelity versus cost tradeoffs.
-We introduce a goal oriented, model adaptive, inference algorithm, which allows users to achieve an aritrary error tolerance, while minmizing the use of high fidelity constraints.
-Numerical experiments test the algorithm on a highly nonlinear inverse problem, and showcase the computational savings and robustness benefits of this new approach.
+We introduce a goal-oriented, model adaptive, inference algorithm, which allows users to achieve an arbitrary error tolerance, while minimizing the use of high fidelity constraints.
+Numerical experiments exercise the algorithm on a highly nonlinear inverse problem, and showcase the computational savings and robustness benefits of this new approach.}

### 2016-09-29 paper/algorithms.tex
small paper edits

@@
-\section{Goal Oriented Inference Algorithm}\label{sect:alg}
+\section{Goal-Oriented Inference Algorithm}\label{sect:alg}
 %
@@
 This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
-Algorithm~\cref{alg:refSeries} describes this approach.
+\Cref{alg:refSeries} describes this approach.
 Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
@@
 %------------------------------------------------------------------------------------------------------------------------%
-Algorithm~\cref{alg:refSeries} does not require a specific method for localizing the error estimate.
+\Cref{alg:refSeries} does not require a specific method for localizing the error estimate.
 A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element.

### 2016-09-29 paper/intro.tex
small paper edits

@@
 Specifically, we consider the case where there is a target quantity of interest to be computed from the inferred parameters.
-The use of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; an extension to inverse problems is described in \cite{OdenPrudetal10}.\red{\footnote{Vikram, this was known at the time of the thesis, but not not cited in the thesis.
-I'm not actually sure how to handle this, since this tries to solve the same problem we do, but I don't understand it well enough to do a detailed analysis.
-I did manage to find the book, if you'd like me to scan the pages to you...}} We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest.
+The use of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; an extension to inverse problems is described in \cite{OdenPrudetal10}.
+We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models, in a target quantity of interest.
 Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.
 
-The rest of the paper is organized as follows, \cref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
-Then, in \cref{sect:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis.
-\cref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.
-Finally, we present conclusions and direction for future work in \cref{sect:conc}.
-
-%% \subsection{draft outline}
-%% \bit
-%% \item background/previous work? to put this work in context?
-%%   %this is probably enough? at least for previous work...
-%%   %what context though? is this another way to approach inverse problems?
-%% \item mathematical formulation
-%%   \bit
-%%   \item define inverse problem and qoi
-%%   \item derive error estimate
-%%   \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
-%%   \item relation to mesh refinement
-%%   \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem?
-(Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
-%%     %solving for adjoint and forward simultaneously (KKT) might cause you to lose an order of accuracy?
-%%     %where was that book that Oden might have mentioned inverse application of his method?
-%%       %Multiscale methods : bridging the scales in science and engineering / edited by Jacob Fish. (TA335.M85 2010 in barker)
-%%   \eit
-%% \item numerical results (perhaps not include all of these...)
-%%   \bit
-%%   \item convection-diffusion(-reaction)
-%%     \bit
-%%     \item interpretation of error estimate breakdown (interaction of QoI with observations)
-%%     \item large reaction term: MF model more cooperative with nonlinear solver
-%%     \eit
-%%   \item convection-diffusion-reaction, field vs scalar description of parameters
-%%     \bit
-%%     \item interface question: do we enforce continuity between the two models' parameters?
-%%       %-navierstokes+stokes seems to require continuity of flux and velocity across boundary...?
-%%       %-is it okay to mix diff and convdiff for the forward like we did?
-does the discontinuous velocity break any intergration-by-parts   assumptions?
-(no that's only if discontinuity in diffusion bit...)
-%%     \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
-%%     %alternative way to describe 'scalar' case?
-but here we say there is one scalar, so this would be how to combine them...if you wanted plateaus to be different, can let LF model be two-scalars...
-%%     %fig 3.10 -> what does the inferred field look like? does it look like two different plateaus?
-%%       % practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r4p2_deref/ (pushed 10/3/15)
-%%         %at the very last refinement, most of refined region seems to be two large humps...and a section that looks pretty much like the surrounding scalar...so maybe 3 patches...
-%%     \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
-%%     \eit
-%%   \item alternate/additional example: use setup from B+V? navier-stokes and another model?
-%%     \bit
-%%     \item potential flow?
-model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
-%%     \item there would still be the question of how to interface the models...(in stokes vs navier-stokes foward paper, they just required continuity of state variables (velocity field and presssure))
-%%     %do scalar + field for infer BCs on BV NS thing? try for different QoIs? (can we have a variable live on a boundary while the rest are inside? vikram will poke roy about implementing)
-%%     %stokes is good in slow flows...not in boundary layer cuz gradient is high...
-%%     %what situation would it make sense to use the LF model in some place?
-%%     \eit
-%%   \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
-%%   \eit
-%% \item conclusion...what goes in this section usually? summary and directions for future work?
-%% \eit
+The rest of the paper is organized as follows.
+\Cref{sect:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
+Then, in \Cref{sect:alg} we discuss the goal-oriented inference algorithm and present a computational complexity analysis.
+\Cref{sect:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.
+Finally, we present conclusions and directions for future work in \Cref{sect:conc}.

### 2016-09-29 paper/numerical_experiments.tex
small paper edits

@@
 %
-We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
-We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
+We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
+We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
 In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
 We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-Finally, in \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings \red{when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}\footnote{\red{Well, compuational savings are only seen in the online-offline case, so that's not the referenced algorithm per se...}}
+In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.
 
@@
 In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
-\cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
+\Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
 %
@@
 \begin{cases}
--42.0 & \textrm{if }x\in\Omega_{HF} \\
+k_r & \textrm{if }x\in\Omega_{HF} \\
 0 & \textrm{if }x\in\Omega_{LF}.
@@
 For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations).
-Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
+Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
 %
@@
 The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
-The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
+The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
 %
@@
 We now present the results for solving the inference problem using \cref{alg:refSeries}.
-Once the QoI error estimate is calculated using \ref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
+Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
@@
 %
-\begin{table}
-\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets; all averages only over those datasets for which the high-fidelity problem converged when given the low-fidelity problem as an intial guess.}
-%\label{tab:ref3D_newdata_times_diffmesh}
-\centering
-\begin{tabular}{ccc|c|c|c}
-\cline{4-5} 
- & & & \multicolumn{2}{|c|}{Error Estimation} & \\
-\cline{1-6}
-\multicolumn{1}{|c|}{\multirow{3}{*}{Case}} & \multicolumn{1}{|c|}{\multirow{3}{*}{DOFs}} & Inverse & Auxiliary & Supplementary & \multicolumn{1}{|c|}{Total} \\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Problem & Variables & Adjoint & \multicolumn{1}{|c|}{Solution}\\
-\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & Time (s) &  Time (s) & Time (s) & \multicolumn{1}{|c|}{Time (s)}\\
-\cline{1-6}
-\multicolumn{1}{|c|}{LF}    & \multicolumn{1}{|c|}{9537}   & 16   & --  & -- & \multicolumn{1}{|c|}{--} \\ \hline
-\multicolumn{1}{|c|}{MF01}  & \multicolumn{1}{|c|}{13147}  & 156  & 101 & 261 & \multicolumn{1}{|c|}{517} \\ \hline
-\multicolumn{1}{|c|}{MF02}  & \multicolumn{1}{|c|}{17895}  & 304  & 175 & 183 & \multicolumn{1}{|c|}{662} \\ \hline
-\multicolumn{1}{|c|}{MF03}  & \multicolumn{1}{|c|}{21001}  & 385  & 228 & 187 & \multicolumn{1}{|c|}{801} \\ \hline
-\multicolumn{1}{|c|}{MF04}  & \multicolumn{1}{|c|}{24528}  & 347  & 202 & 193 & \multicolumn{1}{|c|}{743} \\ \hline
-\multicolumn{1}{|c|}{MF05}  & \multicolumn{1}{|c|}{27984}  & 470  & 275 & 212 & \multicolumn{1}{|c|}{957} \\ \hline
-\multicolumn{1}{|c|}{HF}    & \multicolumn{1}{|c|}{70785}  & 1185 & --  & --  & \multicolumn{1}{|c|}{1185} \\ \hline
-\end{tabular}
-\end{table}
-%
+We see that the mixed-fidelity models, when applied to noisy datasets different from that with which they were generated, continue to perform well in achieving a small error in the QoI while limiting the use of the high-fidelity model to less than a third of the domain.
+Given the same initial guess, the mixed-fidelity inverse problems takes less time on average than the high-fidelity inverse problem to solve, and they converge consistently.
+
+In testing this online-offline setting with a larger range of datasets, we would like to note some additional observations.
+Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference.
+For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$.
+The performance gap tends to widen as the two datasets become more different.
+Suppose one generated $d_1$ using the high-fidelity model $d_2$ using a model which differed from the high-fidelity model in its domain, boundary conditions, and reaction coefficient; then a mixed-fidelity model adaptively formed based on $d_1$ might not give a low QoI error when used to infer from $d_2$.
+However, when the adaptivity algorithm is directly applied to this $d_2$, it is still able to find a mixed-fidelity model with a low QoI error.
+This behavior suggest that, if resources allow, it is best to perform the adaptivity online with the true observations.
+If one is confident that one's high-fidelity model is a good approximation of reality, then the online-offline approach can potentially give a faster yet accurate QoI estimate.

### 2016-09-30 paper/abstract_v1.tex
renamed paper tex files so that we can do latexdiff on them

Inference problems are often constrained by state equations, which arise from conservation laws, and constitutive relations. Often, a hierarchy of models can be derived from such laws and relations, reflecting varying fidelity versus cost tradeoffs. We introduce a goal oriented, model adaptive, inference algorithm, which allows users to achieve an arbitrary error tolerance, while minimizing the use of high fidelity constraints. Numerical experiments exercise the algorithm on a highly nonlinear inverse problem, and showcase the computational savings and robustness benefits of this new approach.

### 2016-09-30 paper/conclusions_v1.tex
renamed paper tex files so that we can do latexdiff on them

--- 2015-05-20 practice/docs/thesis/conclusion_v03.tex
@@
-\chapter{Conclusion} \label{chap:conc}
+\section{Conclusion}\label{sect:conc}
 
-In this chapter we summarize the main contributions of the thesis and discuss future work.
-
-%------------------------------------------------------------%
-\section{Thesis Summary} 
-%------------------------------------------------------------%
-
-The contribution of this work is an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters.
-We applied this method to pairs of models, one that differed in the physics included and one that differed in the space to which the parameters belonged.
-In both cases, we were able to obtain a value for the QoI with a small relative error without having to solve the inverse problem with the high-fidelity model.
-In these cases, the element-wise decomposition of the error estimate also indicated regions of the parameter field that were both informed by the observations and informative to the QoI.
-
-The inverse problem with the high-fidelity models examined were not so expensive to solve as to warrant the adaptive formation of a mixed-fidelity model; however, based on existing work with concurrent multi-fidelity models, savings in computational cost are expected in cases where the high-fidelity model is more complex and solving the inverse problem with the high-fidelity model is less tractable.
-We demonstrated a case where the inverse problem with the high-fidelity model could not be solved without a more complex nonlinear solver, but where our method resulted in a mixed-fidelity model for which the inverse problem could be solved with a simple nonlinear solver, with a small relative error in the QoI.
+We have presented an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters.
+We applied this method to pairs of low- and high-fidelity models of convection-diffusion-reaction phenomena and were able to obtain QoI estimates with a small relative error without having to solve the inverse problem with the high-fidelity model.
+In these cases, the localization of the error estimate also indicated regions of the domain that were important to the interaction of the observations and the QoI.
 
@@
 
-An immediate direction for extension of this work is to the case of the statistical inverse problem.
+A direction for extension of this work is to the case of the statistical inverse problem.
 Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization.
@@
 
-A popular approach to solving the statistical inverse problem is to apply a Bayesian framework.
+The statistical inverse problem is often solved in a Bayesian framework.
 Bayes' rule is used to combine a prior distribution, which captures prior beliefs about the parameters, and a likelihood distribution, which captures the likelihood of observations given an instance of the parameter values and a model of noise in the observations, to give a posterior distribution on the parameters.
@@
 One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled.
-Such a direction is suggested by the results presented in Section \ref{sec:constvfield}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space.
+Such a direction is suggested by the results presented in Section \ref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space.
 In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution.
@@
 
-%soil chapter in Multiscale Modeling: A Bayesian Perspective - seems to do hierachical multiscale in context of mcmc
-%http://arxiv.org/pdf/1402.1694v3.pdf has pointers to where people use surrogate models to avoid evaluating forward model too often...
+%other directions for extensions that I can't seem to fit in:
+%mixing models in time as well? (different mixes of models at different time steps?)
+%superadj on intermediate mesh; preliminary results suggest that error estimates remain reasonable and generation of mixed-fidelity models can continue despite the additional approximations to the supplementary adjoint
 
-%read http://www.stat.osu.edu/~comp_exp/jour.club/KennedyOHagan2000.pdf for the lulz?
-
-%stochastic
-%anything in chad's about curse of dimensionality?
-%wolfgang bangert -> mesh refinement and stochastic, keep coarse sometimes...see if this might be related to extension?
-	%can't seem to find anything by him related to this...at least, not suggested by title...
-%matt parno or patrick's stuff? exploring with surrogate models mostly and then upping fidelity strategically?
-
-%poke stochastic weak form? is that another way we could think about extending to stochastic case?
+%\item \Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
+In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model.
+As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI (NOT TRUE the primary and aux vars appear in the rhs...).
+When these linearities do not all hold, one cannot obtain an exact error estimate.
+The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$.
+As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.

### 2016-09-30 paper/conclusions_v2.tex
renamed paper tex files so that we can do latexdiff on them

--- 2016-09-30 paper/conclusions_v1.tex
@@
 A direction for extension of this work is to the case of the statistical inverse problem.
-Thus far in this work, we have considered the deterministic inverse problem, as described in Section \ref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization.
+Thus far in this work, we have considered the deterministic inverse problem, as described in \Cref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization.
 However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}.
@@
 One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled.
-Such a direction is suggested by the results presented in Section \ref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space.
+Such a direction is suggested by the results presented in \Cref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space.
 In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution.

### 2016-09-30 paper/numerical_experiments_v1.tex
renamed paper tex files so that we can do latexdiff on them

--- 2016-09-29 paper/numerical_experiments.tex
@@
 %
-We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
-We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
+We now use \cref{alg:refSeries} to solve goal oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
+We first consider simple two-dimensional models in order to explore the behavior of the algorithm in relation to iteration number as well as the placement of observations and QoI regions.
 In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
 We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.
+Finally, in \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models to illustrate computational savings \red{when using \cref{alg:refSeries}, as compared to solving the high-fidelity inverse problem.}\footnote{\red{Well, compuational savings are only seen in the online-offline case, so that's not the referenced algorithm per se...}}
 
@@
 In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
-\Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
+\cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
 %
@@
 \begin{cases}
-k_r & \textrm{if }x\in\Omega_{HF} \\
+-42.0 & \textrm{if }x\in\Omega_{HF} \\
 0 & \textrm{if }x\in\Omega_{LF}.
@@
 For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations).
-Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
+Observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
 %
@@
 The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
-The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
+The diffusion coefficient is chosen so that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
 %
@@
 We now present the results for solving the inference problem using \cref{alg:refSeries}.
-Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
+Once the QoI error estimate is calculated using \ref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.

### 2016-10-03 paper/algorithms_v2.tex
stashing paper edits (new intro outline, reorganized some section, clarified some notation)

--- 2016-09-29 paper/algorithms.tex
@@
-\section{Goal-Oriented Inference Algorithm}\label{sect:alg}
+\section{Goal-Oriented Inference Algorithm}\label{sec:alg}
 %
@@
 
-Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Adaptive Model Mixing ALgorithm}\label{sec:adapt_alg}
+%------------------------------------------------------------------------------------------------------------------------%
+
+Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,OTHERS}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
@@
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space~\cite{thesis/SIAM talk?}.
-The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
+The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
 The derived error estimate is not applicable to all models, however.
@@
 %------------------------------------------------------------------------------------------------------------------------%
-\subsection{Extension to Offline-Online Setting}\label{sec:onoff}
+%\subsection{Extension to Offline-Online Setting}\label{sec:onoff}
 %------------------------------------------------------------------------------------------------------------------------%
 
-\Cref{alg:refSeries} can be naturally extended to an offline-online setting.
+%\Cref{alg:refSeries} can be naturally extended to an offline-online setting.
 One variation would be analagous to the offline-online decomposition proposed in \cite{LiebWill13}.
@@
 
-Another variation occurs in the context of a quasi-incremental data assimilation approach.
+%Another variation occurs in the context of a quasi-incremental data assimilation approach.
 A multi-fidelity model adaptive constraint can be generated for a given dataset $d_1$ in the offline phase.
@@
 We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
-Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as,
-%
-\begin{equation}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
-\end{equation}
-%
-We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
-Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \chi_i)$.
-The error estimate,
-%
-\begin{equation}
-\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
-\end{equation}
-%
-where,
-%
-\begin{equation}\label{eq:basisblame}
-\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
-\end{equation}
-%
-can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
+For ease of implementation, we can choose these basis functions to be the same as those spanning the space in which we solve for the primary, auxiliary, and supplementary adjoint vatriables.
 Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution.
-The basis functions with the largest error contributions are flagged, and the elements in their support are refined.
-
-%does B+V's method for 'cheaply' getting auxiliary variables not really work when parameters are a field and not handful of scalars?
-does it even matter, since bulk of costs seem to be going to super-adjoint?
-
-%% Although Equation (\ref{eq:finErrExp}) is exact, the error estimate that can be calculated in practice will not generally be exact.
-Let us refer to a goal-oriented inverse problem as linear when the state $u$ and parameters $q$ are linearly related, the observation operator $C$ is linear in $u$, the regularization term $R$ is at most quadratic in the parameters, and the QoI functional $I$ is linear in $u$ and $q$.
-The remainder term $\mathcal{R}(e^3)$ is included in Equation (\ref{eq:finErrExp}) but would not, in practice, be calculated; in the case of a linear goal-oriented inverse problem, the remainder term disappears, but it is nonzero in general.
-
-%% In motivating our approach, it is assumed that one can most accurately calculate the QoI from the parameter values inferred using the highest-fidelity forward model available, but that solving the inverse problem with this model is prohibitively expensive.
-It is also assumed that solving the inverse problem with a mixed-fidelity model, where this highest-fidelity model is only used in a portion of the domain, will be cheaper.
-There is a cost incurred by using our approach to design such a mixed-fidelity model, however, and it will sometimes be the case that the cost of obtaining this mixed-fidelity model exceeds that of just solving the inverse problem with the highest-fidelity model directly.
-Naively, if the auxiliary variables $\chi$ have $n$ degrees of freedom, they can be found by solving an $n\times n$ linear system, while the supplementary adjoint $\Lambda$ can be found by solving a $2n\times2n$ linear system.
-The cost of solving for the auxiliary variables can be reduced by using a technique described in \cite{BecVex05}, and the cost of solving for the supplementary adjoint $\Lambda$ can be reduced by reusing preconditioners.
-In general there are no guarantees that obtaining a mixed-fidelity model that meets the desired QoI error criterion will be less costly than just solving the inverse problem with the high-fidelity model.
-However, our approach targets problems for which solving the inverse problem with the high-fidelity model is prohibitively expensive, in which case it is expected that the cost of obtaining a satisfactory mixed-fidelity model will be comparatively low.
-Even in the case where a mixed-fidelity model for which the QoI error is adequately small cannot be found before another limit (for example, a maximum number of adaptive iterations) is reached, one still has an estimate for the error in the QoI without solving the prohibitively expensive inverse problem.
+The basis functions with the largest error contributions are flagged, and the elements in their support are added to the high-fidelity subdomain.
+Basis functions whose support lie completely in the high-fidelity region will have a zero contribution and the elements in their support are never flagged for refinement again.

### 2016-10-03 paper/intro_v2.tex
stashing paper edits (new intro outline, reorganized some section, clarified some notation)

\section{Introduction}

In scientific and engineering contexts, physical systems are represented by mathematical models, which often take the form of partial differential equations (PDEs). These models are characterized by a set of parameters, and relate these parameters to states that can be observed. In the inverse problem, the parameters are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}. For a range of applications, the parameters may be numerous, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI); we refer to the setting where the goal of inferring parameters is to use them in predicting a QoI as a \textit{goal-oriented inverse problem}. A given physical system can be represented with varying degrees of fidelity by different models; a higher-fidelity model is able to more accurately represent reality, but is also usually more difficult to solve. In the context of the goal-oriented inverse problem, one may choose a lower-fidelity model with which to perform inference, sacrificing accuracy in the state and/or parameters in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance. In this work, we present an approach to manage the fidelity of modeling choices in solving the inverse problem, so as to achieve a desired level of accuracy in the QoI prediction, without necessarily resolving the parameters accurately. We adaptively form a mixed-fidelity model with which we solve the inverse problem by using models of different levels of fidelity in different parts of the domain.

% Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters. One way to control the cost of the model is to consider different meshes. In the context of the forward problem, so and so have done a-b-c. In the context of the inverse problem, so and so have done x-y-z.

% Another way to control the cost of the model is to change the fidelity to which the physics are represented. The simultaneous use of multifidelity models for forward simulations is well established; two main strategies exist for combining models: hierarchical and concurrent methods. (Describe what these mean)

% We focus on current methods of combining models. concurrent multifidelity models appear in a range of contexts, such as...

We aim to combine the ideas in goal-oriented methods for inverse problems, and goal-oriented model adaptivity approaches for forward modeling. The objective of this work is to formulate a method that allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. To do this, we first assume that solving the inverse problem with the highest-fidelity model would result in the most accurate QoI, but that solving this inverse problem is prohibitively expensive. We derive a third-order estimate for the QoI error from inferring the parameters using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.

The rest of the paper is organized as follows, \Cref{sec:form} presents the mathematical formulation and error analysis for the multi-model inverse problem. Then, in \Cref{sec:alg} we discuss the goal oriented inference algorithm and present a computational complexity analysis. \Cref{sec:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem. Finally, we present conclusions and directions for future work in \Cref{sec:conc}.

### 2016-10-03 paper/mathematical_formulation_v2.tex
renamed paper tex files so that we can do latexdiff on them
stashing paper edits (new intro outline, reorganized some section, clarified some notation)

--- 2016-06-24 paper/mathematical_formulation.tex
@@
-\section{Mathematical Formulation}\label{sect:form}
+\section{Mathematical Formulation}\label{sec:form}
 %
-We first introduce the goal oriented inverse problem formally, providing definitions and optimization, variational statments.
-Then we will derive a rigorous, a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower fidelity constraints.
+We first introduce the goal-oriented inverse problem formally. Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower-fidelity models.
 
@@
 %
-Let $Q$, $U$ be Hilbert spaces.
-We seek to infer an unknown parameter $q \in Q$.
-The parameter is constrained by a state equation, with a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
-%
+Consider a model for which the Galerkin formulation of the weak form is written as
 \begin{equation}
+a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
 \label{eq:weakForm}
-a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U.
 \end{equation}
-%
-The bilinear form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.
+where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
+The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \cref{eq:weakForm}, they are linear with respect to $\phi$).
 Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
@@
 
-The unknown parameter $q$ can then be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
+The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
 Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
@@
 %
-Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the constraints given by \cref{eq:weakForm}.
-
-The constraints given by \cref{eq:weakForm} are typically models of physical processes or systems.
-However, a given physical system need not have a unique model that can describe it; there may be various models of different fidelities.
-This naturally introduces a hierarchy of models and, a tradeoff between fidelity and computational expense.
-Consider two models with which we infer parameters: a high-fidelity (HF) model and a low fidelity (LF) model.
-We then have a specific form of the inverse problem in \cref{eq:invOpt} with this model,
-\begin{equation}
-\begin{array}{r@{}c}
-\min\limits_{q_{HF},u_{HF}} & \quad J_{HF}(q_{HF},u_{HF})=\frac{1}{2}\|d-C_{HF}(u_{HF})\|_2^2 + R_{HF}(q_{HF}) \\ \textrm{s.t.
-}& \quad a_{HF}(u_{HF},q_{HF})(\phi_{HF})=\ell_{HF}(q_{HF})(\phi_{HF}),\quad\forall\phi_{HF}\in U_{HF},
-\end{array}
-\end{equation}
-for which we have the Lagrangian,
-\begin{multline}
-\mathcal{L}_{HF}(q_{HF},u_{HF},z_{HF}) = \\
-J_{HF}(q_{HF},u_{HF})-(a_{HF}(u_{HF},q_{HF})(z_{HF})-\ell_{HF}(q_{HF})(z_{HF})).
-\end{multline}
-The inverse problem formulation and Lagrangian with the lower fidelity model can be similarly defined, and be identified with subscript $LF$.
+Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \cref{eq:weakForm}, which appears as a constraint in \cref{eq:invOpt_cons}.
+The constraints \cref{eq:invOpt_cons} are typically models of physical processes or systems.
+A given physical system can be described to varying degrees of fidelity using different models.
+This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution one is interested in.
 
@@
 Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
-We thus seek to introduce the QoI functional $I$ into the inverse problem formulation, by introducing auxilary variables and additional adjoint equations.
-Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of constraints other than those given by \cref{eq:invOpt_cons}.
+Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is in the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
+We thus seek to introduce the QoI functional $I$ into the inverse problem formulation by introducing auxilary variables and additional adjoint equations.
+Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of difference models in the constraint \cref{eq:invOpt_cons}.
 %
@@
 In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
-The main result is,
 %
@@
 \label{thm:error_estimate}
-Following the notation established in \cref{sec:setup}, let the bilinear form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Consider the inverse problem described by the constrained optimization problem \cref{eq:invOpt}.
+Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
 Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
@@
 
-Denote by $\Psi_{HF}$ and $\Psi_{LF}$, stationary points of the high and low fidelity versions of \cref{eq:InvsOpt_auglag} and, consider the adjoint problem,
+Consider two models with which parameters can be inferred: a high-fidelity model and a lower-fidelity model.
+Let the high-fidelity (HF) and low-fidelity (LF) models, and their corresponding variables, Lagrangians, and augmented Lagrangians, be distinguished by the subscripts $_{HF}$ and $_{LF}$, respectively.
+In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
+Consider the adjoint problem
 %
@@
 %
-for the supplementary adjoint $\Lambda$. Then, the error in the Quantity of Interest $I$ is given by,
+for the supplementary adjoint $\Lambda$, where $\Phi$ is a test function. Then, the error in the Quantity of Interest $I$ is given by,
 %
@@
 \label{eq:beckvex}
-\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
 \end{equation}
@@
 \begin{multline}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3). \nonumber
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3), \nonumber
 \end{multline}
@@
 %
-The above error estimate is general and the lower-fidelity model can also be a mixed-fidelity model that combines the high- and low-fidelity model.
-Given a low-fidelity model and a high-fidelity model, an intermediate, mixed-fidelity (MF) model can be formed by using the high-fidelity model in some parts of the domain, and the low-fidelity model in the rest of the domain.

### 2016-10-03 paper/numerical_experiments_v2.tex
stashing paper edits (new intro outline, reorganized some section, clarified some notation)

--- 2016-09-29 paper/numerical_experiments.tex
@@
-\section{Numerical Experiments}\label{sect:numexp}
+\section{Numerical Experiments}\label{sec:numexp}
 %
@@
 We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
-In \cref{sec:cdvcdr}, the high fidelity model is a convection-diffusion-reaction nonlinear model, and the low fidelity model is a linear convection-diffusion model.
+In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model.
 We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
+In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented.
 In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.
@@
 We now present the results for solving the inference problem using \cref{alg:refSeries}.
-Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions, as described in \cref{eq:basisblame}.
+Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions.
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
@@
 \centering
-\subfloat[MF$_0$ ($0\%$ HF)]{
+\subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
   \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
@@
 In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
-Since the constraining model is an elliptic PDE, with a weak convection, information flow is localized, and is weakly convected from left to right.
+Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right.
 Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region.
@@
 \Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively.
-In this case, we see that the QoI error of only $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
+In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
 We note that, in general, there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
@@
 %
-The error estimate decomposition \cref{eq:basisblame} suggests the use of the high-fidelity model in areas of the domain that are important to the interaction of the observations and QoI; the interaction of these two can be complex, and the areas suggested for refinement may be nonintuitive.
+The error estimate decomposition suggests the use of the high-fidelity model in areas of the domain that are important to the interaction between the observations and QoI; the interaction between these two can be complex, and the areas suggested for refinement may be nonintuitive.
 To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region.
 For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate.
-However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased, but did not consistently increase or decrease with the number of data points.
+However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased.
 
-The error decomposition for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations is shown in \cref{fig:qoiStudy}.
+The error decompositions for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations are shown in \cref{fig:qoiStudy}.
 The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
@@
 }
-  \caption{Compare the error estimate decomposition (\protect\subref{subfig:obsLF}-\protect\subref{subfig:obsMFlast}), given the same observations (teal points in (\protect\subref{subfig:obsSetup})) and varying QoI region (purple box in (\protect\subref{subfig:obsSetup})).}
+  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF}-\protect\subref{subfig:obsMFlast}) given the same observations and different QoI regions.}
   \label{fig:qoiStudy}
@@
 }
-  \caption{Compare the error estimate decomposition (\protect\subref{subfig:obsLF2}-\protect\subref{subfig:obsMFlast2}), given the same QoI region (purple box in (\protect\subref{subfig:obsSetup2})) and varying observations (teal points in (\protect\subref{subfig:obsSetup2})).}
+  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup2}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF2}-\protect\subref{subfig:obsMFlast2}) given different observations and the same QoI region.}
   \label{fig:dataStudy}
 \end{figure}
+
+%------------------------------------------------------------------------------------------------------------------------%
+\subsection{Constant vs Field Parameters} \label{sec:constvfield}
+%------------------------------------------------------------------------------------------------------------------------%
+\red{THIS SUBSECTION IS OLD AND CURRENTLY A PLACEHOLDER TO GAUGE LENGTH}.
+It is not necessary for the low- and high-fidelity models to differ in the physics included.
+A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity.
+In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
+%------------------------------------------------------------%
+\subsubsection{Problem Setup}
+%------------------------------------------------------------%
+We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
+\begin{equation}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
+\end{equation}
+with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
+\begin{equation}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
+\end{equation}
+differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
+Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain.
+For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
+As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
+
+Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
+Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
+%------------------------------------------------------------%
+\subsubsection{Adaptive Model Refinement Results}
+%------------------------------------------------------------%
+As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
+The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
+With each iteration, an additional $10\%$ of the elements are marked for refinement.
+This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
+
+\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
+Each linear Langrange basis function's contribution is plotted at its nonzero node.
+%
+\begin{figure}[htbp]
+\centering
+\subfloat[MF$_0$ ($0\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
+} \\
+\subfloat[MF$_1$ ($10\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
+} \\
+\subfloat[MF$_2$ ($20\%$ HF)]{
+  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
+} \\
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_3$ ($30\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_4$ ($40\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+%\begin{subfigure}[b]{\textwidth}
+%	\centering
+%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
+%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
+%  \vspace{-0.7\baselineskip}
+%  \caption{MF$_5$ ($50\%$ HF)}
+%  \vspace{0.8\baselineskip}
+%\end{subfigure}
+\subfloat[MF$_6$ ($60\%$ HF)]{
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
+}
+\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.
+The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
+\label{fig:svfRef}
+\end{figure}
+%
+Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
+This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
+
+The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
+%
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
+\label{fig:svfErr}
+\end{figure}
+%
+In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
+The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
+We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
 

### 2016-10-04 paper/numerical_experiments_v2.tex
made edits to numerical results section, awaiting comments on intro from karen

@@
 This can be attributed to multiple factors: the high-fidelity problem is mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh.
-Generally, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.
+Generally, as the nonlinearity of the high-fidelity model increases, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm.
 
-To illustrate the first offline-online application described in \cref{sec:onoff}, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values).
+\Cref{alg:refSeries} can be naturally extended to an offline-online setting, where \Cref{alg:refSeries} is first run offline to adaptively create a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
+When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
+The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
+
+To illustrate this offline-online application, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values).
 We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
@@
 In testing this online-offline setting with a larger range of datasets, we would like to note some additional observations.
-Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference.
+Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference on.
 For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$.

### 2016-10-07 paper/intro_v2.tex
New branch created for intro, modified intro in paper/intro_v2.tex

@@
 \section{Introduction}
+%
+Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations.
+Recent years have seen important advances in the accurate and reliable solution of the `forward problem', i.e.\ the solution of such complex models given appropriate initial/boundary conditions and constitutive parameters.
+In particular, adaptive methods have emerged as a highly effective paradigm for solving the forward problem.
+`Goal-oriented error estimation' algorithms are an important subset of adaptive methods, where a computational grid or even the model itself is adapted to obtain the desired accuracy in a particular goal (QoI), while minimizing the number of grid points or model complexity.
 
-In scientific and engineering contexts, physical systems are represented by mathematical models, which often take the form of partial differential equations (PDEs).
-These models are characterized by a set of parameters, and relate these parameters to states that can be observed.
-In the inverse problem, the parameters are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}.
-For a range of applications, the parameters may be numerous, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI); we refer to the setting where the goal of inferring parameters is to use them in predicting a QoI as a \textit{goal-oriented inverse problem}.
-A given physical system can be represented with varying degrees of fidelity by different models; a higher-fidelity model is able to more accurately represent reality, but is also usually more difficult to solve.
-In the context of the goal-oriented inverse problem, one may choose a lower-fidelity model with which to perform inference, sacrificing accuracy in the state and/or parameters in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance.
-In this work, we present an approach to manage the fidelity of modeling choices in solving the inverse problem, so as to achieve a desired level of accuracy in the QoI prediction, without necessarily resolving the parameters accurately.
-We adaptively form a mixed-fidelity model with which we solve the inverse problem by using models of different levels of fidelity in different parts of the domain.
+Often, the solution of the forward problem is embedded in a larger framework, where our objective is to either infer unknown model parameters (inverse problems) or the selection of optimal parameters to minimize or maximize a desired quantity (optimization problems) \cite{Taran05, BanksKuhn89}.
+Such inverse problems present a computational major challenge, since they often involve repeated solutions of the forward problem, and contain additional equations that arise from their mathematical formulation.
+Adaptive methods have been applied to make inverse problems tractable as well, including work on the \textit{goal-oriented inverse problem}.
+In a goal-oriented inverse problem, the emphasis is on identifying a low dimensional subset of the parameter or state space, which is both informed by the data, and has an impact on the goal functional.
+Various algorithms have been presented in the literature for solving the goal-oriented inverse problem, however, there has been little work in the use of adaptive modeling in such a setting.
+
+In this work, we present a robust, adaptive framework for the solution of goal-oriented inverse problems, which can identify the appropriate subset of the parameter, state space or model features/complexity to achieve a desired accuracy in the QoI.
+In doing so, we aim to combine the ideas from goal-oriented model adaptivity for forward problems, and goal-oriented methods for inverse problems.
+In particular, our method that allows one to systematically manage the use of multiple models, in an inverse problem, so as to minimize the error in a QoI prediction.
+Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model.
+This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
 
@@
 
-We aim to combine the ideas in goal-oriented methods for inverse problems, and goal-oriented model adaptivity approaches for forward modeling.
-The objective of this work is to formulate a method that allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
-To do this, we first assume that solving the inverse problem with the highest-fidelity model would result in the most accurate QoI, but that solving this inverse problem is prohibitively expensive.
-We derive a third-order estimate for the QoI error from inferring the parameters using a lower-fidelity model.
-This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
-
 The rest of the paper is organized as follows, \Cref{sec:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.

### 2016-10-09 paper/intro_v2.tex
stashing intro edits (NOT ready for pass back to Karen yet) and more stats on scalar vs field results (the one in paper, and one with smaller reaction coeff)

--- 2016-10-03 paper/intro_v2.tex
@@
 
-In scientific and engineering contexts, physical systems are represented by mathematical models, which often take the form of partial differential equations (PDEs).
-These models are characterized by a set of parameters, and relate these parameters to states that can be observed.
-In the inverse problem, the parameters are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}.
-For a range of applications, the parameters may be numerous, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI); we refer to the setting where the goal of inferring parameters is to use them in predicting a QoI as a \textit{goal-oriented inverse problem}.
+Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs).
+In the inverse problem, the parameters of the model are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}.
+Such inverse problems present a computational major challenge, since they often involve repeated solutions of the forward problem.
 A given physical system can be represented with varying degrees of fidelity by different models; a higher-fidelity model is able to more accurately represent reality, but is also usually more difficult to solve.
-In the context of the goal-oriented inverse problem, one may choose a lower-fidelity model with which to perform inference, sacrificing accuracy in the state and/or parameters in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance.
+The choice of model can be informed by one's goal; for a range of applications, the parameters may be numerous, such as when corresponding to a discretized field, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI).
+In the context of the \textit{goal-oriented inverse problem}, where the goal of inferring parameters is to use them in predicting a QoI, one may choose a lower-fidelity model with which to perform inference, sacrificing accuracy in the state and/or parameters in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance.
 In this work, we present an approach to manage the fidelity of modeling choices in solving the inverse problem, so as to achieve a desired level of accuracy in the QoI prediction, without necessarily resolving the parameters accurately.
@@
 
-% Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters.
-One way to control the cost of the model is to consider different meshes.
-In the context of the forward problem, so and so have done a-b-c.
-In the context of the inverse problem, so and so have done x-y-z.
+Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining acceptably low error estimate of the QoI.
+One way to control the cost of solving the problem the model is to consider different meshes.
+In the context of the forward problem, methods for goal-oriented mesh-refinement using adjoints are described in \cite{PrudOden99,VendDarm00,BecRann01}; an a posteriori error estimate in an output functional is derived, and this estimate is used to guide adaptive mesh-refinement.
+A framework for automated mesh-refinement to calculate a QoI to a prescribed accuracy is described in \cite{Yano12}.
+In \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; however, instead of targeting adaptive mesh refinement, the method adaptively divides the domain into subdomains where models describing different scales are applied.
 
-% Another way to control the cost of the model is to change the fidelity to which the physics are represented.
+Work has also been done on goal-oriented methods for the inverse problem.
+Mesh-refinement in the goal-oriented inverse problem is addressed in \cite{BecVex05}; in this work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite dimensional inverse problem, and this error estimate is used to adaptively refine the mesh.
+For a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI; this subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them \cite{LiebWill13}.
+For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters \cite{Span16}.
+
+Another way to control the cost of solving the problem is to change the fidelity to which the physics are represented in the model.
 The simultaneous use of multifidelity models for forward simulations is well established; two main strategies exist for combining models: hierarchical and concurrent methods.
-(Describe what these mean)
+Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally (for example, modeling the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03}).
+In contrast, concurrent methods simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
 
-% We focus on current methods of combining models. concurrent multifidelity models appear in a range of contexts, such as...
+We focus on concurrent methods of combining models, which appear in a range of contexts.
+For example, in~\cite{Khareetal08} atomistic models capable of describing bond-breaking behaviors are applied to small clusters of atoms in regions relevant to the formation of fractures, while a continuum model is applied in the rest of the domain.
+Concurrent methods are also applied in \cite{vanOpstaletal15} to combine the linear Stokes equation (low-fidelity) and the nonlinear Navier-Stokes equation (high-fidelity) based on an a posteriori estimate of the error in a QoI, and in \cite{LucKinBer02} to combine different reduced-order models, depending on the presence of shocks.
+The adaptive formation of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}; an outline extending the approach to inverse problem is outlined in \cite{OdenPrudetal10}.
 
-We aim to combine the ideas in goal-oriented methods for inverse problems, and goal-oriented model adaptivity approaches for forward modeling.
-The objective of this work is to formulate a method that allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
-To do this, we first assume that solving the inverse problem with the highest-fidelity model would result in the most accurate QoI, but that solving this inverse problem is prohibitively expensive.
-We derive a third-order estimate for the QoI error from inferring the parameters using a lower-fidelity model.
+In this work, we present a robust, adaptive framework for the solution of goal-oriented inverse problems, which can identify the regions of the domain where high-fidelity representation of the physics and the parameter and state space is important to achieving a desired accuracy in the QoI.
+In doing so, we combine ideas from goal-oriented model adaptivity for forward problems, and goal-oriented methods for inverse problems.
+In particular, our method allows one to systematically manage the use of multiple modelsin the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
+Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model.
 This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
+We note that while the approach outlined in \cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.
 

### 2016-10-10 paper/abstract_v2.tex
reorganized intro and added more refs; editted abstract

In scientific and engineering contexts, physical systems are represented by mathematical models, characterized by a set of parameters. The inverse problem arises when the parameters are unknown and one tries to infer these parameters based on observations. Solving the inverse problem can require many model simulations, which may be expensive for complex models; multiple models of varying fidelity and complexity may be available to describe the physical system. In the case of the \textit{goal-oriented inverse problem}, the goal of inferring parameters is to use them in predicting a Quantity of Interest (QoI). We present a novel adaptive framework for the solution of goal-oriented inverse problems, which can identify the regions of the domain where high-fidelity representation of the physics and the parameter and state space is important to achieving a desired accuracy in the QoI. Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI. We demonstrate the method with pairs of steady-state convection-diffusion-reaction models. We are able to obtain a QoI estimate with a small relative error without having to solve the inverse problem with the high-fidelity model. We show that the mixed-fidelity inverse problems can be cheaper to solve and less sensitive to initial guess than the high-fidelity inverse problems.

%from karen about v1: 
%"minimizing the use of high-fidelity constraints" -> won't make sense
%needs to be expanded + 1-2 sentences on approach; sentence on results needs to be more specific

### 2016-10-10 paper/algorithms_v2.tex
reorganized intro and added more refs; editted abstract

@@
 
-Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,OTHERS}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.

### 2016-10-10 paper/intro_v2.tex
reorganized intro and added more refs; editted abstract

@@
 Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs).
-In the inverse problem, the parameters of the model are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}.
-Such inverse problems present a computational major challenge, since they often involve repeated solutions of the forward problem.
+In the inverse problem, the parameters of the model are unknown and one tries to infer their values based on observations of the states or parameters~\cite{Taran05, BanksKuhn89}.
+Such inverse problems present a major computational challenge, since they often involve repeated solutions of the forward problem.
 A given physical system can be represented with varying degrees of fidelity by different models; a higher-fidelity model is able to more accurately represent reality, but is also usually more difficult to solve.
@@
 
+The simultaneous use of multiple models of varying fidelity for forward simulations is well established; two main strategies exist for combining models: hierarchical and concurrent methods~\cite{Liuetal03}.
+Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally.
+A common application is the modeling of the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03,Weietal04}.
+In contrast, concurrent methods simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
+Applications include computational mechanics~\cite{Khareetal08,Prudetal08} and fluid dynamics~\cite{vanOpstaletal15,LucKinBer02,FatGerQua01}.
+We focus on concurrent methods of combining models, which have desirable features: in the case where the high-fidelity model is nonlinear, replacing it with a linear lower-fidelity model in most of the domain can reduce the need for iterative solves; when the high-fidelity model has a fine resolution and/or many parameters, replacing it with a lower-fidelity model can reduce the number of degrees of freedom of the mixed-fidelity model.
+
+The best way to choose the subdomains for the different models depends of course on what one wishes to achieve.
 Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining acceptably low error estimate of the QoI.
-One way to control the cost of solving the problem the model is to consider different meshes.
-In the context of the forward problem, methods for goal-oriented mesh-refinement using adjoints are described in \cite{PrudOden99,VendDarm00,BecRann01}; an a posteriori error estimate in an output functional is derived, and this estimate is used to guide adaptive mesh-refinement.
-A framework for automated mesh-refinement to calculate a QoI to a prescribed accuracy is described in \cite{Yano12}.
-In \cite{OdenPrudetal06}, a method using adjoints for the goal-oriented forward problem is described; however, instead of targeting adaptive mesh refinement, the method adaptively divides the domain into subdomains where models describing different scales are applied.
+The problem of mesh-refinement can be thought of as one of combining models corresponding to different discretizations of a continuous equation.
+In the context of the forward problem, methods for goal-oriented mesh-refinement using adjoints are described in~\cite{PrudOden99,VendDarm00,BecRann01}; an a posteriori error estimate in an output functional is derived, and this estimate is used to guide adaptive mesh-refinement.
+A framework for automated mesh-refinement to calculate a QoI to a prescribed accuracy is described in~\cite{Yano12}.
+Goal-oriented model adaptivity aims to optimally mix models differing in their mesh resolution and/or physics included~\cite{OdenPrudetal06,BraackErn03}.
 
 Work has also been done on goal-oriented methods for the inverse problem.
-Mesh-refinement in the goal-oriented inverse problem is addressed in \cite{BecVex05}; in this work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite dimensional inverse problem, and this error estimate is used to adaptively refine the mesh.
-For a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI; this subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them \cite{LiebWill13}.
-For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters \cite{Span16}.
-
-Another way to control the cost of solving the problem is to change the fidelity to which the physics are represented in the model.
-The simultaneous use of multifidelity models for forward simulations is well established; two main strategies exist for combining models: hierarchical and concurrent methods.
-Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally (for example, modeling the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03}).
-In contrast, concurrent methods simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
-
-We focus on concurrent methods of combining models, which appear in a range of contexts.
-For example, in~\cite{Khareetal08} atomistic models capable of describing bond-breaking behaviors are applied to small clusters of atoms in regions relevant to the formation of fractures, while a continuum model is applied in the rest of the domain.
-Concurrent methods are also applied in \cite{vanOpstaletal15} to combine the linear Stokes equation (low-fidelity) and the nonlinear Navier-Stokes equation (high-fidelity) based on an a posteriori estimate of the error in a QoI, and in \cite{LucKinBer02} to combine different reduced-order models, depending on the presence of shocks.
-The adaptive formation of concurrent multi-fidelity models for the goal-oriented forward problem is described in \cite{OdenPrudetal06}; an outline extending the approach to inverse problem is outlined in \cite{OdenPrudetal10}.
+Mesh-refinement in the goal-oriented inverse problem is addressed in~\cite{BecVex05}; in this work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite dimensional inverse problem, and this error estimate is used to adaptively refine the mesh.
+An outline extending the approach to goal-oriented model adaptivity described in~\cite{OdenPrudetal06} to the inverse problem is presented in~\cite{OdenPrudetal10}.
+In the goal-oriented inverse problem, the data is often insufficient to fully resolve the inferred parameters; in addition, fully resolving these parameters is unnecessary to accurately computing the QoI.
+This idea is formalixed in ~\cite{LiebWill13}; for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI.
+This subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them.
+For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters~\cite{Span16}.
 
@@
 In doing so, we combine ideas from goal-oriented model adaptivity for forward problems, and goal-oriented methods for inverse problems.
-In particular, our method allows one to systematically manage the use of multiple modelsin the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
+In particular, our method allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
 Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model.
 This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
-We note that while the approach outlined in \cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.
+We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.
 

### 2016-11-10 paper/algorithms_v3.tex
add comments from karen on version 2 (not on abstract or intro yet); create v3 files to start incorporating these comments

--- 2016-10-03 paper/algorithms_v2.tex
@@
 %------------------------------------------------------------------------------------------------------------------------%
-\subsection{Adaptive Model Mixing ALgorithm}\label{sec:adapt_alg}
+\subsection{Adaptive Model Mixing Algorithm}\label{sec:adapt_alg}
 %------------------------------------------------------------------------------------------------------------------------%
 
-Just as error estimates can be used to guide mesh-refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,OTHERS}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide the division of the domain for a mixed-fidelity model.
+Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
@@
 \State{Define maximum number of adaptive iterations \texttt{maxIter}}
-\Procedure{$\texttt{BuildMF}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
+\Procedure{$\texttt{BuildMixedFidelity}$}{HF model, LF model, \texttt{errTol}, \texttt{maxIter}}
 	\State{Let the model MF$_0$ be the LF model applied everywhere in the domain.}
@@
 The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
-The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
+The two models could also correspond to two levels of mesh refinement, though in this case the method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
 The derived error estimate is not applicable to all models, however.
@@
 We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For ease of implementation, we can choose these basis functions to be the same as those spanning the space in which we solve for the primary, auxiliary, and supplementary adjoint vatriables.
+For ease of implementation, we can choose these basis functions to be the same as those spanning the space in which we solve for the primary, auxiliary, and supplementary adjoint variables.
 Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution.

### 2016-11-10 paper/mathematical_formulation_v2_kw.tex
add comments from karen on version 2 (not on abstract or intro yet); create v3 files to start incorporating these comments

--- 2016-10-03 paper/mathematical_formulation_v2.tex
@@
 %
-We first introduce the goal-oriented inverse problem formally. Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower-fidelity models.
+We first introduce the goal-oriented inverse problem.
+Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.
 
 %------------------------------------------------------------------------------%
-\subsection{Problem Setup}  \label{sec:setup}
+\subsection{Inverse Problem Formulation}  \label{sec:setup}
 %------------------------------------------------------------------------------%
@@
 The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
-Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
@@
 A given physical system can be described to varying degrees of fidelity using different models.
-This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution one is interested in.
+This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.
 
-In the case of a goal-oriented inverse problem, the ultimate purpose of inferring the unknown parameters is to calculate some Quantity of Interest (QoI).
-Assuming a single scalar QoI, we denote this QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-Since our ultimate goal is to compute this QoI, the particular tradeoff we consider is in the fidelity and resultant computational expense of the model we use, versus the error in the QoI.
-We thus seek to introduce the QoI functional $I$ into the inverse problem formulation by introducing auxilary variables and additional adjoint equations.
-Then we use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those which occur due to the use of difference models in the constraint \cref{eq:invOpt_cons}.
+We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
+We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.
+In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
+We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \cref{eq:invOpt_cons}.
 %
@@
 \end{equation}
+% KW: notation in the equation is \mathcal{M}'_{HF,\Psi}(\Lambda;\Psi_{HF})= M'_{HF}(\Psi_{LF})(\Phi)
+% I don't understand what the difference in notation means.
+Why drop the second subscript on the M'?
+and why the change in arguments?
+And neither instance is consistent with how the ' notation was defined above for the Lagrangian.
+% You can't just introduce new notation and hope that the reader guesses what you mean.
+Everything must be defined!
+Every time you change an argument form, every time you change the form of the subscript, every time you change anything, ...
+% KW: where is \mathcal{Q} defined?
 %
@@
 %
-Observe that,
+Observe that
 %
@@
 
-Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high and low fidelity models, we have,
+Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have,
 %
@@
 %
-Applying Proposition 3 from~\cite{BecVex05} for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
+Applying Proposition 3 from~\cite{BecVex05} 
+% KW: what is Prop 3? is it something we need to state/summarize here for completeness? maybe okay as is, just seems a little mysterious.
+for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
 \begin{equation}

### 2016-11-10 paper/numerical_experiments_v2_kw.tex
add comments from karen on version 2 (not on abstract or intro yet); create v3 files to start incorporating these comments

--- 2016-10-04 paper/numerical_experiments_v2.tex
@@
 We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
-We first consider simple two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
+We first consider two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
 In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model.
@@
 In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented.
-In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models.
+In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.
 
@@
 %------------------------------------------------------------------------------------------------------------------------%
-\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
+\subsection{Variable Physics: Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
 %------------------------------------------------------------------------------------------------------------------------%
@@
 k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
-u = 0 \quad &\text{on } \partial \Omega \label{eq:cdvcdrHF_bdry}
+u = 0 \quad &\text{on } \partial \Omega, \label{eq:cdvcdrHF_bdry}
 \end{align}
@@
 
-The unknown parameters we wish to infer correspond to the forcing field, so that $f(q)=q$.
-For the low-fidelity model, the inverse problem is linear (the inferred parameters are linear in the observations).
-Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
-%
-\begin{equation}
-f_{true}(x_1,x_2)=
-\begin{cases}
-1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
-0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
-0 & \textrm{otherwise}.
-\end{cases}
-\end{equation}
-%
-The locations of the observations and the region $\Omega_I$ over which the QoI is calculated are shown in \cref{fig:baseSetup}.
+The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
+\cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated.
+For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
 Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
+% KW: term in what equation?
+give a reference or re-state the objective here.
 %
@@
 The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
+
+Synthetic observations consisting of the state at three points in the domain are artificially generated by running the high-fidelity model on a finer mesh with the true forcing field
+%
+\begin{equation}
+f_{true}(x_1,x_2)=
+\begin{cases}
+1.0 & \textrm{if }(x_1,x_2)\in[0.125,0.375]\times[0.125,0.375] \\
+0.8 & \textrm{if }(x_1,x_2)\in[2.375,2.625]\times[0.375,0.625] \\
+0 & \textrm{otherwise}.
+\end{cases}
+\end{equation}
+%
 %
@@
 } \\
-\caption{Local error contributions (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
+\caption{Left: Multi-fidelity refinement over the domain (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion).
+Right: local error contributions.
+}
 \label{fig:baseRef}
@@
 We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. 
+% KW: I am not sure how to read the second phrase in this first sentence.
+Is it '...contribution is concentrated in two places: in the QoI region and near the observation location closest to the QoI.'  ??
 In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
+% KW: again here, what is a 'data point' ?
+Do you mean 'observation location' ?
 Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right.
 Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region.
-After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point.
+% KW: same here.
+plus another confusing comma.
+After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point. % KW: and here
 
@@
 In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
-We note that, in general, there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
+We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
 %
@@
 For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate.
-However, it was noticed that the number of iterations needed to achieve a given tolerance increased as the QoI region increased.
+However, in conducting the numerical experiments, it was observed that the number of iterations needed to achieve a given tolerance tended to increase as the QoI region increased.
 
-The error decompositions for three increasingly large, nested QoI regions $\Omega_I$ given the same set of observations are shown in \cref{fig:qoiStudy}.
+\cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
+The error decompositions for each case are also shown in \cref{fig:qoiStudy}.
 The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
+% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
 Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier.
 As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.
+% KW: fix references to 'data point' throughout.
 
@@
 }
-  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF}-\protect\subref{subfig:obsMFlast}) given the same observations and different QoI regions.}
+  \caption{Effects of increasing the QoI region.
+Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
+Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
   \label{fig:qoiStudy}
@@
 
-The error decomposition for three increasing, nested sets of observations and the same QoI region $\Omega_I$ is shown in \cref{fig:dataStudy}.
+\cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
+The error decomposition for the three cases is shown in \cref{fig:dataStudy}.
 Again, the bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger.
@@
 The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.
+% KW: I don't understand a lot of this discussion.
+You need to explain to me what you mean.
 
@@
 }
-  \caption{With each row corresponding to the configuration of observations (teal points) and QoI region (purple box) shown in column \protect\subref{subfig:obsSetup2}, compare the error estimate decompositions (columns \protect\subref{subfig:obsLF2}-\protect\subref{subfig:obsMFlast2}) given different observations and the same QoI region.}
+  \caption{Effects of increasing the number of observations.
+Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
+Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
   \label{fig:dataStudy}
@@
 %------------------------------------------------------------------------------------------------------------------------%
-\subsection{Constant vs Field Parameters} \label{sec:constvfield}
+\subsection{Variable Parameterization: Constant vs.\ Field Parameters} \label{sec:constvfield}
 %------------------------------------------------------------------------------------------------------------------------%
-\red{THIS SUBSECTION IS OLD AND CURRENTLY A PLACEHOLDER TO GAUGE LENGTH}.
-It is not necessary for the low- and high-fidelity models to differ in the physics included.
-A low-fidelity model may be more computationally tractable due to a reduced number of degrees of freedom rather than reduced nonlinearity.
-In this section, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
+
+In this subsection, we consider two models which differ in the space to which the parameter belongs, with the low-fidelity model having fewer degrees of freedom.
+
 %------------------------------------------------------------%
@@
 %------------------------------------------------------------%
+
 We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
@@
 differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
-Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain.
+The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used.
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
 The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
-As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
+As the inverse problem is ill-posed, except for perhaps % KW: is it or not?
+in the case where the low-fidelity model is used throughout the domain, regularization is added; % KW: added to what?
+ the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
+% KW: refer to the actual equation you are adding regularization to, or re-state the objective.
 
-Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
+% KW: I'm commenting out this next statement, unless you strongly disagree.
+%Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
 Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
+
 %------------------------------------------------------------%
@@
 %------------------------------------------------------------%
+
 As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
-The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used and the unknown parameter allowed to be a field.
+The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used.
 With each iteration, an additional $10\%$ of the elements are marked for refinement.
-This is repeated until the estimated absolute relative error in the QoI, is less than $1\%$.
+This is repeated until the estimated absolute relative error in the QoI is less than $1\%$.
 
 \Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated.
-Each linear Langrange basis function's contribution is plotted at its nonzero node.
+Each linear Lagrange basis function's contribution is plotted at its nonzero node.
+% KW: what does this sentence mean and is it really necessary?
 %
@@
 }
-\caption{Local error contributions (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.
+\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion).
+Right: local error contributions.
 The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
@@
 Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
-This reflects the global nature of the differences between the low- and high-fidelity models; the parameter field in all the low-fidelity regions is constant and equal.
+This reflects the global nature of the differences between the low- and high-fidelity models.
+% KW: fix data-point language
 
@@
 The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
-We also see that in this case, compared to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+We also see that in this case, in contrast to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
 
@@
 
-In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, time.
-In this section, we consider a more realistic pair of models which differ in both the physics included and the mesh resolution, and demonstrate computational savings.
+In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, computational effort.
+In this section, we consider a pair of models that differ in both the physics included and the mesh resolution, and we demonstrate computational savings using the multi-fidelity approach.
 In \cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D_diffmesh} we describe the results of applying \cref{alg:refSeries} to this pair of models.
@@
 As in the previous examples in \cref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where \cref{eq:HFeq3D,eq:LFeq3D} are solved, respectively.
-The QoI we wish to calculate is again an integral of the state over a region $\Omega_I$.
+The QoI we wish to calculate is the integral of the state over a region $\Omega_I$.
 
 The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$.
-Observations at 18 points in the domain are artificially generated by running the high-fidelity model on a finer mesh.
+Synthetic observations at 18 points in the domain are generated by running the high-fidelity model on a finer mesh.
 The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}.
 We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
+% KW: again please connect reg term to an equation or just state objective function here.
 %
@@
 
-We continue to use the FEM with a continuous Galerkin formulation and Lagrange elements.
+We use a FEM with a continuous Galerkin formulation and Lagrange elements.
 The lack of a convection term allows the low-fidelity model to be solved on a coarser mesh.
-For the high-fidelity model, the domain is descretized by 32, 64, and 32 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; for the low-fidelity model, the domain is descretized by 16, 32, and 16 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively.
-The cell P\'{e}clet number is less than one and so no stabilization is used.
+For the high-fidelity model, the domain is discretized by 32, 64, and 32 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively; for the low-fidelity model, the domain is discretized by 16, 32, and 16 elements along the $x_1$, $x_2$, and $x_3$ directions, respectively.
+The cell P\'{e}clet number is less than one and so stabilization is not required.
 
@@
 We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
-At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater.
+At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples.
 All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
+% KW: need to add a citation to papers for libMesh and PETSC?
 
@@
 \begin{table}[htbp]
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the true high-fidelity QoI.}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
 \label{tab:ref3D_diffmesh}
@@
 
-We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are very far from the true errors.
-This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are very different from $\Psi_{HF}$.
-Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models are more disimilar, even though the nonlinear term in the high-fidelity models remain the same.
+We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors.
+This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
+Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models are more dissimilar, even though the nonlinear term in the high-fidelity models remain the same.
+% KW: don't know what last part of this sentence means.
+what hi-fi models?
 This behavior suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the predicted high-fidelity QoI $I(q_{MF},u_{MF})+\epsilon_i$ for two consecutive iterations agree to within some tolerance.
+% KW: what behavior?
+this last sentence doesn't follow from the previous one.
+and what predicted hi-fi QOI?
+Do you mean mixed-fi?
+I'm not sure this is a good idea.
+I'd probably delete this last sentence.
 
-The domain divisions for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}.
-Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to be refined around.
-We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
+The multi-fidelity domain refinements for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}.
+Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement.
+We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
 %
@@
 %
+
 In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error, starting from the low-fidelity model.
@@
 Generally, as the nonlinearity of the high-fidelity model increases, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm.
-
-\Cref{alg:refSeries} can be naturally extended to an offline-online setting, where \Cref{alg:refSeries} is first run offline to adaptively create a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
-When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
-The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
+However, one can also consider an ``offline-online" setting, where the mixed-fidelity models are identified up-front by applying \Cref{alg:refSeries} to a set of representative observations $d^*$.
+Then when actual/new data are received, one can solve the inverse problem with the mixed-fidelity model and the new data, and, if desired, compute an updated error estimate for the QoI.
+The mixed-fidelity inverse problems are expected to require less time to solve than the high-fidelity inverse problems.
 
@@
 The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
-The auxiliary and supplementary adjoint variables simply have a zero initial guess.
+The auxiliary and supplementary adjoint variables use a zero initial guess.
 
-\Cref{tab:ref3D_newdata_QoI_diffmesh} shows the average QoI values and error estimates and solution times for the (non)linear solves.
+\Cref{tab:ref3D_newdata_QoI_diffmesh} shows the average QoI values, error estimates and solution times for the (non)linear solves.
 \Cref{tab:ref3D_newdata_times_diffmesh} shows the times needed to solve the inverse problems and to solve for the additional variables needed to obtain an error estimate.
 For six of the ten datasets, the high-fidelity inverse problem does not converge given the low-fidelity solution as an initial guess; these are solved using the $k_r=0$ solution as an initial guess so that true QoI errors can be calculated.
-The average time high-fidelity inverse problem solution time shown in \cref{tab:ref3D_newdata_times_diffmesh} includes only those that converged with the low-fidelity initial guess.
+The average high-fidelity inverse problem solution time shown in \cref{tab:ref3D_newdata_times_diffmesh} includes only those cases (four of ten) that converged with the low-fidelity initial guess.
 %
@@
 %
-We see that the mixed-fidelity models, when applied to noisy datasets different from that with which they were generated, continue to perform well in achieving a small error in the QoI while limiting the use of the high-fidelity model to less than a third of the domain.
+We see that the mixed-fidelity models, when applied to noisy datasets different to those with which they were generated, continue to perform well in achieving a small error in the QoI while limiting the use of the high-fidelity model to less than a third of the domain.
 Given the same initial guess, the mixed-fidelity inverse problems takes less time on average than the high-fidelity inverse problem to solve, and they converge consistently.
 
-In testing this online-offline setting with a larger range of datasets, we would like to note some additional observations.
-Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference on.
-For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$.
+% KW: this paragraph is a bit rambling.
+I think it is obvious: you do better when you optimize the model for the actual dataset.
+I think we leave this out unless you think there is a critical point here that is not captured elsewhere.
+%In testing this online-offline setting with a larger range of datasets, we would note some additional observations.
+Suppose one has two datasets $d_1$ and $d_2$, and wishes to perform inference on $d_2$.
+For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated using $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$.
 The performance gap tends to widen as the two datasets become more different.

### 2016-11-10 paper/paper_v3.tex
add comments from karen on version 2 (not on abstract or intro yet); create v3 files to start incorporating these comments

\documentclass[review]{siamart0516}
%%\usepackage{lgrind}

%\usepackage[square,comma,numbers,sort&compress]{natbib}
%\usepackage{amsmath,amsthm,amssymb,amsfonts,amsbsy,latexsym} %amsthm inclusion conflicts with sisc...
\usepackage{amsmath,amssymb,amsfonts,amsbsy,latexsym}
\usepackage{graphics}
%\usepackage{epsfig}
%%\usepackage[hang,raggedright]{subfigure}
%\usepackage{epsf}
%\usepackage{setspace}
%\usepackage{hangcaption}
\usepackage{graphicx}    % needed for including graphics e.g. EPS, PS
\usepackage{multirow}
%\usepackage{threeparttable}
\usepackage{cancel}
\usepackage{enumerate}
\usepackage{color}
\usepackage{hyperref}

%\usepackage{algorithmicx}
%\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
%\usepackage{caption}
%\usepackage[font=small]{subcaption}
%\usepackage{longtable}
\usepackage{mathrsfs}
\usepackage{upgreek}
\usepackage[caption=false]{subfig} % for \subfloat

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

\newcommand{\R}{{\mathbb{R}}}
\newcommand{\Reals}{{\mathbb{R}}}
\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}
\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\orderof}[1]{{\ensuremath{ {\cal O}(#1)}}}

%\newtheorem{theorem}{Theorem} %conflicts with sisc

\graphicspath{{./figures/}}

\begin{document}
\raggedbottom %avoid weird vertical justification

\title{Model Adaptivity for Goal-Oriented Inference using Adjoints}

\author{Harriet Li, Vikram Garg, Karen Willcox}
%\date{}
\maketitle

\begin{abstract}
\input{abstract_v2.tex}
\end{abstract}

\begin{keywords}
  inference, goal-oriented adaptive modeling, a posteriori error estimation, multifidelity modeling, adjoints, PDEs
\end{keywords}

\begin{AMS}
  35R30, 65G20, 62F35, 35R15
\end{AMS}

\input{intro_v2.tex}
\input{mathematical_formulation_v2.tex}
\input{algorithms_v2.tex}
\input{numerical_experiments_v2.tex}
\input{conclusions_v2.tex}
\input{acknow.tex}

\bibliographystyle{siamplain}
\bibliography{masterBib}
\end{document}

### 2016-11-10 paper/mathematical_formulation_v3.tex
some edits

--- 2016-11-10 paper/mathematical_formulation_v2_kw.tex
@@
 \begin{equation}
+\mathscr{R}_{\Psi_{HF}}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
-\mathcal{M}'_{HF,\Psi}(\Lambda;\Psi_{HF})(\Phi)=\mathcal{Q}(\Phi)=\mathcal M'_{HF}(\Psi_{LF})(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
+\end{equation}
+for the supplementary adjoint $\Lambda$, where $\Phi$ is a test function,  
+\begin{equation}
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:supadjsys}
+\end{equation}
+is the residual form of $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$, and $\mathcal{Q}$ is an output defined by
+\begin{equation}
+\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi).
+\label{eq:supadjout}
 \end{equation}
@@
 %
-for the supplementary adjoint $\Lambda$, where $\Phi$ is a test function. Then, the error in the Quantity of Interest $I$ is given by,
+Then, the error in the Quantity of Interest $I$ is given by,
 %
@@
 %
-Applying Proposition 3 from~\cite{BecVex05} 
+Applying the output error representation described in Proposition 3 from~\cite{BecVex05} 
 % KW: what is Prop 3? is it something we need to state/summarize here for completeness? maybe okay as is, just seems a little mysterious.
@@
 
-Further, the error in the output $\mathcal{Q}$ defined in \cref{eq:superAdjEq} can be expressed as a dual-weighted residual,
+We note that, as a stationary point, $\Psi_{HF}$ satisfies \cref{eq:supadjsys}.
+Further, the error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can be expressed as a dual-weighted residual,
 \begin{equation}
@@
 \end{equation}
-
+%
 Combining \cref{eq:preadj} and \cref{eq:adjOutErr}, we have,

### 2016-11-11 paper/intro_v3.tex
stashing edits

\section{Introduction}

Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs). The inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
%~\cite{Taran05, BanksKuhn89}. 
Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of the mathematical model.  In many cases, a given physical system can be represented with varying degrees of fidelity by different models. A higher-fidelity model more accurately represents reality, but is also usually more computationally expensive to solve. Lower-fidelity models reduce the computational cost of the forward problem, at the expense of introducing approximations.
In this work, we formulate an approach for leveraging multiple models of varying fidelities in solution of an inverse problem.

The choice of model should be informed by one's goal: for a range of applications, the parameters may be numerous, such as when corresponding to a discretized field, and yet what is ultimately of interest may be some low-dimensional quantity of interest (QoI). We consider this \textit{goal-oriented inverse problem}, where the goal of inferring parameters is to use them in predicting a QoI. In this context, one may choose a lower-fidelity model for the inference problem, sacrificing accuracy in the state and/or parameter estimates in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance.  This paper formally poses the problem of managing the fidelity of modeling choices in solving the goal-oriented inverse problem, and develops an adjoint-based model adaptivity approach that achieves a desired level of accuracy in the QoI prediction. In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different parts of the domain.

The simultaneous use of multiple models of varying fidelity for forward simulations is well established in some fields. Ref.~\cite{Liuetal03} categorizes two main strategies for combining models: hierarchical and concurrent methods. Hierarchical methods (also known as information-passing or sequential methods) take the results of a simulation using the high-fidelity model and use them to inform a lower-fidelity model that is used globally. An example application is the modeling of the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03,Weietal04}. In contrast, concurrent methods simultaneously solve the higher- and lower-fidelity models in different parts of the domain. Applications include computational mechanics~\cite{Khareetal08,Prudetal08} and fluid dynamics~\cite{vanOpstaletal15,LucKinBer02,FatGerQua01}.
% KW: I feel that we may be missing some important literature here, e.g., the work of Alexander, Tartakovsky
We focus on concurrent methods of combining models, which have desirable features: in the case where the high-fidelity model is nonlinear, replacing it with a linear lower-fidelity model in most of the domain can reduce the need for iterative solves;
% KW: what does 'reduce the need' mean? you still need iterative solves right? 
when the high-fidelity model has a fine resolution and/or many parameters, replacing it with a lower-fidelity model can reduce the number of degrees of freedom of the mixed-fidelity model.

Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining acceptably low error estimate of the QoI. In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{PrudOden99,VendDarm00,BecRann01,Yano12} and for model adaptivity~\cite{OdenPrudetal06,BraackErn03}. 
%where the goal is to optimally mix models differing in their mesh resolution and/or physics included. 
These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement.
% KW: moved Yano reference. please replace reference to PhD thesis by a journal paper:
%@article{Yano2012,
%  title={An optimization-based framework for anisotropic simplex mesh adaptation},
%  author={Yano, Masayuki and Darmofal, David L},
%  journal={Journal of Computational Physics},
%  volume={231},
%  number={22},
%  pages={7626--7649},
%  year={2012},
%  publisher={Elsevier}
%}

The inverse problem setting has also seen some work on goal-oriented methods. Mesh refinement in the goal-oriented inverse problem is addressed in~\cite{BecVex05}; in that work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite-dimensional inverse problem, and this error estimate is used to adaptively refine the mesh. An outline extending the approach to goal-oriented model adaptivity described in~\cite{OdenPrudetal06} to the inverse problem is presented in~\cite{OdenPrudetal10}. Other work has recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI. This idea is formalized in ~\cite{LiebWill13}; for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI. This subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them. For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters~\cite{Span16}.

In this paper, we target model adaptivity the solution of goal-oriented inverse problems. We present a robust, adaptive framework that identifies the subregions of the domain where high-fidelity representation of physics and parameters is important to achieving a desired accuracy in the QoI. To achieve this, we combine ideas from goal-oriented model adaptivity for forward problems and goal-oriented methods for inverse problems. In particular, our method allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI. 
%We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.

The remainder of this paper is organized as follows, \Cref{sec:form} presents the mathematical formulation and error analysis for the multi-model inverse problem. \Cref{sec:alg} discusses the goal oriented inference algorithm and presents a computational complexity analysis. \Cref{sec:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem. Finally, we present conclusions and directions for future work in \Cref{sec:conc}.

### 2016-11-11 paper/numerical_experiments_v3.tex
stashing edits

--- 2016-11-10 paper/numerical_experiments_v2_kw.tex
@@
 For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
-% KW: term in what equation?
-give a reference or re-state the objective here.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
 %
@@
 
-We see that the largest local error contribution is concentrated in the QoI region, and the data point closest to the QoI. 
-% KW: I am not sure how to read the second phrase in this first sentence.
-Is it '...contribution is concentrated in two places: in the QoI region and near the observation location closest to the QoI.'  ??
-In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is maximum is the leftmost data point.
-% KW: again here, what is a 'data point' ?
-Do you mean 'observation location' ?
+We see that the largest local error contributions are concentrated in the QoI region and around the observation location closest to the QoI.
+In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is greatest is around the leftmost observation location.
 Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right.
-Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost data point, and the QoI region.
-% KW: same here.
-plus another confusing comma.
-After that, the error decomposition suggests refinement in regions upstream and around the middle data point, and then the rightmost data point. % KW: and here
+Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost observation location, and then around the QoI region.
+After that, the error decomposition suggests refinement in regions upstream and around the middle observation location, and then the rightmost observation location.
 
@@
 The error estimate decomposition suggests the use of the high-fidelity model in areas of the domain that are important to the interaction between the observations and QoI; the interaction between these two can be complex, and the areas suggested for refinement may be nonintuitive.
-To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of data points, and for three nested sets of data points given the same QoI region.
+To see this, we compare the error estimate decomposition for three sizes of the QoI region $\Omega_I$ given the same set of observation locations, and for three nested sets of observation locations given the same QoI region.
 For the sake of illustration, we make two refinement iterations for each combination of observations and QoI region, regardless of the magnitude of the relative error estimate.
@@
 The error decompositions for each case are also shown in \cref{fig:qoiStudy}.
-The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, so the proportion of additional refined elements in each iteration is slightly larger.
+The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \cref{sec:cdvcdrBaseRef}.
 % KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
-Although refinement is still most important around the data point closest to $x_1=0$, as the QoI region expands the other two data points become more important in that the error decomposition suggests refinement around them earlier.
+Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier.
 As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.
-% KW: fix references to 'data point' throughout.
 
@@
 The error decomposition for the three cases is shown in \cref{fig:dataStudy}.
-Again, the bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here the basis functions with the largest $5\%$ of the error are chosen, so the proportion of additional refined elements in each iteration is slightly larger.
-Refinement appears to be consistently most important around the data point closest to $x_1=0$ and the QoI region.
-However, as more data points are added, it becomes no longer necessarily true that refinement becomes less important around data points as their distance from the QoI region increases.
-The data points also interact with each other in that placing data points in regions of previously relatively uniform error contribution tends to result in a new error decomposition that is positive or negative around the data points, with valleys of zero magnitude in between.
+The bottom row is the same as that in \cref{fig:qoiStudy}.
+Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region.
+However, as more observation locations are added, it becomes no longer necessarily true that refinement becomes less important around observation locations as their distance from the QoI region increases.
+In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain.
+This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model would be most helpful.
 % KW: I don't understand a lot of this discussion.
@@
 The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
-As the inverse problem is ill-posed, except for perhaps % KW: is it or not?
-in the case where the low-fidelity model is used throughout the domain, regularization is added; % KW: added to what?
- the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
-% KW: refer to the actual equation you are adding regularization to, or re-state the objective.
+As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
 
@@
 \Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
-Each linear Lagrange basis function's contribution is plotted at its nonzero node.
-% KW: what does this sentence mean and is it really necessary?
 %
@@
 %
-Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest data point; here, all three data points and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
+Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
 This reflects the global nature of the differences between the low- and high-fidelity models.
-% KW: fix data-point language
 
@@
 The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}.
-We use a regularization term $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
-% KW: again please connect reg term to an equation or just state objective function here.
+We set the regularization term in \cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
 %
@@
 At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples.
-All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
+All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} \cite{libMeshPaper} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
 % KW: need to add a citation to papers for libMesh and PETSC?
@@
 Given the same initial guess, the mixed-fidelity inverse problems takes less time on average than the high-fidelity inverse problem to solve, and they converge consistently.
-
-% KW: this paragraph is a bit rambling.
-I think it is obvious: you do better when you optimize the model for the actual dataset.
-I think we leave this out unless you think there is a critical point here that is not captured elsewhere.
-%In testing this online-offline setting with a larger range of datasets, we would note some additional observations.
-Suppose one has two datasets $d_1$ and $d_2$, and wishes to perform inference on $d_2$.
-For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated using $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$.
-The performance gap tends to widen as the two datasets become more different.
-Suppose one generated $d_1$ using the high-fidelity model $d_2$ using a model which differed from the high-fidelity model in its domain, boundary conditions, and reaction coefficient; then a mixed-fidelity model adaptively formed based on $d_1$ might not give a low QoI error when used to infer from $d_2$.
-However, when the adaptivity algorithm is directly applied to this $d_2$, it is still able to find a mixed-fidelity model with a low QoI error.
-This behavior suggest that, if resources allow, it is best to perform the adaptivity online with the true observations.
-If one is confident that one's high-fidelity model is a good approximation of reality, then the online-offline approach can potentially give a faster yet accurate QoI estimate.

### 2016-11-11 paper/intro_v3.tex
edits to numerical results, intro

@@
 The inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
-%~\cite{Taran05, BanksKuhn89}. 
 Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of the mathematical model.
@@
 An example application is the modeling of the molecular structure of a material to determine parameters for constitutive equations~\cite{Haoetal03,Weietal04}.
-In contrast, concurrent methods simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
-Applications include computational mechanics~\cite{Khareetal08,Prudetal08} and fluid dynamics~\cite{vanOpstaletal15,LucKinBer02,FatGerQua01}.
+In contrast, concurrent methods (also called hybrid methods) simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
+Applications include computational mechanics~\cite{Khareetal08,Prudetal08} and fluid dynamics~\cite{AlexGarTar02,FatGerQua01,Garcetal99,LucKinBer02,vanOpstaletal15,WadErw90}.
 % KW: I feel that we may be missing some important literature here, e.g., the work of Alexander, Tartakovsky
-We focus on concurrent methods of combining models, which have desirable features: in the case where the high-fidelity model is nonlinear, replacing it with a linear lower-fidelity model in most of the domain can reduce the need for iterative solves;
-% KW: what does 'reduce the need' mean? you still need iterative solves right? 
-when the high-fidelity model has a fine resolution and/or many parameters, replacing it with a lower-fidelity model can reduce the number of degrees of freedom of the mixed-fidelity model.
+We focus on concurrent methods of combining models, which have desirable features: in the case where the high-fidelity model is nonlinear, replacing it with a linear lower-fidelity model in most of the domain can reduce the number of iterative solves needed; when the high-fidelity model has a fine resolution and/or many parameters, replacing it with a lower-fidelity model can reduce the number of degrees of freedom of the mixed-fidelity model.
 
 Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining acceptably low error estimate of the QoI.
-In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{PrudOden99,VendDarm00,BecRann01,Yano12} and for model adaptivity~\cite{OdenPrudetal06,BraackErn03}.
-%where the goal is to optimally mix models differing in their mesh resolution and/or physics included. 
+In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}.
 These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement.
-% KW: moved Yano reference. please replace reference to PhD thesis by a journal paper:
-%@article{Yano2012,
-%  title={An optimization-based framework for anisotropic simplex mesh adaptation},
-%  author={Yano, Masayuki and Darmofal, David L},
-%  journal={Journal of Computational Physics},
-%  volume={231},
-%  number={22},
-%  pages={7626--7649},
-%  year={2012},
-%  publisher={Elsevier}
-%}
 

### 2016-11-11 paper/numerical_experiments_v3.tex
edits to numerical results, intro

@@
 \centering
+\captionsetup{justification=centering}
 \subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
+  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
+  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
   \label{subfig:obsSetup}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
+  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
+  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
   \label{subfig:obsLF}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
+  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
+  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
+  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
   \label{subfig:obsMFlast}
@@
 Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
-Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
+Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
   \label{fig:qoiStudy}
@@
 \centering
+\captionsetup{justification=centering}
 \subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
+  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
+  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
   \label{subfig:obsSetup2}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
+  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
+  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
   \label{subfig:obsLF2}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
+  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
+  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
 }
+\captionsetup{justification=centering}
 \subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
+  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
   \label{subfig:obsMFlast2}
@@
 Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
-Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the error estimate decompositions for different mixed-fidelity models.}
+Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
   \label{fig:dataStudy}
@@
 As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
-
-% KW: I'm commenting out this next statement, unless you strongly disagree.
-%Although using such a pair of models has similarities to the problem of adaptive mesh refinement, we note that in this example only the parameter field changes in its level of refinement, not the state.
-Should the two models differ in the resolution of the state variables instead of the parameters, it is more efficient to use the approach discussed in \cite{BecVex05}.
 
@@
 At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples.
-All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} \cite{libMeshPaper} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver, preconditioned by incomplete factorization.
-% KW: need to add a citation to papers for libMesh and PETSC?
+All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} \cite{libMeshPaper} (Newton's method with Brent line-search), and linear solves are performed using PETSc's \cite{petsc-user-ref} GMRES solver, preconditioned by incomplete factorization.
 
@@
 This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
-Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models are more dissimilar, even though the nonlinear term in the high-fidelity models remain the same.
+Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \cref{eq:cdvcdrHF} and \cref{eq:cdvcdrHF3D} is a quadratic reaction term.
 % KW: don't know what last part of this sentence means.
 what hi-fi models?
-This behavior suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the predicted high-fidelity QoI $I(q_{MF},u_{MF})+\epsilon_i$ for two consecutive iterations agree to within some tolerance.
+The possibility of large inaccuracies in the error estimates of low-fidelity and mostly unrefined mixed-fidelity models suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the estimated high-fidelity QoI ($I(q_{MF},u_{MF})+\epsilon_i$) for two consecutive iterations agree to within some tolerance.
 % KW: what behavior?
@@
 I'd probably delete this last sentence.
+% or just let the reader decide how to deal with possibly inaccurate initial error estimates?
 

### 2016-11-15 paper/algorithms_v3.tex
stashing edits
removed linearization about psi in superadj as a source of error

@@
 \Cref{alg:refSeries} describes this approach.
-Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+%Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
-	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
+	\State{Solve QoI error adjoint equation
+	%, linearized about $\Psi_{MF_0}$,
+	 for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
 	\State{Compute QoI error estimate
@@
 		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
-		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
+		\State{Solve QoI error adjoint equation%, linearized about $\Psi_{MF_i}$,
+		 for
 
@@
 %------------------------------------------------------------------------------------------------------------------------%
-%\subsection{Extension to Offline-Online Setting}\label{sec:onoff}
-%------------------------------------------------------------------------------------------------------------------------%
-
-%\Cref{alg:refSeries} can be naturally extended to an offline-online setting.
-One variation would be analagous to the offline-online decomposition proposed in \cite{LiebWill13}.
-The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$.
-When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI.
-The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.
-
-%Another variation occurs in the context of a quasi-incremental data assimilation approach.
-A multi-fidelity model adaptive constraint can be generated for a given dataset $d_1$ in the offline phase.
-In the online phase, additional data points are included to form an augmented dataset $d_2$, and instead of solving the complete inverse problem with all the data points and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase.
-The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.
-In such a situation where $d_1\in d_2$, we expect that the model refinement will be concentrated around those of the new data points that also inform the QoI.
-Thus, in the online phase, even though the inverse problem will be solved with all data points $d_2$, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.
-
-%------------------------------------------------------------------------------------------------------------------------%
 \subsection{Error Estimate Localization}\label{sec:errLocal}

### 2016-11-15 paper/numerical_experiments_v3.tex
removed linearization about psi in superadj as a source of error

@@
 \Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated.
-Each linear Lagrange basis function's contribution is plotted at its nonzero node.
+%Each linear Lagrange basis function's contribution is plotted at its nonzero node.
 %
@@
 
-We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors.
-This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
+We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors. This can be attributed to the 
+%linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; 
+third-order term that is ignored in the error estimate;
+the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
 Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \cref{eq:cdvcdrHF} and \cref{eq:cdvcdrHF3D} is a quadratic reaction term.

### 2016-11-15 paper/mathematical_formulation_v3.tex
stashing edits
removed linearization about psi in superadj as a source of error
Minor rearrangement of equations 5-7 in Theorem 1

@@
 In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
-Consider the adjoint problem
+Let the variational form,
 %
 \begin{equation}
-\mathscr{R}_{\Psi_{HF}}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
-\label{eq:superAdjEq}
-\end{equation}
-for the supplementary adjoint $\Lambda$, where $\Phi$ is a test function,  
-\begin{equation}
-\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:supadjsys}
 \end{equation}
-is the residual form of $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$, and $\mathcal{Q}$ is an output defined by
+%
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Also, let $\mathcal{Q}$ be an output defined by
+%
 \begin{equation}
@@
 \end{equation}
-% KW: notation in the equation is \mathcal{M}'_{HF,\Psi}(\Lambda;\Psi_{HF})= M'_{HF}(\Psi_{LF})(\Phi)
-% I don't understand what the difference in notation means.
-Why drop the second subscript on the M'?
-and why the change in arguments?
-And neither instance is consistent with how the ' notation was defined above for the Lagrangian.
-% You can't just introduce new notation and hope that the reader guesses what you mean.
-Everything must be defined!
-Every time you change an argument form, every time you change the form of the subscript, every time you change anything, ...
-% KW: where is \mathcal{Q} defined?
 %
+Define the corresponding adjoint problem,
+%
+\begin{equation}
+\mathscr{R}_{\Psi}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:superAdjEq}
+\end{equation}
+for the supplementary adjoint $\Lambda$.
 Then, the error in the Quantity of Interest $I$ is given by,
@@
 %
-Applying the output error representation described in Proposition 3 from~\cite{BecVex05} 
-% KW: what is Prop 3? is it something we need to state/summarize here for completeness? maybe okay as is, just seems a little mysterious.
-for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
+Applying the output error representation described in Proposition 3 from~\cite{BecVex05} for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
 \begin{equation}

### 2016-11-16 paper/abstract_v2_kw.tex
karen's comments...?

An inverse problem seeks to infer unknown model parameters using observed data. We consider a \textit{goal-oriented inverse problem}, where the goal of inferring parameters is to use them in predicting a quantity of interest (QoI). Recognizing that multiple models of varying fidelity and computational cost may be available to describe the physical system, we formulate a goal-oriented model adaptivity approach that leverages multiple models while controlling the error in the QoI prediction. In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different subregions of the domain. Taking the solution of the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive an adjoint-based third-order estimate for the QoI error from using a lower-fidelity model. Localization of this error then guides the formation of mixed-fidelity models. We demonstrate the method for example problems described by convection-diffusion-reaction models. For these examples, our mixed-fidelity models use the high-fidelity model over only a small portion of the domain, but result in QoI estimates with small relative errors. We also demonstrate that the mixed-fidelity inverse problems can be cheaper to solve and less sensitive to the initial guess than the high-fidelity inverse problems.

%from karen about v1:
%"minimizing the use of high-fidelity constraints" -> won't make sense
%needs to be expanded + 1-2 sentences on approach; sentence on results needs to be more specific

### 2016-11-16 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split_clean/convdiff_aux.C
see if this works...

@@ -1,0 +1,354 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_aux.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+#include "libmesh/equation_systems.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_AuxSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+	
+	FEFamily meep = Utility::string_to_enum<FEFamily>(std::string("SCALAR"));
+	aux_fpin_var = this->add_variable("aux_fpin", static_cast<Order>(conc_p), meep); 
+
+	//regularization
+	if(infile.have_variable("beta")){
+		beta_mag = infile("beta",0.1);
+		beta_grad = infile("beta",0.1);
+	}
+	else{
[…]

### 2016-11-16 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split_clean/convdiff_mprime.C

@@ -1,0 +1,429 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_mprime.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_MprimeSys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	aux_c_var = this->add_variable("aux_c", static_cast<Order>(conc_p), fefamily); 
+	aux_zc_var = this->add_variable("aux_zc", static_cast<Order>(conc_p), fefamily);
+	aux_fc_var = this->add_variable("aux_fc", static_cast<Order>(conc_p), fefamily);   
+	
+	//FEFamily meep = Utility::string_to_enum<FEFamily>(std::string("SCALAR"));
[…]

### 2016-11-16 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split_clean/convdiff_mprime.h

@@ -1,0 +1,148 @@
+#include "libmesh/fem_system.h"
+#include "libmesh/getpot.h"
+#include "libmesh/point_locator_tree.h"
+
+using namespace libMesh;
+
+class ConvDiff_MprimeSys : public FEMSystem
+{
+public:
+
+  // Constructor
+  ConvDiff_MprimeSys(EquationSystems& es,
+               const std::string& name_in,
+               const unsigned int number_in)
+    : FEMSystem(es, name_in, number_in){
+    
+    GetPot infile("convdiff_mprime.in");
+		std::string find_velocity_here = infile("velocity_file","velsTtrim.txt");
+		std::string find_data_here = infile("data_file","Measurements_top6.dat");
+		qoi_option = infile("QoI_option",1);
+    
+    const unsigned int dim = this->get_mesh().mesh_dimension();
+    
+    if(FILE *fp=fopen(find_velocity_here.c_str(),"r")){
+    	if(dim == 2){
+				Real u, v, x, y;
+				Real prevx = 1.e10;
+				std::vector<Real> tempvecy;
+				std::vector<NumberVectorValue> tempvecvel;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp, "%lf %lf %lf %lf",&u,&v,&x,&y);
+					if(flag != -1){
+						if(x != prevx){
+							x_pts.push_back(x);
+							prevx = x;
+							if(x_pts.size() > 1){
+								y_pts.push_back(tempvecy);
+								vel_field.push_back(tempvecvel);
+							}
+							tempvecy.clear(); 
+							tempvecvel.clear();
+							tempvecy.push_back(y); 
+							tempvecvel.push_back(NumberVectorValue(u,v));
+						}
+						else{
+							tempvecy.push_back(y); 
+							tempvecvel.push_back(NumberVectorValue(u,v));
+						}
+					}
+				}
+				y_pts.push_back(tempvecy);
+				vel_field.push_back(tempvecvel);
+  		}
+  	}
+		if(FILE *fp=fopen(find_data_here.c_str(),"r")){
+			if(dim == 2){
+				Real x, y, value;
+				int flag = 1;
+				while(flag != -1){
+					flag = fscanf(fp,"%lf %lf %lf",&x,&y,&value);
+					if(flag != -1){
+						datapts.push_back(Point(x,y));
+						datavals.push_back(value);
+					}
+				}
+				fclose(fp);
+	  	}
[…]

### 2016-11-16 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split_clean/convdiff_primary.C

@@ -1,0 +1,311 @@
+#include "libmesh/getpot.h"
+
+#include "convdiff_primary.h"
+
+#include "libmesh/boundary_info.h"
+#include "libmesh/dirichlet_boundaries.h"
+#include "libmesh/dof_map.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fe_interface.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/mesh.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/string_to_enum.h"
+#include "libmesh/zero_function.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+// System initialization
+void ConvDiff_PrimarySys::init_data (){
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+
+	//polynomial order and finite element type
+	unsigned int conc_p = 1;
+	GetPot infile("convdiff_mprime.in");
+	std::string fe_family = infile("fe_family", std::string("LAGRANGE"));
+
+	// LBB needs better-than-quadratic velocities for better-than-linear
+	// pressures, and libMesh needs non-Lagrange elements for
+	// better-than-quadratic velocities.
+	//libmesh_assert((conc_p == 1) || (fe_family != "LAGRANGE"));
+
+	FEFamily fefamily = Utility::string_to_enum<FEFamily>(fe_family);
+	c_var = this->add_variable("c", static_cast<Order>(conc_p), fefamily); 
+	zc_var = this->add_variable("zc", static_cast<Order>(conc_p), fefamily); 
+	fc_var = this->add_variable("fc", static_cast<Order>(conc_p), fefamily); 
+	
+	FEFamily meep = Utility::string_to_enum<FEFamily>(std::string("SCALAR"));
+	fpin_var = this->add_variable("fpin", static_cast<Order>(conc_p), meep); 
+
+	//regularization
+	if(infile.have_variable("beta")){
+		beta_mag = infile("beta",0.1);
+		beta_grad = infile("beta",0.1);
+	}
+	else{
+		beta_mag = infile("beta_mag",0.1);
+		beta_grad = infile("beta_grad",0.1);
+	}
+	
+	//diffusion coefficient
[…]

### 2016-11-16 practice/T_channel/diff_param_res/with_reaction/get_psi_MF_split_clean/element_qoi.C

@@ -1,0 +1,147 @@
+// General libMesh includes
+#include "libmesh/libmesh_common.h"
+#include "libmesh/elem.h"
+#include "libmesh/fe_base.h"
+#include "libmesh/fem_context.h"
+#include "libmesh/point.h"
+#include "libmesh/quadrature.h"
+#include "libmesh/fe_interface.h"
+
+// Local includes
+#include "convdiff_mprime.h"
+
+// Bring in everything from the libMesh namespace
+using namespace libMesh;
+
+//to compute M_HF(psiLF) and M_LF(psiLF) terms of QoI error estimate
+
+void ConvDiff_MprimeSys::element_postprocess (DiffContext &context)
+
+{
+	const unsigned int dim = this->get_mesh().mesh_dimension();
+	Real PI = 3.14159265359;
+	
+  FEMContext &ctxt = cast_ref<FEMContext&>(context);
+
+  FEBase* elem_fe = NULL;
+  ctxt.get_element_fe( c_var , elem_fe );
+  
+  int myElemID = ctxt.get_elem().id();
+
+  // Element Jacobian * quadrature weights for interior integration
+  const std::vector<Real> &JxW = elem_fe->get_JxW();
+
+	//get location of quadrature points
+  const std::vector<Point> &xyz = elem_fe->get_xyz();
+
+  // The number of local degrees of freedom in each variable
+  unsigned int n_qpoints = ctxt.get_element_qrule().n_points();
+
+	//this element's contribution to MHF(psiLF) and MLF(psiLF)
+  Number MHF_psiLF_elem = 0.;
+  Number MLF_psiLF_elem = 0.;
+
+  // Loop over quadrature points
+  for (unsigned int qp = 0; qp != n_qpoints; qp++)
+    {
+      // Get co-ordinate locations of the current quadrature point
+      const Real ptx = xyz[qp](0);
+      const Real pty = xyz[qp](1);
+      
+      Number 
+	      c = ctxt.interior_value(c_var, qp),
+	      zc = ctxt.interior_value(zc_var, qp),
[…]

### 2016-11-17 paper/intro_v3.tex
Reorged intro a little bit

@@
 Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs).
-The inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
-Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of the mathematical model.
+On the other hand, the inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
+Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of complex mathematical models.
 In many cases, a given physical system can be represented with varying degrees of fidelity by different models.
 A higher-fidelity model more accurately represents reality, but is also usually more computationally expensive to solve.
-Lower-fidelity models reduce the computational cost of the forward problem, at the expense of introducing approximations.
-In this work, we formulate an approach for leveraging multiple models of varying fidelities in solution of an inverse problem.
+Lower-fidelity models can solved inexpensively, at the expense of introducing model errors.
+In this work, we formulate an approach for leveraging multiple models of varying fidelities in the solution of an inverse problem.
 
@@
 
-Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining acceptably low error estimate of the QoI.
+Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining an acceptably low error tolerance for the QoI.
 In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}.
@@
 The inverse problem setting has also seen some work on goal-oriented methods.
+To begin with, it has been recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI.
+For example, for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI~\cite{LiebWill13}.
+This subspace provides a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them.
+For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters~\cite{Span16}.
 Mesh refinement in the goal-oriented inverse problem is addressed in~\cite{BecVex05}; in that work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite-dimensional inverse problem, and this error estimate is used to adaptively refine the mesh.
-An outline extending the approach to goal-oriented model adaptivity described in~\cite{OdenPrudetal06} to the inverse problem is presented in~\cite{OdenPrudetal10}.
-Other work has recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI.
-This idea is formalized in ~\cite{LiebWill13}; for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI.
-This subspace is used to produce a low-dimensional map from the observations directly to the QoI, sacrificing accuracy in the inferred parameters for accuracy in the QoI that is computed from them.
-For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters~\cite{Span16}.
+Also, an outline extending the approach to goal-oriented model adaptivity described in~\cite{OdenPrudetal06} to the inverse problem is presented in~\cite{OdenPrudetal10}.
 
-In this paper, we target model adaptivity the solution of goal-oriented inverse problems.
+In this paper, we target model adaptivity in the solution of goal-oriented inverse problems.
 We present a robust, adaptive framework that identifies the subregions of the domain where high-fidelity representation of physics and parameters is important to achieving a desired accuracy in the QoI.

### 2016-11-22 vikram_scalar_field_investigation/element_postprocess.C
Writing out solutions

@@ -1,4 +1,4 @@
-#include "scalarfieldsystem.h"
+#include "scalar_field.h"
 #include "libmesh/fe_base.h"
 #include "libmesh/quadrature.h"
 #include "libmesh/elem.h"
@@ -30,7 +30,7 @@ void ScalarFieldSystem::element_postprocess(DiffContext &context)
 
   FEMContext &c = libmesh_cast_ref<FEMContext&>(context);
 
-  FEBase* u_elem_fe = NULL;
+  FEBase* u_elem_fe;
   c.get_element_fe( 0, u_elem_fe );
 
   // First we get some references to cell-specific data that
@@ -101,12 +101,12 @@ void ScalarFieldSystem::element_postprocess(DiffContext &context)
   std::vector<Gradient> supp_adjoint_grad_aux_zc (n_qpoints, 0);
   std::vector<Gradient> supp_adjoint_grad_aux_fc (n_qpoints, 0);
 
-  c.interior_gradient<Number>(0, adjoint_solution, supp_adjoint_grad_c);
-  c.interior_gradient<Number>(1, adjoint_solution, supp_adjoint_grad_zc);
-  c.interior_gradient<Number>(2, adjoint_solution, supp_adjoint_grad_fc);
-  c.interior_gradient<Number>(3, adjoint_solution, supp_adjoint_grad_aux_c);
-  c.interior_gradient<Number>(4, adjoint_solution, supp_adjoint_grad_aux_zc);
-  c.interior_gradient<Number>(5, adjoint_solution, supp_adjoint_grad_aux_fc);
+  c.interior_gradients<Gradient>(0, adjoint_solution, supp_adjoint_grad_c);
+  c.interior_gradients<Gradient>(1, adjoint_solution, supp_adjoint_grad_zc);
+  c.interior_gradients<Gradient>(2, adjoint_solution, supp_adjoint_grad_fc);
+  c.interior_gradients<Gradient>(3, adjoint_solution, supp_adjoint_grad_aux_c);
+  c.interior_gradients<Gradient>(4, adjoint_solution, supp_adjoint_grad_aux_zc);
+  c.interior_gradients<Gradient>(5, adjoint_solution, supp_adjoint_grad_aux_fc);
 
[…]

### 2016-11-22 vikram_scalar_field_investigation/scalar_field.C

@@ -19,7 +19,7 @@
 
 #include "libmesh/getpot.h"
 
-#include "scalarfieldsystem.h"
+#include "scalar_field.h"
 
 #include "libmesh/fe_base.h"
 #include "libmesh/fe_interface.h"
@@ -64,7 +64,7 @@ void ScalarFieldSystem::init_context(DiffContext &context)
         const_cast<System &>(sys).get_adjoint_solution(0);
 
       // Add this adjoint solution to the vectors that diff context should localize
-      c.add_localized_vector(adjoint_solution0, sys);
+      c.add_localized_vector(adjoint_solution, sys);
     }
 
   FEMSystem::init_context(context);

### 2016-11-22 vikram_scalar_field_investigation/scalar_field.h

@@ -39,6 +39,8 @@ public:
     return computed_QoI[QoI_index];
   }
 
+virtual void postprocess(void);
+
 protected:
   // System initialization
   virtual void init_data ();

### 2016-11-22 vikram_scalar_field_investigation/scalar_field_breakdown.C

@@ -28,6 +28,7 @@
 
 #include "libmesh/getpot.h"
 #include "libmesh/exodusII_io.h"
+#include "libmesh/gmv_io.h"
 
 // To impose Dirichlet boundary conditions
 #include "libmesh/dirichlet_boundaries.h"
@@ -84,6 +85,35 @@ int main (int argc, char** argv)
     // Print information about the mesh and systems to the screen.
     mesh.print_info();
     equation_systems.print_info();
+
+    System &read_system = equation_systems.get_system<System> ("ConvDiff_MprimeSys");
+
+    std::ostringstream file_name_gmv_primal;
+    file_name_gmv_primal << "primal.out.gmv."
+                    << std::setw(3)
+                    << std::setfill('0')
+                    << std::right
+                    << i;
+
+    GMVIO(mesh).write_equation_systems
+      (file_name_gmv_primal.str(), equation_systems);
+
+    NumericVector<Number> &primal_solution = (*read_system.solution);
+    NumericVector<Number> &dual_solution = read_system.get_adjoint_solution(0);
+
+    primal_solution.swap(dual_solution);
+
+    std::ostringstream file_name_gmv_dual;
+    file_name_gmv_dual << "dual.out.gmv."
+                    << std::setw(3)
+                    << std::setfill('0')
+                    << std::right
+                    << i;
+
+    GMVIO(mesh).write_equation_systems
+      (file_name_gmv_dual.str(), equation_systems);
+
+    primal_solution.swap(dual_solution);
 
     equation_systems.reinit();
   }

### 2016-11-22 paper/mathematical_formulation_v3.tex
Reworded and reorder Theorem 1 as discussed.

@@
 %
-\begin{theorem}
+\begin{proposition}
 \label{thm:error_estimate}
@@
 %
-represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Also, let $\mathcal{Q}$ be an output defined by
-%
-\begin{equation}
-\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi).
-\label{eq:supadjout}
-\end{equation}
-%
-Define the corresponding adjoint problem,
-%
-\begin{equation}
-\mathscr{R}_{\Psi}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
-\label{eq:superAdjEq}
-\end{equation}
-for the supplementary adjoint $\Lambda$.
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function.
 Then, the error in the Quantity of Interest $I$ is given by,
@@
 \begin{multline}
-\label{eq:finErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
+\label{eq:semifinErrExp}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
 \end{multline}
@@
 where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$.
-\end{theorem}
+\end{proposition}
 %
@@
 \end{multline}
+which completes the proof.
+\end{proof}
+%
 
-We note that, as a stationary point, $\Psi_{HF}$ satisfies \cref{eq:supadjsys}.
-Further, the error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can be expressed as a dual-weighted residual,
+The above proposition splits the error in the QoI into three components, a third order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
+Although the linear term is not computable, it can be estimated using an appropriate dual problem.
+We describe one method of estimating this term below.
+
+Note that, as a stationary point, $\Psi_{HF}$ satisfies~\cref{eq:supadjsys}. Now, let $\mathcal{Q}$ be an output defined by
+%
+\begin{equation}
+\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi).
+\label{eq:supadjout}
+\end{equation}
+%
+Define the corresponding adjoint problem,
+%
+\begin{equation}
+\mathscr{R}_{\Psi}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:superAdjEq}
+\end{equation}
+for the supplementary adjoint $\Lambda$. The error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can then be expressed as a dual-weighted residual,
 \begin{equation}
@@
 \begin{multline}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3), \nonumber
+\label{eq:finErrExp}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3)
 \end{multline}
 %
-which completes the proof.
-\end{proof}
-%
+Other approaches can become feasible in certain scenarios, for example if the high and low fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can simply be approximated using interpolation or patch recovery methods~\cite{BecVex05}.

### 2016-11-23 paper/intro_v3.tex
ahhh mixed up some versions last commit

@@
 Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs).
-On the other hand, the inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
-Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of complex mathematical models.
+The inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters.
+Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of the mathematical model.
 In many cases, a given physical system can be represented with varying degrees of fidelity by different models.
 A higher-fidelity model more accurately represents reality, but is also usually more computationally expensive to solve.
-Lower-fidelity models can solved inexpensively, at the expense of introducing model errors.
-In this work, we formulate an approach for leveraging multiple models of varying fidelities in the solution of an inverse problem.
+Lower-fidelity models can be solved inexpensively, at the expense of introducing approximations.
+In this work, we formulate an approach for leveraging multiple models of varying fidelities in solution of an inverse problem.
 

### 2016-11-26 paper/algorithms_v3_cmame.tex

--- 2016-11-15 paper/algorithms_v3.tex
@@
 
-Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
+Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \Cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
 The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
@@
 \Cref{alg:refSeries} describes this approach.
-%Note that the QoI error adjoint problem \cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+Note that the QoI error adjoint problem \Cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 	\State{Solve for stationary point $\Psi_{MF_0}$ of augmented Lagrangian $\mathcal{M}_{MF_0}$}
-	\State{Solve QoI error adjoint equation
-	%, linearized about $\Psi_{MF_0}$,
-	 for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_0$ (see \cref{eq:superAdjEq})}
+	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_0}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_0$ (see \Cref{eq:superAdjEq})}
 	\State{Compute QoI error estimate
@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \Cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
 		\State{$i\gets i+1$}
 		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
-		\State{Solve QoI error adjoint equation%, linearized about $\Psi_{MF_i}$,
-		 for
+		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for
 
-		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \cref{eq:superAdjEq})}
+		$\quad\quad$supplementary adjoint $\Lambda_i$ (see \Cref{eq:superAdjEq})}
 		\State{Compute QoI error estimate

### 2016-11-26 paper/mathematical_formulation_v3_cmame.tex

--- 2016-11-22 paper/mathematical_formulation_v3.tex
@@
 where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
-The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \cref{eq:weakForm}, they are linear with respect to $\phi$).
+The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
 Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
@@
 %
-Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \cref{eq:weakForm}, which appears as a constraint in \cref{eq:invOpt_cons}.
-The constraints \cref{eq:invOpt_cons} are typically models of physical processes or systems.
+Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.
+The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems.
 A given physical system can be described to varying degrees of fidelity using different models.
@@
 In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
-We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \cref{eq:invOpt_cons}.
+We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
 %
@@
 \label{thm:error_estimate}
-Consider the inverse problem described by the constrained optimization problem \cref{eq:invOpt}.
+Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}.
 Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
@@
 
-Consider the Lagrangian equation induced by \cref{eq:invOpt},
+Consider the Lagrangian equation induced by \Cref{eq:invOpt},
 %
@@
 Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$.
-Let the augmented Lagrangian be defined as,
+Let the augmented Lagrangian be defined as
 %
@@
 In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
-Let the variational form,
+Let the variational form
 %
 \begin{equation}
-\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:supadjsys}
@@
 represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function.
-Then, the error in the Quantity of Interest $I$ is given by,
+Then, the error in the Quantity of Interest $I$ is given by
 %
@@
 
-Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have,
+Extending the property in \Cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have
 %
@@
 \end{equation}
-Combining \cref{eq:repIwithM} and \cref{eq:beckvex} we obtain
+Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain
 \begin{multline}
@@
 
-Note that, as a stationary point, $\Psi_{HF}$ satisfies~\cref{eq:supadjsys}. Now, let $\mathcal{Q}$ be an output defined by
+Note that, as a stationary point, $\Psi_{HF}$ satisfies~\Cref{eq:supadjsys}. Now, let $\mathcal{Q}$ be an output defined by
 %
@@
 %
-Define the corresponding adjoint problem,
+Define the corresponding adjoint problem
 %
 \begin{equation}
-\mathscr{R}_{\Psi}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}_{\Psi}'(\Psi_{HF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
 \end{equation}
-for the supplementary adjoint $\Lambda$. The error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys}.
+The error in the output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
 \begin{equation}
@@
 %
-Combining \cref{eq:preadj} and \cref{eq:adjOutErr}, we have,
+Combining \Cref{eq:preadj} and \Cref{eq:adjOutErr}, we have,
 \begin{multline}
@@
 %
-Other approaches can become feasible in certain scenarios, for example if the high and low fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can simply be approximated using interpolation or patch recovery methods~\cite{BecVex05}.
+Other approaches can become feasible in certain scenarios; for example, if the high- and low-fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can be approximated using interpolation or patch recovery methods~\cite{BecVex05}.

### 2016-11-26 paper/numerical_experiments_v3_cmame.tex

--- 2016-11-15 paper/numerical_experiments_v3.tex
@@
 %
-We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}.
+We now use \Cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \Cref{sec:errLocal}.
 We first consider two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions.
-In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model.
-We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
-In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented.
-In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.
+In \Cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model.
+We apply \Cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region.
+In \Cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented.
+In \Cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.
 
@@
 In this section, we consider a pair of models which differ in the physics included.
-In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
-\Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
+In \Cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem.
+\Cref{sec:cdvcdrBaseRef} describes the results of applying \Cref{alg:refSeries} to the baseline problem, and \Cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
 %
@@
 The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
-\cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated.
+\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated.
 For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
 %
@@
 
-We now present the results for solving the inference problem using \cref{alg:refSeries}.
-Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions.
+We now present the results for solving the inference problem using \Cref{alg:refSeries}.
+Once the QoI error estimate is calculated using \Cref{eq:finErrExp}, the error estimate is then decomposed into local contributions.
 At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement.
@@
 We see that the largest local error contributions are concentrated in the QoI region and around the observation location closest to the QoI.
-In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is greatest is around the leftmost observation location.
+In the first decomposition of the error (\Cref{fig:baseRef0}), the region where the elemental error is greatest is around the leftmost observation location.
 Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right.
@@
 
-\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively.
+\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively.
 In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain.
@@
 
-\cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
-The error decompositions for each case are also shown in \cref{fig:qoiStudy}.
-The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \cref{sec:cdvcdrBaseRef}.
+\Cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
+The error decompositions for each case are also shown in \Cref{fig:qoiStudy}.
+The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
 % KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
@@
   \caption{Effects of increasing the QoI region.
-Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
-Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
+Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box).
+Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
   \label{fig:qoiStudy}
@@
 
-\cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
-The error decomposition for the three cases is shown in \cref{fig:dataStudy}.
-The bottom row is the same as that in \cref{fig:qoiStudy}.
+\Cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
+The error decomposition for the three cases is shown in \Cref{fig:dataStudy}.
+The bottom row is the same as that in \Cref{fig:qoiStudy}.
 Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region.
@@
 
-We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
+We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
 \begin{equation}
@@
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}.
-As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \Cref{sec:cdvcdr}.
+As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
 
@@
 
-As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
+As with the previous examples in \Cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model.
 The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used.
@@
 %
-Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
+Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration.
 This reflects the global nature of the differences between the low- and high-fidelity models.
 
-The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
+The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
 %
@@
 The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
-We also see that in this case, in contrast to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
 
@@
 
-In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, computational effort.
+In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \Cref{alg:refSeries}, they are both simple enough and similar enough that using \Cref{alg:refSeries} saves little, if any, computational effort.
 In this section, we consider a pair of models that differ in both the physics included and the mesh resolution, and we demonstrate computational savings using the multi-fidelity approach.
-In \cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D_diffmesh} we describe the results of applying \cref{alg:refSeries} to this pair of models.
+In \Cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \Cref{sec:ref3D_diffmesh} we describe the results of applying \Cref{alg:refSeries} to this pair of models.
 
@@
 The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day.
-Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}.
+Given this velocity field and letting the molecular diffusion be negligible, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}.
 We have porosity $n=0.1$.
 The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions.
-Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.
+Although the reaction term $k_ru^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degradation of petroleum hydrocarbons in soils \cite{Jack94}.
 
@@
 The boundary conditions remain unchanged.
-As in the previous examples in \cref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where \cref{eq:HFeq3D,eq:LFeq3D} are solved, respectively.
+As in the previous examples in \Cref{sec:cdvcdr}, the mixed-fidelity models are formed by dividing the domain into complementary subdomains $\Omega_{HF}$ and $\Omega_{LF}$, where \Cref{eq:HFeq3D,eq:LFeq3D} are solved, respectively.
 The QoI we wish to calculate is the integral of the state over a region $\Omega_I$.
@@
 Synthetic observations at 18 points in the domain are generated by running the high-fidelity model on a finer mesh.
-The locations of the observations as well as the QoI region $\Omega_I$ are shown in \cref{fig:setup3D}.
-We set the regularization term in \cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
+The locations of the observations as well as the QoI region $\Omega_I$ are shown in \Cref{fig:setup3D}.
+We set the regularization term in \Cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
 %
@@
 
-We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
+We now present the results of solving the inference problem using \Cref{alg:refSeries}, with a relative error tolerance of $0.1\%$.
 At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples.
@@
 
-We notice that, compared to the results in \cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors. This can be attributed to the 
-%linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints; 
-third-order term that is ignored in the error estimate;
-the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
-Compared to the pair of models in \cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \cref{eq:cdvcdrHF} and \cref{eq:cdvcdrHF3D} is a quadratic reaction term.
+We notice that, compared to the results in \Cref{fig:baseErr}, the error estimates for the low-fidelity and first mixed-fidelity models are far from the true errors.
+This can be attributed to the linearization about $\Psi_{LF}$ and $\Psi_{MF_{1}}$ instead of $\Psi_{HF}$ in solving the supplementary adjoints as well as the third-order term that is ignored in the error estimate; the large differences in the QoI for the LF and MF01 models compared to the high-fidelity QoI indicate that $\Psi_{LF}$ and $\Psi_{MF_{1}}$ are significantly different from $\Psi_{HF}$.
+Compared to the pair of models in \Cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \Cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \Cref{eq:cdvcdrHF} and \Cref{eq:cdvcdrHF3D} is a quadratic reaction term.
 % KW: don't know what last part of this sentence means.
 what hi-fi models?
-The possibility of large inaccuracies in the error estimates of low-fidelity and mostly unrefined mixed-fidelity models suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the estimated high-fidelity QoI ($I(q_{MF},u_{MF})+\epsilon_i$) for two consecutive iterations agree to within some tolerance.
+%The possibility of large inaccuracies in the error estimates of low-fidelity and mostly unrefined mixed-fidelity models suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the estimated high-fidelity QoI ($I(q_{MF},u_{MF})+\epsilon_i$) for two consecutive iterations agree to within some tolerance.
 % KW: what behavior?
@@
 
-The multi-fidelity domain refinements for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}.
-Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement.
+The multi-fidelity domain refinements for the five adaptive iterations are shown in \Cref{fig:divvy3D_diffmesh}.
+Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement.
 We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
@@
 To illustrate this offline-online application, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values).
-We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
+We then solve the inverse problem using each of the mixed-fidelity models depicted in \Cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
 The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
@@
 For six of the ten datasets, the high-fidelity inverse problem does not converge given the low-fidelity solution as an initial guess; these are solved using the $k_r=0$ solution as an initial guess so that true QoI errors can be calculated.
-The average high-fidelity inverse problem solution time shown in \cref{tab:ref3D_newdata_times_diffmesh} includes only those cases (four of ten) that converged with the low-fidelity initial guess.
+The average high-fidelity inverse problem solution time shown in \Cref{tab:ref3D_newdata_times_diffmesh} includes only those cases (four of ten) that converged with the low-fidelity initial guess.
 %

### 2016-11-26 paper/paper_v3_cmame.tex

--- 2016-11-10 paper/paper_v3.tex
@@
-\documentclass[review]{siamart0516}
+\documentclass[review,sort&compress]{elsarticle}
 %%\usepackage{lgrind}
@@
 %\usepackage[square,comma,numbers,sort&compress]{natbib}
-%\usepackage{amsmath,amsthm,amssymb,amsfonts,amsbsy,latexsym} %amsthm inclusion conflicts with sisc...
-\usepackage{amsmath,amssymb,amsfonts,amsbsy,latexsym}
+\usepackage{amsmath,amsthm,amssymb,amsfonts,amsbsy,latexsym} %amsthm inclusion conflicts with sisc...
+%\usepackage{amsmath,amssymb,amsfonts,amsbsy,latexsym}
 \usepackage{graphics}
@@
 \usepackage{hyperref}
+\usepackage{cleveref}
 
-%\usepackage{algorithmicx}
-%\usepackage[ruled]{algorithm}
+\usepackage{algorithmicx}
+\usepackage[ruled]{algorithm}
 \usepackage{algpseudocode}
@@
 
-%\newtheorem{theorem}{Theorem} %conflicts with sisc
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
 
@@
 
-\author{Harriet Li, Vikram Garg, Karen Willcox}
+\author{Harriet Li\textsuperscript{a,}\footnote{\red{Corresponding author ? \textit{Email address: foo@bar.edu}}}, Vikram Garg\textsuperscript{b}, Karen Willcox\textsuperscript{c}}
+\address{\textsuperscript{a} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}\protect\\
+\textsuperscript{b} Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}\protect\\
+\textsuperscript{c} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
 %\date{}
@@
 \begin{abstract}
-\input{abstract_v2.tex}
+\input{abstract_v3.tex}
 \end{abstract}
 
-\begin{keywords}
-  inference, goal-oriented adaptive modeling, a posteriori error estimation, multifidelity modeling, adjoints, PDEs
-\end{keywords}
+\begin{keyword}
+  inference \sep goal-oriented adaptive modeling \sep a posteriori error estimation \sep multifidelity modeling \sep adjoints
+\end{keyword}
 
-\begin{AMS}
-  35R30, 65G20, 62F35, 35R15
-\end{AMS}
-
-\input{intro_v2.tex}
-\input{mathematical_formulation_v2.tex}
-\input{algorithms_v2.tex}
-\input{numerical_experiments_v2.tex}
-\input{conclusions_v2.tex}
+\input{intro_v3_cmame.tex}
+\input{mathematical_formulation_v3_cmame.tex}
+\input{algorithms_v3_cmame.tex}
+\input{numerical_experiments_v3_cmame.tex}
+\input{conclusions_v3_cmame.tex}
 \input{acknow.tex}
 
-\bibliographystyle{siamplain}
+\section*{References}
+\bibliographystyle{plain}
 \bibliography{masterBib}

### 2016-12-12 paper/mathematical_formulation_v4_cmame.tex
adding edits from karen

--- 2016-11-26 paper/mathematical_formulation_v3_cmame.tex
@@
 In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
-Let the variational form
-%
-\begin{equation}
-\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
-\label{eq:supadjsys}
-\end{equation}
-%
-represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function.
 Then, the error in the Quantity of Interest $I$ is given by
@@
 \label{eq:semifinErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
 \end{multline}
@@
 %
-Define the corresponding adjoint problem
+Let the variational form
+%
+\begin{equation}
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:supadjsys}
+\end{equation}
+%
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
 %
@@
 \label{eq:finErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3)
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
 \end{multline}

### 2016-12-12 paper/numerical_experiments_v4_cmame.tex
adding edits from karen

--- 2016-11-26 paper/numerical_experiments_v3_cmame.tex
@@
 Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box).
-Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
+Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
   \label{fig:qoiStudy}
@@
 In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain.
-This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model would be most helpful.
-% KW: I don't understand a lot of this discussion.
-You need to explain to me what you mean.
+This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model leads to well-supported modeling choices.
 
@@
 Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box).
-Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
+Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
   \label{fig:dataStudy}

### 2016-12-14 paper/paper_v4_cmame.tex
adding edits from karen
fixing latex formatting issues in cmame version

--- 2016-11-26 paper/paper_v3_cmame.tex
@@
 \begin{document}
-\raggedbottom %avoid weird vertical justification
+%\raggedbottom %avoid weird vertical justification
+
+\begin{frontmatter}
 
@@
 
-\author{Harriet Li\textsuperscript{a,}\footnote{\red{Corresponding author ? \textit{Email address: foo@bar.edu}}}, Vikram Garg\textsuperscript{b}, Karen Willcox\textsuperscript{c}}
-\address{\textsuperscript{a} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}\protect\\
-\textsuperscript{b} Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}\protect\\
-\textsuperscript{c} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
+%\author{Harriet Li\textsuperscript{a,}\footnote{Corresponding author. \textit{Email address: kameeko@mit.edu}}, Vikram Garg\textsuperscript{b}, Karen Willcox\textsuperscript{c}}
+%\address{\textsuperscript{a} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}\protect\\
+%\textsuperscript{b} Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}\protect\\
+%\textsuperscript{c} Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
 %\date{}
-\maketitle
+%\maketitle
+
+\author[adr1]{Harriet Li\corref{cor1}}
+\cortext[cor1]{Corresponding author. \textit{Email address: kameeko@mit.edu}}
+\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}}
+\author[adr2]{Vikram Garg}
+\address[adr2]{Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}}
+\author[adr3]{Karen Willcox}
+\address[adr3]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
 
 \begin{abstract}
-\input{abstract_v3.tex}
+\input{abstract_v4.tex}
 \end{abstract}
@@
 \begin{keyword}
-  inference \sep goal-oriented adaptive modeling \sep a posteriori error estimation \sep multifidelity modeling \sep adjoints
+  inference \sep goal-oriented adaptive modeling \sep a posteriori error estimation \sep multi-fidelity modeling \sep adjoints
 \end{keyword}
 
-\input{intro_v3_cmame.tex}
-\input{mathematical_formulation_v3_cmame.tex}
-\input{algorithms_v3_cmame.tex}
-\input{numerical_experiments_v3_cmame.tex}
-\input{conclusions_v3_cmame.tex}
+\end{frontmatter}
+
+\input{intro_v4_cmame.tex}
+\input{mathematical_formulation_v4_cmame.tex}
+\input{algorithms_v4_cmame.tex}
+\input{numerical_experiments_v4_cmame.tex}
+\input{conclusions_v4_cmame.tex}
 \input{acknow.tex}
@@
 \section*{References}
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
+\bibliographystyle{elsarticle-harv} %this seems to get initials in bibliography, without doing name-year citation style as bst file claims?
 \bibliography{masterBib}

### 2016-12-15 paper/paper_v4_cmame.tex
added missing abstract

@@
 \author[adr1]{Harriet Li\corref{cor1}}
-\cortext[cor1]{Corresponding author. \textit{Email address: kameeko@mit.edu}}
-\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}}
+\cortext[cor1]{Corresponding author. \textit{Email address: hli@alum.mit.edu}}
+\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{hli@alum.mit.edu}}
 \author[adr2]{Vikram Garg}

### 2016-12-15 paper/numerical_experiments_v4_cmame.tex
added missing abstract
minor edits

@@
 \begin{table}[htbp]
-\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
 \label{tab:ref3D_diffmesh}
@@
 \end{tabular}
+\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
 \end{table}
@@
 To illustrate this offline-online application, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values).
-We then solve the inverse problem using each of the mixed-fidelity models depicted in \Cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model.
+We then solve the inverse problem using each of the mixed-fidelity models depicted in \Cref{tab:ref3D_diffmesh} and \Cref{fig:divvy3D_diffmesh} as well as the high-fidelity model.
 The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models.
@@
 \begin{table}
-\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
 \label{tab:ref3D_newdata_QoI_diffmesh}
@@
 \end{tabular}
+\caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
 \end{table}

### 2016-12-16 paper/submitted/round1_jpeg/numerical_experiments_v4_cmame.tex
cleaned latex files and trimmed figures folders for submission

--- 2016-12-15 paper/numerical_experiments_v4_cmame.tex
@@
 In \Cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.
-
-%In all experiments, starting the simulation with the low fidelity model, we seek to add regions of high fidelity, until the estimated relative error in the target QoI is less than 1$\%$.
 
@@
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
-%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
 The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
@@
 \Cref{fig:baseRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. 
-%Each linear Lagrange basis function's contribution is plotted at its nonzero node.
 %
@@
 \subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.jpeg}
   \label{fig:baseRef0}
@@
 \subfloat[MF$_1$ ($5\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.jpeg}
 } \\
 \subfloat[MF$_2$ ($10\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
+  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.jpeg}
 } \\
@@
 The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
-% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
 Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier.
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
-  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
+  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.jpeg}
   \label{subfig:obsSetup}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
-  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
+  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.jpeg}
   \label{subfig:obsLF}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
-  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
+  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.jpeg}
 }
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
+  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.jpeg}
   \label{subfig:obsMFlast}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
-  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
+  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.jpeg}
   \label{subfig:obsSetup2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
-  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
+  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.jpeg}
   \label{subfig:obsLF2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
-  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
+  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.jpeg}
 }
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
+  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.jpeg}
   \label{subfig:obsMFlast2}
@@
 \subfloat[MF$_0$ ($0\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.jpeg}
 } \\
 \subfloat[MF$_1$ ($10\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.jpeg}
 } \\
 \subfloat[MF$_2$ ($20\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
+  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.jpeg}
 } \\
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_3$ ($30\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_4$ ($40\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
-%\begin{subfigure}[b]{\textwidth}
-%	\centering
-%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
-%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
-%  \vspace{-0.7\baselineskip}
-%  \caption{MF$_5$ ($50\%$ HF)}
-%  \vspace{0.8\baselineskip}
-%\end{subfigure}
 \subfloat[MF$_6$ ($60\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
+	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.jpeg}
+  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.jpeg}
 }
@@
 Compared to the pair of models in \Cref{sec:cdvcdrSetup}, the low- and high-fidelity models in this case are more dissimilar, even though in both \Cref{sec:cdvcdrSetup} and this case the nonlinear term in the high-fidelity model \Cref{eq:cdvcdrHF} and \Cref{eq:cdvcdrHF3D} is a quadratic reaction term.
-% KW: don't know what last part of this sentence means.
-what hi-fi models?
-%The possibility of large inaccuracies in the error estimates of low-fidelity and mostly unrefined mixed-fidelity models suggests that one should use more than just the error estimate to decide when to stop the adaptive algorithm; a possible additional criterion could be to require that the estimated high-fidelity QoI ($I(q_{MF},u_{MF})+\epsilon_i$) for two consecutive iterations agree to within some tolerance.
-% KW: what behavior?
-this last sentence doesn't follow from the previous one.
-and what predicted hi-fi QOI?
-Do you mean mixed-fi?
-I'm not sure this is a good idea.
-I'd probably delete this last sentence.
-% or just let the reader decide how to deal with possibly inaccurate initial error estimates?
 
@@
 \subfloat[MF$_1$ ($5.2\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png}
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.jpeg}
 }
 \subfloat[MF$_2$ ($11.4\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png}
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.jpeg}
 }
 \subfloat[MF$_3$ ($16.3\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png}
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.jpeg}
 } \\
 \subfloat[MF$_4$ ($22.0\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png}
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.jpeg}
 }
 \subfloat[MF$_5$ ($27.7\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png}
+\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.jpeg}
 }

### 2016-12-17 paper/algorithms_v4_cmame.tex

--- 2016-11-26 paper/algorithms_v3_cmame.tex
@@
 Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \Cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
-The error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
-This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some threshold is reached.
+After refinement, the error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
+This process can be repeated, successively increasing the proportion of the domain in which the high-fidelity model is used, until some error threshold is reached.
 \Cref{alg:refSeries} describes this approach.
-Note that the QoI error adjoint problem \Cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
+%Note that the QoI error adjoint problem \Cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %

### 2016-12-17 paper/mathematical_formulation_v3.tex

@@
 In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
-Let the variational form,
-%
-\begin{equation}
-\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
-\label{eq:supadjsys}
-\end{equation}
-%
-represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function.
-Then, the error in the Quantity of Interest $I$ is given by,
+Then, the error in the Quantity of Interest $I$ is given by
 %
@@
 
-Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have,
+Extending the property in \cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have
 %
@@
 %
-Define the corresponding adjoint problem,
+Let the variational form
 %
 \begin{equation}
-\mathscr{R}_{\Psi}'(\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:supadjsys}
+\end{equation}
+%
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
+%
+\begin{equation}
+\mathscr{R}_{\Psi}'(\Psi_{HF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
 \end{equation}
-for the supplementary adjoint $\Lambda$. The error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \cref{eq:supadjsys}.
+The error in the output $\mathcal{Q}$ defined in \cref{eq:supadjout} can then be expressed as a dual-weighted residual,
 \begin{equation}

### 2016-12-17 paper/submitted/round1_jpeg/intro_v4_cmame.tex

--- 2016-11-23 paper/intro_v3.tex
@@
 In contrast, concurrent methods (also called hybrid methods) simultaneously solve the higher- and lower-fidelity models in different parts of the domain.
-Applications include computational mechanics~\cite{Khareetal08,Prudetal08} and fluid dynamics~\cite{AlexGarTar02,FatGerQua01,Garcetal99,LucKinBer02,vanOpstaletal15,WadErw90}.
-% KW: I feel that we may be missing some important literature here, e.g., the work of Alexander, Tartakovsky
+Applications include computational mechanics~\cite{Khareetal08,Prudetal08}, porous media flow~\cite{tartakovsky2008hybrid,battiato2011hybrid}, and fluid dynamics~\cite{AlexGarTar02,FatGerQua01,Garcetal99,LucKinBer02,vanOpstaletal15,WadErw90}.
 We focus on concurrent methods of combining models, which have desirable features: in the case where the high-fidelity model is nonlinear, replacing it with a linear lower-fidelity model in most of the domain can reduce the number of iterative solves needed; when the high-fidelity model has a fine resolution and/or many parameters, replacing it with a lower-fidelity model can reduce the number of degrees of freedom of the mixed-fidelity model.
@@
 The inverse problem setting has also seen some work on goal-oriented methods.
-To begin with, it has been recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI.
+It has been recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI.
 For example, for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI~\cite{LiebWill13}.
@@
 For the linear Gaussian Bayesian inverse problem, one can calculate an optimal approximation to the predictive posterior of the QoI without fully calculating the posterior distribution of the parameters~\cite{Span16}.
-Mesh refinement in the goal-oriented inverse problem is addressed in~\cite{BecVex05}; in that work, Becker and Vexler derive an a posteriori estimate of the error in the QoI caused by discretizing the infinite-dimensional inverse problem, and this error estimate is used to adaptively refine the mesh.
-Also, an outline extending the approach to goal-oriented model adaptivity described in~\cite{OdenPrudetal06} to the inverse problem is presented in~\cite{OdenPrudetal10}.
+Mesh refinement in the goal-oriented inverse problem is addressed in~\cite{BecVex05}; that work derives an a posteriori estimate of the error in the QoI caused by discretizing the infinite-dimensional inverse problem, and uses this error estimate to adaptively refine the mesh.
+The idea of goal-oriented model adaptivity for an inverse problem is introduced in~\cite{OdenPrudetal10}, which outlines a possible extension of the adjoint-based adaptivity method of~\cite{OdenPrudetal06}.
 
@@
 This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
-%We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.
 
 The remainder of this paper is organized as follows, \Cref{sec:form} presents the mathematical formulation and error analysis for the multi-model inverse problem.
-\Cref{sec:alg} discusses the goal oriented inference algorithm and presents a computational complexity analysis.
+\Cref{sec:alg} discusses the goal-oriented inference algorithm and presents a computational complexity analysis.
 \Cref{sec:numexp} shows the application of this algorithm to a model problem and a contaminant flow problem.

### 2017-05-30 paper/submitted/reviews/reviewer_response.tex
stash reviewer comments; start reviewer response doc and minor edits

\documentclass[12pt, letterpaper]{article}
\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,amsfonts,amsbsy,latexsym}
\usepackage{color}
\usepackage{changepage}
\usepackage{parskip}
\usepackage[margin=0.75in]{geometry}

\newcommand{\answer}[1]{\begin{adjustwidth}{1cm}{}{\color{blue}#1}\end{adjustwidth}}
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\green}[1]{{\color{green}#1}}

\newcommand{\notdone}{{\color{red}{Changes not yet made.}}}
\newcommand{\done}{{\color{green}{Changes made.}}}

\begin{document}

\section*{Response to Referee Comments}

We thank the reviewers for their detailed and insightful comments and helping us strengthen the manuscript. Our point-by-point responses to the critique are outlined below, with reviewer comments in black and \blue{responses in blue}. Reviewers are ordered by the order in which their comments were received.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 4}

The paper is basically an application of [7] to modeling error demonstrated with rather transparent problems in 2D flow. The authors ignore the first papers on Goal-Oriented Estimation and modeling error laid out in the papers of Oden and Vemaganti in JCP in 2000, and extended by these authors in CMAME in 2001. The relationship between the current work and these papers should be clearly explained and cited. These revisions and re-review would be advised.

\answer{We apologize for not referencing the aforementioned papers; we had not encountered them in our literature review and did not intend to imply their irrelevance. Citations of these papers and explanation of their relevance to our work has been added in \red{Section x.x.x}}
\notdone

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 1}

On page 8 (before equation 10), the sentence “Note that, ..” references equation 11 before it is
presented. It may be better to move this comment to immediately follow the description of equation
11.

\answer{blah}
\notdone

I found the motivation in the beginning of the manuscript somewhat lacking. The description of use
cases, and conditions for which the algorithm is suitable, from the last paragraph on page 9 were very
helpful. I believe the presentation would be strengthened by mentioning some of this earlier in the
introduction.

\answer{}
\notdone

Although it is represented graphically in Figure 8, $\Omega_I$ for the final example is not defined in the text.

\answer{}
\notdone

At the beginning of the second paragraph of Section 4.3.2 (pg. 25) I think the reference to “Section
4.3.2” should be Table 1.

\answer{}
\notdone

The sub-figures of Figure 9 could be larger. It is difficult to verify the claim in the text that “. . . the
domain is refined completely in the x 3 direction first around the QoI region. . . ”. Even going as far as
to include 2-D slices (as in Figure 8) may be warranted.

\answer{}
\notdone

The second to last paragraph on page 28 starts “Section 4.3.2 shows the average QoI. . . ”. Again, I
believe this is a reference to a table, Table 2 in this case.

\answer{}
\notdone

I find the potential to apply this approach to surrogate design, as discussed in the final paragraph, very
interesting. I believe this is a good case for overcoming the cumulative cost of performing multiple
adaptive steps where the overall cost is comparable to evaluating the high-fidelity inverse problem.
If the final adaptive step was significantly cheaper to evaluate (say 2X as in the last example) the
cumulative cost of the adaptive algorithm would be amortized across a large number of posterior
samples with the final mixed-fidelity model.

\answer{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 2}

The main results in the paper are Proposition 1 and Eq. (14). These results are very close to existing results as presented in [7]. It is not clearly explained in the introduction, and in Section 2, in what sense the current results follow from [7] and in what sense they are new.

\answer{}
\notdone

The main theoretical section, Section 2, is vague, lacks proper structure and needs clarification. It is not clear how the high-fidelity and low-fidelity models are defined. These models should be the starting point of the section, not introduced in some proposition. Some degree of compatibility is assumed, but not explained. The proof of Proposition 1 refers to Proposition 3 in [7] which is worth stating in full in order to understand how it is employed. Given that (5) was stated as a Proposition 1, it is also natural to state the result in (14) as a proposition too.

\answer{}
\notdone

Specifics of the models are introduced in Section 4 (numerical experiments), which is out of place. It would benefit the reader to move the relevant parts to after Section 2, as examples of the abstract framework. It would also help if the propositions would then be re-interpreted in terms of the specific low/high fidelity model setting: In other words, the authors should explain what is actually computed to do the model adaptivity. This is currently very unclear. (It is also necessary to explain the contents of Algorithm 1.)

\answer{}
\notdone

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Reviewer 3}

I’d like to actually see the statement and proof of Proposition 3 from reference 7 included in
the manuscript. It is at the crux of the proof and it’s frustrating to have to go dig up that
detail.

\answer{}
\notdone

I’d like to see the details of the error estimate localization included in the manuscript instead
of delegating to a reference. The given description is quite “wordy” and not very precise.

\answer{}
\notdone

The spirit of the examples is fine, but I’m not following some of the details. They state for
the example in Section 4.1 that f (q) = q, but then the exact underlying field varies in space.

\answer{}
\notdone

To what space does f (q) belong? Based on the example in Section 4.2.1, it looks like it’s
a constant. If the parameters are spatially dependent, what underlying basis is being used
for its representation? Is the mesh refined enough to rule out pollution of the results due to
discretization error?

\answer{}
\notdone

It could be illustrative to see how the parameters q change with the refinement process.

\answer{}
\notdone

Figure 3 is not particularly illustrative, especially on linear scale. Perhaps some tuning of the
refinement parameters? What were the refinement parameters for the examples?

\answer{}
\notdone

\end{document}

### 2017-05-30 paper/submitted/round2_png/conclusions_v4_cmame.tex
stash reviewer comments; start reviewer response doc and minor edits

--- 2016-09-30 paper/conclusions_v2.tex
@@
-\section{Conclusion}\label{sect:conc}
+\section{Conclusion}\label{sec:conc}
 
-We have presented an error estimator that can be used to adaptively create a mixed-fidelity model with which to solve a goal-oriented inverse problem, so as to minimize the error in the QoI calculated from the inferred parameters.
-We applied this method to pairs of low- and high-fidelity models of convection-diffusion-reaction phenomena and were able to obtain QoI estimates with a small relative error without having to solve the inverse problem with the high-fidelity model.
-In these cases, the localization of the error estimate also indicated regions of the domain that were important to the interaction of the observations and the QoI.
-
-%------------------------------------------------------------%
-\section{Future Work} 
-%------------------------------------------------------------%
-
+We adaptively create mixed-fidelity models to solve goal-oriented inverse problems.
+The paper develops an error estimator that drives the adaptation, so as to minimize the error in the QoI calculated from the inferred parameters.
+We applied this method to pairs of low- and high-fidelity models of convection-diffusion-reaction phenomena.
+The results showed QoI estimates with a small relative error even when the high-fidelity model was used only in a small portion of the domain.
+In these cases, the localization of the error estimate also indicated regions of the domain that were important to the interactions between the observations and the QoI.
 A direction for extension of this work is to the case of the statistical inverse problem.
-Thus far in this work, we have considered the deterministic inverse problem, as described in \Cref{sec:setup}; we seek to infer the parameter values that optimally fit the observations and the prior beliefs embedded in the regularization.
-However, we can rarely, if ever, be certain that the inferred values are correct, whether this be due to epistemic uncertainty from a lack of knowledge or aleatoric uncertainty from inherent variability in the physical system, or both \cite{Ober04}.
-One may attempt to capture the uncertainty in the inferred parameters by representing them as random variables with a probability distribution; inferring the distribution of the parameters given some observations is the statistical inverse problem.
-
-The statistical inverse problem is often solved in a Bayesian framework.
-Bayes' rule is used to combine a prior distribution, which captures prior beliefs about the parameters, and a likelihood distribution, which captures the likelihood of observations given an instance of the parameter values and a model of noise in the observations, to give a posterior distribution on the parameters.
-Since there is generally no analytical expression for this posterior distribution, it is usually characterized by samples from the distribution.
-Sampling methods like the widely-used Markov chain Monte Carlo (MCMC) method require many evaluations of the forward model, and since the number of samples needed grows exponentially with the dimension of the parameter space, this problem becomes intractable for large parameter spaces.
-In engineering contexts, it is still usually the case, however, that we are ultimately interested in a low-dimensional QoI, and it is the uncertainty in this low-dimensional quantity that we wish to capture; this low-dimensional distribution is referred to as the predictive posterior.
-
 One way we could potentially apply this work to the statistical inverse problem is by reducing the parameter space that needs to be sampled.
 Such a direction is suggested by the results presented in \Cref{sec:diffvcdr3D}, where the mixed-fidelity model had significantly fewer degrees of freedom in its parameter field than the high-fidelity model, and thus a smaller parameter space.
-In the case of a linear model and observation operator with a Gaussian prior and additive Gaussian noise, there are parallels between the objective function of the deterministic inverse problem with Tikhonov regularization and the mode of the posterior distribution.
-In \cite{Martetal12}, a method is described for creating proposal distributions, drawing from these parallels; both the linear Gaussian and nonlinear cases are addressed.
-Similarly, these parallels could potentially be drawn upon to extend this work to the creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.
+One could explore creation of an alternative statistical inverse problem that, by utilizing a mixed-fidelity model with fewer degrees of freedom in its parameter field, requires exploration of a small parameter space with minimal compromise in the predictive posterior.
 
 Another potential approach would be to extend our method to the creation of mixed-fidelity models that are used as surrogates; these surrogate models can be evaluated in place of the high-fidelity model, thus decoupling the number of expensive forward evaluations of the high-fidelity model needed from the number of posterior parameter distribution samples that is desired \cite{Con14}.
-The samples obtained using such a surrogate might sacrifice accuracy in representing the posterior parameter distribution for accuracy in representing the predictive posterior distribution.
-
-%other directions for extensions that I can't seem to fit in:
-%mixing models in time as well? (different mixes of models at different time steps?)
-%superadj on intermediate mesh; preliminary results suggest that error estimates remain reasonable and generation of mixed-fidelity models can continue despite the additional approximations to the supplementary adjoint
-
-%\item \Cref{alg:refSeries} is also ammenable to an offline-online decomposition, analagous to that proposed in \cite{LiebWill13}.
-In the case where both the low-fidelity and high-fidelity inverse problems are linear in the data, and the QoI is linear in the state and parameters, one may first compute and store the supplementary adjoint $\Lambda_0$ for the low-fidelity model.
-As new data is received, one can compute the $\Psi_{LF}$ for this new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_0$ and the new $\Psi_{LF}$ gives an exact estimate of the error in the QoI, and thus effectively the high-fidelity QoI (NOT TRUE the primary and aux vars appear in the rhs...).
-When these linearities do not all hold, one cannot obtain an exact error estimate.
-The offline phase would consist of adaptively creating a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$, and storing its suppementary adjoint $\Lambda_{MF}^*$.
-As new data is received, one can compute the $\Psi_{MF}$ for the mixed-fidelity model and the new data; evaluating \cref{eq:finErrExp} with the stored $\Lambda_{MF}^*$ and the new $\Psi_{MF}$ gives an estimate of the error in the QoI, and thus an effective estimate of the high-fidelity QoI.

### 2017-05-30 paper/submitted/round2_png/intro_v4_cmame.tex
stash reviewer comments; start reviewer response doc and minor edits

--- 2016-12-17 paper/submitted/round1_jpeg/intro_v4_cmame.tex
@@
 Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining an acceptably low error tolerance for the QoI.
-In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}.
+In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,Park04,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}.
 These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement.
 
-The inverse problem setting has also seen some work on goal-oriented methods.
-It has been recognized that for the goal-oriented inverse problem, fully resolving the parameters is often unnecessary to accurately compute the QoI.
+For inverse problems, computational cost has been addressed by employing surrogate and reduced-order models \cite{MarzNajmRahn07, WangZab04, StefSanNav15, Frangosetal10}.
+For the particular case of a goal-oriented inverse problem, methods exploit the possibility of accurately computing the QoI without fully resolving the parameters.
 For example, for a discretized linear inverse problem, one can find a low-dimensional subspace of the parameter space that is both informed by observations and informative to the QoI~\cite{LiebWill13}.
@@
 This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
+%We note that while the approach outlined in~\cite{OdenPrudetal10} could be applied to the same task, one main difference is that we compute additional quantities to obtain a higher-order QoI error estimate.
 

### 2017-05-30 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
stash reviewer comments; start reviewer response doc and minor edits

--- 2016-12-12 paper/mathematical_formulation_v4_cmame.tex
@@
 \label{eq:preadj}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
 \end{multline}

### 2017-05-30 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
stash reviewer comments; start reviewer response doc and minor edits

--- 2016-12-15 paper/numerical_experiments_v4_cmame.tex
@@
 For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}.
+The regularization term in the objective function \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
 %
@@
 \begin{table}[htbp]
-\label{tab:ref3D_diffmesh}
 \centering
@@
 \caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.1\%$; relative errors are given with respect to the high-fidelity QoI estimate.}
+\label{tab:ref3D_diffmesh}
 \end{table}
@@
 \begin{table}
-\label{tab:ref3D_newdata_QoI_diffmesh}
 \centering
@@
 \caption{Average QoI values and errors from solving inverse problem with mixed- and high-fidelity models and noisy data; relative errors are with respect to true high-fidelity QoI.}
+\label{tab:ref3D_newdata_QoI_diffmesh}
 \end{table}
@@
 \begin{table}
-\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets.}
-\label{tab:ref3D_newdata_times_diffmesh}
 \centering
@@
 \end{tabular}
+\caption{Average times to solve inverse problem and obtain error estimate with mixed- and high-fidelity models and noisy datasets.}
+\label{tab:ref3D_newdata_times_diffmesh}
 \end{table}

### 2017-06-05 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
modified some figures, maybe now closer to what reviewer wanted?

@@
 \centering
+\subfloat[Slice location]{
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/slice_diagram.png}
+}
+\hfill
 \subfloat[MF$_1$ ($5.2\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png}
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff_and_midslice.png}
 }
+\\
 \subfloat[MF$_2$ ($11.4\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png}
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff_and_midslice.png}
 } 
+\hfill
 \subfloat[MF$_3$ ($16.3\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png}
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff_and_midslice.png}
 } \\
 \subfloat[MF$_4$ ($22.0\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png}
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff_and_midslice.png}
 } 
+\hfill
 \subfloat[MF$_5$ ($27.7\%$ HF)]{
-\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png}
+\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff_and_midslice.png}
 }
+
 \caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}

### 2017-06-05 paper/submitted/reviews/reviewer_response.tex
more paper changes

@@
 
-\answer{}
-\notdone
+\answer{We added a sentence about the use cases to the second paragraph of the introduction.}
 
@@
 
-\answer{}
-\notdone
+\answer{It is now defined just before Figure 8 is referenced.}
 
@@
 
-\answer{}
-\notdone
+\answer{Thanks for the catch. We've corrected the reference.}
 
 The sub-figures of Figure 9 could be larger. It is difficult to verify the claim in the text that “. . . the
-domain is refined completely in the x 3 direction first around the QoI region. . . ”. Even going as far as
+domain is refined completely in the $x_3$ direction first around the QoI region. . . ”. Even going as far as
 to include 2-D slices (as in Figure 8) may be warranted.
 
-\answer{}
-\notdone
+\answer{We made the figure larger, made the wording of that claim more specific, and included a 2D slice for each mixed-fidelity model that cuts through the QoI region, to aid in visual verification.}
 
@@
 
-\answer{}
-\notdone
+\answer{Thanks for the catch. We've corrected the reference.}
 
@@
 the example in Section 4.1 that f (q) = q, but then the exact underlying field varies in space.
-
-\answer{}
-\notdone
-
 To what space does f (q) belong? Based on the example in Section 4.2.1, it looks like it’s
@@
 
-\answer{}
+\answer{Modified figures to be on log scale and include line for target QoI error, and removed 100\% refinement point, since we don't keep refining after target is reached...not sure what is meant by 'refinement parameters'...Figure 3 was only meant to show that error decreased with refinement and that only two iterations were necessary...the amount to refine in each iteration is arbitrarily/chosen-by-used...}
 \notdone

### 2017-06-05 paper/submitted/round2_png/algorithms_v4_cmame.tex
more paper changes

--- 2016-12-17 paper/algorithms_v4_cmame.tex
@@
 Basis functions whose support lie completely in the high-fidelity region will have a zero contribution and the elements in their support are never flagged for refinement again.
+
+%%%% FIX BELOW ONCE YOU HAVE NOTATION DOWN FOR SECTION 2
+
+We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
+For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$.
+Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as,
+%
+\begin{equation}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
+\end{equation}
+%
+We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$.
+Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \chi_i)$.
+The error estimate,
+%
+\begin{equation}
+\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
+\end{equation}
+%
+where,
+%
+\begin{equation}\label{eq:basisblame}
+\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
+\end{equation}
+%
+can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
+Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution.
+The basis functions with the largest error contributions are flagged, and the elements in their support are refined.

### 2017-06-05 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
more paper changes

@@
 
-For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements.
+For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with linear Lagrange elements.
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
 %\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
-The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable.
+The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable; all variables are represented by the same basis.
 The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
+%\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
+\includegraphics[width=0.8\textwidth]{baseSeries/err_est_v2.pdf}
+%\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.
+In this case, only two refinement iterations are necessary to achieve the target relative QoI error (dotted line).}
 \label{fig:baseErr}
@@
 
-\Cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
-The error decompositions for each case are also shown in \Cref{fig:qoiStudy}.
+\Cref{subfig:obsSetup} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
+The error decompositions for each case are shown in \Cref{subfig:obsLF,subfig:obsMF1,subfig:obsMFlast}.
 The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
@@
   \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
+  \label{subfig:obsMF1}
 }
@@
 \Cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
-The error decomposition for the three cases is shown in \Cref{fig:dataStudy}.
+The error decomposition for the three cases is shown in \Cref{subfig:obsLF2,subfig:obsMF1_2,subfig:obsMFlast2}.
 The bottom row is the same as that in \Cref{fig:qoiStudy}.
@@
   \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
+  \label{subfig:obsMF1_2}
 }
@@
 \end{equation}
-differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field.
-The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used.
+differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field; $f(q)$ is a constant function equal to $q$ everywhere in the domain.
+The intermediate mixed-fidelity models thus have parameter fields (and forcing functions) that are constant over the subregions of the domain where the low-fidelity model is used; disconnected low-fidelity regions still share the same parameter value.
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \Cref{sec:cdvcdr}.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field.
+The forcing field (and its auxiliary and supplementary adjoint conterparts) are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions.
 As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
-\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
+%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
+\includegraphics[width=0.8\textwidth]{svf/err_est_v2.pdf}
+\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.
+The dotted line indicates the target relative QoI error.}
 \label{fig:svfErr}
@@
 Synthetic observations at 18 points in the domain are generated by running the high-fidelity model on a finer mesh.
-The locations of the observations as well as the QoI region $\Omega_I$ are shown in \Cref{fig:setup3D}.
+The locations of the observations as well as the QoI region $\Omega_I=[1100\textrm{m},1200\textrm{m}]\times[775\textrm{m},875\textrm{m}]\times[80\textrm{m},100\textrm{m}]$ are shown in \Cref{fig:setup3D}.
 We set the regularization term in \Cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
@@
 Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement.
-We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
+We also see that the domain is refined completely in the $x_3$ direction first in an area slightly upstream of the QoI region (see \Cref{subfig:3DMF2}), reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
 %
@@
 \centering
-\subfloat[Slice location]{
+\subfloat[Slice location and color key]{
 \includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/slice_diagram.png}
+\label{subfig:3Dsliceloc}
 }
@@
 \includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff_and_midslice.png}
+\label{subfig:3DMF1}
 }
@@
 \includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff_and_midslice.png}
+\label{subfig:3DMF2}
 } 
@@
 \includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff_and_midslice.png}
+\label{subfig:3Dfinref}
 }
 
-\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
+\caption{Domain division for mixed-fidelity models (\protect\subref{subfig:3DMF1}--\protect\subref{subfig:3Dfinref}): 3D view with 2D slice through domain below (see \protect\subref{subfig:3Dsliceloc} for slice location and orientation).
+Low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors in 3D view due to transparency indicate a mix of the two models along the line of sight).
+Slices cut through QoI region, indicated by purple box.
+$x_3$ direction scaled for clarity.}
 \label{fig:divvy3D_diffmesh}

### 2017-06-05 practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r42_basis_blame_all_fine/plot_err.m

@@ -17,8 +17,20 @@ qoiHF = 0.0036276258;
 relErrTrue = abs(errTrue/qoiHF);
 ref = [0; 0.1168; 0.206; 0.3032; 0.4049; 0.5006; 0.6023];
 
+% figure('Position',[470 580 765 205])
+% plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',1.5);
+% legend('True','Estimated')
+% title('True and Estimated Absolute Relative Error in QoI','FontWeight','normal')
+% ylabel({'Absolute Relative', '\quad Error in QoI'})
+% xlabel('$\%$ HF')
+% set(gca,'FontSize',fntsize); 
+
 figure('Position',[470 580 765 205])
-plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',1.5);
+semilogy(100*ref, relErrTrue, 'x','LineWidth',1.5,'Color',[.19,.5,.13]);
+xlim([0 100])
+hold on
+semilogy(100*ref, relErrEst, 'o','LineWidth',1.5,'Color',[255, 127, 80]/255);
+plot([0 100],[0.01 0.01],':','LineWidth',1.5,'Color',[0.5 0 0.5]); %level below which we stop refining
 legend('True','Estimated')
 title('True and Estimated Absolute Relative Error in QoI','FontWeight','normal')
 ylabel({'Absolute Relative', '\quad Error in QoI'})

### 2017-06-05 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/qoi3_sens3_alt_err_all/plot_err.m

@@ -17,8 +17,20 @@ qoiHF = 0.0033906304;
 relErrTrue = abs(errTrue/qoiHF);
 ref = [0; 0.0578; 0.105];
 
+% figure('Position',[470 580 765 205])
+% plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',1.5);
+% legend('True','Estimated')
+% title('True and Estimated Absolute Relative Error in QoI','FontWeight','normal')
+% ylabel({'Absolute Relative', '\quad Error in QoI'})
+% xlabel('$\%$ HF')
+% set(gca,'FontSize',fntsize); 
+
 figure('Position',[470 580 765 205])
-plot(100*[ref; 1], [relErrTrue; 0], '-*', 100*[ref; 1], [relErrEst; 0], '-*','LineWidth',1.5);
+semilogy(100*ref, relErrTrue, 'x','LineWidth',1.5,'Color',[.19,.5,.13]);
+xlim([0 100])
+hold on
+semilogy(100*ref, relErrEst, 'o','LineWidth',1.5,'Color',[255, 127, 80]/255);
+plot([0 100],[0.01 0.01],':','LineWidth',1.5,'Color',[0.5 0 0.5]); %level below which we stop refining
 legend('True','Estimated')
 title('True and Estimated Absolute Relative Error in QoI','FontWeight','normal')
 ylabel({'Absolute Relative', '\quad Error in QoI'})

### 2017-06-06 paper/submitted/round2_png/algorithms_v4_cmame.tex
more edits...

--- 2016-12-17 paper/algorithms_v4_cmame.tex
@@
 %------------------------------------------------------------------------------------------------------------------------%
+
 \Cref{alg:refSeries} does not require a specific method for localizing the error estimate.
@@
 We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements.
-For ease of implementation, we can choose these basis functions to be the same as those spanning the space in which we solve for the primary, auxiliary, and supplementary adjoint variables.
+Recall the error estimate
+%
+\begin{equation}
+\epsilon=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF})(\Lambda)+\mathcal M_{HF}(\Psi_{MF})-\mathcal M_{MF}(\Psi_{MF})
+\end{equation}
+%
+from \Cref{alg:refSeries}.
+Let $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ be the finite-dimensional conforming subspace in which we solve for the approximations $\Lambda^h$ and $\Psi_{MF}^h$; we seek to decompose the error estimate
+%
+\begin{equation}
+\epsilon^h=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF}^h)(\Lambda^h)+\mathcal M_{HF}(\Psi_{MF}^h)-\mathcal M_{MF}(\Psi_{MF}^h).
+\end{equation}
+%
+Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that $\textrm{span}(\Phi^h)=(Q^h\times U^h\times U^h)^3$, so that we can write $(\Lambda^h,\Psi_{MF}^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \psi_i)$.
+Then the error estimate satisfies
+%
+\begin{equation}
+\epsilon^h \leq \sum_{i\in I} \varepsilon^h_i,
+\end{equation}
+%
+where,
+%
+\begin{equation}\label{eq:basisblame}
+\varepsilon^h_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF})(\lambda_i\varphi_i)+\mathcal M_{HF}(\upvarphi_i \psi_i)-\mathcal M_{MF}(\upvarphi_i \psi_i) \right|
+\end{equation}
+%
+can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$.
 Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution.

### 2017-06-06 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
more edits...

@@
 
-For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with linear Lagrange elements.
+For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with first-order Lagrange elements.
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
@@
 \begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in H^1(\Omega),
 \end{equation}
@@
 \begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U_{LF}
 \end{equation}
-differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field; $f(q)$ is a constant function equal to $q$ everywhere in the domain.
+differs from the high-fidelity model only in that $U_{LF}$ is limited to the space of constant functions over $\Omega$; we maintain $f(q)=q$.
 The intermediate mixed-fidelity models thus have parameter fields (and forcing functions) that are constant over the subregions of the domain where the low-fidelity model is used; disconnected low-fidelity regions still share the same parameter value.
+The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field.
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field.
-The forcing field (and its auxiliary and supplementary adjoint conterparts) are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions.
+Also for ease of implementation and for localizing the error, the forcing field and its auxiliary and supplementary adjoint conterparts are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions using a penalty term.
+Although the chosen pair of models has the potential to give mixed-fidelity models with fewer degreees of freedom in the parameter, this is not the case in our implementation; however, we are not looking to demonstrate computational savings with this example, but rather to explore the behavior of \Cref{alg:refSeries} when applied to such a pair of models.
 As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
@@
 
+\Cref{fig:svfRefParams} shows the inferred parameters using some of the mixed-fidelity models and the high-fidelity model.
+%
+\begin{figure}[htbp]
+\centering
+\subfloat[MF$_1$ ($10\%$ HF)]{
+	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
+	\label{subfig:svfparamMF1}
+} \\
+\subfloat[MF$_3$ ($30\%$ HF)]{
+	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
+	\label{subfig:svfparamMF3}
+} \\
+\subfloat[MF$_6$ ($60\%$ HF)]{
+  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
+  \label{subfig:svfparamMF6}
+} \\
+\subfloat[HF]{
+	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
+	\label{subfig:svfparamHF}
+}
+\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models.
+All figures share the color-scale for the high-fidelity plot.}
+\label{fig:svfRefParams}
+\end{figure}
+%
 The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
@@
 In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
-The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain.
+The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare \Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}).
 We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
+Note that although the inferred parameters in the first and third mixed-fidelity models (see \Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
+These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.
+
+%compare MF01 and MF03, MF06 and HF
+%1 and 3 look very different but have very similar true errors - different params can give similar qoi, though in this case the qoi is not close to HF; more HF doesn't necessarily decrease error, interplay between having freedom to match data and all LF regions being flat...
+%6 and HF look very similar; most of HF is very flat
 
@@
 %
-and use the solution as an initial guess for the high-fidelity problem; equivalently, we use two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
+with $k_r=0$, and use the solution as an initial guess for the high-fidelity problem; this is equivalent to using two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
 %

### 2017-06-07 paper/submitted/round2_png/reviewer_response.tex
update reviewer responses

--- 2017-06-05 paper/submitted/reviews/reviewer_response.tex
@@
 \begin{document}
+
+%%%%% ASK KAREN/ELIZABETH
+%do we need to refer to line numbers?
+%if a comment asks for clarification, do we reproduce it here or point to the changed lines/sections?
 
@@
 
-\answer{blah}
+\answer{let vikram do his thing first}
 \notdone
@@
 
-\answer{It is now defined just before Figure 8 is referenced.}
+\answer{It is now defined just before Figure 8 (now Figure 9) is referenced.}
 
@@
 
-\answer{We made the figure larger, made the wording of that claim more specific, and included a 2D slice for each mixed-fidelity model that cuts through the QoI region, to aid in visual verification.}
+\answer{We made the figure (now Figure 10) larger, made the wording of that claim more specific, and included a 2D slice for each mixed-fidelity model that cuts through the QoI region, to aid in visual verification.}
 
@@
 
-\answer{}
+\answer{???}
 
@@
 
-I’d like to actually see the statement and proof of Proposition 3 from reference 7 included in
-the manuscript. It is at the crux of the proof and it’s frustrating to have to go dig up that
+I'd like to actually see the statement and proof of Proposition 3 from reference 7 included in
+the manuscript. It is at the crux of the proof and it's frustrating to have to go dig up that
 detail.
@@
 
-I’d like to see the details of the error estimate localization included in the manuscript instead
+I'd like to see the details of the error estimate localization included in the manuscript instead
 of delegating to a reference. The given description is quite “wordy” and not very precise.
 
-\answer{}
-\notdone
+\answer{We've added the relevant parts of the reference to Section 3.2.}
 
-The spirit of the examples is fine, but I’m not following some of the details. They state for
-the example in Section 4.1 that f (q) = q, but then the exact underlying field varies in space.
-To what space does f (q) belong? Based on the example in Section 4.2.1, it looks like it’s
+The spirit of the examples is fine, but I'm not following some of the details. They state for
+the example in Section 4.1 that $f (q) = q$, but then the exact underlying field varies in space.
+To what space does $f (q)$ belong? Based on the example in Section 4.2.1, it looks like it's
 a constant. If the parameters are spatially dependent, what underlying basis is being used
@@
 
-\answer{}
+\answer{We reworded the description of the parameters in Section 4.2.1 to be more clear/explicit about the relevant spaces and representations.
+\red{Not sure what to make of discretization error comment...}}
 \notdone
@@
 
-\answer{}
-\notdone
+\answer{We added an additional figure (now Figure 7) showing the parameters $q$ for some of the refinement iterations, along with commentary.}
 

### 2017-06-07 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
Added distinction between in low and high fidelity models clearly, with separate statements for the two.

@@
 %
-We first introduce the goal-oriented inverse problem.
-Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.
+\edit{In this section, we clearly define the low, mixed and high fidelity inverse problems.
+We also develop theoretical results which extend the work of~\cite{} to multimodel settings, in particular obtaining a computable, rigorous error estimate for QoI targeted generation of mixed fidelity formulations of inverse problems.}
 
@@
 %
-Consider a model for which the Galerkin formulation of the weak form is written as
+We begin by defining a generic goal-oriented inverse problem.
+Given observations (data) $d\in\R^{n_d}$, we seek to infer parameter(s) $q\in Q$, where $Q$ is a Hilbert space.
+An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, where $u$ satisfies,
 \begin{equation}
@@
 \end{equation}
-where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
-The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
-Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
-The actual observations (data) are denoted by $d\in\R^{n_d}$.
+where $U$ is also a Hilbert space.
+Equation \Cref{eq:weakForm} is called the state equation.
+The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
+Finally, our objective functional or the QoI, is a scalar functional $I(q,u)$, where $I:Q\times U\to\R$.
 
 The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
-In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
@@
 Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.
-The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems.
-A given physical system can be described to varying degrees of fidelity using different models.
-This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.
 
-We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
-We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
+In an inverse problem, multiple choices are apparent for the structure of the inferred parameter $q$, the data $d$ and state equation.
+Together these constitute a model for formulating the inverse problem.
+For example, the parameter $q$ can be modeled as a single scalar value or an infinite dimensional field variable, the data $d$ can be the entire time series of measurements from a sensor, or simply a smaller subset of those measurements.
+The state equation can be complex, nonlinear relationship requiring an expensive computation to resolve (for e.g./ the Navier Stokes equations) or a linear, single physics diffusion model (for e.g./ Laplace's equation).
+All these different modeling choices lead to different versions of the optimization problem that would need to be solved to infer the unknown parameter.
+
+We assume that there exists an ideal model for solving the inverse problem, called the high fidelity model.
+Giving infinite computational resources, we would use this high fidelity to formulate and solve our inverse problem.
+Mathematically we differentiate this high fidelity inverse problem with the subscript $HF$,
+%
+\begin{subequations}
+\label{eq:invOpt}
+\begin{align}
+\min\limits_{q,u} & \quad J(q_{HF},u_{HF})=\frac{1}{2}\|d-C(u_{HF})\|_2^2 + R(q_{HF}), \label{eq:invOpt_obj} \\
+\textrm{s.t. }& \quad a(u_{HF},q_{HF})(\phi)=\ell(q_{HF})(\phi),\quad\forall\phi\in U_{HF}. \label{eq:invOpt_cons}
+\end{align}
+\end{subequations}
+%
+where $q \in Q_{HF}$.
+Due to the constraints presented by limited computational resources, one may instead attempt to infer the parameter $q$ using a different, less computationally demanding model, which we call the low fidelity model,
+%
+\begin{subequations}
+\label{eq:invOpt}
+\begin{align}
+\min\limits_{q,u} & \quad J(q_{LF},u_{LF})=\frac{1}{2}\|d-C(u_{LF})\|_2^2 + R(q_{LF}), \label{eq:invOpt_obj} \\
+\textrm{s.t. }& \quad a(u_{LF},q_{LF})(\phi)=\ell(q_{LF})(\phi),\quad\forall\phi\in U_{LF}. \label{eq:invOpt_cons}
+\end{align}
+\end{subequations}
+%
+where $q \in Q_{LF}$.
+If there is compatibility between the low fidelity and high fidelity solution spaces for $q$ and $u$, one may combine the two models to solve the inverse problem.
+The low fidelity model can be used in part of the computational domain, and the high fidelity in the remainder, and such a model is called a mixed fidelity model, which we distinguish by the subscript $MF$.
+
+We further consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI.
 We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.

### 2017-06-11 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
Minor edits, more to come

@@
 
-We further consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
-We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI.
+In a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$.
+The QoI evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values.
 We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.

### 2017-06-12 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
Finished reworking section 2.1 text, and statement of Proposition 1.

--- 2017-05-30 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
@@
 %
-We first introduce the goal-oriented inverse problem.
-Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.
+In this section, we introduce the high, low and mixed fidelity inverse problems.
+We also develop theoretical results which extend the work in~\cite{BecVex05} to multimodel settings, in particular obtaining a computable error estimate for QoI targeted generation of mixed fidelity formulations of inverse problems.
 
@@
 %
-Consider a model for which the Galerkin formulation of the weak form is written as
+In a typical inverse problem, we are given observations (data) $d\in\R^{n_d}$ and seek to infer parameter(s) $q\in Q$, where $Q$ is some function space.
+In this exposition, we assume that $Q$ is a Hilbert space.
+An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, with $u$ satisfying,
+%
 \begin{equation}
@@
 \end{equation}
-where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
-The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
-Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
-The actual observations (data) are denoted by $d\in\R^{n_d}$.
+%
+where $U$ is also a Hilbert space.
+Equation~\ref{eq:weakForm} is called the state equation.
+The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
 
-The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
-In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations in a chosen norm, leading to an inverse problem.
+Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
@@
 Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.
-The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems.
-A given physical system can be described to varying degrees of fidelity using different models.
-This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.
 
-We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
-We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.
-In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
-We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
+In an inverse problem, we can have multiple choices to define the structure of the inferred parameter $q$, and the state equation/variables.
+For example, the parameter $q$ can be modeled as a single scalar value or an infinite dimensional field variable.
+The state equation can be nonlinear and multiscale, requiring an expensive computation to resolve (for e.g.\ the Navier Stokes equations) or a linear, single physics diffusion model (for e.g.\ Laplace's equation).
+All these different modeling choices lead to different versions of the optimization problem~\ref{eq:invOpt} that would need to be solved to infer the unknown parameter.
+
+We assume that there exists an `ideal model' for solving the inverse problem, called the high fidelity model.
+Given adequate computational resources, we would use this high fidelity to formulate and solve our inverse problem.
+We label this high fidelity inverse problem with the subscript $HF$,
+%
+\begin{subequations}
+\label{eq:invOptHF}
+\begin{align}
+\min\limits_{q_{HF},u_{LF}} & \quad J(q_{HF},u_{HF})=\frac{1}{2}\|d-C(u_{HF})\|_2^2 + R(q_{HF}), \label{eq:invOpt_objHF} \\
+\textrm{s.t. }& \quad a_{HF}(u_{HF},q_{HF})(\phi)=\ell_{HF}(q_{HF})(\phi),\quad\forall\phi\in U_{HF}. \label{eq:invOpt_consHF}
+\end{align}
+\end{subequations}
+%
+where $q \in Q_{HF}$.
+On the other hand, due to the constraints presented by limited computational resources, one may instead attempt to infer the parameter $q$ using a less computationally demanding model, which we call the low fidelity model,
+%
+\begin{subequations}
+\label{eq:invOptLF}
+\begin{align}
+\min\limits_{q_{LF},u_{LF}} & \quad J(q_{LF},u_{LF})=\frac{1}{2}\|d-C(u_{LF})\|_2^2 + R(q_{LF}), \label{eq:invOpt_objLF} \\
+\textrm{s.t. }& \quad a_{LF}(u_{LF},q_{LF})(\phi)=\ell_{LF}(q_{LF})(\phi),\quad\forall\phi\in U_{LF}. \label{eq:invOpt_consLF}
+\end{align}
+\end{subequations}
+%
+If there is compatibility between the low fidelity and high fidelity solution spaces for the parameter and state variables, one may combine the two models to solve the inverse problem.
+The low fidelity model can be used in part of the computational domain, and the high fidelity in the remainder, and such a model is called a mixed fidelity model, which we distinguish by the subscript $MF$.
+
+In a {\em goal-oriented inverse problem}, the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$.
+The QoIs evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values.
+We consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use, seeking computable estimates for the error incurred in approximating the high fidelity QoI with low or mixed fidelity models.
+Such an estimate allows us to adaptively chose regions where the high fidelity model is to be used, starting from an initial low or mixed fidelity model.
+
+We build on the work in~\cite{BecVex05, becker2004posteriori} which utilize the special structure of the coupled system of PDEs induced by deriving optimality conditions for~\Cref{eq:invOpt_cons}, and derives error estimates for the discretization error in a single model setting.
+Details of why such an approach is effective for the nature of systems and QoIs we encounter in inverse problems can be found in~\cite{becker2004posteriori} (see Section 3.1 in particular).
+Here we extend the work in~\cite{BecVex05} to include the situation where the model structure differs, and it is the modeling error that needs to be estimated.
+
+As in~\cite{BecVex05}, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
+We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models.
+However, unlike~\cite{BecVex05}, this estimate cannot be estimated by patch recovery or projection techniques.
+This is because the low and high fidelity solutions do not differ merely in mesh resolution, but in the very structure of their underlying models.
+Therefore, to compute this error estimate we have to introduce further supplementary adjoint variables, that are able to bring in additional information from the high fidelity model into the estimate.
+
 %
@@
 %
-For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
-In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
+For a given hierarchy of models, taking the QoI calculated from inferring the parameters with the highest-fidelity model as the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
 %
@@
 Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}.
-Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
-Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
-Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
+Let the forms $a_{HF/LF}:U_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u_{HF/LF}$ and parameters $q_{HF/LF}$.
+Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u_{HF/LF}$.
+Also, let the regularization operator $R:Q_{HF/LF}\to\Reals$ be differentiable with respect to the parameter $q_{HF/LF}$, and the functional $I:Q_{HF/LF}\times U_{HF/LF}\to\Reals$ be differentiable with respect to the state $u_{HF/LF}$ and parameter $q_{HF/LF}$.
 
@@
 \label{eq:InvsOpt_lag}
-\mathcal{L}(q,u,z)= J(q,u)-(a(u,q)(z)-\ell(q)(z)),
+\mathcal{L}(q_{HF},u_{HF},z_{HF})= J(q_{HF},u_{HF})-(a(u_{HF},q_{HF})(z_{HF})-\ell(q_{HF})(z_{HF})),
 \end{equation}
 %
-where $z\in U$ is the adjoint.
-Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$.
+where $z\in U_{HF}$ is the adjoint.
+Denoting the primary variables as $\xi_{HF}=(q_{HF},u_{HF},z_{HF})$, introduce corresponding auxiliary variables $\chi_{HF} = (p_{HF},v_{HF},y_{HF})\in Q_{HF}\times U_{HF}\times U_{HF}$.
 Let the augmented Lagrangian be defined as
@@
 \label{eq:InvsOpt_auglag}
-\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}_{quz}'(q,u,z)(p,v,y),
+\mathcal{M}_{HF}((q_{HF},u_{HF},z_{HF}),(p_{HF},v_{HF},y_{HF})) = I(q_{HF},u_{HF}) + \mathcal{L}_{HF}'(q_{HF},u_{HF},z_{HF})(p_{HF},v_{HF},y_{HF}),
 \end{equation}
 %
-where $\mathcal{L}_{quz}'(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$.
-Let $\Psi = (\xi_\Psi,\chi_\Psi)$ denote the stationary point of $\mathcal{M}$.
+where $\mathcal{L}_{HF}'(q_{HF},u_{HF},z_{HF})(p_{HF},v_{HF},y_{HF})$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q_{HF},u_{HF},z_{HF})$, in the direction of the auxiliary variables $(p_{HF},v_{HF},y_{HF})$.
+Let $\Psi_{HF} = (\xi_{HF},\chi_{HF})$ denote the stationary point of $\mathcal{M}_{HF}$.
 
-Consider two models with which parameters can be inferred: a high-fidelity model and a lower-fidelity model.
-Let the high-fidelity (HF) and low-fidelity (LF) models, and their corresponding variables, Lagrangians, and augmented Lagrangians, be distinguished by the subscripts $_{HF}$ and $_{LF}$, respectively.
-In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
+Let $\Psi_{LF}$ denote the stationary point of the low-fidelity augmented Lagrangian $\mathcal{M}_{LF}$ induced by~\Cref{eq:invOptLF}, respectively.
 Then, the error in the Quantity of Interest $I$ is given by

### 2017-06-15 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
Expanded proposition 1. amd turned Eq. 14 back into a proposition

@@
 \label{eq:semifinErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
 \end{multline}
@@
 %
-Applying the output error representation described in Proposition 3 from~\cite{BecVex05} for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
+Following~\cite{BecVex05}, we rewrite the term $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ using the Fundamental Theorem of Calculus,
+%
+\begin{equation}
+\label{eq:Mantiderivative}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \int\limits_{0}^{1} \mathcal{M}'_{HF}\left(\Psi_{HF} + se\right)\left(e\right) \, ds
+\end{equation}
+%
+Now using the trapezoidal rule for the integral in~\Cref{eq:Mantiderivative}, we further have,
+%
+\begin{equation}
+\label{eq:Mprimetrapezoid}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{HF})(e) + \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(e) + \mathcal{R}\textrm{.}
+\end{equation}
+%
+where the remainder $R$ is given as,
+%
+\begin{equation}
+\label{eq:trapezoidremainder}
+R = \frac{1}{2} \int\limits_{0}^{1} \mathcal{M}'''_{HF}\left(\Psi_{LF} + se\right)(e,e,e) \, s(s-1) \, ds
+\end{equation}
+%
+which is finite due to the third order differentiability assumptions in the Proposition.
+We further note that $\mathcal{M}'_{HF}(\Psi_{HF})(e)$ vanishes since $\Psi_{HF}$ is a stationary point of $\mathcal{M}_{HF}$, and~\Cref{eq:Mprimetrapezoid} can be simplified to,
+%
 \begin{equation}
 \label{eq:beckvex}
-\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}\textrm{.}
 \end{equation}
-Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain
+%
+Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain,
+%
 \begin{multline}
 \label{eq:preadj}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
 \end{multline}
@@
 
-The above proposition splits the error in the QoI into three components, a third order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
-Although the linear term is not computable, it can be estimated using an appropriate dual problem.
-We describe one method of estimating this term below.
+The above proposition splits the error in the QoI into three components, a third order remainder term $\mathcal{R}$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
+Although the linear term is not computable, it can be estimated.
+We describe one method of estimating this term below, using an appropriate dual problem.
 
-Note that, as a stationary point, $\Psi_{HF}$ satisfies~\Cref{eq:supadjsys}. Now, let $\mathcal{Q}$ be an output defined by
+%
+\begin{proposition}
+\label{thm:error_estimate_dual}
+Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let $Lambda$ be the solution of the dual problem,
 %
 \begin{equation}
-\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi).
+\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\end{equation}
+%
+where $\mathcal{Q}:(U \times U \times Q)^2 \to \R$ is a linear functional defined by,
+%
+\begin{equation}
+\mathcal{Q}(\Phi)=\mathcal{M}'_{HF}(\Psi_{LF})(\Phi).
 \label{eq:supadjout}
@@
 %
-Let the variational form
+Then we have,
+%
+\begin{multline}
+\label{eq:finErrExp}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}) + R_{\mathscr{R}} + R
+\end{multline}
+%
+where $R_{\mathscr{R}}$ is a second order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $R$ is as defined in Proposition~\ref{thm:error_estimate}.
+%
+\end{proposition}
+%
+\begin{proof}
+%
+The proof simply follows from the classic dual based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies~\Cref{eq:supadjsys}. Let the variational form
 %
 \begin{equation}
-\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:supadjsys}
@@
 %
-represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
+represent the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
 %
 \begin{equation}
-\mathscr{R}_{\Psi}'(\Psi_{HF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}'(\Psi_{LF};\Phi,\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
 \end{equation}
-for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys}.
-The error in the output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+%
+for the supplementary adjoint $\Lambda$. The error in the linear output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+%
 \begin{equation}
 \label{eq:adjOutErr}
-\mathcal M'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})=-\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda).
+\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF},\Lambda) + R_{\mathscr{R}}
 \end{equation}
 %
-Combining \Cref{eq:preadj} and \Cref{eq:adjOutErr}, we have,
-\begin{multline}
-\label{eq:finErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
-\end{multline}
+where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$. This implies the required result.
+%
+\end{proof}
 %

### 2017-06-18 paper/submitted/round2_png/algorithms_v4_cmame.tex
stashing changes in integrating Vikram's theoretical changes

@@
 
-Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate \Cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
+Just as error estimates can be used to guide mesh refinement~\cite{BecRann01,VendDarm00,PrudOden99,BecVex05,AinsOden11}, the error estimate obtained after dropping the remainder terms $\mathcal{R}$ and $\mathcal{R}_\mathscr{R}$ in \Cref{eq:finErrExp} can be localized to give elemental contributions and used to guide physics-based refinement over the domain to create a mixed-fidelity model.
 After refinement, the error estimate can be calculated again, using the mixed-fidelity model as the lower-fidelity model.
@@
 
-	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
+	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
 	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
@@
 
-		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
+		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
 		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
@@
 The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
-We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
+We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
 
@@
 \begin{equation}
-\epsilon=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF})(\Lambda)+\mathcal M_{HF}(\Psi_{MF})-\mathcal M_{MF}(\Psi_{MF})
+\epsilon=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF})(\Lambda)+\mathcal M_{HF}(\Psi_{MF})-\mathcal M_{MF}(\Psi_{MF})
 \end{equation}
@@
 \begin{equation}
-\epsilon^h=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF}^h)(\Lambda^h)+\mathcal M_{HF}(\Psi_{MF}^h)-\mathcal M_{MF}(\Psi_{MF}^h).
+\epsilon^h=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF}^h)(\Lambda^h)+\mathcal M_{HF}(\Psi_{MF}^h)-\mathcal M_{MF}(\Psi_{MF}^h).
 \end{equation}
@@
 \begin{equation}\label{eq:basisblame}
-\varepsilon^h_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF})(\lambda_i\varphi_i)+\mathcal M_{HF}(\upvarphi_i \psi_i)-\mathcal M_{MF}(\upvarphi_i \psi_i) \right|
+\varepsilon^h_i = \left| -\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF})(\lambda_i\varphi_i)+\mathcal M_{HF}(\upvarphi_i \psi_i)-\mathcal M_{MF}(\upvarphi_i \psi_i) \right|
 \end{equation}

### 2017-06-18 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
stashing changes in integrating Vikram's theoretical changes

\section{Mathematical Formulation}\label{sec:form}
%
In this section, we introduce the high-, low- and mixed-fidelity inverse problems. We develop theoretical results which extend the work in~\cite{BecVex05} to multi-model settings; in particular, we obtain a computable error estimate in the QoI that can be used for targeted generation of mixed-fidelity formulations of inverse problems.

%------------------------------------------------------------------------------%
\subsection{Inverse Problem Formulation}  \label{sec:setup}
%------------------------------------------------------------------------------%
%
Consider the inverse problem where, given observations (data) $d\in\R^{n_d}$, we seek to infer parameter(s) $q\in Q$, where $Q$ is some function space. In this exposition, we assume that $Q$ is a Hilbert space. An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, with $u$ satisfying,
%
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
%
where $U$ is also a Hilbert space. Equation~\ref{eq:weakForm} is called the state equation. The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).

The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations in a chosen norm, leading to an inverse problem. We consider the case where observations are sparse; this leads to inverse problems that are ill-posed, since the sparse observations are insufficiently informative to uniquely determine the parameters. To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation. The regularized inverse problem can thus be written as a constrained optimization problem,
%
\begin{subequations}
\label{eq:invOpt}
\begin{align}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_obj} \\
\textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U. \label{eq:invOpt_cons}
\end{align}
\end{subequations}
%
Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.

A given physical system can be described to varying degrees of fidelity using different models. One has a choice in how to define the stucture of the inferred parameters $q$, as well as how to define the state equation and variables. For example, the parameter $q$ can be modeled as a single scalar value or as an infinite-dimensional distributed field variable. The state equation can be nonlinear and \red{multiscale}, requiring an expensive computation to resolve (e.g.\ the Navier Stokes equations) or a linear, \red{single physics} model (e.g.\ Laplace's equation) \red{are NS and Laplace's possibly different modeling choices for the same situation?}. All these different modeling choices lead to different versions of the optimization problem described by \Cref{eq:invOpt} that would need to be solved to infer the unknown parameters.

We assume that there exists an `ideal' model for solving the inverse problem, which we will call the high-fidelity model; given adequate computational resources, we would use this high-fidelity to formulate and solve our inverse problem. We use the subscript $_{HF}$ to denote the high-fidelity inverse problem,
%
\begin{subequations}
\label{eq:invOptHF}
\begin{align}
q_{HF},u_{HF} &=&\arg\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_objHF} \\
&&\textrm{s.t. }& \quad a_{HF}(u,q)(\phi)=\ell_{HF}(q)(\phi),\quad\forall\phi\in U_{HF} \label{eq:invOpt_consHF}
\end{align}
\end{subequations}
%
where $q_{HF} \in Q_{HF}$ and $u_{HF}\in U_{HF}$ are the inferred parameters and corresponding state. In practice, one has limited computational resources, so one may need to instead infer the parameters using a less computationally demanding model, which we call the low-fidelity model. We use the subscript $_{LF}$ to denote the low-fidelity inverse problem,
%
\begin{subequations}
\label{eq:invOptLF}
\begin{align}
q_{LF},u_{LF} &=& \arg\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_objLF} \\
&& \textrm{s.t. }& \quad a_{LF}(u,q)(\phi)=\ell_{LF}(q)(\phi),\quad\forall\phi\in U_{LF}, \label{eq:invOpt_consLF}
\end{align}
\end{subequations}
%
where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state. If there is \red{compatibility (need to elaborate on "compatibility" somehow; was this discussed in the stokes-NS paper? compatibility comes up in fusing the models, and having the same QoI functional apply to variables of all fidelities)} between the low-fidelity and high-fidelity solution spaces for the parameter and state variables, one may combine the two models to form a mixed-fidelity model and corresponding inverse problem. The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$. How one chooses to combine the low- and high-fidelity models can be informed by what aspect of the inferred parameters is of interest.

In a {\em goal-oriented inverse problem}, the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI). We denote a scalar QoI by a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$. %The QoIs evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values. 
We assume that the parameter and state spaces of the high-, low-, and mixed-fidelity models are such that the same QoI functional can be applied to each to obtain the corresponding QoI values. \red{Don't we also have to assume that the same regularization $R$ and observation $C$ can be applied? does that limit compatibility more than QoI?}
We consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use, seeking computable estimates for the error incurred in approximating the high-fidelity model with lower fidelity models. Such an estimate allows us to adaptively choose regions where the high-fidelity model is used, starting from an initial low- or mixed- fidelity model.

%We build on the work in~\cite{BecVex05, becker2004posteriori} which utilize the special structure of the coupled system of PDEs induced by deriving optimality conditions for~\Cref{eq:invOpt_cons}, and derives error estimates for the discretization error in a single model setting. Details of why such an approach is effective for the nature of systems and QoIs we encounter in inverse problems can be found in~\cite{becker2004posteriori} (see Section 3.1 in particular). Here we extend the work in~\cite{BecVex05} to include the situation where the model structure differs, and it is the modeling error that needs to be estimated.

We build on the work in~\cite{BecVex05, becker2004posteriori} which utilize the special structure of the coupled system of PDEs corresponding to the optimality conditions for~\Cref{eq:invOpt} to derive estimates for the QoI error due to discretization in a single model setting; they consider the case where the high- and low-fidelity models represent different discretizations in the variables corresponding to the same infinite-dimensional model. Details of how the structure of the goal-oriented inverse problem is exploited can be found in~\cite{becker2004posteriori} (see Section 3.1 in particular). Here we extend the work in~\cite{BecVex05} to include the situation where state equations the high- and low-fidelity models differ in more than the discretization of the variable spaces, and it is the QoI error induced by modeling differences that needs to be estimated.

As in~\cite{BecVex05}, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations. We then use this formulation to derive an a posteriori error estimate for the QoI, where the errors considered are those due to the use of different multi-fidelity models. However, unlike in~\cite{BecVex05}, this estimate cannot be computed by patch recovery or projection techniques, since the low- and high- fidelity solutions do not differ merely in mesh resolution, but in the underlying equations being discretized. To compute this error estimate, we instead introduce additional supplementary adjoint variables; these new variables serve a similar role to the patch recovery or projection techniques in that they carry information about the high-fidelity solution to the error estimate.

%
%------------------------------------------------------------------------------%
\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%
%
For a given hierarchy of models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
%
\begin{proposition}
\label{thm:error_estimate}
Consider the high- and low-fidelity inverse problems described by the constrained optimization problems in \Cref{eq:invOptHF,eq:invOptLF}. Let the forms \red{$a_{HF/LF}:U_{HF/LF} \times U_{HF/LF} \to \Reals$ (doesn't $a$ need three inputs for the output to be a scalar? also what happened to parameter space?)} be three times continuously differentiable with respect to the state $u$ and parameters $q$. Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$. Also, let the regularization operator $R:Q_{HF/LF}\to\Reals$ be differentiable with respect to the parameter $q$, and the Quantity of Interest (QoI) functional $I:Q_{HF/LF}\times U_{HF/LF}\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.

Consider the Lagrangian equation induced by \Cref{eq:invOptHF},
%
\begin{equation}
\label{eq:InvsOpt_lag}
\mathcal{L}_{HF}(q,u,z)= J_{HF}(q,u)-(a_{HF}(u,q)(z)-\ell_{HF}(q)(z)),
\end{equation}
%
where $z\in U_{HF}$ is the adjoint. Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q_{HF}\times U_{HF}\times U_{HF}$. Let the augmented Lagrangian be defined as
%
\begin{equation}
\label{eq:InvsOpt_auglag}
\mathcal{M}_{HF}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}'_{HF}(q,u,z)(p,v,y),
\end{equation}
%
where $\mathcal{L}'_{HF}(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$. One can define a similar Langrangian $\mathcal{L}_{LF}$ induced by \Cref{eq:invOptLF}, and a corresponding augmented Lagrangian $\mathcal{M}_{LF}$, for the low-fidelity model. Let $\Psi_{HF}= (\xi_{HF},\chi_{HF})=((q_{HF},u_{HF},z_{HF}),(p_{HF},v_{HF},y_{HF}))$ and $\Psi_{LF}= (\xi_{LF},\chi_{LF})=((q_{LF},u_{LF},z_{LF}),(p_{LF},v_{LF},y_{LF}))$ denote the stationary points of the high- and low- fidelity augmented Lagrangians, respectively. Then, the error in the QoI is given by,
%
\begin{multline}
\label{eq:semifinErrExp}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
\end{multline}
%
where $\mathcal{R}$ is a remainder term that is third-order in the error $e=\Psi_{HF}-\Psi_{LF}$.
\end{proposition}
%
\begin{proof}
%
Observe that
%
\begin{equation}
\label{eq:MeqI}
\mathcal{M}_{HF}(\Psi_{HF})=I(q_{HF},u_{HF})\quad\textrm{and}\quad\mathcal{M}_{LF}(\Psi_{LF})=I(q_{LF},u_{LF}),
\end{equation}
%
since taking variations of $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$ with respect to the auxiliary variables gives that $\xi_{HF}$ and $\xi_{LF}$ are stationary points of $\mathcal{L}_{HF}$ and $\mathcal{L}_{LF}$, respectively.

Extending the property in \Cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have,
%
\begin{multline}
\label{eq:repIwithM}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})\textrm{.}
\end{multline}
%
Following~\cite{BecVex05}, we rewrite the term $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ using the Fundamental Theorem of Calculus,
%
\begin{equation}
\label{eq:Mantiderivative}
\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \int\limits_{0}^{1} \mathcal{M}'_{HF}\left(\Psi_{HF} + se\right)\left(e\right) \, \textrm{d}s.
\end{equation}
%
Applying the trapezoidal rule to the integral in~\Cref{eq:Mantiderivative} gives,
%
\begin{equation}
\label{eq:Mprimetrapezoid}
\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{HF})(e) + \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(e) + \mathcal{R}\textrm{.}
\end{equation}
%
where the remainder $\mathcal{R}$ is given as,
%
\begin{equation}
\label{eq:trapezoidremainder}
\mathcal{R} = \frac{1}{2} \int\limits_{0}^{1} \mathcal{M}'''_{HF}\left(\Psi_{LF} + se\right)(e,e,e) \, s(s-1) \, \textrm{d}s,
\end{equation}
%
which is finite due to the third order differentiability assumptions. We further note that $\mathcal{M}'_{HF}(\Psi_{HF})(e)$ vanishes since $\Psi_{HF}$ is a stationary point of $\mathcal{M}_{HF}$, and~\Cref{eq:Mprimetrapezoid} can be simplified to,
%
\begin{equation}
\label{eq:beckvex}
\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}\textrm{.}
\end{equation}
%
Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain,
%
\begin{multline}
\label{eq:preadj}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
\end{multline}
which completes the proof.
\end{proof}
%

The above \Cref{thm:error_estimate} splits the error in the QoI into three components: a third-order remainder term $\mathcal{R}$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$. Although the linear term is not computable without solving for $\Psi_{HF}$, it can be estimated. We describe one method of estimating this term, using an appropriate dual problem, in \Cref{thm:error_estimate_dual} below.

%
\begin{proposition}
\label{thm:error_estimate_dual}
Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
%
\begin{equation}
\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
\end{equation}
%
where $\mathcal{Q}:(U_{HF} \times U_{HF} \times Q_{HF})^2 \to \R$ is a linear functional defined by,
%
\begin{equation}
\mathcal{Q}(\Phi)=\mathcal{M}'_{HF}(\Psi_{LF})(\Phi).
\label{eq:supadjout}
\end{equation}
%
Then we have,
%
\begin{multline}
\label{eq:finErrExp}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}) + \mathcal{R}_{\mathscr{R}} + \mathcal{R}
\end{multline}
%
where $\mathcal{R}_{\mathscr{R}}$ is a second-order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $\mathcal{R}$ is as defined in \Cref{thm:error_estimate}. \red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
%
\end{proposition}
%
\begin{proof}
%
The proof simply follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
%
\begin{equation}
\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:supadjsys}
\end{equation}
%
which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
%
\begin{equation}
\mathscr{R}'(\Psi_{LF};\Phi,\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
\label{eq:superAdjEq}
\end{equation}
%
for the supplementary adjoint $\Lambda$. The error in the linear output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
%
\begin{equation}
\label{eq:adjOutErr}
\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF},\Lambda) + R_{\mathscr{R}},
\end{equation}
%
where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$. This implies the required result. \red{What is the classical notation for adjoint problems? Is it okay that we're breaking from the previous notation where a second pair of parentheses denotes things that we are linear in?}
%
\end{proof}
%
Other approaches to estimating the term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ can become feasible in certain scenarios; for example, if the high- and low-fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can be approximated using interpolation or patch recovery methods~\cite{BecVex05}.

### 2017-06-20 paper/submitted/round2_png/intro_v4_cmame.tex
more paper changes
stashing edits

@@
 In this context, one may choose a lower-fidelity model for the inference problem, sacrificing accuracy in the state and/or parameter estimates in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance.
+Compared to the highest-fidelity model, the lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space; this generalizes the setup where one only refines the mesh to create high-fidelity models.
 This paper formally poses the problem of managing the fidelity of modeling choices in solving the goal-oriented inverse problem, and develops an adjoint-based model adaptivity approach that achieves a desired level of accuracy in the QoI prediction.
 In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different parts of the domain.
+%Compared to the high-fidelity model, inclusion of low-fidelity regions can make this mixed-fidelity model less nonlinear, and/or have a reduced state and/or parameter space;.
 
@@
 These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement.
+%CITE REVIEWER 4 PAPERS HERE (with braack and oden), SAY THAT ONE COULD USE GOAL-ORIENTED-FWD APPROACHES FOR INVERSE PROBLEMS BY RUNNING WITH FWD THAT IS KKT SYSTEM, BUT SAY THAT HERE TAKE ADVANTAGE OF THE PARTICULAR STRUCTURE ON AN INVERSE PROBLEM?
 
@@
 Finally, we present conclusions and directions for future work in \Cref{sec:conc}.
+
+\red{STILL NEED TO ADD REFERENCES TO THE TWO POINTED OUT BY REVIEWER 4}

### 2017-06-20 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
stashing edits

@@
 where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state.
-If there is \red{compatibility (need to elaborate on "compatibility" somehow; was this discussed in the stokes-NS paper?
-compatibility comes up in fusing the models, and having the same QoI functional apply to variables of all fidelities)} between the low-fidelity and high-fidelity solution spaces for the parameter and state variables, one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
+If there is \blue{compatibility (need to elaborate on "compatibility" somehow; was this discussed in the stokes-NS paper?
+compatibility comes up in fusing the models, and having the same QoI functional apply to variables of all fidelities) (just refer to section 3.1 here for more details on 'compatibility')} between the low-fidelity and high-fidelity solution spaces for the parameter and state variables, one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
@@
 We assume that the parameter and state spaces of the high-, low-, and mixed-fidelity models are such that the same QoI functional can be applied to each to obtain the corresponding QoI values.
-\red{Don't we also have to assume that the same regularization $R$ and observation $C$ can be applied?
+\blue{Don't we also have to assume that the same regularization $R$ and observation $C$ can be applied?
 does that limit compatibility more than QoI?}

### 2017-06-21 paper/submitted/round2_png/algorithms_v4_cmame.tex
more edits

@@
 	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))|>$ \texttt{errTol}}
-		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \Cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
+		\State{Localize $\epsilon_i$ (see \Cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$}
 		\State{$i\gets i+1$}
@@
 
-		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
+		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$\label{alg-line:MFerrorest}}
 		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
@@
 
+As an example, consider a pair of low- and high-fidelity models described by the convection-diffusion and convection-diffusion-reaction equations
+\begin{subequations}
+\begin{align}
+\textrm{low-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u = q, \\
+\textrm{high-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = q,
+\end{align}
+\end{subequations}
+where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions.
+To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively.
+The resulting mixed-fidelity models can be described by,
+%
+\begin{equation}
+k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= q,
+\end{equation}
+%
+where $k^{MF}_r$ is a piecewise-constant reaction coefficient that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; initially, $\Omega_{LF}=\Omega$.
+Let the QoI be described by $I(q,u)=\int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega$, where $\Omega_I$ is the QoI region.
+Let the observations be of the state at some set of locations, so that the data-misfit term is $\frac{1}{2}\int_\Omega \delta_{obs}(u-d)^2\:\textrm{d}\Omega$, where $\delta_{obs}$ is a sum of Dirac delta functions indicating the locations of the observations.
+Let the regularization term be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla q\|_2^2\:\textrm{d}\Omega$, where $\beta$ is a regularization coefficient.
+Assuming divergence-free velocity $\vec{V}$, the mixed-fidelity model has augmented Lagrangian
+\begin{eqnarray}
+\mathcal{M}_{MF}((q,u,z)(p,v,y)) &=& \int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega \nonumber\\
+&+& \int_\Omega p(-\beta\nabla^2q+z) \nonumber\\
+&+& v(k_d\nabla^2z+\vec{V}\cdot\nabla z+2k^{MF}_rzu+\delta_{obs}(u-d)) \nonumber\\ 
+&+& y(k_d\nabla^2u-\vec{V}\cdot\nabla u+k^{MF}_ru^2+q)\:\textrm{d}\Omega.
+\end{eqnarray}
+Taking variations with respect to the auxiliary variables $(p,v,y)$ recovers the equations for the primary variables; taking variations with respect to the primary variables gives the equations for the auxiliary variables.
+Solving for the primary variables and then the auxiliary variables gives the stationary point $\Psi_{MF}$ of $\mathcal{M}_{MF}$.
+The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}).
+Taking the adjoint of these high-fidelity primary and auxiliary systems, with output described by this linear functional, gives the supplementary adjoint; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately.
+Having obtained $\Psi_{MF}$ and the supplementary adjoint $\Lambda$, we evaluate the error estimate (see Step \ref{alg-line:MFerrorest} of \Cref{alg:refSeries}), localize it (see \Cref{sec:errLocal}), and use the localization to guide the selection of elements currently in $\Omega_{LF}$ to include in $\Omega_{HF}$ in the next iteration.
+We return to this example and give results of applying \Cref{alg:refSeries} to this pair of models in \Cref{sec:cdvcdr}.
+
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space.
-The two models could also correspond to two levels of mesh refinement, though in this case the method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter and/or state space.
 The derived error estimate is not applicable to all models, however.
-The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
-We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
+It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
+\red{The high-fidelity model must by expressible in a weak form}, so this cannot be applied to, for example, a high-fidelity model of chemical reactions using kinetic Monte Carlo.
+%if the LF model does not have a weak form, say it's from a response surface...what would the components of Psi be?
+We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$.
+For example, compared to the high-fidelity model, low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
+The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy.
+We note that in the case where the two models correspond to two levels of mesh refinement, method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
+%, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$. %implied by admissibility of LF to HF
 
@@
 \begin{equation}\label{eq:basisblame}
-\varepsilon^h_i = \left| -\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF})(\lambda_i\varphi_i)+\mathcal M_{HF}(\upvarphi_i \psi_i)-\mathcal M_{MF}(\upvarphi_i \psi_i) \right|
+\varepsilon^h_i = \left| -\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{MF}^h)(\lambda_i\varphi_i)+\mathcal M_{HF}(\upvarphi_i \psi_i)-\mathcal M_{MF}(\upvarphi_i \psi_i) \right|
 \end{equation}

### 2017-06-21 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
more edits

--- 2017-06-18 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
@@
 For example, the parameter $q$ can be modeled as a single scalar value or as an infinite-dimensional distributed field variable.
-The state equation can be nonlinear and \red{multiscale}, requiring an expensive computation to resolve (e.g.\ the Navier Stokes equations) or a linear, \red{single physics} model (e.g.\ Laplace's equation) \red{are NS and Laplace's possibly different modeling choices for the same situation?}.
+The state equation can be nonlinear and multiscale, requiring an expensive computation to resolve (e.g.\ the Navier-Stokes equations) or a linear, single physics model (e.g.\ Laplace's equation).
 All these different modeling choices lead to different versions of the optimization problem described by \Cref{eq:invOpt} that would need to be solved to infer the unknown parameters.
@@
 where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state.
-If there is \red{compatibility (need to elaborate on "compatibility" somehow; was this discussed in the stokes-NS paper?
-compatibility comes up in fusing the models, and having the same QoI functional apply to variables of all fidelities)} between the low-fidelity and high-fidelity solution spaces for the parameter and state variables, one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
+If there is compatibility between the low-fidelity and high-fidelity solution spaces for the parameter and state variables (the solutions of one can be interpreted in the context of the other; see \Cref{sec:adapt_alg} for more details), one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
@@
 We denote a scalar QoI by a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$.
-%The QoIs evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values.
-We assume that the parameter and state spaces of the high-, low-, and mixed-fidelity models are such that the same QoI functional can be applied to each to obtain the corresponding QoI values.
-\red{Don't we also have to assume that the same regularization $R$ and observation $C$ can be applied?
-does that limit compatibility more than QoI?}
-We consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use, seeking computable estimates for the error incurred in approximating the high-fidelity model with lower fidelity models.
+The QoIs evaluated with the high- ($I(q_{HF},u_{HF})$), low- ($I(q_{LF},u_{LF})$), or mixed- ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high-, low- or mixed- fidelity function spaces to QoI values.
+We consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use, seeking computable estimates for the error incurred in approximating the high-fidelity model with lower-fidelity models.
 Such an estimate allows us to adaptively choose regions where the high-fidelity model is used, starting from an initial low- or mixed- fidelity model.
@@
 Consider the high- and low-fidelity inverse problems described by the constrained optimization problems in \Cref{eq:invOptHF,eq:invOptLF}.
-Let the forms \red{$a_{HF/LF}:U_{HF/LF} \times U_{HF/LF} \to \Reals$ (doesn't $a$ need three inputs for the output to be a scalar?
-also what happened to parameter space?)} be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
 Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.

### 2017-06-26 paper/submitted/round2_png/abstract_v4.tex
notation edits

--- 2016-11-16 paper/abstract_v2_kw.tex
@@
 In particular, we adaptively form a mixed-fidelity model by using models of different levels of fidelity in different subregions of the domain.
-Taking the solution of the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive an adjoint-based third-order estimate for the QoI error from using a lower-fidelity model.
+Taking the solution of the inverse problem with the highest-fidelity model as our reference QoI prediction, we extend previous results to obtain a third-order estimate, evaluated using an adjoint approach, for the QoI error from using a lower-fidelity model.
 Localization of this error then guides the formation of mixed-fidelity models.
@@
 We also demonstrate that the mixed-fidelity inverse problems can be cheaper to solve and less sensitive to the initial guess than the high-fidelity inverse problems.
-
-%from karen about v1:
-%"minimizing the use of high-fidelity constraints" -> won't make sense
-%needs to be expanded + 1-2 sentences on approach; sentence on results needs to be more specific

### 2017-06-26 paper/submitted/round2_png/algorithms_v4_cmame.tex
notation edits

@@
 \begin{align}
-\textrm{low-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u = q, \\
-\textrm{high-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = q,
+\textrm{low-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u = q, \label{eq:cdvcdrLF}\\
+\textrm{high-fidelity:   } & k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = q, \label{eq:cdvcdrHF}
 \end{align}
@@
 where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions.
-To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively.
+To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively; initially, $\Omega_{LF}=\Omega$.
 The resulting mixed-fidelity models can be described by,
@@
 %
-where $k^{MF}_r$ is a piecewise-constant reaction coefficient that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; initially, $\Omega_{LF}=\Omega$.
-Let the QoI be described by $I(q,u)=\int_{\Omega_I\subset\Omega} u \:\textrm{d}\Omega$, where $\Omega_I$ is the QoI region.
+where $k^{MF}_r$ is a piecewise-constant reaction coefficient, %that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; 
+%
+\begin{equation}
+k^{MF}_r=
+\begin{cases}
+k_r & \textrm{if }x\in\Omega_{HF} \\
+0 & \textrm{if }x\in\Omega_{LF}.
+\end{cases}
+\end{equation}
+%
+Let the QoI be described by $I(q,u)=\int_{\Omega_I} u \:\textrm{d}\Omega$, where $\Omega_I\subset\Omega$ is the QoI region.
 Let the observations be of the state at some set of locations, so that the data-misfit term is $\frac{1}{2}\int_\Omega \delta_{obs}(u-d)^2\:\textrm{d}\Omega$, where $\delta_{obs}$ is a sum of Dirac delta functions indicating the locations of the observations.
-Let the regularization term be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla q\|_2^2\:\textrm{d}\Omega$, where $\beta$ is a regularization coefficient.
+Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}, with $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla q\|_2^2\:\textrm{d}\Omega$, where $\beta$ is a regularization coefficient.
 Assuming divergence-free velocity $\vec{V}$, the mixed-fidelity model has augmented Lagrangian

### 2017-06-26 paper/submitted/round2_png/intro_v4_cmame.tex
notation edits

@@
 Goal-oriented approaches prioritize accuracy in the QoI over accuracy in the states and/or parameters; one aims to reduce the cost of solving the problem (whether forward or inverse) while maintaining an acceptably low error tolerance for the QoI.
-In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,Park04,PrudOden99,VendDarm00,Yano12} and for model adaptivity~\cite{BraackErn03,OdenPrudetal06}.
+In the context of the forward problem, goal-oriented methods have been developed for mesh refinement \cite{BecRann01,Park04,PrudOden99,VendDarm00,Yano12} and for more general model adaptivity~\cite{OdenVem00,VemOden01,BraackErn03,OdenPrudetal06}.
 These methods derive an adjoint-based a posteriori error estimate for an output functional, and this estimate is used to guide adaptive mesh and/or model refinement.
-%CITE REVIEWER 4 PAPERS HERE (with braack and oden), SAY THAT ONE COULD USE GOAL-ORIENTED-FWD APPROACHES FOR INVERSE PROBLEMS BY RUNNING WITH FWD THAT IS KKT SYSTEM, BUT SAY THAT HERE TAKE ADVANTAGE OF THE PARTICULAR STRUCTURE ON AN INVERSE PROBLEM?
+Approaches for the goal-oriented forward problem can be applied to the inverse problem by treating the optimality conditions of the inverse problem as a forward model, though one more complex than the original forward model.
+Methods tailored to the goal-oriented inverse problem, including the one proposed in this work, make use of the particular structure of the inverse problem.
 
@@
 In particular, our method allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction.
-Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model.
+Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we obtain a third-order estimate, evaluated using an adjoint approach, for the QoI error from using a lower-fidelity model.
 This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.
@@
 Finally, we present conclusions and directions for future work in \Cref{sec:conc}.
-
-\red{STILL NEED TO ADD REFERENCES TO THE TWO POINTED OUT BY REVIEWER 4}

### 2017-06-26 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
notation edits

--- 2017-06-11 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
@@
 %
-\edit{In this section, we clearly define the low, mixed and high fidelity inverse problems.
-We also develop theoretical results which extend the work of~\cite{} to multimodel settings, in particular obtaining a computable, rigorous error estimate for QoI targeted generation of mixed fidelity formulations of inverse problems.}
+We first introduce the goal-oriented inverse problem.
+Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.
 
@@
 %
-We begin by defining a generic goal-oriented inverse problem.
-Given observations (data) $d\in\R^{n_d}$, we seek to infer parameter(s) $q\in Q$, where $Q$ is a Hilbert space.
-An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, where $u$ satisfies,
+Consider a model for which the Galerkin formulation of the weak form is written as
 \begin{equation}
@@
 \end{equation}
-where $U$ is also a Hilbert space.
-Equation \Cref{eq:weakForm} is called the state equation.
-The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
-Finally, our objective functional or the QoI, is a scalar functional $I(q,u)$, where $I:Q\times U\to\R$.
+where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
+The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
+Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
+The actual observations (data) are denoted by $d\in\R^{n_d}$.
 
 The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
-Such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
@@
 Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.
+The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems.
+A given physical system can be described to varying degrees of fidelity using different models.
+This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.
 
-In an inverse problem, multiple choices are apparent for the structure of the inferred parameter $q$, the data $d$ and state equation.
-Together these constitute a model for formulating the inverse problem.
-For example, the parameter $q$ can be modeled as a single scalar value or an infinite dimensional field variable, the data $d$ can be the entire time series of measurements from a sensor, or simply a smaller subset of those measurements.
-The state equation can be complex, nonlinear relationship requiring an expensive computation to resolve (for e.g./ the Navier Stokes equations) or a linear, single physics diffusion model (for e.g./ Laplace's equation).
-All these different modeling choices lead to different versions of the optimization problem that would need to be solved to infer the unknown parameter.
-
-We assume that there exists an ideal model for solving the inverse problem, called the high fidelity model.
-Giving infinite computational resources, we would use this high fidelity to formulate and solve our inverse problem.
-Mathematically we differentiate this high fidelity inverse problem with the subscript $HF$,
-%
-\begin{subequations}
-\label{eq:invOpt}
-\begin{align}
-\min\limits_{q,u} & \quad J(q_{HF},u_{HF})=\frac{1}{2}\|d-C(u_{HF})\|_2^2 + R(q_{HF}), \label{eq:invOpt_obj} \\
-\textrm{s.t. }& \quad a(u_{HF},q_{HF})(\phi)=\ell(q_{HF})(\phi),\quad\forall\phi\in U_{HF}. \label{eq:invOpt_cons}
-\end{align}
-\end{subequations}
-%
-where $q \in Q_{HF}$.
-Due to the constraints presented by limited computational resources, one may instead attempt to infer the parameter $q$ using a different, less computationally demanding model, which we call the low fidelity model,
-%
-\begin{subequations}
-\label{eq:invOpt}
-\begin{align}
-\min\limits_{q,u} & \quad J(q_{LF},u_{LF})=\frac{1}{2}\|d-C(u_{LF})\|_2^2 + R(q_{LF}), \label{eq:invOpt_obj} \\
-\textrm{s.t. }& \quad a(u_{LF},q_{LF})(\phi)=\ell(q_{LF})(\phi),\quad\forall\phi\in U_{LF}. \label{eq:invOpt_cons}
-\end{align}
-\end{subequations}
-%
-where $q \in Q_{LF}$.
-If there is compatibility between the low fidelity and high fidelity solution spaces for $q$ and $u$, one may combine the two models to solve the inverse problem.
-The low fidelity model can be used in part of the computational domain, and the high fidelity in the remainder, and such a model is called a mixed fidelity model, which we distinguish by the subscript $MF$.
-
-In a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
-We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$.
-The QoI evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values.
+We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
 We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.
@@
 
-The above proposition splits the error in the QoI into three components, a third order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
+The above proposition splits the error in the QoI into three components, a third-order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
 Although the linear term is not computable, it can be estimated using an appropriate dual problem.

### 2017-06-26 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
notation edits

@@
 %
-which is finite due to the third order differentiability assumptions.
+which is finite due to the third-order differentiability assumptions.
 We further note that $\mathcal{M}'_{HF}(\Psi_{HF})(e)$ vanishes since $\Psi_{HF}$ is a stationary point of $\mathcal{M}_{HF}$, and~\Cref{eq:Mprimetrapezoid} can be simplified to,
@@
 \label{thm:error_estimate_dual}
-Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
+Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let the variational form
 %
 \begin{equation}
-\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:supadjsys_prop}
 \end{equation}
+%
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define an adjoint problem
+%
+\begin{equation}
+\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:superAdjEq}
+\end{equation}
+for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys_prop}, and where
+%Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
+%
+%\begin{equation}
+%\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
+%\end{equation}
 %
@@
 where $\mathcal{R}_{\mathscr{R}}$ is a second-order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $\mathcal{R}$ is as defined in \Cref{thm:error_estimate}.
-\red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
+%\red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
 %
@@
 \begin{equation}
-\mathscr{R}(\Psi_{HF},\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:supadjsys}
@@
 %
-which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
+which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the adjoint problem
 %
 \begin{equation}
-\mathscr{R}'(\Psi_{LF};\Phi,\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
@@
 \label{eq:adjOutErr}
-\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF},\Lambda) + R_{\mathscr{R}},
+\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF})(\Lambda) + R_{\mathscr{R}},
 \end{equation}
 %
-where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$.
+where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$ in \Cref{eq:superAdjEq}.
 This implies the required result.
-\red{What is the classical notation for adjoint problems?
+%\red{What is the classical notation for adjoint problems?
 Is it okay that we're breaking from the previous notation where a second pair of parentheses denotes things that we are linear in?}

### 2017-06-26 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
notation edits

@@
 We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates.
-The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
-%
-\begin{subequations}
-\label{eq:cdvcdrHF}
-\begin{align}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
-u = 0 \quad &\text{on } \partial \Omega, \label{eq:cdvcdrHF_bdry}
-\end{align}
-\end{subequations}
-%
-where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters.
+Recall the pair of models introduced in \Cref{sec:adapt_alg}.
+The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by \Cref{eq:cdvcdrHF}.
+The low-fidelity model, described by \Cref{eq:cdvcdrLF}, differs only in the removal of the reaction term.
 We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively.
-The low-fidelity model,
-%
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
-\end{equation}
-%
-differs only in the removal of the reaction term.
-To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively.
-The resulting mixed-fidelity models can be described by,
-%
-\begin{equation}
-k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
-\end{equation}
-%
-where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
-%
-\begin{equation}
-k^{MF}_r=
-\begin{cases}
-k_r & \textrm{if }x\in\Omega_{HF} \\
-0 & \textrm{if }x\in\Omega_{LF}.
-\end{cases}
-\end{equation}
-%
-Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
-%
-\begin{equation}
-I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
-\end{equation}
-%
-over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.
+Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain.
 
-The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
+The QoI region is $\Omega_I=[0.625,0.875]\times[0.375,0.625]$. The parameters $q$ we wish to infer correspond to the forcing function. The observations are sparse measurements of the state.
 \Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated.
-For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}.
-The regularization term in the objective function \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
+Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
+We arbitarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
 %

### 2017-06-29 paper/submitted/round2_png/mathematical_formulation_v4_cmame_vikram_HLedit.tex
Added remark on when we actually get a third order estimate after Proposition 2.

@@
 %
+If the state equations of the high fidelity model are linear, the derivative of the Lagrangian in~\Cref{eq:InvsOpt_auglag} is linear.
+In this case, the $R_{\mathscr{R}}$ term in~\Cref{eq:finErrExp} disappears, even if the QoI functional $I$ is nonlinear, and we get a fully third order error estimate.
+
 Other approaches to estimating the term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ can become feasible in certain scenarios; for example, if the high- and low-fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can be approximated using interpolation or patch recovery methods~\cite{BecVex05}.

### 2017-07-06 paper/submitted/round2_png/reviewer_response.tex
edits to paper, after karen's comments

@@
 Our point-by-point responses to the critique are outlined below, with reviewer comments in black and \blue{responses in blue}.
-Reviewers are ordered by the order in which their comments were received.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Reviewer 4}
-
-The paper is basically an application of [7] to modeling error demonstrated with rather transparent problems in 2D flow.
-The authors ignore the first papers on Goal-Oriented Estimation and modeling error laid out in the papers of Oden and Vemaganti in JCP in 2000, and extended by these authors in CMAME in 2001.
-The relationship between the current work and these papers should be clearly explained and cited.
-These revisions and re-review would be advised.
-
-\answer{We apologize for not referencing the aforementioned papers; we had not encountered them in our literature review and did not intend to imply their irrelevance.
-Citations of these papers and explanation of their relevance to our work has been added in \red{Section x.x.x}}
-\notdone
 
@@
 
-\answer{let vikram do his thing first}
-\notdone
+\answer{Content was rearranged.}
 
@@
 
-\answer{We added a sentence about the use cases to the second paragraph of the introduction.}
+\answer{We added text about the use cases to the second paragraph of the introduction, at the bottom of page 2.}
 
@@
 
-\answer{Thanks for the catch. We've corrected the reference.}
+\answer{We corrected the reference.}
 
@@
 
-\answer{???}
+\answer{We added a sentence to the final paragraph to this effect.}
 
@@
 
-\answer{}
-\notdone
+\answer{We elaborated upon the similarities with, and differences from, [7] in the last two paragraphs of Section 2.1.}
 
@@
 
-\answer{}
-\notdone
+\answer{We have made major revisions to Section 2.
+We moved the description of the low- and high-fidelity models earlier, to Section 2.1, and elaborated upon them.
+We expanded our explanation of compatibility at the end of Section 3.1.
+References to Propositions and proofs in [7] have been replicated within the manuscript and adapted to our setting.
+We added an additional proposition as suggested.}
 
@@
 
-\answer{}
-\notdone
+\answer{We moved the introduction of the first and simplest numerical example to Section 3.1 and added a description of Algorithm 1 in terms of this example.}
+%egh, does the new explanation make sense?
 
@@
 
-\answer{}
-\notdone
+\answer{References to Propositions and proofs in [7] have been replicated within the manuscript and adapted to our setting.}
 
@@
 \answer{We reworded the description of the parameters in Section 4.2.1 to be more clear/explicit about the relevant spaces and representations.
-\red{Not sure what to make of discretization error comment...}}
-\notdone
+The mesh was sufficiently refined that further refinements did not significantly change the solutions.}
 
-It could be illustrative to see how the parameters q change with the refinement process.
+It could be illustrative to see how the parameters $q$ change with the refinement process.
 
@@
 
-\answer{Modified figures to be on log scale and include line for target QoI error, and removed 100\% refinement point, since we don't keep refining after target is reached...not sure what is meant by 'refinement parameters'...Figure 3 was only meant to show that error decreased with refinement and that only two iterations were necessary...the amount to refine in each iteration is arbitrarily/chosen-by-used...}
-\notdone
+\answer{Figure 3 is intended to show the change in QoI error with refinement, until the target QoI is reached.
+We modified Figure 3 to be on log scale and included a line denoting the target QoI error.
+We removed the 100\% refinement point, since it did not actually correspond to a refinement iteration.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection*{Reviewer 4}
+
+The paper is basically an application of [7] to modeling error demonstrated with rather transparent problems in 2D flow.
+The authors ignore the first papers on Goal-Oriented Estimation and modeling error laid out in the papers of Oden and Vemaganti in JCP in 2000, and extended by these authors in CMAME in 2001.
+The relationship between the current work and these papers should be clearly explained and cited.
+These revisions and re-review would be advised.
+
+\answer{We apologize for not referencing the aforementioned papers; we missed them in our literature review and did not intend to imply their irrelevance.
+Citations of these papers have been added to the fourth paragraph of the introduction.}
 

### 2017-07-06 paper/submitted/round2_png/algorithms_v4_cmame.tex
edits to paper, after karen's comments

@@
 Solving for the primary variables and then the auxiliary variables gives the stationary point $\Psi_{MF}$ of $\mathcal{M}_{MF}$.
-The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}).
+The high-fidelity versions of these primary and auxiliary systems are satisfied by $\Psi_{HF}$; we seek the error in the linear functional described by \Cref{eq:supadjout} induced by applying it to $\Psi_{MF}$ instead of $\Psi_{HF}$.
+We take the classical dual-weighted residual approach and solve for the supplementary adjoint $\Lambda$, linearizing about $\Psi_{MF}$ instead of $\Psi_{HF}$ when necessary, since the latter is not available; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately.
+Having obtained $\Psi_{MF}$ and the supplementary adjoint $\Lambda$, we evaluate the error estimate (see Step \ref{alg-line:MFerrorest} of \Cref{alg:refSeries}), localize it (see \Cref{sec:errLocal}), and use the localization to guide the selection of elements currently in $\Omega_{LF}$ to include in $\Omega_{HF}$ in the next iteration.
+We return to this example and give results of applying \Cref{alg:refSeries} to this pair of models in \Cref{sec:cdvcdr}.
+%The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}).
 Taking the adjoint of these high-fidelity primary and auxiliary systems, with output described by this linear functional, gives the supplementary adjoint; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately.
@@
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter and/or state space.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, or be a reduced-order model, or have a reduced parameter and/or state space.
 The derived error estimate is not applicable to all models, however.
 It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
-\red{The high-fidelity model must by expressible in a weak form}, so this cannot be applied to, for example, a high-fidelity model of chemical reactions using kinetic Monte Carlo.
-%if the LF model does not have a weak form, say it's from a response surface...what would the components of Psi be?
+The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
 We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$.
-For example, compared to the high-fidelity model, low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
+For example, compared to the high-fidelity model, the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
 The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy.

### 2017-07-06 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
edits to paper, after karen's comments

@@
 %
-We first introduce the goal-oriented inverse problem.
-Then we derive a rigorous a posteriori error estimate for the error induced in the QoI due to the use of mixed-fidelity and/or lower-fidelity models.
+In this section, we introduce the high-, low- and mixed-fidelity inverse problems.
+We develop theoretical results which extend the work in~\cite{BecVex05} to multi-model settings; in particular, we obtain a computable error estimate in the QoI that can be used for targeted generation of mixed-fidelity formulations of inverse problems.
 
@@
 %
-Consider a model for which the Galerkin formulation of the weak form is written as
+Consider the inverse problem where, given observations (data) $d\in\R^{n_d}$, we seek to infer parameter(s) $q\in Q$, where $Q$ is a Hilbert space.
+An observation operator $C:U\to\Reals^{n_d}$ relates the parameter to the observations via state variable(s) $u\in U$, with $u$ satisfying,
+%
 \begin{equation}
@@
 \end{equation}
-where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and the state space $U$ and parameter space $Q$ are Hilbert spaces.
-The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
-Further, we define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations.
-The actual observations (data) are denoted by $d\in\R^{n_d}$.
+%
+where $U$ is also a Hilbert space.
+Equation~\ref{eq:weakForm} is called the state equation.
+The form $a$, and the functional $\ell$ are linear with respect to the arguments in the second pair of parentheses (in \Cref{eq:weakForm}, they are linear with respect to $\phi$).
 
-The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations, leading to an inverse problem.
-In our setting, such inverse problems are typically ill-posed, since the observations are sparse, and insufficiently informative to uniquely determine the parameters.
+The unknown parameter $q$ can be inferred by minimizing the difference between the predicted and actual observations in a chosen norm, leading to an inverse problem.
+We consider the case where observations are sparse; this leads to inverse problems that are ill-posed, since the sparse observations are insufficiently informative to uniquely determine the parameters.
 To make the inverse problem well-posed, a regularization, denoted by $R(q)$, is used to inject prior information or beliefs about the parameters into the formulation.
@@
 Thus, we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model given by \Cref{eq:weakForm}, which appears as a constraint in \Cref{eq:invOpt_cons}.
-The constraints \Cref{eq:invOpt_cons} are typically models of physical processes or systems.
+
 A given physical system can be described to varying degrees of fidelity using different models.
-This naturally introduces a hierarchy of models and a tradeoff between fidelity and computational expense; how one manages this tradeoff depends on what aspect of the solution is of interest.
+One has a choice in how to define the stucture of the inferred parameters $q$, as well as how to define the state equation and variables.
+For example, the parameter $q$ can be modeled as a single scalar value or as an infinite-dimensional distributed field variable.
+The state equation can be nonlinear and multiscale, requiring an expensive computation to resolve (e.g.\ the Navier-Stokes equations) or a linear, single physics model (e.g.\ Laplace's equation).
+All these different modeling choices lead to different versions of the optimization problem described by \Cref{eq:invOpt} that would need to be solved to infer the unknown parameters.
 
-We consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
-We denote a scalar QoI by $I(q,u)$, where $I:Q\times U\to\R$ is a functional that maps the parameters and state to our QoI.
-We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use.
-In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
-We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
+We assume that there exists an `ideal' model for solving the inverse problem, which we will call the high-fidelity model; given adequate computational resources, we would use this high-fidelity to formulate and solve our inverse problem.
+We use the subscript $_{HF}$ to denote the high-fidelity inverse problem,
+%
+\begin{subequations}
+\label{eq:invOptHF}
+\begin{align}
+q_{HF},u_{HF} &=&\arg\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_objHF} \\
+&&\textrm{s.t. }& \quad a_{HF}(u,q)(\phi)=\ell_{HF}(q)(\phi),\quad\forall\phi\in U_{HF} \label{eq:invOpt_consHF}
+\end{align}
+\end{subequations}
+%
+where $q_{HF} \in Q_{HF}$ and $u_{HF}\in U_{HF}$ are the inferred parameters and corresponding state, respectively.
+In practice, one has limited computational resources, so one may need to instead infer the parameters using a less computationally demanding model, which we call the low-fidelity model.
+We use the subscript $_{LF}$ to denote the low-fidelity inverse problem,
+%
+\begin{subequations}
+\label{eq:invOptLF}
+\begin{align}
+q_{LF},u_{LF} &=& \arg\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q), \label{eq:invOpt_objLF} \\
+&& \textrm{s.t. }& \quad a_{LF}(u,q)(\phi)=\ell_{LF}(q)(\phi),\quad\forall\phi\in U_{LF}, \label{eq:invOpt_consLF}
+\end{align}
+\end{subequations}
+%
+where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state, respectively.
+If there is compatibility between the low-fidelity and high-fidelity solution spaces for the parameter and state variables (i.e., if the solutions of one can be interpreted in the context of the other; see \Cref{sec:adapt_alg} for more details), one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
+The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
+How one chooses to combine the low- and high-fidelity models can be informed by what aspect of the inferred parameters is of interest.
+
+In a {\em goal-oriented inverse problem}, the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI).
+We denote a scalar QoI by a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$.
+The QoIs evaluated with the high- ($I(q_{HF},u_{HF})$), low- ($I(q_{LF},u_{LF})$), or mixed- ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high-, low- or mixed- fidelity function spaces to QoI values.
+We consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use, seeking computable estimates for the error incurred in approximating the high-fidelity model with lower-fidelity models.
+Such an estimate allows us to adaptively choose regions where the high-fidelity model is used, starting from an initial low- or mixed- fidelity model.
+
+%We build on the work in~\cite{BecVex05, becker2004posteriori} which utilize the special structure of the coupled system of PDEs induced by deriving optimality conditions for~\Cref{eq:invOpt_cons}, and derives error estimates for the discretization error in a single model setting.
+Details of why such an approach is effective for the nature of systems and QoIs we encounter in inverse problems can be found in~\cite{becker2004posteriori} (see Section 3.1 in particular).
+Here we extend the work in~\cite{BecVex05} to include the situation where the model structure differs, and it is the modeling error that needs to be estimated.
+
+We build on the work in~\cite{BecVex05, becker2004posteriori} which utilize the special structure of the coupled system of PDEs corresponding to the optimality conditions for~\Cref{eq:invOpt} to derive estimates for the QoI error due to discretization in a single model setting; they consider the case where the high- and low-fidelity models represent different discretizations in the variables corresponding to the same infinite-dimensional model.
+Details of how the structure of the goal-oriented inverse problem is exploited can be found in~\cite{becker2004posteriori} (see Section 3.1 in particular).
+Here we extend the work in~\cite{BecVex05} to include the situation where state equations the high- and low-fidelity models differ in more than the discretization of the variable spaces, and it is the QoI error induced by modeling differences that needs to be estimated.
+
+As in~\cite{BecVex05}, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations.
+We then use this formulation to derive an a posteriori error estimate for the QoI, where the errors considered are those due to the use of different multi-fidelity models.
+However, unlike in~\cite{BecVex05}, this estimate cannot be computed by patch recovery or projection techniques, since the low- and high- fidelity solutions do not differ merely in mesh resolution, but in the underlying equations being discretized.
+To compute this error estimate, we instead introduce additional supplementary adjoint variables; these new variables serve a similar role to the patch recovery or projection techniques in that they carry information about the high-fidelity solution to the error estimate.
+
 %
@@
 %
-For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates.
-In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
+For a given hierarchy of models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
 %
@@
 \label{thm:error_estimate}
-Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}.
-Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
-Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
-Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
+Consider the high- and low-fidelity inverse problems described by the constrained optimization problems in \Cref{eq:invOptHF,eq:invOptLF}.
+Let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
+Also, let the regularization operator $R:Q_{HF/LF}\to\Reals$ be differentiable with respect to the parameter $q$, and the Quantity of Interest (QoI) functional $I:Q_{HF/LF}\times U_{HF/LF}\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
 
-Consider the Lagrangian equation induced by \Cref{eq:invOpt},
+Consider the Lagrangian equation induced by \Cref{eq:invOptHF},
 %
@@
 \label{eq:InvsOpt_lag}
-\mathcal{L}(q,u,z)= J(q,u)-(a(u,q)(z)-\ell(q)(z)),
+\mathcal{L}_{HF}(q,u,z)= J_{HF}(q,u)-(a_{HF}(u,q)(z)-\ell_{HF}(q)(z)),
 \end{equation}
 %
-where $z\in U$ is the adjoint.
-Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q\times U\times U$.
+where $z\in U_{HF}$ is the adjoint.
+Denoting the primary variables as $\xi=(q,u,z)$, introduce corresponding auxiliary variables $\chi=(p,v,y)\in Q_{HF}\times U_{HF}\times U_{HF}$.
 Let the augmented Lagrangian be defined as
@@
 \label{eq:InvsOpt_auglag}
-\mathcal{M}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}_{quz}'(q,u,z)(p,v,y),
+\mathcal{M}_{HF}((q,u,z),(p,v,y)) = I(q,u) + \mathcal{L}'_{HF}(q,u,z)(p,v,y),
 \end{equation}
 %
-where $\mathcal{L}_{quz}'(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$.
-Let $\Psi = (\xi_\Psi,\chi_\Psi)$ denote the stationary point of $\mathcal{M}$.
-
-Consider two models with which parameters can be inferred: a high-fidelity model and a lower-fidelity model.
-Let the high-fidelity (HF) and low-fidelity (LF) models, and their corresponding variables, Lagrangians, and augmented Lagrangians, be distinguished by the subscripts $_{HF}$ and $_{LF}$, respectively.
-In particular, let $\Psi_{HF}$ and $\Psi_{LF}$ denote the stationary points of the high- and low- fidelity augmented Lagrangians $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$, respectively.
-Then, the error in the Quantity of Interest $I$ is given by
+where $\mathcal{L}'_{HF}(q,u,z)(p,v,y)$ denotes the Fr\'{e}chet derivative of the Lagrangian about the primary variables $(q,u,z)$, in the direction of the auxiliary variables $(p,v,y)$.
+One can define a similar Lagrangian $\mathcal{L}_{LF}$ induced by \Cref{eq:invOptLF}, and a corresponding augmented Lagrangian $\mathcal{M}_{LF}$, for the low-fidelity model.
+Let $\Psi_{HF}= (\xi_{HF},\chi_{HF})=((q_{HF},u_{HF},z_{HF}),(p_{HF},v_{HF},y_{HF}))$ and $\Psi_{LF}= (\xi_{LF},\chi_{LF})=((q_{LF},u_{LF},z_{LF}),(p_{LF},v_{LF},y_{LF}))$ denote the stationary points of the high- and low- fidelity augmented Lagrangians, respectively.
+Then, the error in the QoI is given by,
 %
@@
 \label{eq:semifinErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
 \end{multline}
@@
 \label{eq:MeqI}
-\mathcal{M}(\Psi)=I(q,u),
+\mathcal{M}_{HF}(\Psi_{HF})=I(q_{HF},u_{HF})\quad\textrm{and}\quad\mathcal{M}_{LF}(\Psi_{LF})=I(q_{LF},u_{LF}),
 \end{equation}
 %
-since taking variations of $\mathcal{M}$ with respect to the auxiliary variables gives that $\xi_\Psi$ is a stationary point of $\mathcal{L}$.
+since taking variations of $\mathcal{M}_{HF}$ and $\mathcal{M}_{LF}$ with respect to the auxiliary variables gives that $\xi_{HF}$ and $\xi_{LF}$ are stationary points of $\mathcal{L}_{HF}$ and $\mathcal{L}_{LF}$, respectively.
 
-Extending the property in \Cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have
+Extending the property in \Cref{eq:MeqI} to the augmented Lagrangians for the high- and low-fidelity models, we have,
 %
@@
 %
-Applying the output error representation described in Proposition 3 from~\cite{BecVex05} for the difference $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$,
+Following~\cite{BecVex05}, we rewrite the term $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ using the Fundamental Theorem of Calculus,
+%
+\begin{equation}
+\label{eq:Mantiderivative}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \int\limits_{0}^{1} \mathcal{M}'_{HF}\left(\Psi_{HF} + se\right)\left(e\right) \, \textrm{d}s.
+\end{equation}
+%
+Applying the trapezoidal rule to the integral in~\Cref{eq:Mantiderivative} gives,
+%
+\begin{equation}
+\label{eq:Mprimetrapezoid}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{HF})(e) + \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(e) + \mathcal{R}\textrm{.}
+\end{equation}
+%
+where the remainder $\mathcal{R}$ is given as,
+%
+\begin{equation}
+\label{eq:trapezoidremainder}
+\mathcal{R} = \frac{1}{2} \int\limits_{0}^{1} \mathcal{M}'''_{HF}\left(\Psi_{LF} + se\right)(e,e,e) \, s(s-1) \, \textrm{d}s,
+\end{equation}
+%
+which is finite due to the third-order differentiability assumptions.
+We further note that $\mathcal{M}'_{HF}(\Psi_{HF})(e)$ vanishes since $\Psi_{HF}$ is a stationary point of $\mathcal{M}_{HF}$, and~\Cref{eq:Mprimetrapezoid} can be simplified to,
+%
 \begin{equation}
 \label{eq:beckvex}
-\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}(e^3)\textrm{.}
+\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF}) = \frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{R}\textrm{.}
 \end{equation}
-Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain
+%
+Combining \Cref{eq:repIwithM} and \Cref{eq:beckvex} we obtain,
+%
 \begin{multline}
 \label{eq:preadj}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}(e^3)\textrm{,}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})+\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})+\mathcal{R}\textrm{,}
 \end{multline}
@@
 
-The above proposition splits the error in the QoI into three components, a third-order remainder term $\mathcal{R}(e^3)$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
-Although the linear term is not computable, it can be estimated using an appropriate dual problem.
-We describe one method of estimating this term below.
+The above \Cref{thm:error_estimate} splits the error in the QoI into three components: a third-order remainder term $\mathcal{R}$, a computable `bias' term $\mathcal{M}_{HF}(\Psi_{LF})-\mathcal{M}_{LF}(\Psi_{LF})$, and a linear term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$.
+Although the linear term is not computable without solving for $\Psi_{HF}$, it can be estimated.
+We describe one method of estimating this term, using an appropriate dual problem, in \Cref{thm:error_estimate_dual} below.
 
-Note that, as a stationary point, $\Psi_{HF}$ satisfies~\Cref{eq:supadjsys}. Now, let $\mathcal{Q}$ be an output defined by
+%
+\begin{proposition}
+\label{thm:error_estimate_dual}
+Let the hypotheses of Proposition~\ref{thm:error_estimate} hold. Let the variational form
 %
 \begin{equation}
-\mathcal{Q}(\Phi)=\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Phi).
+\mathscr{R}(\Psi_{HF})(\Phi)=0,\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:supadjsys_prop}
+\end{equation}
+%
+represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define an adjoint problem
+%
+\begin{equation}
+\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\label{eq:superAdjEq}
+\end{equation}
+for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys_prop}, and where
+%Let $\Lambda$ be the solution of the dual problem, \red{$\mathcal{M}'$ has just one '?}
+%
+%\begin{equation}
+%\mathcal{M}_{HF}'(\Psi_{LF};\Phi, \Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2,
+%\end{equation}
+%
+where $\mathcal{Q}:(U_{HF} \times U_{HF} \times Q_{HF})^2 \to \R$ is a linear functional defined by,
+%
+\begin{equation}
+\mathcal{Q}(\Phi)=\mathcal{M}'_{HF}(\Psi_{LF})(\Phi).
 \label{eq:supadjout}
@@
 %
-Let the variational form
+Then we have,
+%
+\begin{multline}
+\label{eq:finErrExp}
+I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF}) + \mathcal{R}_{\mathscr{R}} + \mathcal{R}
+\end{multline}
+%
+where $\mathcal{R}_{\mathscr{R}}$ is a second-order term in the error $e=\Psi_{HF}-\Psi_{LF}$, and $\mathcal{R}$ is as defined in \Cref{thm:error_estimate}.
+%\red{Now that we've explicitly pointed out the second-order error term, can we really say that we derived "an adjoint-based third-order estimate" (in abstract and intro)?}
+%
+\end{proposition}
+%
+\begin{proof}
+%
+The proof simply follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
 %
@@
 %
-represent the equation $\mathcal{M}'_{HF,\Psi}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the corresponding adjoint problem
+which is represents the equation $\mathcal{M}'_{HF}(\Psi_{HF})(\Phi)=0$ in residual form, where $\Phi$ is a test function. Define the adjoint problem
 %
 \begin{equation}
-\mathscr{R}_{\Psi}'(\Psi_{HF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
+\mathscr{R}'(\Psi_{LF},\Phi)(\Lambda)=\mathcal{Q}(\Phi),\quad\forall\Phi\in(Q_{HF}\times U_{HF}\times U_{HF})^2
 \label{eq:superAdjEq}
 \end{equation}
-for the supplementary adjoint $\Lambda$, where $\mathscr{R}$ is defined in \Cref{eq:supadjsys}.
-The error in the output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+%
+for the supplementary adjoint $\Lambda$. The error in the linear output $\mathcal{Q}$ defined in \Cref{eq:supadjout} can then be expressed as a dual-weighted residual,
+%
 \begin{equation}
 \label{eq:adjOutErr}
-\mathcal M'_{HF,\Psi}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})=-\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda).
+\mathcal{Q}(\Psi_{HF}-\Psi_{LF})=-\mathscr{R}(\Psi_{LF})(\Lambda) + R_{\mathscr{R}},
 \end{equation}
 %
-Combining \Cref{eq:preadj} and \Cref{eq:adjOutErr}, we have,
-\begin{multline}
-\label{eq:finErrExp}
-I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
-\end{multline}
+where $R_{\mathscr{R}}$ is a second order remainder term due to the linearization of $\mathscr{R}$ about $\Psi_{LF}$ in \Cref{eq:superAdjEq}.
+This implies the required result.
+%\red{What is the classical notation for adjoint problems?
+Is it okay that we're breaking from the previous notation where a second pair of parentheses denotes things that we are linear in?}
 %
-Other approaches can become feasible in certain scenarios; for example, if the high- and low-fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can be approximated using interpolation or patch recovery methods~\cite{BecVex05}.
+\end{proof}
+%
+We note that if the state equations of the high-fidelity model are linear, the remainder term $R_\mathscr{R}$ in the supplementary adjoint formulation in \Cref{eq:adjOutErr} vanishes, and the error estimate in \Cref{eq:finErrExp} becomes fully third-order.
+This occurs even if the QoI functional $I$ is nonlinear.
+%If the state equations of the high fidelity model are linear, the derivative of the Lagrangian in~\Cref{eq:InvsOpt_auglag} is linear.
+In this case, the $R_{\mathscr{R}}$ term in~\Cref{eq:finErrExp} disappears, even if the QoI functional $I$ is nonlinear, and we get a fully third order error estimate.
+
+Other approaches to estimating the term $\frac{1}{2}\mathcal{M}'_{HF}(\Psi_{LF})(\Psi_{HF}-\Psi_{LF})$ can become feasible in certain scenarios; for example, if the high- and low-fidelity models only differ in the computational grid used, the difference $\Psi_{HF}-\Psi_{LF}$ can be approximated using interpolation or patch recovery methods~\cite{BecVex05}.

### 2017-07-06 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
edits to paper, after karen's comments

@@
 \subfloat[LF $\equiv$ MF$_0$ ($0\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
+  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
   \label{fig:baseRef0}
@@
 \subfloat[MF$_1$ ($5\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
+  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
 } \\
 \subfloat[MF$_2$ ($10\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
+  \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
 } \\
@@
 %\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
-\includegraphics[width=0.8\textwidth]{baseSeries/err_est_v2.pdf}
+\includegraphics[width=\textwidth]{baseSeries/err_est_v2.pdf}
 %\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
@@
 \subfloat[MF$_0$ ($0\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
+	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_LF_divvy.pdf} %0.465 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.pdf} %0.49 round1 png
 } \\
 \subfloat[MF$_1$ ($10\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
+	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF01_divvy.pdf} %0.465 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.pdf} %0.49 round1 png
 } \\
 \subfloat[MF$_2$ ($20\%$ HF)]{
-  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
+  \includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF02_divvy.pdf} %0.465 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.pdf} %0.49 round1 png
 } \\
@@
 \subfloat[MF$_6$ ($60\%$ HF)]{
-	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
-  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
+	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF06_divvy.pdf} %0.465 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.pdf} %0.49 round1 png
 }
@@
 \centering
-\subfloat[MF$_1$ ($10\%$ HF)]{
-	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
-	\label{subfig:svfparamMF1}
-} \\
-\subfloat[MF$_3$ ($30\%$ HF)]{
-	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
-	\label{subfig:svfparamMF3}
-} \\
-\subfloat[MF$_6$ ($60\%$ HF)]{
-  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
-  \label{subfig:svfparamMF6}
-} \\
-\subfloat[HF]{
-	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
-	\label{subfig:svfparamHF}
-}
-\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models.
+%\subfloat[MF$_1$ ($10\%$ HF)]{
+%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF01_clim_HF_whitebg.png}
+%	\label{subfig:svfparamMF1}
+%} \\
+%\subfloat[MF$_3$ ($30\%$ HF)]{
+%	\includegraphics[width=0.8\textwidth]{svf/svf_param_MF03_clim_HF_whitebg.png}
+%	\label{subfig:svfparamMF3}
+%} \\
+%\subfloat[MF$_6$ ($60\%$ HF)]{
+%  \includegraphics[width=0.8\textwidth]{svf/svf_param_MF06_clim_HF_whitebg.png}
+%  \label{subfig:svfparamMF6}
+%} \\
+%\subfloat[HF]{
+%	\includegraphics[width=0.8\textwidth]{svf/svf_params_HF_whitebg.png}
+%	\label{subfig:svfparamHF}
+%}
+%\caption{Inferred parameters using mixed-fidelity (\protect\subref{subfig:svfparamMF1}--\protect\subref{subfig:svfparamMF6}) and high-fidelity (\protect\subref{subfig:svfparamHF}) models.
 All figures share the color-scale for the high-fidelity plot.}
+\includegraphics[width=0.95\textwidth]{svf/svf_param_fused.pdf}
+\caption{Inferred parameters using mixed-fidelity (top three) and high-fidelity (bottom) models. All figures share the color-scale for the high-fidelity plot.}
 \label{fig:svfRefParams}
@@
 %\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
-\includegraphics[width=0.8\textwidth]{svf/err_est_v2.pdf}
+\includegraphics[width=\textwidth]{svf/err_est_v2.pdf}
 \caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.
@@
 In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
-The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare \Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}).
+The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare
+%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
+the bottom two figures of \Cref{fig:svfRefParams}
+).
 We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-Note that although the inferred parameters in the first and third mixed-fidelity models (see \Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
+Note that although the inferred parameters in the first and third mixed-fidelity models (see
+%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
+the top two figures of \Cref{fig:svfRefParams}
+) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
 These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.

### 2017-07-06 practice/T_channel/with_reaction/long_channel_stash/3by3_suite_fine/make_pretties_alt_err_all.m

@@ -5,12 +5,14 @@ set(0,'defaultTextInterpreter','latex');
 set(0,'defaultAxesTickLabelInterpreter','latex');
 set(0,'defaultLegendInterpreter','latex');
 
-fntsize = 32;
+fntsize = 36; %32
+colorbar_fntsize = 42; %round2
 finer = true; %true = 250x50, false = 75x15
 
-refLevel = 'LF';
+refLevel = 'MF06';
 % dir_root = ['qoi3_sens3_alt_err_all/',refLevel,'/'];
-dir_root = 'vs_qoi_alt_err_all/qoi3_sens3/';
+% dir_root = 'vs_qoi_vs_data_alt_err_all/qoi3_sens3/';
+dir_root = ['../../../diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r42_basis_blame_all_fine/',refLevel,'/'];
 
 if finer
     if exist('fine_dof_info.mat','file') == 2
@@ -71,7 +73,7 @@ else
 end
 
 %read in things to plot
-err_dof = dlmread([dir_root,'error_est_breakdown_basis_blame3.dat'],' ');
+err_dof = dlmread([dir_root,'error_est_breakdown_basis_blame.dat'],' ');
 divFileID = ...
   fopen([dir_root,'divvy.txt'],'r');
 divFormatSpec = '%d %d';
@@ -98,44 +100,47 @@ xlabel('$x_1$');
 c = colorbar; set(c,'TickLabelInterpreter','latex');
 title('Local Contributions to QoI Error Estimate','FontWeight','normal')
 set(gca,'FontSize',fntsize); 
+caxis([0 1.e-8])
 set(findall(gcf,'type','text'),'FontSize',fntsize)
+set(c,'FontSize',colorbar_fntsize) 
 % set(gcf,'PaperPositionMode','auto','Position',[66 253 1535 297])
 % set(gcf,'PaperPositionMode','auto','Position',[66 140 1535 407])
 set(gcf,'PaperPositionMode','auto','Position',[88 202 1336 409])
-% print(h,[dir_root, 'err_breakdown_', refLevel],'-depsc');
-print(h,[dir_root, 'err_breakdown_', refLevel],'-dpng','-r300')
+print(h,[dir_root, 'err_breakdown_', refLevel],'-depsc'); %round2 revisions
+% print(h,[dir_root, 'err_breakdown_', refLevel],'-dpng','-r300')
 
[…]

### 2017-07-12 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
updated graphics, changes to acknowledgement, updated numerical section to remove third-order-if-linear-fwd claim and integrated continuation remark into 3d example

@@
 %
-We note that if the state equations of the high-fidelity model are linear, the remainder term $R_\mathscr{R}$ in the supplementary adjoint formulation in \Cref{eq:adjOutErr} vanishes, and the error estimate in \Cref{eq:finErrExp} becomes fully third-order.
+%We note that if the state equations of the high-fidelity model are linear, the remainder term $R_\mathscr{R}$ in the supplementary adjoint formulation in \Cref{eq:adjOutErr} vanishes, and the error estimate in \Cref{eq:finErrExp} becomes fully third-order.
 This occurs even if the QoI functional $I$ is nonlinear.

### 2017-07-12 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
updated graphics, changes to acknowledgement, updated numerical section to remove third-order-if-linear-fwd claim and integrated continuation remark into 3d example

@@
 Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-We arbitarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
+We arbitrarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
 %
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
-  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
+  %\includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
+  \includegraphics[width=0.19\textwidth]{vs_qoi/yarp.pdf}
   \label{subfig:obsSetup}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
-  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
+  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
+  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp0.pdf}
   \label{subfig:obsLF}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
-  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
+  %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
+  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp1.pdf}
   \label{subfig:obsMF1}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
-  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
+  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
+  \includegraphics[width=0.224\textwidth]{vs_qoi/yarp2.pdf}
   \label{subfig:obsMFlast}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
-  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
+  %\includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
+  \includegraphics[width=0.19\textwidth]{vs_data/yarp.pdf}
   \label{subfig:obsSetup2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
-  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
+  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
+  \includegraphics[width=0.162\textwidth]{vs_data/yarp0.pdf}
   \label{subfig:obsLF2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
-  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
+  %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
+  \includegraphics[width=0.171\textwidth]{vs_data/yarp1.pdf}
   \label{subfig:obsMF1_2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
-  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
+  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
+  \includegraphics[width=0.224\textwidth]{vs_data/yarp2.pdf}
   \label{subfig:obsMFlast2}
@@
 For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold.
-Also for ease of implementation and for localizing the error, the forcing field and its auxiliary and supplementary adjoint conterparts are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions using a penalty term.
-Although the chosen pair of models has the potential to give mixed-fidelity models with fewer degreees of freedom in the parameter, this is not the case in our implementation; however, we are not looking to demonstrate computational savings with this example, but rather to explore the behavior of \Cref{alg:refSeries} when applied to such a pair of models.
+Also for ease of implementation and for localizing the error, the forcing field and its auxiliary and supplementary adjoint counterparts are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions using a penalty term.
+Although the chosen pair of models has the potential to give mixed-fidelity models with fewer degrees of freedom in the parameter, this is not the case in our implementation; however, we are not looking to demonstrate computational savings with this example, but rather to explore the behavior of \Cref{alg:refSeries} when applied to such a pair of models.
 As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.
@@
 %\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
-the bottom two figures of \Cref{fig:svfRefParams}
-).
+the bottom two figures of \Cref{fig:svfRefParams}).
 We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
@@
 %\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
-the top two figures of \Cref{fig:svfRefParams}
-) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
+the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
 These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.
@@
 The number of degrees of freedom of each of the primary (and, if applicable, auxiliary) variables at each iteration is also given; the supplementary adjoint is solved on the high-fidelity mesh and thus each of its variables has the same number of degrees of freedom as each of the primary variables in the high-fidelity inverse problem.
-The high-fidelity inverse problem does not converge when the low-fidelity solution is used as an initial guess.
+We note that convergence of the high-fidelity inverse problem is sensitive to the initial guess; the solve does not converge when the low-fidelity solution is used as an initial guess.
 Instead, we solve the inverse problem for an intermediate model
@@
 with $k_r=0$, and use the solution as an initial guess for the high-fidelity problem; this is equivalent to using two steps of natural continuation on the reaction parameter: $k_r=0$, then $k_r=4.2\cdot10^{-4}$.
+In comparison, the adaptive algorithm needs no such continuation in $k_r$ to converge; each step can be viewed as implicit continuation in the addition of high-fidelity regions.
 %

### 2017-07-13 paper/submitted/round2_png/algorithms_v4_cmame.tex
small wording/spelling changes

@@
 \end{subequations}
-where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogenous Dirichlet boundary conditions.
+where $k_d$ and $k_r$ are diffusion and reaction coefficients, respectively, and the state $u$ and parameters $q$ are continuous functions over a domain $\Omega$ with homogeneous Dirichlet boundary conditions.
 To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively; initially, $\Omega_{LF}=\Omega$.
@@
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, or be a reduced-order model, or have a reduced parameter and/or state space.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena (as in the example above), or be a reduced-order model, or have a reduced parameter and/or state space.
 The derived error estimate is not applicable to all models, however.

### 2017-07-13 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
small wording/spelling changes

@@
 Note that for the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters).
-We arbitrarily choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
+We choose the regularization coefficient to be $\beta=10^{-5}$; in this work, $\beta$ is chosen arbitrarily, though methods exist for choosing optimal regularization coefficients~\cite{BelgeKilmerMiller02,Calvetal00}.
 %

### 2017-07-13 paper/submitted/round2_png/reviewer_response.tex
updated graphics, changes to acknowledgement, updated numerical section to remove third-order-if-linear-fwd claim and integrated continuation remark into 3d example
stashing files that ended up being submitted; tweaked reviewer response to take into account shifted reference number

@@
 \begin{document}
-
-%%%%% ASK KAREN/ELIZABETH
-%do we need to refer to line numbers?
-%if a comment asks for clarification, do we reproduce it here or point to the changed lines/sections?
 
@@
 
-\answer{We elaborated upon the similarities with, and differences from, [7] in the last two paragraphs of Section 2.1.}
+\answer{We elaborated upon the similarities with, and differences from, [7] (now [8]) in the last two paragraphs of Section 2.1.}
 
@@
 We expanded our explanation of compatibility at the end of Section 3.1.
-References to Propositions and proofs in [7] have been replicated within the manuscript and adapted to our setting.
+References to Propositions and proofs in [7] (now [8]) have been replicated within the manuscript and adapted to our setting.
 We added an additional proposition as suggested.}
@@
 
-\answer{References to Propositions and proofs in [7] have been replicated within the manuscript and adapted to our setting.}
+\answer{References to Propositions and proofs in [7] (now [8]) have been replicated within the manuscript and adapted to our setting.}
 

### 2017-07-13 paper/submitted/round2_png/cleaned_for_submit/numerical_experiments_v5_cmame.tex
stashing files that ended up being submitted; tweaked reviewer response to take into account shifted reference number

--- 2017-07-13 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
@@
 We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
-%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
 The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable; all variables are represented by the same basis.
@@
   %\includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
-  \includegraphics[width=0.19\textwidth]{vs_qoi/yarp.pdf}
+  \includegraphics[width=0.19\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.pdf}
   \label{subfig:obsSetup}
@@
   %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
-  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp0.pdf}
+  \includegraphics[width=0.166\textwidth]{vs_qoi/vs_qoi_err0_nobar.pdf}
   \label{subfig:obsLF}
@@
   %\includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
-  \includegraphics[width=0.166\textwidth]{vs_qoi/yarp1.pdf}
+  \includegraphics[width=0.166\textwidth]{vs_qoi/vs_qoi_err1_nobar.pdf}
   \label{subfig:obsMF1}
@@
   %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
-  \includegraphics[width=0.224\textwidth]{vs_qoi/yarp2.pdf}
+  \includegraphics[width=0.224\textwidth]{vs_qoi/vs_qoi_err2_barnorm.pdf}
   \label{subfig:obsMFlast}
@@
   %\includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
-  \includegraphics[width=0.19\textwidth]{vs_data/yarp.pdf}
+  \includegraphics[width=0.19\textwidth]{vs_data/vs_data_setup_sidetrim.pdf}
   \label{subfig:obsSetup2}
@@
   %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
-  \includegraphics[width=0.162\textwidth]{vs_data/yarp0.pdf}
+  \includegraphics[width=0.162\textwidth]{vs_data/vs_data_err0_nobar.pdf}
   \label{subfig:obsLF2}
@@
   %\includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
-  \includegraphics[width=0.171\textwidth]{vs_data/yarp1.pdf}
+  \includegraphics[width=0.171\textwidth]{vs_data/vs_data_err1_nobar.pdf}
   \label{subfig:obsMF1_2}
@@
   %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
-  \includegraphics[width=0.224\textwidth]{vs_data/yarp2.pdf}
+  \includegraphics[width=0.224\textwidth]{vs_data/vs_data_err2_barnorm.pdf}
   \label{subfig:obsMFlast2}
@@
 In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI.
-The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare
-%\Cref{subfig:svfparamMF6} and \Cref{subfig:svfparamHF}
-the bottom two figures of \Cref{fig:svfRefParams}).
+The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain (compare the bottom two figures of \Cref{fig:svfRefParams}).
 We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.
-Note that although the inferred parameters in the first and third mixed-fidelity models (see
-%\Cref{subfig:svfparamMF1} and \Cref{subfig:svfparamMF3}
-the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
+Note that although the inferred parameters in the first and third mixed-fidelity models (see the top two figures of \Cref{fig:svfRefParams}) are very different, they give very similar QoI error; the same is true for the second and fourth mixed-fidelity models.
 These provide additional examples supporting the idea that using inferring parameters with models of different mixtures of fidelities can produce similar QoIs.
-
-%compare MF01 and MF03, MF06 and HF
-%1 and 3 look very different but have very similar true errors - different params can give similar qoi, though in this case the qoi is not close to HF; more HF doesn't necessarily decrease error, interplay between having freedom to match data and all LF regions being flat...
-%6 and HF look very similar; most of HF is very flat
 

### 2017-10-09 paper/submitted/round3_png/algorithms_v6_cmame.tex
edits for second round of revisions

--- 2017-06-26 paper/submitted/round2_png/algorithms_v4_cmame.tex
@@
 \Cref{alg:refSeries} describes this approach.
-%Note that the QoI error adjoint problem \Cref{eq:superAdjEq} involves linearization about $\Psi_{HF}$, which is not available, so in the case of a nonlinear goal-oriented inverse problem, the QoI error adjoint problem is approximated by linearizing about $\Psi_{LF}$ instead.
 %
@@
 %
-where $k^{MF}_r$ is a piecewise-constant reaction coefficient, %that's zero in the $\Omega_{LF}$ and equal to $k_r$ in $\Omega_{HF}$; 
+where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
 %
@@
 Solving for the primary variables and then the auxiliary variables gives the stationary point $\Psi_{MF}$ of $\mathcal{M}_{MF}$.
-The weighted residual of the high-fidelity primary and auxiliary equations, evaluated at $\Psi_{MF}$, describes a linear functional in the weights (see \Cref{eq:supadjout}).
-Taking the adjoint of these high-fidelity primary and auxiliary systems, with output described by this linear functional, gives the supplementary adjoint; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately.
+The high-fidelity versions of these primary and auxiliary systems are satisfied by $\Psi_{HF}$; we seek the error in the linear functional described by \Cref{eq:supadjout} induced by applying it to $\Psi_{MF}$ instead of $\Psi_{HF}$.
+We take the classical dual-weighted residual approach and solve for the supplementary adjoint $\Lambda$, linearizing about $\Psi_{MF}$ instead of $\Psi_{HF}$ when necessary, since the latter is not available; the components of the supplementary adjoint corresponding to the primary and auxiliary systems can be solved separately.
 Having obtained $\Psi_{MF}$ and the supplementary adjoint $\Lambda$, we evaluate the error estimate (see Step \ref{alg-line:MFerrorest} of \Cref{alg:refSeries}), localize it (see \Cref{sec:errLocal}), and use the localization to guide the selection of elements currently in $\Omega_{LF}$ to include in $\Omega_{HF}$ in the next iteration.
@@
 \Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter and/or state space.
+The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena (as in the example above), or be a reduced-order model, or have a reduced parameter and/or state space.
 The derived error estimate is not applicable to all models, however.
-It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
-\red{The high-fidelity model must by expressible in a weak form}, so this cannot be applied to, for example, a high-fidelity model of chemical reactions using kinetic Monte Carlo.
-%if the LF model does not have a weak form, say it's from a response surface...what would the components of Psi be?
-We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$.
-For example, compared to the high-fidelity model, low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
-The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy.
+The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
+In addition, as described in \Cref{sec:setup}, the models must be compatible, in that the low-fidelity parameters and states $q_{LF}$ and $u_{LF}$ must lie in the high-fidelity parameter and state spaces as well.
+This implies the two models must share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
+Models that differ in discretization can be compatible; the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
+Models that have different states and/or parameters can also be compatible; for example, the high-fidelity model could describe changes in states that have a fixed value (often zero) in the low-fidelity model.
+The high-fidelity model could allow anisotropy in its parameters while the low-fidelity model could constrain their components and require isotropy.
 We note that in the case where the two models correspond to two levels of mesh refinement, method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.
-%, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$. %implied by admissibility of LF to HF
 

### 2017-10-09 paper/submitted/round3_png/mathematical_formulation_v6_cmame.tex
edits for second round of revisions

--- 2017-07-12 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
@@
 A given physical system can be described to varying degrees of fidelity using different models.
-One has a choice in how to define the stucture of the inferred parameters $q$, as well as how to define the state equation and variables.
-For example, the parameter $q$ can be modeled as a single scalar value or as an infinite-dimensional distributed field variable.
+One has a choice in how to define the structure of the inferred parameters $q$, as well as how to define the state equation and variables.
+For example, the parameter $q$ can be modeled as a single scalar value or as a distributed field variable.
 The state equation can be nonlinear and multiscale, requiring an expensive computation to resolve (e.g.\ the Navier-Stokes equations) or a linear, single physics model (e.g.\ Laplace's equation).
 All these different modeling choices lead to different versions of the optimization problem described by \Cref{eq:invOpt} that would need to be solved to infer the unknown parameters.
+Note that in order to solve \Cref{eq:invOpt} numerically, the description of a model must usually include a choice of discretization method in addition to a choice of equations.
 
@@
 where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state, respectively.
-If there is compatibility between the low-fidelity and high-fidelity solution spaces for the parameter and state variables (i.e., if the solutions of one can be interpreted in the context of the other; see \Cref{sec:adapt_alg} for more details), one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
+
+Assume there is compatibility between the low-fidelity and high-fidelity parameter and state solution spaces; specifically, assume that the low-fidelity parameters and states $q_{LF}$ and $u_{LF}$ lie in the high-fidelity parameter and state spaces as well, so that we have $q_{LF}\in Q_{HF}$ and $u_{LF}\in U_{HF}$ (see \Cref{sec:adapt_alg} for interpretation details).
+Given this compatibility, one may combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
@@
 %
-For a given hierarchy of models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
+For a given hierarchy of compatible models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
 %
@@
 Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
-Also, let the regularization operator $R:Q_{HF/LF}\to\Reals$ be differentiable with respect to the parameter $q$, and the Quantity of Interest (QoI) functional $I:Q_{HF/LF}\times U_{HF/LF}\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
+Also, let the regularization operator $R:Q_{HF/LF}\to\Reals$ be differentiable with respect to the parameter $q$, and the QoI functional $I:Q_{HF/LF}\times U_{HF/LF}\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
 
@@
 %
-The proof simply follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
+The proof follows from the classic dual-based a posteriori error estimation strategy. Note that, as a stationary point, $\Psi_{HF}$ satisfies,
 %

### 2017-10-09 paper/submitted/round2_png/cleaned_for_submit/algorithms_v5_cmame.tex

--- 2017-10-09 paper/submitted/round3_png/algorithms_v6_cmame.tex
@@
 The derived error estimate is not applicable to all models, however.
+It is assumed that the two models share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
 The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
-In addition, as described in \Cref{sec:setup}, the models must be compatible, in that the low-fidelity parameters and states $q_{LF}$ and $u_{LF}$ must lie in the high-fidelity parameter and state spaces as well.
-This implies the two models must share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
-Models that differ in discretization can be compatible; the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
-Models that have different states and/or parameters can also be compatible; for example, the high-fidelity model could describe changes in states that have a fixed value (often zero) in the low-fidelity model.
-The high-fidelity model could allow anisotropy in its parameters while the low-fidelity model could constrain their components and require isotropy.
+We need some degree of compatibility between the two models, in that we require the low-fidelity solutions to be interpretable in the context of the high-fidelity model; specifically, we require that $\Psi_{LF}$ be in a space admissible to $\mathcal{M}'_{HF}$ and $\mathcal{M}_{HF}$.
+For example, compared to the high-fidelity model, the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.
+The high-fidelity model could describe changes in states that have a fixed nominal value in the low-fidelity model; the high-fidelity model could allow anisotropy of the inferred parameters while the low-fidelity model could constrain their components and require isotropy.
 We note that in the case where the two models correspond to two levels of mesh refinement, method described in~\cite{BecVex05} would likely be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead.

### 2017-10-09 paper/submitted/round2_png/cleaned_for_submit/mathematical_formulation_v5_cmame.tex

--- 2017-07-12 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
@@
 A given physical system can be described to varying degrees of fidelity using different models.
-One has a choice in how to define the stucture of the inferred parameters $q$, as well as how to define the state equation and variables.
+One has a choice in how to define the structure of the inferred parameters $q$, as well as how to define the state equation and variables.
 For example, the parameter $q$ can be modeled as a single scalar value or as an infinite-dimensional distributed field variable.
@@
 where $q_{LF} \in Q_{LF}$ and $u_{LF}\in U_{LF}$ are the inferred parameters and corresponding state, respectively.
-If there is compatibility between the low-fidelity and high-fidelity solution spaces for the parameter and state variables (i.e., if the solutions of one can be interpreted in the context of the other; see \Cref{sec:adapt_alg} for more details), one may combine the two models to form a mixed-fidelity model and corresponding inverse problem.
+If there is compatibility between the low-fidelity and high-fidelity solution spaces for the parameter and state variables (i.e., if the solutions of one can be interpreted in the context of the other; see \Cref{sec:adapt_alg} for more details), one may combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.

### 2017-10-14 paper/submitted/round3_png/algorithms_v6_cmame.tex
more edits

@@
 
-\Cref{alg:refSeries} is applicable to a large class of models.
-The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena (as in the example above), or be a reduced-order model, or have a reduced parameter and/or state space.
-The derived error estimate is not applicable to all models, however.
-The low- and high-fidelity models must be expressible in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
-In addition, as described in \Cref{sec:setup}, the models must be compatible, in that the low-fidelity parameters and states $q_{LF}$ and $u_{LF}$ must lie in the high-fidelity parameter and state spaces as well.
-This implies the two models must share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
+\Cref{alg:refSeries} is applicable to many, though not all, models.
+One restriction to note is that the low- and high-fidelity models must be expressible in a weak form, so \Cref{alg:refSeries} cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo.
+The models must also be compatible (see \Cref{sec:setup}).
+Note that this implies the two models must share the same domain; for example, the low-fidelity model can not be a one-dimensional average of a two-dimensional high-fidelity model.
+
+The requirements for compatibility are loose enough so that \Cref{alg:refSeries} is applicable to a large class of models.
 Models that differ in discretization can be compatible; the low-fidelity model may have a coarser mesh, basis functions of a lower order, or basis functions spanning a reduced subspace.

### 2017-10-14 paper/submitted/round3_png/mathematical_formulation_v6_cmame.tex
more edits

@@
 All these different modeling choices lead to different versions of the optimization problem described by \Cref{eq:invOpt} that would need to be solved to infer the unknown parameters.
-Note that in order to solve \Cref{eq:invOpt} numerically, the description of a model must usually include a choice of discretization method in addition to a choice of equations.
+In practice, \Cref{eq:invOpt} often has no analytical solutions and must be solved numerically, in which case the description of a model includes a choice of discretization method in addition to a choice of equations.
 
@@
 
-Assume there is compatibility between the low-fidelity and high-fidelity parameter and state solution spaces; specifically, assume that the low-fidelity parameters and states $q_{LF}$ and $u_{LF}$ lie in the high-fidelity parameter and state spaces as well, so that we have $q_{LF}\in Q_{HF}$ and $u_{LF}\in U_{HF}$ (see \Cref{sec:adapt_alg} for interpretation details).
-Given this compatibility, one may combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
+Assume the high- and low-fidelity models are \emph{compatible}, in that $U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$.
+Then this compatibility allows one to combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
@@
 Consider the high- and low-fidelity inverse problems described by the constrained optimization problems in \Cref{eq:invOptHF,eq:invOptLF}.
-Let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Let the high- and low-fidelity models be compatible ($U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$), and let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
 Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.

### 2017-10-21 paper/submitted/round3_png/mathematical_formulation_v6_cmame.tex
formalization of compatibility

@@
 
-Assume the high- and low-fidelity models are \emph{compatible}, in that $U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$.
-Then this compatibility allows one to combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
+Assume the high- and low-fidelity models are compatible (formally defined in \Cref{defn:comp}), so that one can combine the two models to form a mixed-fidelity model and corresponding mixed-fidelity inverse problem.
 The low-fidelity model can be used in part of the computational domain, and the high fidelity in the remainder; we denote the mixed-fidelity model and its variables with the subscript $_{MF}$.
@@
 %
-For a given hierarchy of compatible models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution; we now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
+For a given hierarchy of compatible models, we take the QoI calculated from inferring the parameters with the highest-fidelity model to be the `exact' or `true' solution.
+Let compatibility be formally defined as follows:
+%
+\begin{definition}
+The high- and low-fidelity models described by \Cref{eq:invOpt_consHF} and \Cref{eq:invOpt_consLF}, respectively, are \emph{compatible} if $U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$.
+Compatibility allows one to evaluate residuals associated with the high-fidelity inverse problem, such as optimality conditions, at solutions to the low-fidelity inverse problem.
+\label{defn:comp}
+\end{definition}
+% 
+We now derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
 %
@@
 Consider the high- and low-fidelity inverse problems described by the constrained optimization problems in \Cref{eq:invOptHF,eq:invOptLF}.
-Let the high- and low-fidelity models be compatible ($U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$), and let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
+Let the high- and low-fidelity models be compatible (in the sense of \Cref{defn:comp}), and let the forms $a_{HF/LF}:U_{HF/LF} \times Q_{HF/LF} \times U_{HF/LF} \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$.
 Let the observation operator $C:U_{HF/LF}\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$.
@@
 %
+Note that $\mathcal{M}_{HF}(\Psi_{LF})$ is well-defined due to model compatibility.
 Following~\cite{BecVex05}, we rewrite the term $\mathcal{M}_{HF}(\Psi_{HF})-\mathcal{M}_{HF}(\Psi_{LF})$ using the Fundamental Theorem of Calculus,

### 2017-10-24 paper/submitted/round3_png/reviewer_response_round3.tex
added reviewer response

--- 2017-06-07 paper/submitted/round2_png/reviewer_response.tex
@@
 
-%%%%% ASK KAREN/ELIZABETH
-%do we need to refer to line numbers?
-%if a comment asks for clarification, do we reproduce it here or point to the changed lines/sections?
-
 \section*{Response to Referee Comments}
@@
 Our point-by-point responses to the critique are outlined below, with reviewer comments in black and \blue{responses in blue}.
-Reviewers are ordered by the order in which their comments were received.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Reviewer 4}
-
-The paper is basically an application of [7] to modeling error demonstrated with rather transparent problems in 2D flow.
-The authors ignore the first papers on Goal-Oriented Estimation and modeling error laid out in the papers of Oden and Vemaganti in JCP in 2000, and extended by these authors in CMAME in 2001.
-The relationship between the current work and these papers should be clearly explained and cited.
-These revisions and re-review would be advised.
-
-\answer{We apologize for not referencing the aforementioned papers; we had not encountered them in our literature review and did not intend to imply their irrelevance.
-Citations of these papers and explanation of their relevance to our work has been added in \red{Section x.x.x}}
-\notdone
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Reviewer 1}
-
-On page 8 (before equation 10), the sentence “Note that, ..” references equation 11 before it is
-presented. It may be better to move this comment to immediately follow the description of equation
-11.
-
-\answer{let vikram do his thing first}
-\notdone
-
-I found the motivation in the beginning of the manuscript somewhat lacking. The description of use
-cases, and conditions for which the algorithm is suitable, from the last paragraph on page 9 were very
-helpful. I believe the presentation would be strengthened by mentioning some of this earlier in the
-introduction.
-
-\answer{We added a sentence about the use cases to the second paragraph of the introduction.}
-
-Although it is represented graphically in Figure 8, $\Omega_I$ for the final example is not defined in the text.
-
-\answer{It is now defined just before Figure 8 (now Figure 9) is referenced.}
-
-At the beginning of the second paragraph of Section 4.3.2 (pg. 25) I think the reference to “Section
-4.3.2” should be Table 1.
-
-\answer{Thanks for the catch. We've corrected the reference.}
-
-The sub-figures of Figure 9 could be larger. It is difficult to verify the claim in the text that “. . . the
-domain is refined completely in the $x_3$ direction first around the QoI region. . . ”. Even going as far as
-to include 2-D slices (as in Figure 8) may be warranted.
-
-\answer{We made the figure (now Figure 10) larger, made the wording of that claim more specific, and included a 2D slice for each mixed-fidelity model that cuts through the QoI region, to aid in visual verification.}
-
-The second to last paragraph on page 28 starts “Section 4.3.2 shows the average QoI. . . ”. Again, I
-believe this is a reference to a table, Table 2 in this case.
-
-\answer{Thanks for the catch. We've corrected the reference.}
-
-I find the potential to apply this approach to surrogate design, as discussed in the final paragraph, very
-interesting. I believe this is a good case for overcoming the cumulative cost of performing multiple
-adaptive steps where the overall cost is comparable to evaluating the high-fidelity inverse problem.
-If the final adaptive step was significantly cheaper to evaluate (say 2X as in the last example) the
-cumulative cost of the adaptive algorithm would be amortized across a large number of posterior
-samples with the final mixed-fidelity model.
-
-\answer{???}
 
@@
 
-The main results in the paper are Proposition 1 and Eq.
-(14).
-These results are very close to existing results as presented in [7].
-It is not clearly explained in the introduction, and in Section 2, in what sense the current results follow from [7] and in what sense they are new.
+I had three major concerns with the previous version.
 
-\answer{}
-\notdone
+My first and last concern have been dealt with.
 
-The main theoretical section, Section 2, is vague, lacks proper structure and needs clarification.
-It is not clear how the high-fidelity and low-fidelity models are defined.
-These models should be the starting point of the section, not introduced in some proposition.
-Some degree of compatibility is assumed, but not explained.
-The proof of Proposition 1 refers to Proposition 3 in [7] which is worth stating in full in order to understand how it is employed.
-Given that (5) was stated as a Proposition 1, it is also natural to state the result in (14) as a proposition too.
+However, my second concern (on the degree of compatibility) is not dealt with adequately (in particular, Proposition 1 is not true in general).
+I therefore recommend that the authors re-submit an updated version for a subsequent review.
+My concern is further outlined below.
 
-\answer{}
-\notdone
+Although the part below Eqs (4a) and (4b) contains some explanation regarding compatibility of $U_{HF}$ and $U_{LF}$, this is not made mathematically explicit.
+Therefore the result (7) of Proposition 1 is not necessarily true.
+For example, there is no reason why a low-fidelity solution can be substituted in a high-fidelity (bi)linear form, as done in (7).
+This requires suitable compatibility of the low-fidelity space with the high-fidelity space that has not been made mathematically explicit (some inclusion is actually assumed).
+In the proof, for example, eq.
+(9) is not necessarily true.
+I have two recommendations: 1. restrict the assumption of different spaces to it being the same space, or 2. introduce suitable required inclusions for these spaces.
 
-Specifics of the models are introduced in Section 4 (numerical experiments), which is out of place.
-It would benefit the reader to move the relevant parts to after Section 2, as examples of the abstract framework.
-It would also help if the propositions would then be re-interpreted in terms of the specific low/high fidelity model setting: In other words, the authors should explain what is actually computed to do the model adaptivity.
-This is currently very unclear.
-(It is also necessary to explain the contents of Algorithm 1.)
-
-\answer{}
-\notdone
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Reviewer 3}
-
-I'd like to actually see the statement and proof of Proposition 3 from reference 7 included in
-the manuscript. It is at the crux of the proof and it's frustrating to have to go dig up that
-detail.
-
-\answer{}
-\notdone
-
-I'd like to see the details of the error estimate localization included in the manuscript instead
-of delegating to a reference. The given description is quite “wordy” and not very precise.
-
-\answer{We've added the relevant parts of the reference to Section 3.2.}
-
-The spirit of the examples is fine, but I'm not following some of the details. They state for
-the example in Section 4.1 that $f (q) = q$, but then the exact underlying field varies in space.
-To what space does $f (q)$ belong? Based on the example in Section 4.2.1, it looks like it's
-a constant. If the parameters are spatially dependent, what underlying basis is being used
-for its representation? Is the mesh refined enough to rule out pollution of the results due to
-discretization error?
-
-\answer{We reworded the description of the parameters in Section 4.2.1 to be more clear/explicit about the relevant spaces and representations.
-\red{Not sure what to make of discretization error comment...}}
-\notdone
-
-It could be illustrative to see how the parameters q change with the refinement process.
-
-\answer{We added an additional figure (now Figure 7) showing the parameters $q$ for some of the refinement iterations, along with commentary.}
-
-Figure 3 is not particularly illustrative, especially on linear scale. Perhaps some tuning of the
-refinement parameters? What were the refinement parameters for the examples?
-
-\answer{Modified figures to be on log scale and include line for target QoI error, and removed 100\% refinement point, since we don't keep refining after target is reached...not sure what is meant by 'refinement parameters'...Figure 3 was only meant to show that error decreased with refinement and that only two iterations were necessary...the amount to refine in each iteration is arbitrarily/chosen-by-used...}
-\notdone
+\answer{We added a formal definition of compatibility just before Proposition 1.}
 

### 2017-10-27 paper/submitted/round3_png/reviewer_response_round3.tex
made changes based on karen's feedback

@@
 
-\answer{We added a formal definition of compatibility just before Proposition 1.}
+\answer{We added a formal definition explicitly describing suitable inclusions for compatibility ($U_{LF}\subseteq U_{HF}$ and $Q_{LF}\subseteq Q_{HF}$) just before Proposition 1; this allows the substitution of a low-fidelity solution into a high-fidelity form.
+References to this definition were added to Section 2.1 (page 7) where compatibility is first mentioned, to Proposition 1 where the assumption of compatibility is first used in proving the result in Equation 7, and to Section 3.1 (page 15-16) where we give examples of potential pairs of compatible models.}
 

### 2017-10-27 paper/submitted/round3_png/numerical_experiments_v6_cmame.tex
made changes based on karen's feedback

--- 2017-07-13 paper/submitted/round2_png/cleaned_for_submit/numerical_experiments_v5_cmame.tex
@@
   \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf} %0.46 round1 png
-  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_LF.png} %0.49 round1 png
   \label{fig:baseRef0}
@@
   \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf} %0.46 round1 png
-  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF01.png} %0.49 round1 png
 } \\
@@
   \includegraphics[width=0.465\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf} %0.46 round1 png
-  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{baseSeries/err_breakdown_MF02.png} %0.49 round1 png
 } \\
@@
 	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_LF_divvy.pdf} %0.465 round1 png
-  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_LF.png} %0.49 round1 png
 } \\
@@
 	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF01_divvy.pdf} %0.465 round1 png
-  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF01.png} %0.49 round1 png
 } \\
@@
   \includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF02_divvy.pdf} %0.465 round1 png
-  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF02.png} %0.49 round1 png
 } \\
@@
 	\includegraphics[width=0.465\textwidth]{svf/cd_cdr_MF06_divvy.pdf} %0.465 round1 png
-  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.pdf} %0.49 round1 png
+  \includegraphics[width=0.52\textwidth]{svf/err_breakdown_MF06.png} %0.49 round1 png
 }
